### 2016-06-02 hpmoon-hpca.tex
Added template and previous text

% sage_latex_guidelines.tex V1.01, 11 June 2015

\documentclass[Afour,sageh,times]{sagej}

\usepackage{moreverb,url}

\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\def\volumeyear{2015}

\begin{document}

\runninghead{Garc\'ia-S\'anchez et al.}

\title{Parallel Multi-objective optimization using co-evolutionary islands and search space overlapping}

\author{Pablo Garc\'ia-S\'anchez, Julio Ortega, Jes\'us Gonz\'alez, Pedro Angel Castill and Juan Juli\'an Merelo\affilnum{1}}

\affiliation{\affilnum{1}Dept. of Computer Architecture and Computer Technology, University of Granada, Spain}

\corrauth{Pablo Garc\'ia-S\'anchez,
ETS. Ingenierías en Inform\'atica y Telecomunicaci\'on and CITIC-UGR,
C/Periodista Daniel Saucedo s/n,
Universidad de Granada,
18071, Granada, Spain.}

\email{pablogarcia@ugr.es}

\begin{abstract}
This paper...
\end{abstract}

\keywords{Multi-objective algorithms, NSGA-II, Island model, distributed evolutionary algorithms}

\maketitle

\section{Introduction}

%Evolutionary Algorithms (EAs) are inherently parallelizable, as each
%individual can be considered as an independent unit
%\cite{Alba13parallel}, and therefore, the
%computational performance can be improved over their non-parallel
%versions. This can also be applied to Multi-Objective Evolutionary 
%Algorithms (MOEAs). Besides, as this kind of algorithms may be computationally
%expensive, several parallelization methods have been proposed
%\cite{Luna15Survey}. However, as MOEAs deal with whole solution sets
%called Pareto Fronts (PFs), different distribution and sharing
%mechanisms need to be addressed, as there exist a tension between 
%the speedup achievable from parallelization and the need to globally 
%recombine results to accurately identify the PF \cite{Branke04Parallelizingcone}.
%
%
%Classic approaches, such as the
%global parallel EAs (Master-Slave), or the spatially structured
%algorithms (Island model or Cellular EAs) have been applied successfully in the past \cite{Folino03cellular,Alba02Parallelism}.  
%
%MOEAs have gained attention in the last years, mostly because their application in real-world problems \cite{Luna15Survey,Mukhopadhyay14Survey}. Usually these problems require a higher number of decision variables, and these larger individuals require a significant extra time for crossover, mutation and transmission. Therefore, dividing the decision space (that is, the chromosome) may improve high performance and solution quality. In this aspect, the co-%evolution model is a dimension-distributed model where a
%high-dimensional problem is divided into lower dimensional problems
%\cite{Gong15models}, and evolved separately. Also, applying parallelism techniques in EAs not only implies a reduction in the execution time, 
%but developing new and more efficient search models \cite{Luna15Survey}.  The idea of dividing the decision space has been
%studied in \cite{Kimovski15Parallel}. In that work, different workers
%evolve sub-populations created and recombined by a master process,
%which performs different recombination alternatives from the parts returned by
%worker processes. A high dimensional problem was used to compare these
%alternatives. In \cite{Dorronsoro13superlinear}, a distributed coevolutionary island model was used.  In both previous works
%significant speedups were attained, although only a low number of nodes were used (8). However, when increasing the number of islands, the division of %each section of the chromosome becomes smaller, and the scalability may be affected by obtaining lower quality solutions in the same amount of time.
%
%
%The hypothesis of this paper is that using overlapped sections of the chromosome in a coevolutionary multi-objective island-based algorithm can improve %the quality of the
%solutions in the same computing time when the number of islands increases. To demonstrate this, a new overlapping islands scheme will be compared with a baseline version of a distributed NSGA-II \cite{Deb00NSGAII} and with a coevolutionary disjoint section approach, in different benchmarks problems and %with different large number of islands. Results show that this new technique can improve different quality indicators in
%the same amount of time. 
%
%The rest of the paper is structured as follows: after a background in parallelization in MOEAs, 
 %the compared algorithms and the used methodology (Section \ref{sec:met}) are presented. 
%Then, the results of the experiments are shown (Section \ref{sec:res}), followed by conclusions and suggestions for future work lines.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  STATE OF THE ART  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{State of the Art}
\label{sec:soa}

%Distributed and parallel Evolutionary Algorithms have been used since
%the early 2000s \cite{Talbi08Parallel} to leverage the capabilities of new common parallel computer architectures, such as
%clusters or grids. However, distributing MOEAs is not as easy as it is
%in single-objective EAs, as they have to deal with a whole set of dependent solutions, the Pareto Front, that should be managed in several steps of the %algorithm. %unfinished Pablo: Done
%Some authors have focused on Master-Slave approaches to parallelize this kind of EAs. For example, Durillo et
%al. \cite{Durillo08masterslave} compared different master-slave
%approaches to save time when running the EA. The method proposed by
%Hiroyasu \cite{Hiroyasu07discussion} generates offspring depending on
%the computation power.  
%
%
%
%First approaches for distributed MOEAs (dMOEAs) were studied in
%\cite{Deb03distributed}. In that work, the dominance of solutions is
%divided in the islands using a transformation of coordinates. Authors
%concluded that dividing the search space is a good idea, but achieve
%this is not trivial. Other ideas for dividing the search space include
%objective separation in different processors \cite{Xiao03specialized},
%or divide in two populations: one for elite and other search
%\cite{Wang09parallel}. Martens, in \cite{Martens13asynchronous} generated a
%Barabasi-Albert network as the island topology, and selection based on migrating
%individuals from a not-crowded area and acceptance based on
%diversity. 
%
%More similar approaches to the one presented here were studied in the
 %next two works, also using cooperative coevolution for high-dimensional problems. Dorronsoro et al. in
%\cite{Dorronsoro13superlinear} obtained super-linear performance
%in several instances using cooperative coevolution, focusing each island on a portion of the chromosome. However, in some instances the parallel version %not always 
%improved the sequential version.  Kimovski et al. \cite{Kimovski15Parallel} proposed a
%master-slave method that splits the population into several processors,
%each one running in parallel a MOEA that only affects some portion of
%the individuals. After a certain number of generations, the master
%process receives all the sub-populations to be combined. Different
%combination alternatives in this step are compared. Up to 8 processors
%were used in the experimental setup. Our approach in this paper does not
%broadcast all solutions to all islands for recombination, as previous
%works, but only one solution to a random island, needing less
%communication time. Besides, the maximum number of islands of
%Dorronsoro or Kimovsky approaches was 8, while in this paper we have
%used up to 128 islands. 
%
%Lately, some researchers \cite{cheng2015adaptive} have focused on
%working on solution space, dividing the Pareto front in different
%clusters in order to model it. This {\em divide and conquer} approach
%is readily paralellizable and, in the sense of giving the
%responsibility of different parts of the search space to different
%modules, is similar to the one presented in this paper. We will
%describe how we have tested our approach in the next Section.

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  METHODOLOGY  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Methodology and experimental setup}
\label{sec:met}
%This section describes the quality indicators used and the methods
%compared. The chosen quality indicators,
%are:
%
%\begin{itemize}
%\item Hypervolume (HV): measures the area formed by all non-dominated solutions found with, respect to a reference point. Higher values imply better %quality of the PF.
%\item Inverted Generational distance (IGD): calculates the distance of the obtained set of solutions to the optimal PF. Therefore, this metric requires %the optimal PF found in the literature, or the theoretical one. In this metric, the lower the better. %Pablo: theoretical?
%\item Spread (S): Measures the spread between solutions, taking into account the euclidean distance between consecutive solutions. As in previous %metric, the lower value, the better, as it implies solutions distributed along all the PF.
%\end{itemize}
%
%These metrics have been used extensively, especially in some of the papers
%presented previously in Section \ref{sec:soa}.
%
%
%% --------------------------------------------------------------
%
%\subsection{Baseline algorithm}
%
%This algorithm is a regular NSGA-II algorithm distributed along a
%number $P$ of islands. After a fixed number of generations, one
%individual is migrated to another random island. At the end of the
%run, all PFs of all islands are aggregated in a new one to compute the
%quality measures.
%% some justification on why this was chosen - JJ
%
%% And some liaison to next subsection - JJ
%
%\subsection{Coevolutionary algorithms compared}
%Two different coevolutionary methods have also been used. In both
%methods, each island only performs crossover and mutation in specific sections of the
%individuals.
%
%As in the baseline, every 
%certain number of generations, an individual is migrated to another
%random island.  In the new island, this individual will be considered as one of the others in the island, crossed and
%mutated in the same way, depending of the island identifier. Note that, on the
%contrary of other works such as the ones described
%\cite{Talbi08Parallel} all the islands deal with complete chromosomes
%for fitness calculation, so our approach can deal with no decomposable
%problems. 
%
%\subsubsection{Coevolution with disjoint islands} 
%In this approach, each individual of size $L$ is split into $P$ chunks
%of size $L/P$. Every island $p$ only performs crossover and mutation
%on the $p_{th}$ part of the individuals. Figure \ref{fig:disjoint} describes this approach.  
%
%\begin{figure}
%\includegraphics[width=12cm]{islandDisjoint.jpg}
%\caption{Disjoint algorithm: every island $p$ only modifies the $p_{th}$ components (in grey) of the individuals.}
%\label{fig:disjoint}
%\end{figure}
%
%\subsubsection{Coevolution with overlapping islands}
%This approach is similar to the previous one, but every island also
%uses the $p+1$ and $p-1$ (module size) chunks of the individual for
%crossover and migration. Therefore, some kind of overlapping of the
%crossed and mutated parts exists between islands. Figure
%\ref{fig:overlapping} shows the affected parts of the individuals in
%each island. 
%
% 
%\begin{figure}
%\includegraphics[width=12cm]{islandNoDisjoint.jpg}
%\caption{Overlapping algorithm: every island $p$ modifies the  $p+1$,
  %$p_{th}$ and $p-1$  components (in grey) of the individuals.}
%\label{fig:overlapping}
%\end{figure}

% --------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%  EXPERIMENTS AND RESULTS  %%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Experiments and Results}
\label{sec:res}

%The three approaches have been run with two different 
%chromosome lengths ($L$): 512 and 2048. Different number of
%islands ($P$) have also been compared: 8, 32 and 128. This maximum number
%of islands have also been  used in previous work in the literature
%\cite{Martens13asynchronous}. The crossover and mutation chosen, SBX
%and polynomial, have been used previously by other authors in
%\cite{Durillo08masterslave}.

%ZDT \cite{zdt2000a} has been chosen as a benchmark, since it is the most widely
%used in this area
%\cite{Deb03distributed,Martens13asynchronous,Wang09parallel,Durillo08masterslave}. The
%optimal PF distribution used for comparison has 1000
%solutions \footnote{Optimal PFs are available at:
%  \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.}.

%The termination criterion used is the execution time: 25 seconds for dimension 512 and 100 (four times more) for 2048. We have used the time instead the number of evaluations firstly because our hypothesis argue that the time saved in crossover in mutation can be spent on improving the sub-populations and more operations and migrations can be achieved. Also, we are using different number of islands (with different sub-population sizes) that could lead to different execution times, so it would be difficult to compare different times and quality solutions at the same time.

\begin{table}
\begin{center}
\begin{tabular}{|c|c|}
\hline
{\em Parameter Name} & {\em Value} \\ \hline
Number of islands ($P$) & 8, 32 and 128 \\ \hline
Chromosome size ($L$) & 512 and 2048 \\ \hline
Execution time (s) & 25 (for 512) and 100 (for 2048) \\ \hline \hline
Global population size ($N$) & 1024 \\ \hline
Selection type & Binary Tournament Selection \\ \hline
Replacement type & Generational \\ \hline 
Crossover type & SBX \\ \hline
Mutation  type & Polynomial\\ \hline
Mutation probability & 1/$L$ \\ \hline
Generations between migration & 5 \\ \hline
Individuals per migration & 1 \\ \hline
Selection for migration & Binary Tournament\\ \hline
Runs per configuration & 30 \\ \hline
\end{tabular}
\caption{Parameters and operators used in the experiments.}
\label{tab:parameters}
\end{center}
\end{table}

%The ECJ framework \cite{ECJ} has been used to run the experiments. Specific operators have been developed as new modules for ECJ, and they can be downloaded from our GitHub repository under a LGPL V3 License \footnote{\url{https://https://github.com/hpmoon/hpmoon-islands}}. The island model has been executed synchronously, using the ECJ Internal Island Model, in a CentOS 5.4 machine with Intel(R) Xeon(R) CPU E5520 @2.27GHz, 16 GB RAM, with Java Version 1.6.0\_16. As in this paper we only focus on the behaviour of our model in a single machine scenario (the islands share the same memory and processor), the migration time will not be as important factor as in a real distributed system. This task will be addressed in future works. %Pablo: no sé si decir esto aquí%
%
%

%Different metrics, explained in the previous section, have been used to calculate the quality of the obtained PFs in each configuration. As some of the metrics require a reference point to be calculated (such as HV), the point (1,9) has been chosen as reference, as none of the generated PFs in all runs are dominated by it. Metrics are then normalized with respect to that point. A Kruskall-Wallis significance test has been performed to the metrics of all runs of the configurations, as the Kolmogorov-Smirnov test detected non-normal distributions. The average results for each configuration are shown in Table \ref{tab:results}.

%At a first glance results show that dividing the chromosome produces
%an improvement in all the quality indicators in all the
%configurations, with respect to the baseline. Also, results show that
%all the quality indicators lowers when the number of islands is
%increased, as the subpopulations are smaller. This is consistent with
%the claim by Durillo in \cite{Dorronsoro13superlinear}, who found that
%cooperative coevolutionary MOEAs work better on bigger populations
%(more than 100 individuals). Paying attention to the disjoint and
%overlapping methods, only when using 8 islands the disjoint method
%always attain better metrics, and even more times with the 2048 chromosome
%length. This can be explained because only 1/8 of the individual is
%changed in each island, while in the overlapping, 3/8 of the island
%may be more similar to the baseline configuration. Therefore, there exist some kind
%of limit point where one method will be preferable to another,
%depending the number of islands, population size and length. 
%
%This can be explained also comparing the number of generations and
%average solutions per island. Table \ref{tab:gens} shows these values
%obtained in each method. It is clear that in the same amount of time,
%the disjoint and overlapping method needs more generations than the
%baseline. This is even clearer with $L=$2048, where almost 10 times
%the number of generations is attained, and therefore, more migrations
%and crossovers/mutations can be achieved. Surprisingly, the average
%number of solutions of PFs per island in the baseline configuration is significantly
%higher in some configurations (mostly with 128 islands), but their
%combination in the final PF never attains higher values than Disjoint
%and Overlapping methods.

\section{Conclusions}

%High-performance problems that require a large number of decision
%variables can leverage the division of the decision space that parallel
%and distributed algorithms imply. This can be done in dMOEAs by dividing the
%chromosome into different parts, each one modified by a different
%island. This paper compares a baseline distributed NSGA-II with two
%different strategies to separate the chromosome (disjoint or overlapping
%parts), using a high number of islands. Results show that these 
%methods can achieve better quality metrics
%than the baseline in the same amount of time. This can be explained 
%because of the time reduction in crossover and mutation in the chromosomes,
%producing a higher number of generations and more modifications of the 
%solutions of the PF in each sub-population, and therefore improving
%quality of the global PF.%

%Results also show that when increasing the number of islands, the overlapping 
%method significantly improves the results with respect to the disjoint method.
%Therefore, the relation between the number of islands used, the global population size,
%and the length of the chromosome may be a key factor to decide if using the 
%overlapping method or the disjoint one. Studying this factor with more types 
%of problems, and new configurations of population size and chromosome lengths will be addressed in the future.%
%

%Also, distributed implementations in several systems (such as a GRID or cluster) with more different
%quantities of islands/processors, will be used to perform a scalability study of the different
%methods, being the transmission time between islands a relevant issue to
%address. New benchmarks and real problems will also be  used to validate
%our approach.

\begin{acks}
Agradecimientos
\end{acks}

\bibliographystyle{splncs}
\bibliography{hpmoon-hpca}
%\begin{thebibliography}{99}
%\bibitem[Kopka and Daly(2003)]{R1}
%Kopka~H and Daly~PW (2003) \textit{A Guide to \LaTeX}, 4th~edn.
%Addison-Wesley.%

%\bibitem[Lamport(1994)]{R2}
%Lamport~L (1994) \textit{\LaTeX: a Document Preparation System},
%2nd~edn. Addison-Wesley.%

%\bibitem[Mittelbach and Goossens(2004)]{R3}
%Mittelbach~F and Goossens~M (2004) \textit{The \LaTeX\ Companion},
%2nd~edn. Addison-Wesley.%

%\end{thebibliography}

\end{document}

### 2016-06-05 hpmoon-hpca.tex
Conseguí que funcionara la bibliografía
He descomentado un párrafo para probar, pero se puede borrar de nuevo si se quiere.

@@
 
-\begin{table}
+\begin{table*}
 \begin{center}
@@
 \end{center}
-\end{table}
+\end{table*}
 
-%The ECJ framework \cite{ECJ} has been used to run the experiments.
-Specific operators have been developed as new modules for ECJ, and they can be downloaded from our GitHub repository under a LGPL V3 License \footnote{\url{https://https://github.com/hpmoon/hpmoon-islands}}.
-The island model has been executed synchronously, using the ECJ Internal Island Model, in a CentOS 5.4 machine with Intel(R) Xeon(R) CPU E5520 @2.27GHz, 16 GB RAM, with Java Version 1.6.0\_16.
-As in this paper we only focus on the behaviour of our model in a single machine scenario (the islands share the same memory and processor), the migration time will not be as important factor as in a real distributed system.
-This task will be addressed in future works.
-%Pablo: no sé si decir esto aquí%
+The ECJ framework \cite{ECJ} has been used to run the
+experiments. Specific operators have been developed as new modules for
+ECJ, and they can be downloaded from our GitHub repository under a
+LGPL V3 License
+\footnote{\url{https://https://github.com/hpmoon/hpmoon-islands}}. The
+island model has been executed synchronously, using the ECJ Internal
+Island Model, in a CentOS 5.4 machine with Intel(R) Xeon(R) CPU E5520
+@2.27GHz, 16 GB RAM, with Java Version 1.6.0\_16. As in this paper we
+only focus on the behaviour of our model in a single machine scenario
+(the islands share the same memory and processor), the migration time
+will not be as important factor as in a real distributed system. This
+task will be addressed in future works. %Pablo: no sé si decir esto
+                                %aquí% 
 %
@@
 \begin{acks}
-Agradecimientos
+Acknowledgements
 \end{acks}
 
-\bibliographystyle{splncs}
+\bibliographystyle{SageH}
+
 \bibliography{hpmoon-hpca}

### 2016-06-08 hpmoon-hpca.tex
Added result tables

--- 2016-06-02 hpmoon-hpca.tex
@@
 
+\begin{table*}
+\centering
+\resizebox{12cm}{!}{
+\begin{tabular}{|c||c|c|c|c||c|c|c|c||c|c|c|c||}
+\hline
+	&	\multicolumn{4}{|c|}{HV}													&	\multicolumn{4}{|c|}{Spread}														&	\multicolumn{4}{|c|}{IGD}														\\ \hline
+%\multicolumn{13}{|c|}{2048 dimenOionO}																																													\\ \hline
+\#Island	&	B		&	D		&	O			&	A			&	B		&	D			&	O			&	A			&	B		&	D		&	O		&	A					\\ \hline
+\multicolumn{13}{|c|}{ZDT1}																																													\\ \hline
+8	&	0.900		&	0.816		& \textbf{	0.926	}		&	Equiv. D			& \textbf{	0.729	}	&	1.041			&	0.898			&	Equiv. D			&	0.013		&	0.029		& \textbf{	0.007	}	&	Equiv. D					\\
+16	& \textbf{	0.880	}	&	0.675		&	0.839			&	Equiv. O			& \textbf{	0.721	}	&	0.897			&	0.983		D	&	Equiv. O			& \textbf{	0.017	}	&	0.062		&	0.025		&	Equiv. O					\\
+32	& \textbf{	0.829	}	&	0.618		&	0.698			&	0.790			& \textbf{	0.763	}	&	0.879			&	0.886		D	&	0.913	DO		& \textbf{	0.027	}	&	0.076		&	0.056		&	0.036					\\
+64	& \textbf{	0.769	}	&	0.596		&	0.628			&	0.736			& \textbf{	0.820	}	&	0.897			&	0.872			&	0.890	DO		& \textbf{	0.040	}	&	0.080		&	0.071		&	0.047					\\
+128	& \textbf{	0.707	}	&	0.585		&	0.598			&	0.668			& \textbf{	0.850	}	&	0.956			&	0.883			&	0.910	O		& \textbf{	0.053	}	&	0.083		&	0.079		&	0.062					\\ \hline
+\multicolumn{13}{|c|}{ZDT2}																																													\\ \hline
+8	&	0.830		&	0.786		& \textbf{	0.851	}		&	Equiv. D			& \textbf{	0.866	}	&	0.996			&	0.987		D	&	Equiv. D			&	0.023		&	0.037		& \textbf{	0.017	}	&	Equiv. D					\\
+16	& \textbf{	0.810	}	&	0.601		&	0.776			&	Equiv. O			& \textbf{	0.916	}	&	0.990			&	1.005		D	&	Equiv. O			& \textbf{	0.029	}	&	0.091		&	0.040		&	Equiv. O					\\
+32	& \textbf{	0.756	}	&	0.498		&	0.617			&	0.682			& \textbf{	0.976	}	& \textbf{	0.976	}	B	& \textbf{	0.978	}	BD	&	1.054			& \textbf{	0.045	}	&	0.119		&	0.086		&	0.068					\\
+64	& \textbf{	0.668	}	&	0.451		&	0.504			&	0.601			&	1.002		& \textbf{	0.976	}		& \textbf{	0.974	}	D	&	1.025	B		& \textbf{	0.070	}	&	0.132		&	0.117		&	0.091					\\
+128	& \textbf{	0.576	}	&	0.434		&	0.452			&	0.526			&	1.002		&	1.023			& \textbf{	0.978	}		&	1.015	BD		& \textbf{	0.096	}	&	0.137		&	0.132		&	0.110					\\ \hline
+\multicolumn{13}{|c|}{ZDT3}																																													\\ \hline
+8	&	0.928		&	0.838		& \textbf{	0.951	}		&	Equiv. D			& \textbf{	0.869	}	&	1.028			&	0.983		D	&	Equiv. D			& \textbf{	0.008	}	&	0.018		&	0.005		&	Equiv. D					\\
+16	& \textbf{	0.903	}	&	0.715		&	0.870			&	Equiv. O			& \textbf{	0.846	}	&	0.899			&	0.960			&	Equiv. O			& \textbf{	0.011	}	&	0.032		&	0.014		&	Equiv. O					\\
+32	& \textbf{	0.857	}	&	0.655		&	0.737			&	0.824			& \textbf{	0.845	}	&	0.879			&	0.873		D	&	0.881	DO		& \textbf{	0.016	}	&	0.039		&	0.030		&	0.019					\\
+64	& \textbf{	0.796	}	&	0.632		&	0.662			&	0.761			& \textbf{	0.859	}	&	0.887			&	0.885		D	&	0.879	BDO		& \textbf{	0.023	}	&	0.042		&	0.038		&	0.027					\\
+128	& \textbf{	0.738	}	&	0.620		&	0.633			&	0.705			& \textbf{	0.882	}	&	0.968			& \textbf{	0.888	}	B	&	0.911			& \textbf{	0.029	}	&	0.044		&	0.042		&	0.033					\\ \hline
+\multicolumn{13}{|c|}{ZDT6}																																													\\ \hline
+8	&	0.268		&	0.223		& \textbf{	0.298	}		&	Equiv. D			& \textbf{	0.988	}	& \textbf{	0.972	}	B	& \textbf{	0.996	}	B	&	Equiv. D			& \textbf{	0.173	}	&	0.191		&	0.160		&	Equiv. D					\\
+16	& \textbf{	0.243	}	&	0.113		&	0.219			&	Equiv. O			& \textbf{	0.995	}	& \textbf{	0.987	}	B	& \textbf{	0.987	}	BD	&	Equiv. O			& \textbf{	0.184	}	&	0.240		&	0.193		&	Equiv. O					\\
+32	& \textbf{	0.196	}	&	0.071		&	0.115			&	0.162			& \textbf{	0.998	}	& \textbf{	0.989	}	B	& \textbf{	0.988	}	BD	&	1.005	B		& \textbf{	0.204	}	&	0.257		&	0.238		&	0.220					\\
+64	& \textbf{	0.145	}	&	0.056		&	0.075			&	0.120			&	0.996		&	0.986		B	& \textbf{	0.983	}	D	&	0.998	B		& \textbf{	0.226	}	&	0.264		&	0.255		&	0.235					\\
+128	& \textbf{	0.104	}	&	0.049		&	0.055			&	0.084			&	0.993		&	1.007			& \textbf{	0.979	}		&	0.998	BD		& \textbf{	0.244	}	&	0.266		&	0.263		&	0.251					\\ \hline
+
+\end{tabular}
+}
+\caption{Métricas de calidad obtenidas después de 30 ejecuciones por configuración, para los cuatro métodos comparados: baseline (B), disjunto (D), solapado (S) y solapado adaptativo (A).
+Los acrónimos junto a los valores indican que no hay diferencia significativa con respecto a ese método para ese valor.
+Los mejores valores están marcados en negrita.}
+\label{tab:results512}
+\end{table*}
+
+\begin{table*}
+\centering
+\resizebox{12cm}{!}{
+\begin{tabular}{|c||c|c|c|c||c|c|c|c||c|c|c|c||}
+\hline
+	&	\multicolumn{4}{|c|}{HV}													&	\multicolumn{4}{|c|}{Spread}														&	\multicolumn{4}{|c|}{IGD}														\\ \hline
+
+\#Island	&	B		&	D		&	O			&	A			&	B		&	D			&	O			&	A			&	B		&	D		&	O		&	A					\\ \hline
+\multicolumn{13}{|c|}{ZDT1}																																													\\ \hline
+8	&	0.891		& \textbf{	0.953	}	&	0.937			&	Equiv. D			& \textbf{	0.681	}	& \textbf{	0.635	}	B	&	0.661		D	&	Equiv. D			&	0.015		& \textbf{	0.002	}	&	0.005		&	Equiv. D					\\
+16	&	0.884		&	0.850		& \textbf{	0.942	}		&	Equiv. O			& \textbf{	0.705	}	&	0.908			& \textbf{	0.670	}	B	&	Equiv. O			&	0.016		&	0.022		& \textbf{	0.004	}	&	Equiv. O					\\
+32	&	0.851		&	0.674		&	0.859		B	& \textbf{	0.900	}		& \textbf{	0.754	}	&	0.868			&	0.826		D	& \textbf{	0.763	}	B	&	0.023		&	0.062		&	0.020	B	& \textbf{	0.012	}				\\
+64	& \textbf{	0.800	}	&	0.608		&	0.697			& \textbf{	0.824	}	B	& \textbf{	0.808	}	&	0.880			& \textbf{	0.861	}	B	& \textbf{	0.823	}	B	&	0.033		&	0.078		&	0.056		& \textbf{	0.027	}				\\
+128	&	0.735		&	0.582		&	0.613			& \textbf{	0.745	}		& \textbf{	0.841	}	&	0.888			&	0.878		D	&	0.865		O	&	0.047		&	0.084		&	0.075		& \textbf{	0.043	}				\\ \hline
+\multicolumn{13}{|c|}{ZDT2}																																													\\ \hline
+8	&	0.832		& \textbf{	0.895	}	&	0.869			&	Equiv. D			& \textbf{	0.849	}	& \textbf{	0.886	}	B	&	0.853		D	&	Equiv. D			&	0.023		& \textbf{	0.006	}	&	0.013		&	Equiv. D					\\
+16	&	0.831		&	0.833	B	& \textbf{	0.884	}		&	Equiv. O			& \textbf{	0.810	}	&	1.001			& \textbf{	0.802	}	B	&	Equiv. O			&	0.023		&	0.022	B	& \textbf{	0.009	}	&	Equiv. O					\\
+32	&	0.800		&	0.628		&	0.800		B	& \textbf{	0.817	}		& \textbf{	0.848	}	&	0.974			&	0.983		D	&	0.908			&	0.031		&	0.082		&	0.032	B	& \textbf{	0.027	}				\\
+64	& \textbf{	0.729	}	&	0.491		&	0.623			&	0.716			& \textbf{	0.909	}	&	0.967			&	0.979		D	& \textbf{	0.997	}	BD	& \textbf{	0.052	}	&	0.121		&	0.084		& \textbf{	0.055	}	B			\\
+128	& \textbf{	0.630	}	&	0.441		&	0.500			& \textbf{	0.614	}	B	& \textbf{	0.957	}	&	0.989			&	0.978		D	& \textbf{	0.994	}	BO	& \textbf{	0.080	}	&	0.136		&	0.119		& \textbf{	0.085	}	B			\\ \hline
+\multicolumn{13}{|c|}{ZDT3}																																													\\ \hline
+8	&	0.917		& \textbf{	0.971	}	&	0.960			&	Equiv. D			& \textbf{	0.843	}	& \textbf{	0.854	}	B	&	0.868		D	&	Equiv. D			&	0.009		& \textbf{	0.001	}	&	0.004		&	Equiv. D					\\
+16	&	0.911		&	0.876	B	& \textbf{	0.963	}		&	Equiv. O			& \textbf{	0.864	}	&	0.899		B	& \textbf{	0.837	}	B	&	Equiv. O			&	0.010		&	0.014		& \textbf{	0.003	}	&	Equiv. O					\\
+32	&	0.884		&	0.710		&	0.883		B	& \textbf{	0.931	}		& \textbf{	0.856	}	& \textbf{	0.870	}	B	& \textbf{	0.842	}	B	& \textbf{	0.842	}	BDO	&	0.013		&	0.032		&	0.013	B	& \textbf{	0.008	}				\\
+64	&	0.828		&	0.645		&	0.728			& \textbf{	0.854	}		& \textbf{	0.878	}	& \textbf{	0.896	}	B	& \textbf{	0.871	}	BD	& \textbf{	0.873	}	BDO	& \textbf{	0.019	}	&	0.040		&	0.030		& \textbf{	0.016	}	B			\\
+128	& \textbf{	0.770	}	&	0.620		&	0.651			& \textbf{	0.773	}	B	& \textbf{	0.887	}	& \textbf{	0.901	}	B	& \textbf{	0.890	}	BD	& \textbf{	0.885	}	BDO	& \textbf{	0.026	}	&	0.043		&	0.039		& \textbf{	0.025	}	B			\\ \hline
+\multicolumn{13}{|c|}{ZDT6}																																													\\ \hline
+8	&	0.271		& \textbf{	0.398	}	&	0.323			&	Equiv. D			& \textbf{	0.982	}	& \textbf{	0.982	}	B	&	0.994			&	Equiv. D			&	0.171		& \textbf{	0.115	}	&	0.149		&	Equiv. D					\\
+16	&	0.275		&	0.295	B	& \textbf{	0.354	}		&	Equiv. O			& \textbf{	0.981	}	& \textbf{	0.970	}	B	&	1.006			&	Equiv. O			&	0.170		&	0.161	B	& \textbf{	0.136	}	&	Equiv. O					\\
+32	&	0.239		&	0.123		&	0.240			& \textbf{	0.254	}		& \textbf{	0.989	}	& \textbf{	0.991	}	B	& \textbf{	0.982	}	BD	& \textbf{	0.999	}	BD	&	0.186		&	0.235		&	0.185	B	& \textbf{	0.179	}				\\
+64	& \textbf{	0.184	}	&	0.068		&	0.125			& \textbf{	0.178	}	B	& \textbf{	0.985	}	& \textbf{	0.982	}	B	& \textbf{	0.992	}	B	& \textbf{	0.995	}	BO	& \textbf{	0.209	}	&	0.259		&	0.235		&	0.212					\\
+128	& \textbf{	0.128	}	&	0.051		&	0.071			& \textbf{	0.124	}	B	& \textbf{	0.991	}	& \textbf{	0.992	}	B	& \textbf{	0.988	}	BD	&	1.003			& \textbf{	0.233	}	&	0.266		&	0.257		& \textbf{	0.235	}	B			\\ \hline
+
+\end{tabular}
+}
+\caption{Métricas de calidad obtenidas después de 30 ejecuciones por configuración, para los cuatro métodos comparados: baseline (B), disjunto (D), solapado (S) y solapado adaptativo (A).
+Los acrónimos junto a los valores indican que no hay diferencia significativa con respecto a ese método para ese valor.
+Los mejores valores están marcados en negrita.}
+\label{tab:results512}
+\end{table*}
+
 %At a first glance results show that dividing the chromosome produces

### 2016-06-08 hpmoon-hpca.tex
Added intro and SOA

@@
 
-\author{Pablo Garc\'ia-S\'anchez, Julio Ortega, Jes\'us Gonz\'alez, Pedro Angel Castill and Juan Juli\'an Merelo\affilnum{1}}
+\author{Pablo Garc\'ia-S\'anchez, Julio Ortega, Jes\'us Gonz\'alez, Pedro Angel Castillo and Juan Juli\'an Merelo\affilnum{1}}
 
@@
 
-%Evolutionary Algorithms (EAs) are inherently parallelizable, as each
-%individual can be considered as an independent unit
-%\cite{Alba13parallel}, and therefore, the
-%computational performance can be improved over their non-parallel
-%versions. This can also be applied to Multi-Objective Evolutionary 
-%Algorithms (MOEAs). Besides, as this kind of algorithms may be computationally
-%expensive, several parallelization methods have been proposed
-%\cite{Luna15Survey}. However, as MOEAs deal with whole solution sets
-%called Pareto Fronts (PFs), different distribution and sharing
-%mechanisms need to be addressed, as there exist a tension between 
-%the speedup achievable from parallelization and the need to globally 
-%recombine results to accurately identify the PF \cite{Branke04Parallelizingcone}.
-%
-%
-%Classic approaches, such as the
-%global parallel EAs (Master-Slave), or the spatially structured
-%algorithms (Island model or Cellular EAs) have been applied successfully in the past \cite{Folino03cellular,Alba02Parallelism}.  
-%
-%MOEAs have gained attention in the last years, mostly because their application in real-world problems \cite{Luna15Survey,Mukhopadhyay14Survey}.
-Usually these problems require a higher number of decision variables, and these larger individuals require a significant extra time for crossover, mutation and transmission.
-Therefore, dividing the decision space (that is, the chromosome) may improve high performance and solution quality.
-In this aspect, the co-%evolution model is a dimension-distributed model where a
-%high-dimensional problem is divided into lower dimensional problems
-%\cite{Gong15models}, and evolved separately. Also, applying parallelism techniques in EAs not only implies a reduction in the execution time, 
-%but developing new and more efficient search models \cite{Luna15Survey}.  The idea of dividing the decision space has been
-%studied in \cite{Kimovski15Parallel}. In that work, different workers
-%evolve sub-populations created and recombined by a master process,
-%which performs different recombination alternatives from the parts returned by
-%worker processes. A high dimensional problem was used to compare these
-%alternatives. In \cite{Dorronsoro13superlinear}, a distributed coevolutionary island model was used.  In both previous works
-%significant speedups were attained, although only a low number of nodes were used (8).
-However, when increasing the number of islands, the division of %each section of the chromosome becomes smaller, and the scalability may be affected by obtaining lower quality solutions in the same amount of time.
-%
-%
-%The hypothesis of this paper is that using overlapped sections of the chromosome in a coevolutionary multi-objective island-based algorithm can improve %the quality of the
-%solutions in the same computing time when the number of islands increases.
-To demonstrate this, a new overlapping islands scheme will be compared with a baseline version of a distributed NSGA-II \cite{Deb00NSGAII} and with a coevolutionary disjoint section approach, in different benchmarks problems and %with different large number of islands.
-Results show that this new technique can improve different quality indicators in
-%the same amount of time. 
-%
-%The rest of the paper is structured as follows: after a background in parallelization in MOEAs, 
- %the compared algorithms and the used methodology (Section \ref{sec:met}) are presented. 
-%Then, the results of the experiments are shown (Section \ref{sec:res}), followed by conclusions and suggestions for future work lines.
+Different approaches have been used to parallelize Evolutionary Algorithms (EAs), as each individual can be considered as an independient unit \cite{Alba13parallel}.
+Classic methods, such as the global parallel EAs (Master-Slave), or the spatially structured algorithms (Island model or Cellular EAs) have been applied successfully in the past \cite{Folino03cellular,Alba02Parallelism}.
+In the case of Multi-Objective Evolutionary Algorithms (MOEAs), these approaches \cite{Luna15Survey} need to deal with a whole solution set called Pareto Front (PFs).
+This imply to use different distribution and sharing mechanisms, as there exist a tension between the speedup achievable from parallelization and the need to globally recombine results to accurately identify the PF \cite{Branke04Parallelizingcone}.
+
+The application of MOEAs to solve real-world problems have gained attention in the last years \cite{Luna15Survey,Mukhopadhyay14Survey}.
+These kind of problems require a high number of variables, meaning that the EAs need to deal with large individuals and spent significant extra time for crossover, mutation and migration.
+Different authors have proposed methods to divide the decision space (the chromosome) to improve the performance and solution quality.
+In this aspect, the co-evolution model is a dimension-distributed model where a high-dimensional problem is divided into lower dimensional problems \cite{Gong15models}, and evolved separately.
+One example of application of this technique was described in \cite{Kimovski15Parallel}.
+The method presented in that works involves different workers that evolve sub-populations created and recombined by a master process, which performs different recombination alternatives from the parts returned by worker processes.
+A high dimensional problem was used to compare these
+alternatives.
+In \cite{Dorronsoro13superlinear}, a distributed coevolutionary island model was used.
+Although in both previous works significant speedups were attained, only a low number of nodes were used (8).
+However, when increasing the number of islands, the division of each section of the chromosome becomes smaller, and the scalability may be affected by obtaining lower quality solutions in the same amount of time.
+
+In \cite{Garcia16Evostar} we tried to demonstrate that using overlapped sections of the chromosome in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time when the number of islands increases.
+We discovered that the most adequate overlapping size chosen varies depending on a relation between the number of islands and the indidivual size.
+Moreover, the experiments were conducted in a mono-processor and synchronous island model.
+This motivates us to continue this research line, but this time, proposing a new method to automatically adapt the size of the overlapped sections, but also, performing all the experiments in a real cluster with up to 128 nodes, with extra number of islands.
+
+The hypothesis of this paper is that using overlapped sections of the chromosome, calculated depending the number of islands to use, in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time with respect to disjoint and partly overlaped methods.
+To demonstrate this, a new overlapping islands scheme has been compared with a baseline version of a distributed NSGA-II \cite{Deb00NSGAII}, a coevolutionary disjoint section approach, and a fixed-size overlapped method.
+Different benchmarks problems and different large number of islands have been used.
+Results show that this new technique can improve different quality indicators in the same amount of time when the problem size is large.
+
+The rest of the paper is organized as follows: after a background in parallelization in MOEAs, 
+the compared algorithms and the used methodology (Section \ref{sec:met}) are presented. 
+Then, the results of the experiments are shown (Section \ref{sec:res}), followed by conclusions and suggestions for future work lines.
 
@@
 
-%Distributed and parallel Evolutionary Algorithms have been used since
-%the early 2000s \cite{Talbi08Parallel} to leverage the capabilities of new common parallel computer architectures, such as
-%clusters or grids. However, distributing MOEAs is not as easy as it is
-%in single-objective EAs, as they have to deal with a whole set of dependent solutions, the Pareto Front, that should be managed in several steps of the %algorithm. %unfinished Pablo: Done
-%Some authors have focused on Master-Slave approaches to parallelize this kind of EAs. For example, Durillo et
-%al. \cite{Durillo08masterslave} compared different master-slave
-%approaches to save time when running the EA. The method proposed by
-%Hiroyasu \cite{Hiroyasu07discussion} generates offspring depending on
-%the computation power.  
-%
-%
-%
-%First approaches for distributed MOEAs (dMOEAs) were studied in
-%\cite{Deb03distributed}. In that work, the dominance of solutions is
-%divided in the islands using a transformation of coordinates. Authors
-%concluded that dividing the search space is a good idea, but achieve
-%this is not trivial. Other ideas for dividing the search space include
-%objective separation in different processors \cite{Xiao03specialized},
-%or divide in two populations: one for elite and other search
-%\cite{Wang09parallel}. Martens, in \cite{Martens13asynchronous} generated a
-%Barabasi-Albert network as the island topology, and selection based on migrating
-%individuals from a not-crowded area and acceptance based on
-%diversity. 
-%
-%More similar approaches to the one presented here were studied in the
- %next two works, also using cooperative coevolution for high-dimensional problems. Dorronsoro et al. in
-%\cite{Dorronsoro13superlinear} obtained super-linear performance
-%in several instances using cooperative coevolution, focusing each island on a portion of the chromosome. However, in some instances the parallel version %not always 
-%improved the sequential version.  Kimovski et al. \cite{Kimovski15Parallel} proposed a
-%master-slave method that splits the population into several processors,
-%each one running in parallel a MOEA that only affects some portion of
-%the individuals. After a certain number of generations, the master
-%process receives all the sub-populations to be combined. Different
-%combination alternatives in this step are compared. Up to 8 processors
-%were used in the experimental setup. Our approach in this paper does not
-%broadcast all solutions to all islands for recombination, as previous
-%works, but only one solution to a random island, needing less
-%communication time. Besides, the maximum number of islands of
-%Dorronsoro or Kimovsky approaches was 8, while in this paper we have
-%used up to 128 islands. 
-%
-%Lately, some researchers \cite{cheng2015adaptive} have focused on
-%working on solution space, dividing the Pareto front in different
-%clusters in order to model it. This {\em divide and conquer} approach
-%is readily paralellizable and, in the sense of giving the
-%responsibility of different parts of the search space to different
-%modules, is similar to the one presented in this paper. We will
-%describe how we have tested our approach in the next Section.
+Since the early 2000s, the distributed and parallel Evolutionary Algorithms have been used, mostly to take the most from systems such as clusters or grids \cite{Talbi08Parallel}.
+But in the case of MOEAs, the distribution and parallelization is not as direct as in single-objective EAs.
+This is because in different steps of the algorithm a whole set of dependent solutions, the Pareto Front, should be managed as a whole, spending time in gather all individuals from the different process or islands.
+
+To solve this issue, some authors have proposed the usage of Master-Slave approaches.
+For example, Durillo et al.
+\cite{Durillo08masterslave} compared different master-slave approaches TODO DESCRIBIR MEJOR ESTE TRABAJO.
+The method proposed by Hiroyasu \cite{Hiroyasu07discussion} generates offspring depending on the computation power.
+TODO Y ESTE
+
+The work by Deb in 2003 was one of the first approaches for distributed MOEAs (dMOEAs).
+In that work, the dominance of solutions was divided in the islands using a transformation of coordinates.
+Their authors concluded that dividing the search space is a good idea, but achieve this is not trivial.
+Other approaches for dividing the search space include objective separation in different processors \cite{Xiao03specialized}, or divide in two populations: one for elite and other search \cite{Wang09parallel}.
+Martens, in \cite{Martens13asynchronous} generated a Barabasi-Albert network as the island topology, and selection based on migrating individuals from a not-crowded area and acceptance based on diversity.
+
+More similar approaches to the one presented here were studied in the
+next two works, also using cooperative coevolution for high-dimensional problems. Dorronsoro et al. in
+\cite{Dorronsoro13superlinear} obtained super-linear performance
+in several instances using cooperative coevolution, focusing each island on a portion of the chromosome. However, in some instances the parallel version 
+improved the sequential version.  Kimovski et al. \cite{Kimovski15Parallel} proposed a
+master-slave method that splits the population into several processors,
+each one running in parallel a MOEA that only affects some portion of
+the individuals. After a certain number of generations, the master
+process receives all the sub-populations to be combined. Different
+combination alternatives in this step are compared. Up to 8 processors
+were used in the experimental setup. Our approach in this paper does not
+broadcast all solutions to all islands for recombination, as previous
+works, but only one solution to a random island, needing less
+communication time. Besides, the maximum number of islands of
+Dorronsoro or Kimovsky approaches was 8, while in this paper we have
+used up to 128 islands.
+
+Lately, some researchers \cite{cheng2015adaptive} have focused on
+working on solution space, dividing the Pareto front in different
+clusters in order to model it. This {\em divide and conquer} approach
+is readily paralellizable and, in the sense of giving the
+responsibility of different parts of the search space to different
+modules, is similar to the one presented in this paper.
+
+In our previous work \cite{Garcia16Evostar} we used some of the previous ideas to compare two co-evolutionary dMOEAs.
+The first one divided the chromosome in $P$ sections, being $P$ the number of islands.
+Every island $p$ only performed the mutation and crossover in that part ($p_{th}$) of the chromosome, while the fitness was calculated using the whole individual.
+After certain number of generations, individuals were migrated randomly to other islands.
+The performance metrics were calculated at the end of the run.
+The second method, coevolution with overlapping islands, used the $p_{th-1}$ and $p_{th+1}$ sections of each chromosome, besides the $p_{th}$ part.
+During the same amount of time both methods obtained better results than a baseline algorithm that dealt with the whole chromosome in each island for crossover and mutation.
+We discovered that the performance using one or another method depends on the number of sections of the individuals and the number of islands used.
+This motivates us to find a new adaptive method to select this number of sections of the chromosome to use, depending on the number of islands.
+Moreover, previous experiments were performed in a single processor synchronous island model with a limited number of islands (8, 32 and 128).
+In this paper, we have used 8, 16, 32, 64 and 128 islands, and this time, using a real cluster.
+Therefore, at the same time we are proposing an adaptive method to divide the individual search space, we are validating the previous methods.
+
+We will describe how we have tested our approach in the next Section.
 

### 2016-06-08 hpmoon-hpca.tex
Changed citation format and added reference

@@
 
-Different approaches have been used to parallelize Evolutionary Algorithms (EAs), as each individual can be considered as an independient unit \cite{Alba13parallel}.
-Classic methods, such as the global parallel EAs (Master-Slave), or the spatially structured algorithms (Island model or Cellular EAs) have been applied successfully in the past \cite{Folino03cellular,Alba02Parallelism}.
-In the case of Multi-Objective Evolutionary Algorithms (MOEAs), these approaches \cite{Luna15Survey} need to deal with a whole solution set called Pareto Front (PFs).
-This imply to use different distribution and sharing mechanisms, as there exist a tension between the speedup achievable from parallelization and the need to globally recombine results to accurately identify the PF \cite{Branke04Parallelizingcone}.
+Different approaches have been used to parallelize Evolutionary Algorithms (EAs), as each individual can be considered as an independient unit \citep{Alba13parallel}.
+Classic methods, such as the global parallel EAs (Master-Slave), or the spatially structured algorithms (Island model or Cellular EAs) have been applied successfully in the past \citep{Folino03cellular,Alba02Parallelism}.
+In the case of Multi-Objective Evolutionary Algorithms (MOEAs), these approaches \citep{Luna15Survey} need to deal with a whole solution set called Pareto Front (PFs).
+This imply to use different distribution and sharing mechanisms, as there exist a tension between the speedup achievable from parallelization and the need to globally recombine results to accurately identify the PF \citep{Branke04Parallelizingcone}.
 
-The application of MOEAs to solve real-world problems have gained attention in the last years \cite{Luna15Survey,Mukhopadhyay14Survey}.
+The application of MOEAs to solve real-world problems have gained attention in the last years \citep{Luna15Survey,Mukhopadhyay14Survey}.
 These kind of problems require a high number of variables, meaning that the EAs need to deal with large individuals and spent significant extra time for crossover, mutation and migration.
 Different authors have proposed methods to divide the decision space (the chromosome) to improve the performance and solution quality.
-In this aspect, the co-evolution model is a dimension-distributed model where a high-dimensional problem is divided into lower dimensional problems \cite{Gong15models}, and evolved separately.
-One example of application of this technique was described in \cite{Kimovski15Parallel}.
+In this aspect, the co-evolution model is a dimension-distributed model where a high-dimensional problem is divided into lower dimensional problems \citep{Gong15models}, and evolved separately.
+One example of application of this technique was described in \citep{Kimovski15Parallel}.
 The method presented in that works involves different workers that evolve sub-populations created and recombined by a master process, which performs different recombination alternatives from the parts returned by worker processes.
@@
 alternatives.
-In \cite{Dorronsoro13superlinear}, a distributed coevolutionary island model was used.
+In \citep{Dorronsoro13superlinear}, a distributed coevolutionary island model was used.
 Although in both previous works significant speedups were attained, only a low number of nodes were used (8).
@@
 
-In \cite{Garcia16Evostar} we tried to demonstrate that using overlapped sections of the chromosome in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time when the number of islands increases.
+In \citep{Garcia16hpmoon} we tried to demonstrate that using overlapped sections of the chromosome in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time when the number of islands increases.
 We discovered that the most adequate overlapping size chosen varies depending on a relation between the number of islands and the indidivual size.
@@
 The hypothesis of this paper is that using overlapped sections of the chromosome, calculated depending the number of islands to use, in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time with respect to disjoint and partly overlaped methods.
-To demonstrate this, a new overlapping islands scheme has been compared with a baseline version of a distributed NSGA-II \cite{Deb00NSGAII}, a coevolutionary disjoint section approach, and a fixed-size overlapped method.
+To demonstrate this, a new overlapping islands scheme has been compared with a baseline version of a distributed NSGA-II \citep{Deb00NSGAII}, a coevolutionary disjoint section approach, and a fixed-size overlapped method.
 Different benchmarks problems and different large number of islands have been used.
@@
 
-Since the early 2000s, the distributed and parallel Evolutionary Algorithms have been used, mostly to take the most from systems such as clusters or grids \cite{Talbi08Parallel}.
+Since the early 2000s, the distributed and parallel Evolutionary Algorithms have been used, mostly to take the most from systems such as clusters or grids \citep{Talbi08Parallel}.
 But in the case of MOEAs, the distribution and parallelization is not as direct as in single-objective EAs.
@@
 For example, Durillo et al.
-\cite{Durillo08masterslave} compared different master-slave approaches TODO DESCRIBIR MEJOR ESTE TRABAJO.
-The method proposed by Hiroyasu \cite{Hiroyasu07discussion} generates offspring depending on the computation power.
+\citep{Durillo08masterslave} compared different master-slave approaches TODO DESCRIBIR MEJOR ESTE TRABAJO.
+The method proposed by Hiroyasu \citep{Hiroyasu07discussion} generates offspring depending on the computation power.
 TODO Y ESTE
@@
 Their authors concluded that dividing the search space is a good idea, but achieve this is not trivial.
-Other approaches for dividing the search space include objective separation in different processors \cite{Xiao03specialized}, or divide in two populations: one for elite and other search \cite{Wang09parallel}.
-Martens, in \cite{Martens13asynchronous} generated a Barabasi-Albert network as the island topology, and selection based on migrating individuals from a not-crowded area and acceptance based on diversity.
+Other approaches for dividing the search space include objective separation in different processors \citep{Xiao03specialized}, or divide in two populations: one for elite and other search \citep{Wang09parallel}.
+Martens, in \citep{Martens13asynchronous} generated a Barabasi-Albert network as the island topology, and selection based on migrating individuals from a not-crowded area and acceptance based on diversity.
 
@@
 next two works, also using cooperative coevolution for high-dimensional problems. Dorronsoro et al. in
-\cite{Dorronsoro13superlinear} obtained super-linear performance
+\citep{Dorronsoro13superlinear} obtained super-linear performance
 in several instances using cooperative coevolution, focusing each island on a portion of the chromosome. However, in some instances the parallel version 
-improved the sequential version.  Kimovski et al. \cite{Kimovski15Parallel} proposed a
+improved the sequential version.  Kimovski et al. \citep{Kimovski15Parallel} proposed a
 master-slave method that splits the population into several processors,
@@
 
-Lately, some researchers \cite{cheng2015adaptive} have focused on
+Lately, some researchers \citep{cheng2015adaptive} have focused on
 working on solution space, dividing the Pareto front in different
@@
 
-In our previous work \cite{Garcia16Evostar} we used some of the previous ideas to compare two co-evolutionary dMOEAs.
+In our previous work \citep{Garcia16hpmoon} we used some of the previous ideas to compare two co-evolutionary dMOEAs.
 The first one divided the chromosome in $P$ sections, being $P$ the number of islands.
@@
 %contrary of other works such as the ones described
-%\cite{Talbi08Parallel} all the islands deal with complete chromosomes
+%\citep{Talbi08Parallel} all the islands deal with complete chromosomes
 %for fitness calculation, so our approach can deal with no decomposable
@@
 %of islands have also been  used in previous work in the literature
-%\cite{Martens13asynchronous}. The crossover and mutation chosen, SBX
+%\citep{Martens13asynchronous}. The crossover and mutation chosen, SBX
 %and polynomial, have been used previously by other authors in
-%\cite{Durillo08masterslave}.
+%\citep{Durillo08masterslave}.
 
-%ZDT \cite{zdt2000a} has been chosen as a benchmark, since it is the most widely
+%ZDT \citep{zdt2000a} has been chosen as a benchmark, since it is the most widely
 %used in this area
-%\cite{Deb03distributed,Martens13asynchronous,Wang09parallel,Durillo08masterslave}. The
+%\citep{Deb03distributed,Martens13asynchronous,Wang09parallel,Durillo08masterslave}. The
 %optimal PF distribution used for comparison has 1000
@@
 
-The ECJ framework \cite{ECJ} has been used to run the
+The ECJ framework \citep{ECJ} has been used to run the
 experiments. Specific operators have been developed as new modules for
@@
 %increased, as the subpopulations are smaller. This is consistent with
-%the claim by Durillo in \cite{Dorronsoro13superlinear}, who found that
+%the claim by Durillo in \citep{Dorronsoro13superlinear}, who found that
 %cooperative coevolutionary MOEAs work better on bigger populations

### 2016-06-09 hpmoon-hpca.tex
Added sols and gens table
Some results discussion added

@@
 
-%Different metrics, explained in the previous section, have been used to calculate the quality of the obtained PFs in each configuration.
+Different metrics, explained in the previous section, have been used to calculate the quality of the obtained PFs in each configuration.
 As some of the metrics require a reference point to be calculated (such as HV), the point (1,9) has been chosen as reference, as none of the generated PFs in all runs are dominated by it.
@@
 A Kruskall-Wallis significance test has been performed to the metrics of all runs of the configurations, as the Kolmogorov-Smirnov test detected non-normal distributions.
-The average results for each configuration are shown in Table \ref{tab:results}.
+The average results for each configuration are shown in Table \ref{tab:results512} (for 512 dimensions) and \ref{tab:results2048} (for 2048).
 
@@
 \centering
-\resizebox{12cm}{!}{
+\resizebox{14cm}{!}{
 \begin{tabular}{|c||c|c|c|c||c|c|c|c||c|c|c|c||}
@@
 }
-\caption{Métricas de calidad obtenidas después de 30 ejecuciones por configuración, para los cuatro métodos comparados: baseline (B), disjunto (D), solapado (S) y solapado adaptativo (A).
-Los acrónimos junto a los valores indican que no hay diferencia significativa con respecto a ese método para ese valor.
-Los mejores valores están marcados en negrita.}
+\caption{Quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 512 dimensions.
+Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
+Best values are marked in bold.}
 \label{tab:results512}
@@
 \centering
-\resizebox{12cm}{!}{
+\resizebox{16cm}{!}{
 \begin{tabular}{|c||c|c|c|c||c|c|c|c||c|c|c|c||}
@@
 }
-\caption{Métricas de calidad obtenidas después de 30 ejecuciones por configuración, para los cuatro métodos comparados: baseline (B), disjunto (D), solapado (S) y solapado adaptativo (A).
-Los acrónimos junto a los valores indican que no hay diferencia significativa con respecto a ese método para ese valor.
-Los mejores valores están marcados en negrita.}
-\label{tab:results512}
+\caption{Quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 512 dimensions.
+Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
+Best values are marked in bold.}
+\label{tab:results2048}
 \end{table*}
 
-%At a first glance results show that dividing the chromosome produces
-%an improvement in all the quality indicators in all the
-%configurations, with respect to the baseline. Also, results show that
-%all the quality indicators lowers when the number of islands is
-%increased, as the subpopulations are smaller. This is consistent with
-%the claim by Durillo in \citep{Dorronsoro13superlinear}, who found that
-%cooperative coevolutionary MOEAs work better on bigger populations
-%(more than 100 individuals). Paying attention to the disjoint and
+\begin{table*}
+\centering
+\resizebox{12cm}{!}{
+\begin{tabular}{|c||c|c|c|c||c|c|c|c||}
+\hline
+	&	\multicolumn{4}{|c|}{Average solutions per island}													&	\multicolumn{4}{|c|}{Generations}															\\ \hline
+
+\#Island	&	B		&	D		&	O			&	A			&	B		&	D			&	O			&	A				\\ \hline
+\multicolumn{9}{|c|}{ZDT1}																				\\ \hline
+8	&	182.700		&	128.500		&	158.167			&	Equiv. D			&	397.367		&	776.967			&	603.667			&	Equiv. D				\\
+16	&	132.567		&	43.633		&	76.167			&	Equiv. O			&	567.933		&	908.467			&	838.000			&	Equiv. O				\\
+32	&	102.200		&	37.533		&	34.133	D		&	52.033			&	731.067		&	959.067			&	938.167			&	917.000				\\
+64	&	81.100		&	46.267		&	26.300			&	30.167		O	&	846.733		&	978.733			&	972.567			&	927.133	B			\\
+128	&	77.167		&	57.767		&	35.767			&	29.167		O	&	923.133		&	984.767			&	984.233	D		&	967.933				\\ \hline
+\multicolumn{9}{|c|}{ZDT2}																															\\ \hline
+8	&	122.700		&	91.633		&	108.833	BD		&	Equiv. D			&	398.167		&	772.000			&	605.100			&	Equiv. D				\\
+16	&	94.867		&	28.033		&	62.467			&	Equiv. O			&	574.567		&	908.433			&	840.900			&	Equiv. O				\\
+32	&	56.633		&	11.433		&	19.467	D		&	31.567			&	735.867		&	960.167			&	939.200			&	904.900				\\
+64	&	33.467		&	10.267		&	9.367	D		&	19.067			&	849.900		&	978.600			&	972.167			&	929.800	B			\\
+128	&	22.833		&	12.633		&	7.800			&	13.967		D	&	929.433		&	984.567			&	984.233	D		&	971.700				\\ \hline
+\multicolumn{9}{|c|}{ZDT3}																															\\ \hline
+8	&	212.900		&	129.233		&	171.367			&	Equiv. D			&	398.633		&	776.000			&	603.333			&	Equiv. D				\\
+16	&	176.133		&	43.567		&	90.100			&	Equiv. O			&	573.033		&	908.667			&	838.000			&	Equiv. O				\\
+32	&	121.500		&	42.800		&	33.200			&	56.900			&	733.233		&	959.000			&	937.967			&	918.833				\\
+64	&	96.500		&	54.267		&	34.900			&	37.800		O	&	849.200		&	977.167			&	972.200			&	933.167				\\
+128	&	76.700		&	62.200		&	41.767			&	33.867		D	&	924.000		&	984.733			&	984.367	D		&	966.433				\\ \hline
+\multicolumn{9}{|c|}{ZDT6}																															\\ \hline
+8	&	42.233		&	28.633		&	35.967	BD		&	Equiv. D			&	396.900		&	773.400			&	603.533			&	Equiv. D				\\
+16	&	43.733		&	7.733		&	18.967			&	Equiv. O			&	568.200		&	908.900			&	836.033			&	Equiv. O				\\
+32	&	35.533		&	8.033		&	8.633	D		&	16.233		DO	&	735.700		&	958.900			&	938.600			&	926.167				\\
+64	&	22.600		&	10.700		&	7.500	D		&	7.533		DO	&	850.267		&	978.067			&	972.467			&	940.267				\\
+128	&	18.133		&	15.000	B	&	9.067			&	11.367		D	&	927.233		&	984.667			&	983.933	D		&	969.433				\\ \hline
+\end{tabular}
+}
+\caption{Average number of generations and average number of solutions per island, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 512 dimensions.
+Acronyms next to values indicate that there is not significant difference with respect to that method for that value.}
+\label{tab:sols512}
+\end{table*}
+
+\begin{table*}
+\centering
+\resizebox{12cm}{!}{
+\begin{tabular}{|c||c|c|c|c||c|c|c|c||}
+\hline
+	&	\multicolumn{4}{|c|}{Average solutions per island}													&	\multicolumn{4}{|c|}{Generations}															\\ \hline
+%\multicolumn{13}{|c|}{2048 dimensions}																															\\ \hline
+\#Island	&	B		&	D		&	O			&	A			&	B		&	D			&	O			&	A				\\ \hline
+\multicolumn{9}{|c|}{ZDT1}																					\\ \hline
+8	&	137.733		&	47.167		&	119.933	B		&	Equiv. D			&	175.067		&	225.667			&	207.933			&	Equiv. D				\\
+16	&	92.633		&	38.233		&	47.533	D		&	Equiv. O			&	204.867		&	238.533			&	232.900			&	Equiv. O				\\
+32	&	56.167		&	41.167		&	28.667			&	32.567	O		&	225.433		&	243.833			&	242.533			&	242.000	O			\\
+64	&	50.900		&	49.667	B	&	35.600			&	25.367			&	236.500		&	245.967			&	245.700			&	244.033	D			\\
+128	&	45.767		&	64.933		&	44.167	B		&	31.867			&	242.800		&	247.000			&	247.000	D		&	245.733				\\ \hline
+\multicolumn{9}{|c|}{ZDT2}																															\\ \hline
+8	&	64.267		&	22.733		&	56.867	B		&	Equiv. D			&	175.633		&	226.000			&	208.100			&	Equiv. D				\\
+16	&	52.300		&	10.733		&	20.067	D		&	Equiv. O			&	205.033		&	238.867			&	233.100			&	Equiv. O				\\
+32	&	34.400		&	10.367		&	10.433	D		&	17.900	O		&	225.600		&	244.267			&	242.633			&	242.000	O			\\
+64	&	24.600		&	10.900		&	9.267	D		&	12.867	DO		&	236.700		&	246.000			&	245.767			&	244.033	D			\\
+128	&	18.667		&	17.833	B	&	10.367			&	12.933	O		&	243.367		&	247.000			&	247.000	d		&	245.833				\\ \hline
+\multicolumn{9}{|c|}{ZDT3}																															\\ \hline
+8	&	163.767		&	83.367		&	119.467			&	Equiv. D			&	176.533		&	226.400			&	207.700			&	Equiv. D				\\
+16	&	108.467		&	49.433		&	47.700	D		&	Equiv. O			&	205.333		&	238.467			&	232.933			&	Equiv. O				\\
+32	&	72.133		&	44.333		&	31.833			&	36.533	O		&	225.100		&	243.900			&	242.433			&	242.000	O			\\
+64	&	54.867		&	57.600	B	&	40.633			&	29.300			&	236.333		&	245.933			&	245.733			&	244.000	D			\\
+128	&	50.600		&	72.133		&	49.033	B		&	34.933			&	243.200		&	247.000			&	247.000	D		&	245.833				\\ \hline
+\multicolumn{9}{|c|}{ZDT6}																															\\ \hline
+8	&	22.133		&	13.833		&	14.433	D		&	Equiv. D			&	175.733		&	226.100			&	207.767			&	Equiv. D				\\
+16	&	20.767		&	15.867		&	13.300	D		&	Equiv. O			&	205.033		&	238.433			&	232.933			&	Equiv. O				\\
+32	&	22.600		&	10.700		&	10.033	D		&	11.967	DO		&	225.833		&	243.667			&	242.500			&	242.000	O			\\
+64	&	19.033		&	11.267		&	10.533	D		&	10.567	DO		&	236.433		&	245.900			&	245.833			&	244.000	D			\\
+128	&	15.800		&	24.500		&	11.600			&	12.233	DO		&	243.800		&	247.000			&	247.000	D		&	245.533				\\ \hline
+\end{tabular}
+}
+\caption{Average number of generations and average number of solutions per island, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 2048 dimensions.
+Acronyms next to values indicate that there is not significant difference with respect to that method for that value.}
+\label{tab:sols2048}
+\end{table*}
+
+Results show that there is a difference in performance when using 512 or 2048 dimensions.
+Although in some cases the overlapped methods obtain quality metrics values significantly equal than the obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply this methods.
+This contradicts the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping methods obtained best results than the baseline in both dimension lengths.
+This can be explained because the added migration latency between nodes requires more time than the time saved during the crossover and migration.
+
+However, with 2048 dimensions, results show that dividing the chromosome produces an improvement in all the quality indicators using the adaptive version (Table \ref{tab:results2048}), even improving the overlapping and disjoint methods.
+
+Therefore, there exist some kind of limit point in chromosome length where one method will be preferable to another, depending the number of islands, population size and length.
+
+This can be explained comparing the number non-dominated solutions in each island and the average number of generations (Table \ref{tab:sols512} and Table \ref{tab:sols2048}).
+With both chromosome lengths, increasing the number of islands implies more generations with all the methods (logically, as there are less individuals in each island).
+But also, the co-evolutionary methods approach to the number of generations with the baseline when increasing the number of islands.
+However, with $L=2048$ the migration time is enough big to almost not improve the number of generations with respect to the baseline, even in the lower number of islands, as it happens with $L=512$.
+Therefore, more generations do not necessarily improve the solution of the global PF, but focusing in different elements of the chromosome.
+As indicated previously, every island is unaware of the other islands PFs, and they are trying to optimize their solutions independently...
+%TENGO QUE COMENTAR MAS LOS RESULTADOS Y ENTENDERLO TODO Y JUSTIFICARLO FINAMENTE
+
+Finally, as happened in \citep{Garcia16hpmoon}, results show that all the quality indicators lowers when the number of islands is increased, as the subpopulations are smaller.
+This is consistent with the claim by Durillo in \citep{Dorronsoro13superlinear}, who found that cooperative coevolutionary MOEAs work better on bigger populations (more than 100 individuals).
+
+%Surprisingly, the average
+%number of solutions of PFs per island in the baseline configuration is significantly
+%higher in some configurations (mostly with 128 islands), but their
+%combination in the final PF never attains higher values than Disjoint
+%and Overlapping methods.
+
+%configurations, with respect to the baseline.  Paying attention to the disjoint and
 %overlapping methods, only when using 8 islands the disjoint method
@@
 %changed in each island, while in the overlapping, 3/8 of the island
-%may be more similar to the baseline configuration. Therefore, there exist some kind
-%of limit point where one method will be preferable to another,
-%depending the number of islands, population size and length. 
+%may be more similar to the baseline configuration. 
 %
-%This can be explained also comparing the number of generations and
-%average solutions per island. Table \ref{tab:gens} shows these values
-%obtained in each method. It is clear that in the same amount of time,
-%the disjoint and overlapping method needs more generations than the
-%baseline. This is even clearer with $L=$2048, where almost 10 times
-%the number of generations is attained, and therefore, more migrations
-%and crossovers/mutations can be achieved. Surprisingly, the average
-%number of solutions of PFs per island in the baseline configuration is significantly
-%higher in some configurations (mostly with 128 islands), but their
-%combination in the final PF never attains higher values than Disjoint
-%and Overlapping methods.
 

### 2016-06-10 hpmoon-hpca.tex
Added more comments

@@
 \label{sec:met}
-%This section describes the quality indicators used and the methods
-%compared. The chosen quality indicators,
-%are:
-%
-%\begin{itemize}
-%\item Hypervolume (HV): measures the area formed by all non-dominated solutions found with, respect to a reference point. Higher values imply better %quality of the PF.
-%\item Inverted Generational distance (IGD): calculates the distance of the obtained set of solutions to the optimal PF.
-Therefore, this metric requires %the optimal PF found in the literature, or the theoretical one.
+
+This section describes the quality indicators used and the methods compared. The chosen quality indicators, are:
+
+\begin{itemize}
+\item Hypervolume (HV): measures the area formed by all non-dominated solutions found with, respect to a reference point. Higher values imply better quality of the PF.
+\item Inverted Generational distance (IGD): calculates the distance of the obtained set of solutions to the optimal PF.
+Therefore, this metric requires the optimal PF found in the literature, or the theoretical one.
 In this metric, the lower the better.
 %Pablo: theoretical?
-%\item Spread (S): Measures the spread between solutions, taking into account the euclidean distance between consecutive solutions.
-As in previous %metric, the lower value, the better, as it implies solutions distributed along all the PF.
-%\end{itemize}
-%
-%These metrics have been used extensively, especially in some of the papers
-%presented previously in Section \ref{sec:soa}.
-%
-%
+\item Spread (S): Measures the spread between solutions, taking into account the euclidean distance between consecutive solutions.
+As in previous metric, the lower value, the better, as it implies solutions distributed along all the PF.
+\end{itemize}
+
+These metrics have been used extensively, especially in some of the papers presented previously in Section \ref{sec:soa}.
+
 %% --------------------------------------------------------------
-%
-%\subsection{Baseline algorithm}
-%
-%This algorithm is a regular NSGA-II algorithm distributed along a
-%number $P$ of islands. After a fixed number of generations, one
-%individual is migrated to another random island. At the end of the
-%run, all PFs of all islands are aggregated in a new one to compute the
-%quality measures.
-%% some justification on why this was chosen - JJ
+
+\subsection{Baseline algorithm}
+
+This algorithm is a regular NSGA-II algorithm distributed along a number $P$ of islands.
+After a fixed number of generations, one individual is migrated to another random island.
+At the end of the run, all PFs of all islands are aggregated in a new one to compute the quality measures.
+This method as been chosen as it do not require synchronization of the global PF every certain number of generations, as other methods described in Section \ref{sec:soa}, and because it can TERMINAAAAAA
+%% some justification on why this was chosen - JJ PABLO: Added 
 %
 %% And some liaison to next subsection - JJ
-%
-%\subsection{Coevolutionary algorithms compared}
-%Two different coevolutionary methods have also been used. In both
-%methods, each island only performs crossover and mutation in specific sections of the
-%individuals.
-%
-%As in the baseline, every 
-%certain number of generations, an individual is migrated to another
-%random island.  In the new island, this individual will be considered as one of the others in the island, crossed and
-%mutated in the same way, depending of the island identifier. Note that, on the
-%contrary of other works such as the ones described
-%\citep{Talbi08Parallel} all the islands deal with complete chromosomes
-%for fitness calculation, so our approach can deal with no decomposable
-%problems. 
-%
-%\subsubsection{Coevolution with disjoint islands} 
-%In this approach, each individual of size $L$ is split into $P$ chunks
-%of size $L/P$. Every island $p$ only performs crossover and mutation
-%on the $p_{th}$ part of the individuals. Figure \ref{fig:disjoint} describes this approach.  
-%
-%\begin{figure}
-%\includegraphics[width=12cm]{islandDisjoint.jpg}
-%\caption{Disjoint algorithm: every island $p$ only modifies the $p_{th}$ components (in grey) of the individuals.}
-%\label{fig:disjoint}
-%\end{figure}
-%
-%\subsubsection{Coevolution with overlapping islands}
-%This approach is similar to the previous one, but every island also
-%uses the $p+1$ and $p-1$ (module size) chunks of the individual for
-%crossover and migration. Therefore, some kind of overlapping of the
-%crossed and mutated parts exists between islands. Figure
-%\ref{fig:overlapping} shows the affected parts of the individuals in
-%each island. 
-%
-% 
-%\begin{figure}
-%\includegraphics[width=12cm]{islandNoDisjoint.jpg}
-%\caption{Overlapping algorithm: every island $p$ modifies the  $p+1$,
-  %$p_{th}$ and $p-1$  components (in grey) of the individuals.}
-%\label{fig:overlapping}
-%\end{figure}
+This method will be compared to different coevolutionary approaches, that are similar to the baseline, with the exception on the decision space to explore in each island.
+\subsection{Coevolutionary algorithms compared}
+Three different coevolutionary methods have also been used. In all these methods, each island only performs crossover and mutation in specific sections of the individuals.
+
+As in the baseline, every certain number of generations, an individual is migrated to another random island.
+In the new island, this individual will be considered as one of the others in the island, crossed and mutated in the same way, depending of the island identifier.
+Note that, on the contrary of other works such as the ones described by \cite{Talbi08Parallel} all the islands deal with complete chromosomes for fitness calculation, so our approach can deal with no decomposable problems.
+
+\subsubsection{Coevolution with disjoint islands} 
+In this approach, each individual of size $L$ is split into $P$ chunks of size $L/P$.
+Every island $p$ only performs crossover and mutation on the $p_{th}$ part of the individuals.
+Figure \ref{fig:disjoint} describes this approach.
+
+\begin{figure*}
+\includegraphics[width=12cm]{islandDisjoint.jpg}
+\caption{Disjoint algorithm: every island $p$ only modifies the $p_{th}$ components (in grey) of the individuals.}
+\label{fig:disjoint}
+\end{figure*}
+
+\subsubsection{Coevolution with overlapping islands}
+This approach is similar to the previous one, but every island also uses the $p+1$ and $p-1$ (module size) chunks of the individual for crossover and migration.
+Therefore, some kind of overlapping of the crossed and mutated parts exists between islands.
+Figure \ref{fig:overlapping} shows the affected parts of the individuals in
+each island.
+
+\begin{figure*}
+\includegraphics[width=12cm]{islandNoDisjoint.jpg}
+\caption{Overlapping algorithm: every island $p$ modifies the  $p+1$,
+  $p_{th}$ and $p-1$  components (in grey) of the individuals.}
+  \label{fig:overlapping}
+\end{figure*}
+
+\subsubsection{Adaptive coevolution with overlapping islands} 
+As in the previous method, the sections to address are overlapped, but instead using one extra section on each side of the $p$ section ($p+1$ and $p-1$), it uses $c$ fragments on each side ($p+c$ y $p-c$), being $c$ a value depending on the number of islands.
+The results shown in \citep{Garcia16evostar} have been used as a base to calculate $c$.
+In that work, the overlapped method ($c=1$) obtained better results when the number of islands were >8.
+Therefore, we have used the formula $c=round(0.2*P-1)/2$ to calculate the extra sections to overlap.
+%TODO TERMINA Y PONER MAS EJEMPLOS Y DECIR QUE ESTA ES UNA PRIMERA APROXIMACION
 
@@
 
-%The three approaches have been run with two different 
-%chromosome lengths ($L$): 512 and 2048. Different number of
-%islands ($P$) have also been compared: 8, 32 and 128. This maximum number
-%of islands have also been  used in previous work in the literature
-%\citep{Martens13asynchronous}. The crossover and mutation chosen, SBX
-%and polynomial, have been used previously by other authors in
-%\citep{Durillo08masterslave}.
+The four approaches have been run with two different chromosome lengths ($L$): 512 and 2048.
+Different number of islands ($P$) have also been compared: 8, 32 and 128.
+This maximum number of islands have also been  used in previous work in the literature \citep{Martens13asynchronous}.
+The crossover and mutation chosen, SBX and polynomial, have been used previously by other authors in \citep{Durillo08masterslave}.
 
-%ZDT \citep{zdt2000a} has been chosen as a benchmark, since it is the most widely
-%used in this area
-%\citep{Deb03distributed,Martens13asynchronous,Wang09parallel,Durillo08masterslave}. The
-%optimal PF distribution used for comparison has 1000
-%solutions \footnote{Optimal PFs are available at:
-%  \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.}.
+ZDT \citep{zdt2000a} has been chosen as a benchmark, since it is the most widely used in this area \citep{Deb03distributed,Martens13asynchronous,Wang09parallel,Durillo08masterslave}.
+The optimal PF distribution used for comparison has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.}.
 
-%The termination criterion used is the execution time: 25 seconds for dimension 512 and 100 (four times more) for 2048.
+The termination criterion used is the execution time: 25 seconds for dimension 512 and 100 (four times more) for 2048.
 We have used the time instead the number of evaluations firstly because our hypothesis argue that the time saved in crossover in mutation can be spent on improving the sub-populations and more operations and migrations can be achieved.
@@
 }
-\caption{Quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 512 dimensions.
+\caption{Quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 2048 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 
+%DESCRIPTION OF THE RESULTS
 Results show that there is a difference in performance when using 512 or 2048 dimensions.
-Although in some cases the overlapped methods obtain quality metrics values significantly equal than the obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply this methods.
-This contradicts the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping methods obtained best results than the baseline in both dimension lengths.
+Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than the obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply these methods.
+This contradicts the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained best results than the baseline in both dimension lengths.
 This can be explained because the added migration latency between nodes requires more time than the time saved during the crossover and migration.
@@
 However, with 2048 dimensions, results show that dividing the chromosome produces an improvement in all the quality indicators using the adaptive version (Table \ref{tab:results2048}), even improving the overlapping and disjoint methods.
-
 Therefore, there exist some kind of limit point in chromosome length where one method will be preferable to another, depending the number of islands, population size and length.
 
+%EXPLANATION OF THE RESULTS
 This can be explained comparing the number non-dominated solutions in each island and the average number of generations (Table \ref{tab:sols512} and Table \ref{tab:sols2048}).
@@
 Therefore, more generations do not necessarily improve the solution of the global PF, but focusing in different elements of the chromosome.
-As indicated previously, every island is unaware of the other islands PFs, and they are trying to optimize their solutions independently...
-%TENGO QUE COMENTAR MAS LOS RESULTADOS Y ENTENDERLO TODO Y JUSTIFICARLO FINAMENTE
+As indicated previously, every island is unaware of the other islands PFs, and they are trying to optimize their solutions independently.
+With respect to the average number of solution in each island, there is a clear difference in number with the baseline with $L=512$, where this value is in the most of the cases, less than a half.
+The number of non-dominated solutions also improves a better Spread indicator, where the baseline almost always obtains better values %TENGO QUE COMENTAR MAS LOS RESULTADOS Y ENTENDERLO TODO Y JUSTIFICARLO FINAMENTE
 
@@
 
+TIN2014-56494-C4-3-P y TIN2015-67020-P (Ministerio de Economía y Competitividad), PROY-PP2015-06 (Plan Propio 2015 UGR),  y MSTR (PRY142/14, Fundación Pública Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigación).
+
 \bibliographystyle{SageH}

### 2016-06-10 hpmoon-hpca.tex
First draft

@@
 
-\author{Pablo Garc\'ia-S\'anchez, Julio Ortega, Jes\'us Gonz\'alez, Pedro Angel Castillo and Juan Juli\'an Merelo\affilnum{1}}
+\author{Pablo Garc\'ia-S\'anchez, Julio Ortega, Jes\'us Gonz\'alez, \\Pedro Angel Castillo and Juan Juli\'an Merelo\affilnum{1}}
 
@@
 \begin{abstract}
-This paper...
+Multi-objective optimization methods have gained interest in the last years because the performance they can achieve solving real-world problems.
+These kind of problems usually require a high-dimensional decision space, and multi-objective Evolutionary Algorithms have been successfully used in the past.
+Due to the large computational cost these algorithms require, different parallelization and distribution methods have been proposed, with different parallel and distributed computer architectures to cope with them.
+One of the most extended methods are the distributed co-evolutionary evolutionary algorithms, where each processor only deals with a part of the decision space, that is, the individuals belonging to the same sub-population (island) explore the same subset of decision variables.
+
+In this paper, a new method to automatically adapt the overlapping sections of the individuals have been compared to other collaborative evolutionary methods.
+Different number of islands, chromosome sizes and problems have been used. The analysis of the obtained experimental results, by using different 
+metrics, shows that coevolutionary approaches can provide statistically significant improvements with respect to the base algorithm, being the method to automatically adapt the overlapping size the one to obtain better performance during the same execution time.
+Results also show that the relation of the number of
+islands (subpopulations) to the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distribute the decision variables.
 \end{abstract}
@@
 
-In \citep{Garcia16hpmoon} we tried to demonstrate that using overlapped sections of the chromosome in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time when the number of islands increases.
-We discovered that the most adequate overlapping size chosen varies depending on a relation between the number of islands and the indidivual size.
+In our preliminary work in \citep{Garcia16hpmoon} we tried to demonstrate that using overlapped sections of the chromosome in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time when the number of islands increases.
+We discovered that the most adequate overlapping size may vary depending on a relation between the number of islands and the individual size.
 Moreover, the experiments were conducted in a mono-processor and synchronous island model.
@@
 
-The hypothesis of this paper is that using overlapped sections of the chromosome, calculated depending the number of islands to use, in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time with respect to disjoint and partly overlaped methods.
+The hypothesis of this paper is that using overlapped sections of the chromosome, calculated depending the number of islands to use, in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time with respect to the baseline, disjoint and partly overlapped methods.
 To demonstrate this, a new overlapping islands scheme has been compared with a baseline version of a distributed NSGA-II \citep{Deb00NSGAII}, a coevolutionary disjoint section approach, and a fixed-size overlapped method.
@@
 To solve this issue, some authors have proposed the usage of Master-Slave approaches.
-For example, Durillo et al.
-\citep{Durillo08masterslave} compared different master-slave approaches TODO DESCRIBIR MEJOR ESTE TRABAJO.
+For example,  \cite{Durillo08masterslave} compared different master-slave approaches TODO DESCRIBIR MEJOR ESTE TRABAJO.
 The method proposed by Hiroyasu \citep{Hiroyasu07discussion} generates offspring depending on the computation power.
@@
 
-The work by Deb in 2003 was one of the first approaches for distributed MOEAs (dMOEAs).
+The work by \cite{Deb03distributed} was one of the first approaches for distributed MOEAs (dMOEAs).
 In that work, the dominance of solutions was divided in the islands using a transformation of coordinates.
@@
 More similar approaches to the one presented here were studied in the
-next two works, also using cooperative coevolution for high-dimensional problems. Dorronsoro et al. in
-\citep{Dorronsoro13superlinear} obtained super-linear performance
+next two works, also using cooperative coevolution for high-dimensional problems. 
+\cite{Dorronsoro13superlinear} obtained super-linear performance
 in several instances using cooperative coevolution, focusing each island on a portion of the chromosome. However, in some instances the parallel version 
-improved the sequential version.  Kimovski et al. \citep{Kimovski15Parallel} proposed a
+improved the sequential version.  \cite{Kimovski15Parallel} proposed a
 master-slave method that splits the population into several processors,
@@
 \begin{itemize}
-\item Hypervolume (HV): measures the area formed by all non-dominated solutions found with, respect to a reference point. Higher values imply better quality of the PF.
+\item Hypervolume (HV): measures the area formed by all non-dominated solutions found with, respect to a reference point.
+Higher values imply better quality of the PF.
+Figure \ref{fig:hypervolume} clarifies how the hypervolume is calculated.
 \item Inverted Generational distance (IGD): calculates the distance of the obtained set of solutions to the optimal PF.
@@
 \end{itemize}
+
+\begin{figure}
+\centering
+\includegraphics[width=6cm]{hypervolume.pdf}
+\caption{Hypervolume calculation. Areas from Pareto Front solutions (black points) to a reference point (white point) are added.}
+\label{fig:hypervolume}
+\end{figure}
 
@@
 
-\subsubsection{Coevolution with disjoint islands} 
+\subsubsection{Coevolution with disjoint islands (D)} 
 In this approach, each individual of size $L$ is split into $P$ chunks of size $L/P$.
@@
 \begin{figure*}
+\centering
 \includegraphics[width=12cm]{islandDisjoint.jpg}
@@
 
-\subsubsection{Coevolution with overlapping islands}
+\subsubsection{Coevolution with overlapping islands (O)}
 This approach is similar to the previous one, but every island also uses the $p+1$ and $p-1$ (module size) chunks of the individual for crossover and migration.
@@
 \begin{figure*}
+\centering
 \includegraphics[width=12cm]{islandNoDisjoint.jpg}
@@
 
-\subsubsection{Adaptive coevolution with overlapping islands} 
-As in the previous method, the sections to address are overlapped, but instead using one extra section on each side of the $p$ section ($p+1$ and $p-1$), it uses $c$ fragments on each side ($p+c$ y $p-c$), being $c$ a value depending on the number of islands.
-The results shown in \citep{Garcia16evostar} have been used as a base to calculate $c$.
+\subsubsection{Adaptive coevolution with overlapping islands (A)} 
+As in the previous method, the sections to address are overlapped, but instead using one extra section on each side of the $p$ section ($p+1$ and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$), being $c$ a value depending on the number of islands.
+As a first approach to automatically calculate this value the results shown in \citep{Garcia16hpmoon} have been used as a base to obtain $c$.
 In that work, the overlapped method ($c=1$) obtained better results when the number of islands were >8.
 Therefore, we have used the formula $c=round(0.2*P-1)/2$ to calculate the extra sections to overlap.
-%TODO TERMINA Y PONER MAS EJEMPLOS Y DECIR QUE ESTA ES UNA PRIMERA APROXIMACION
+Therefore, when $P=8$ then $c=0$ (equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so on.
+Figure \ref{fig:adaptive}
 
+\begin{figure*}
+\centering
+\includegraphics[width=12cm]{islandNoDisjoint.jpg}
+\caption{NOTA: ESTA FIGURA TIENE QUE ACTUALIZARSE CON LA ADAPTATIVA!!!!! Adaptive overlapping algorithm: every island $p$ modifies the  $p+c$,
+  $p_{th}$ and $p-c$  components (in grey) of the individuals. $c$ is calculated depending on the number of islands.}
+  \label{fig:adaptive}
+\end{figure*}
 % --------------------------------------------------------------
@@
 The four approaches have been run with two different chromosome lengths ($L$): 512 and 2048.
-Different number of islands ($P$) have also been compared: 8, 32 and 128.
+Different number of islands ($P$) have also been compared: 8, 16, 32, 64 and 128.
 This maximum number of islands have also been  used in previous work in the literature \citep{Martens13asynchronous}.
@@
 {\em Parameter Name} & {\em Value} \\ \hline
-Number of islands ($P$) & 8, 32 and 128 \\ \hline
+Number of islands ($P$) & 8, 16, 32, 64 and 128 \\ \hline
 Chromosome size ($L$) & 512 and 2048 \\ \hline
@@
 Island Model, in a CentOS 5.4 machine with Intel(R) Xeon(R) CPU E5520
-@2.27GHz, 16 GB RAM, with Java Version 1.6.0\_16. As in this paper we
-only focus on the behaviour of our model in a single machine scenario
-(the islands share the same memory and processor), the migration time
-will not be as important factor as in a real distributed system. This
-task will be addressed in future works. %Pablo: no sé si decir esto
-                                %aquí% 
-%
-%
+@2.27GHz, 16 GB RAM, with Java Version 1.6.0\_16.
 
@@
 Finally, as happened in \citep{Garcia16hpmoon}, results show that all the quality indicators lowers when the number of islands is increased, as the subpopulations are smaller.
-This is consistent with the claim by Durillo in \citep{Dorronsoro13superlinear}, who found that cooperative coevolutionary MOEAs work better on bigger populations (more than 100 individuals).
+This is consistent with the claim by \cite{Dorronsoro13superlinear}, who found that cooperative coevolutionary MOEAs work better on bigger populations (more than 100 individuals).
 
@@
 
-%High-performance problems that require a large number of decision
-%variables can leverage the division of the decision space that parallel
-%and distributed algorithms imply. This can be done in dMOEAs by dividing the
-%chromosome into different parts, each one modified by a different
-%island. This paper compares a baseline distributed NSGA-II with two
-%different strategies to separate the chromosome (disjoint or overlapping
-%parts), using a high number of islands. Results show that these 
-%methods can achieve better quality metrics
-%than the baseline in the same amount of time. This can be explained 
-%because of the time reduction in crossover and mutation in the chromosomes,
-%producing a higher number of generations and more modifications of the 
-%solutions of the PF in each sub-population, and therefore improving
-%quality of the global PF.%
+High-performance problems that require a large number of decision variables can leverage the division of the decision space that parallel and distributed algorithms imply.
+This can be done in dMOEAs by dividing the chromosome into different parts, each one modified by a different island.
+This paper compares a baseline distributed NSGA-II with three different strategies to separate the chromosome (disjoint or overlapping parts), using a high number of islands.
+Results show that these methods can achieve better quality metrics than the baseline in the same amount of time, with larger chromosome lengths.
 
-%Results also show that when increasing the number of islands, the overlapping 
-%method significantly improves the results with respect to the disjoint method.
-%Therefore, the relation between the number of islands used, the global population size,
-%and the length of the chromosome may be a key factor to decide if using the 
-%overlapping method or the disjoint one. Studying this factor with more types 
-%of problems, and new configurations of population size and chromosome lengths will be addressed in the future.%
+Results also show that when increasing the number of islands, the adaptive overlapping method significantly improves the results with respect to the disjoint and overlapped methods.
+However, this is only apparent with larger chromosome sizes.
+Therefore, the length of the chromosome is also a key factor to take into account in adaptive methods, and not only the number of islands.
+Studying this factor with more types of problems, and new configurations of population size and chromosome lengths will be addressed in the future.%
 %
 
-%Also, distributed implementations in several systems (such as a GRID or cluster) with more different
-%quantities of islands/processors, will be used to perform a scalability study of the different
-%methods, being the transmission time between islands a relevant issue to
-%address. New benchmarks and real problems will also be  used to validate
-%our approach.
+Also, more distributed implementations in several systems (such as a GPUs or heterogeneous clusters) with more different quantities of islands/processors, will be used to perform a scalability study of the different methods, being the transmission time between islands a relevant issue to address.
+New benchmarks and real problems will also be  used to validate this approach.
 
@@
 
-TIN2014-56494-C4-3-P y TIN2015-67020-P (Ministerio de Economía y Competitividad), PROY-PP2015-06 (Plan Propio 2015 UGR),  y MSTR (PRY142/14, Fundación Pública Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigación).
+TIN2014-56494-C4-3-P y TIN2015-67020-P (Ministerio de Economía y Competitividad), PROY-PP2015-06 (Plan Propio 2015 UGR),  y MSTR (PRY142/14, Fundaci\'on P\'ublica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci\'on).
 

### 2016-06-10 hpmoon-hpca.tex
More changes

@@
 
-\usepackage{moreverb,url}
+\usepackage{moreverb,url,color}
 
@@
 Different authors have proposed methods to divide the decision space (the chromosome) to improve the performance and solution quality.
-In this aspect, the co-evolution model is a dimension-distributed model where a high-dimensional problem is divided into lower dimensional problems \citep{Gong15models}, and evolved separately.
+In this aspect, the co-evolution model is a dimension-distributed model where a high-dimensional problem is divided into lower dimensional problems \citep{Gong15models,Tonda12cooperative}, and evolved separately.
 One example of application of this technique was described in \citep{Kimovski15Parallel}.
@@
 The rest of the paper is organized as follows: after a background in parallelization in MOEAs, 
-the compared algorithms and the used methodology (Section \ref{sec:met}) are presented. 
-Then, the results of the experiments are shown (Section \ref{sec:res}), followed by conclusions and suggestions for future work lines.
+the compared algorithms and the used methodology (Section 3) are presented. %PABLO: no puedo usar \ref{sec:met} porque la plantilla de esta revista no lo coge :/
+Then, the results of the experiments are shown (Section 4), followed by conclusions and suggestions for future work lines.
 
@@
 
-These metrics have been used extensively, especially in some of the papers presented previously in Section \ref{sec:soa}.
+These metrics have been used extensively, especially in some of the papers presented previously in Section 2.
 
@@
 At the end of the run, all PFs of all islands are aggregated in a new one to compute the quality measures.
-This method as been chosen as it do not require synchronization of the global PF every certain number of generations, as other methods described in Section \ref{sec:soa}, and because it can TERMINAAAAAA
+This method as been chosen as it do not require synchronization of the global PF every certain number of generations, as other methods described in Section 2, and because it can {\color{red} QUE MAS SE PUEDE PONER AQUI PARA JUSTIFICARLO?}
 %% some justification on why this was chosen - JJ PABLO: Added 
@@
 \includegraphics[width=12cm]{islandNoDisjoint.jpg}
-\caption{NOTA: ESTA FIGURA TIENE QUE ACTUALIZARSE CON LA ADAPTATIVA!!!!! Adaptive overlapping algorithm: every island $p$ modifies the  $p+c$,
+\caption{{\color{red} NOTA: ESTA FIGURA TIENE QUE ACTUALIZARSE CON LA ADAPTATIVA!!!!!} Adaptive overlapping algorithm: every island $p$ modifies the  $p+c$,
   $p_{th}$ and $p-c$  components (in grey) of the individuals. $c$ is calculated depending on the number of islands.}

### 2016-06-14 hpmoon-hpca.tex
Added Julio's comments and other stuff

@@
 Multi-objective optimization methods have gained interest in the last years because the performance they can achieve solving real-world problems.
-These kind of problems usually require a high-dimensional decision space, and multi-objective Evolutionary Algorithms have been successfully used in the past.
+Many of these problems usually require a high-dimensional decision space, and multi-objective Evolutionary Algorithms have been successfully used in the past.
 Due to the large computational cost these algorithms require, different parallelization and distribution methods have been proposed, with different parallel and distributed computer architectures to cope with them.
@@
 Different number of islands, chromosome sizes and problems have been used. The analysis of the obtained experimental results, by using different 
-metrics, shows that coevolutionary approaches can provide statistically significant improvements with respect to the base algorithm, being the method to automatically adapt the overlapping size the one to obtain better performance during the same execution time.
+metrics, shows that coevolutionary approaches can provide statistically significant improvements with respect to the base algorithm, being the method to automatically adapt the overlapping size the one to obtain the best performance during the same execution time.
 Results also show that the relation of the number of
@@
 
-The application of MOEAs to solve real-world problems have gained attention in the last years \citep{Luna15Survey,Mukhopadhyay14Survey}.
+The application of MOEAs to solve real-world problems have gained attention in the last years \citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress}.
 These kind of problems require a high number of variables, meaning that the EAs need to deal with large individuals and spent significant extra time for crossover, mutation and migration.
@@
 
+Evolutionary algorithms (EAs) \citep{DBLP:series/ncs/EibenS15,DeJong2006} are bio-inspired meta-heuristics that can be effectively used to find nearly optimal solutions for optimization problems.
+Usually an EA starts by generating a set of random solutions, called \emph{population}, following a user-defined description.
+Then, it evaluates each candidate solution, called \emph{individual}, assigning it a \emph{fitness} value, that describes how good the individual is, with regards to the target problem.
+New solutions are then generated by the application of \emph{operators} that either mutate a single existing solutions or recombine different existing solutions.
+After each iteration, called \emph{generation}, the least fit individuals are removed, and the process continues until a user-defined stop condition is met.
+
+Multi-objective optimization problems (MOP) are those where several objectives have to be simultaneously optimized \cite{Mora13paretobased}.
+Solving a MOP implies maximize or minimize a function composed by several cost functions (one per objective).
+In these problems the aim is to obtain a set of solutions that are better than the rest considering all the objectives; this set is known as the Pareto Front.
+The solutions in this set are {\em non-dominated}, that is, none is better than the others for all the objectives.
+MOEAs are sub-set of EAs used to solve MOPs.
+One of the most well-known and referenced MOEAs \cite{Dorronsoro13superlinear} is the {\em Non-dominated Sorting Genetic Algorithm} (NSGA-II) \cite{Deb00NSGAII}.
+Classical genetic operators are applied to all the individuals, and divided in different ranks (based on the dominance) to be selected for next generations.
+
 Since the early 2000s, the distributed and parallel Evolutionary Algorithms have been used, mostly to take the most from systems such as clusters or grids \citep{Talbi08Parallel}.
@@
 To solve this issue, some authors have proposed the usage of Master-Slave approaches.
-For example,  \cite{Durillo08masterslave} compared different master-slave approaches TODO DESCRIBIR MEJOR ESTE TRABAJO.
-The method proposed by Hiroyasu \citep{Hiroyasu07discussion} generates offspring depending on the computation power.
-TODO Y ESTE
+For example,  \cite{Durillo08masterslave} compared different master-slave approaches {\color{red} TODO DESCRIBIR MEJOR ESTE TRABAJO}.
+The method proposed by Hiroyasu \citep{Hiroyasu07discussion} generates offspring depending on the computation power {\color{red} TODO Y ESTE}.
 
@@
 As a first approach to automatically calculate this value the results shown in \citep{Garcia16hpmoon} have been used as a base to obtain $c$.
-In that work, the overlapped method ($c=1$) obtained better results when the number of islands were >8.
-Therefore, we have used the formula $c=round(0.2*P-1)/2$ to calculate the extra sections to overlap.
+In that work, the overlapped method ($c=1$) obtained better results when the number of islands were $>$8.
+So, we have used the formula $c=round(0.2*P-1)/2$ to calculate the extra sections to overlap.
 Therefore, when $P=8$ then $c=0$ (equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so on.
-Figure \ref{fig:adaptive}
+Figure \ref{fig:adaptive} explains this method.
 
@@
 This maximum number of islands have also been  used in previous work in the literature \citep{Martens13asynchronous}.
-The crossover and mutation chosen, SBX and polynomial, have been used previously by other authors in \citep{Durillo08masterslave}.
+The crossover and mutation chosen, SBX and polynomial, have been also used previously by other authors in \citep{Durillo08masterslave}.
 
@@
 Different metrics, explained in the previous section, have been used to calculate the quality of the obtained PFs in each configuration.
-As some of the metrics require a reference point to be calculated (such as HV), the point (1,9) has been chosen as reference, as none of the generated PFs in all runs are dominated by it.
+As some of the metrics  (such as HV) require a reference point to be calculated, the point (1,9) has been chosen as reference, as none of the generated PFs in all runs are dominated by it.
 Metrics are then normalized with respect to that point.
@@
 }
-\caption{Quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 512 dimensions.
+\caption{Average quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 512 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 }
-\caption{Quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 2048 dimensions.
+\caption{Average quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 2048 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 
-Finally, as happened in \citep{Garcia16hpmoon}, results show that all the quality indicators lowers when the number of islands is increased, as the subpopulations are smaller.
+Finally, as happened in \citep{Garcia16hpmoon}, results show that all the quality indicators decrease when the number of islands is increased, as the the sizes of the subpopulations are smaller.
 This is consistent with the claim by \cite{Dorronsoro13superlinear}, who found that cooperative coevolutionary MOEAs work better on bigger populations (more than 100 individuals).

### 2016-06-14 hpmoon-hpca.tex
Minor changes

@@
 
-Different approaches have been used to parallelize Evolutionary Algorithms (EAs), as each individual can be considered as an independient unit \citep{Alba13parallel}.
+Different approaches have been used to parallelize Evolutionary Algorithms (EAs), as each individual can be considered as an independent unit \citep{Alba13parallel}.
 Classic methods, such as the global parallel EAs (Master-Slave), or the spatially structured algorithms (Island model or Cellular EAs) have been applied successfully in the past \citep{Folino03cellular,Alba02Parallelism}.
 In the case of Multi-Objective Evolutionary Algorithms (MOEAs), these approaches \citep{Luna15Survey} need to deal with a whole solution set called Pareto Front (PFs).
-This imply to use different distribution and sharing mechanisms, as there exist a tension between the speedup achievable from parallelization and the need to globally recombine results to accurately identify the PF \citep{Branke04Parallelizingcone}.
+This imply to use different distribution and sharing mechanisms, as there exist a tension between the speedup achievable from parallelization and the need to globally recombine the results to accurately identify the PF \citep{Branke04Parallelizingcone}.
 
 The application of MOEAs to solve real-world problems have gained attention in the last years \citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress}.
-These kind of problems require a high number of variables, meaning that the EAs need to deal with large individuals and spent significant extra time for crossover, mutation and migration.
+These kind of problems requires a high number of variables, meaning that the EAs need to deal with large individuals and spent significant extra time for crossover, mutation and migration.
 Different authors have proposed methods to divide the decision space (the chromosome) to improve the performance and solution quality.
@@
 Then, it evaluates each candidate solution, called \emph{individual}, assigning it a \emph{fitness} value, that describes how good the individual is, with regards to the target problem.
-New solutions are then generated by the application of \emph{operators} that either mutate a single existing solutions or recombine different existing solutions.
+New solutions are then generated by the application of \emph{operators} that either mutate a single solution or recombine different existing solutions.
 After each iteration, called \emph{generation}, the least fit individuals are removed, and the process continues until a user-defined stop condition is met.
@@
 Multi-objective optimization problems (MOP) are those where several objectives have to be simultaneously optimized \cite{Mora13paretobased}.
-Solving a MOP implies maximize or minimize a function composed by several cost functions (one per objective).
-In these problems the aim is to obtain a set of solutions that are better than the rest considering all the objectives; this set is known as the Pareto Front.
+Solving a MOP implies maximize or minimize a function composed of several cost functions (one per objective).
+In these problems the aim is to obtain a set of solutions that are better than the rest, considering all the objectives; this set is known as the Pareto Front.
 The solutions in this set are {\em non-dominated}, that is, none is better than the others for all the objectives.
@@
 One of the most well-known and referenced MOEAs \cite{Dorronsoro13superlinear} is the {\em Non-dominated Sorting Genetic Algorithm} (NSGA-II) \cite{Deb00NSGAII}.
-Classical genetic operators are applied to all the individuals, and divided in different ranks (based on the dominance) to be selected for next generations.
+Classical genetic operators are applied to all the individuals, and divided into different ranks (based on the dominance) to be selected for the next generations.
 
@@
 But in the case of MOEAs, the distribution and parallelization is not as direct as in single-objective EAs.
-This is because in different steps of the algorithm a whole set of dependent solutions, the Pareto Front, should be managed as a whole, spending time in gather all individuals from the different process or islands.
+This is because in different steps of the algorithm a whole set of dependent solutions, the Pareto Front, should be managed as a whole, spending time in gathering all individuals from the different processors or islands.
 
@@
 For example,  \cite{Durillo08masterslave} compared different master-slave approaches {\color{red} TODO DESCRIBIR MEJOR ESTE TRABAJO}.
-The method proposed by Hiroyasu \citep{Hiroyasu07discussion} generates offspring depending on the computation power {\color{red} TODO Y ESTE}.
+The method proposed by Hiroyasu \citep{Hiroyasu07discussion} generates offspring depending on the computational power {\color{red} TODO Y ESTE}.
 
 The work by \cite{Deb03distributed} was one of the first approaches for distributed MOEAs (dMOEAs).
-In that work, the dominance of solutions was divided in the islands using a transformation of coordinates.
+In that work, the dominance of solutions was divided into the islands using a transformation of coordinates.
 Their authors concluded that dividing the search space is a good idea, but achieve this is not trivial.
@@
 Every island $p$ only performed the mutation and crossover in that part ($p_{th}$) of the chromosome, while the fitness was calculated using the whole individual.
-After certain number of generations, individuals were migrated randomly to other islands.
+After a certain number of generations, individuals were migrated randomly to other islands.
 The performance metrics were calculated at the end of the run.
@@
 This motivates us to find a new adaptive method to select this number of sections of the chromosome to use, depending on the number of islands.
-Moreover, previous experiments were performed in a single processor synchronous island model with a limited number of islands (8, 32 and 128).
+Moreover, previous experiments were performed on a single processor synchronous island model with a limited number of islands (8, 32 and 128).
 In this paper, we have used 8, 16, 32, 64 and 128 islands, and this time, using a real cluster.
@@
 \centering
-\includegraphics[width=12cm]{islandNoDisjoint.jpg}
-\caption{{\color{red} NOTA: ESTA FIGURA TIENE QUE ACTUALIZARSE CON LA ADAPTATIVA!!!!!} Adaptive overlapping algorithm: every island $p$ modifies the  $p+c$,
-  $p_{th}$ and $p-c$  components (in grey) of the individuals. $c$ is calculated depending on the number of islands.}
+\includegraphics[width=12cm]{islandAdaptive.jpg}
+\caption{Adaptive overlapping algorithm: every island $p$ modifies the  $p+c$,
+  $p_{th}$ and $p-c$  components (in grey) of the individuals. $c$ is calculated depending on the number of islands. In this case, $c=2$.}
   \label{fig:adaptive}
@@
 The average results for each configuration are shown in Table \ref{tab:results512} (for 512 dimensions) and \ref{tab:results2048} (for 2048).
+As previously explained, when $P=8$ the results of A are equivalent to the obtained with D (because $c=0$), and when $P=16$ they are equivalent to O ($c=1$).
 
@@
 Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than the obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply these methods.
-This contradicts the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained best results than the baseline in both dimension lengths.
+This contradicts the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths.
 This can be explained because the added migration latency between nodes requires more time than the time saved during the crossover and migration.
@@
 However, with $L=2048$ the migration time is enough big to almost not improve the number of generations with respect to the baseline, even in the lower number of islands, as it happens with $L=512$.
-Therefore, more generations do not necessarily improve the solution of the global PF, but focusing in different elements of the chromosome.
+Therefore, more generations do not necessarily improve the solution of the global PF, but focusing on different elements of the chromosome.
 As indicated previously, every island is unaware of the other islands PFs, and they are trying to optimize their solutions independently.
-With respect to the average number of solution in each island, there is a clear difference in number with the baseline with $L=512$, where this value is in the most of the cases, less than a half.
+With respect to the average number of solutions in each island, there is a clear difference in number with the baseline with $L=512$, where this value is in the most of the cases, less than a half.
 The number of non-dominated solutions also improves a better Spread indicator, where the baseline almost always obtains better values %TENGO QUE COMENTAR MAS LOS RESULTADOS Y ENTENDERLO TODO Y JUSTIFICARLO FINAMENTE
 
-Finally, as happened in \citep{Garcia16hpmoon}, results show that all the quality indicators decrease when the number of islands is increased, as the the sizes of the subpopulations are smaller.
+Finally, as happened in \citep{Garcia16hpmoon}, results show that all the quality indicators decrease when the number of islands is increased, as the  sizes of the subpopulations are smaller.
 This is consistent with the claim by \cite{Dorronsoro13superlinear}, who found that cooperative coevolutionary MOEAs work better on bigger populations (more than 100 individuals).

### 2016-06-14 hpmoon-hpca.tex
Changed bibliography style to Vancouver

@@
 
-\documentclass[Afour,sageh,times]{sagej}
+\documentclass[Afour,sagev,times]{sagej}
 
 \usepackage{moreverb,url,color}
-
 \usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
@@
 
-Multi-objective optimization problems (MOP) are those where several objectives have to be simultaneously optimized \cite{Mora13paretobased}.
+Multi-objective optimization problems (MOP) are those where several objectives have to be simultaneously optimized \citep{Mora13paretobased}.
 Solving a MOP implies maximize or minimize a function composed of several cost functions (one per objective).
@@
 MOEAs are sub-set of EAs used to solve MOPs.
-One of the most well-known and referenced MOEAs \cite{Dorronsoro13superlinear} is the {\em Non-dominated Sorting Genetic Algorithm} (NSGA-II) \cite{Deb00NSGAII}.
+One of the most well-known and referenced MOEAs \citep{Dorronsoro13superlinear} is the {\em Non-dominated Sorting Genetic Algorithm} (NSGA-II) \citep{Deb00NSGAII}.
 Classical genetic operators are applied to all the individuals, and divided into different ranks (based on the dominance) to be selected for the next generations.
@@
 To solve this issue, some authors have proposed the usage of Master-Slave approaches.
-For example,  \cite{Durillo08masterslave} compared different master-slave approaches {\color{red} TODO DESCRIBIR MEJOR ESTE TRABAJO}.
+For example,  \citep{Durillo08masterslave} compared different master-slave approaches {\color{red} TODO DESCRIBIR MEJOR ESTE TRABAJO}.
 The method proposed by Hiroyasu \citep{Hiroyasu07discussion} generates offspring depending on the computational power {\color{red} TODO Y ESTE}.
 
-The work by \cite{Deb03distributed} was one of the first approaches for distributed MOEAs (dMOEAs).
+The work by Deb et al.
+\citep{Deb03distributed} was one of the first approaches for distributed MOEAs (dMOEAs).
 In that work, the dominance of solutions was divided into the islands using a transformation of coordinates.
@@
 next two works, also using cooperative coevolution for high-dimensional problems. 
-\cite{Dorronsoro13superlinear} obtained super-linear performance
+Dorronsoro et al. \citep{Dorronsoro13superlinear} obtained super-linear performance
 in several instances using cooperative coevolution, focusing each island on a portion of the chromosome. However, in some instances the parallel version 
-improved the sequential version.  \cite{Kimovski15Parallel} proposed a
+improved the sequential version. Kimovski et al. \citep{Kimovski15Parallel} proposed a
 master-slave method that splits the population into several processors,
@@
 In the new island, this individual will be considered as one of the others in the island, crossed and mutated in the same way, depending of the island identifier.
-Note that, on the contrary of other works such as the ones described by \cite{Talbi08Parallel} all the islands deal with complete chromosomes for fitness calculation, so our approach can deal with no decomposable problems.
+Note that, on the contrary of other works such as the ones described by Talbi et al.
+\citep{Talbi08Parallel} all the islands deal with complete chromosomes for fitness calculation, so our approach can deal with no decomposable problems.
 
@@
 Finally, as happened in \citep{Garcia16hpmoon}, results show that all the quality indicators decrease when the number of islands is increased, as the  sizes of the subpopulations are smaller.
-This is consistent with the claim by \cite{Dorronsoro13superlinear}, who found that cooperative coevolutionary MOEAs work better on bigger populations (more than 100 individuals).
+This is consistent with the claim by Dorronsoro et al.
+\citep{Dorronsoro13superlinear}, who found that cooperative coevolutionary MOEAs work better on bigger populations (more than 100 individuals).
 
@@
 
-\bibliographystyle{SageH}
+\bibliographystyle{SageV}
 

### 2016-06-15 hpmoon-hpca.tex
Modifications for blind review and format

@@
 
-\documentclass[Afour,sagev,times]{sagej}
+%\documentclass[Afour,sagev,times]{sagej}
+\documentclass[Crown,sagev,times,doublespace]{sagej}
 
@@
 
-\runninghead{Garc\'ia-S\'anchez et al.}
-
+%\runninghead{Garc\'ia-S\'anchez et al.}
+\runninghead{anonymous}
 \title{Parallel Multi-objective optimization using co-evolutionary islands and search space overlapping}
 
-\author{Pablo Garc\'ia-S\'anchez, Julio Ortega, Jes\'us Gonz\'alez, \\Pedro Angel Castillo and Juan Juli\'an Merelo\affilnum{1}}
+%\author{Pablo Garc\'ia-S\'anchez, Julio Ortega, Jes\'us Gonz\'alez, \\Pedro Angel Castillo and Juan Juli\'an Merelo\affilnum{1}}
+\author{ANONYMOUS FOR BLIND REVIEW \affilnum{1}}
+\affiliation{\affilnum{1} ANONYMOUS FOR BLIND REVIEW}
+%\affiliation{\affilnum{1}Dept. of Computer Architecture and Computer Technology, University of Granada, Spain}
 
-\affiliation{\affilnum{1}Dept. of Computer Architecture and Computer Technology, University of Granada, Spain}
+%\corrauth{Pablo Garc\'ia-S\'anchez,
+%ETS. Ingenier\'ias en Inform\'atica y Telecomunicaci\'on and CITIC-UGR,
+%C/Periodista Daniel Saucedo s/n,
+%Universidad de Granada,
+%18071, Granada, Spain.}
 
-\corrauth{Pablo Garc\'ia-S\'anchez,
-ETS. Ingenierías en Inform\'atica y Telecomunicaci\'on and CITIC-UGR,
-C/Periodista Daniel Saucedo s/n,
-Universidad de Granada,
-18071, Granada, Spain.}
+\corrauth{ANONYMOUS FOR BLIND REVIEW.}
 
-\email{pablogarcia@ugr.es}
+%\email{pablogarcia@ugr.es}
+\email{anonymous}
 
@@
 
-\keywords{Multi-objective algorithms, NSGA-II, Island model, distributed evolutionary algorithms}
+\keywords{Multi-objective algorithms, NSGA-II, Island model, distributed evolutionary algorithms, coevolution}
 
@@
 To solve this issue, some authors have proposed the usage of Master-Slave approaches.
-For example,  \citep{Durillo08masterslave} compared different master-slave approaches {\color{red} TODO DESCRIBIR MEJOR ESTE TRABAJO}.
-The method proposed by Hiroyasu \citep{Hiroyasu07discussion} generates offspring depending on the computational power {\color{red} TODO Y ESTE}.
+For example,  \citep{Durillo08masterslave} compared different master-slave approaches: synchronous generational, asynchronous generational and asynchronous steady-state, being the latter the most promising option.
+The method proposed by Hiroyasu \citep{Hiroyasu07discussion} generates offspring depending on the computational power.
 
@@
 \centering
-\resizebox{16cm}{!}{
+\resizebox{13cm}{!}{
 \begin{tabular}{|c||c|c|c|c||c|c|c|c||c|c|c|c||}

### 2016-06-15 hpmoon-hpca.tex
Added @pacastillo and Julio comments

@@
 
-\def\volumeyear{2015}
+\def\volumeyear{2016}
 
@@
 \affiliation{\affilnum{1} ANONYMOUS FOR BLIND REVIEW}
-%\affiliation{\affilnum{1}Dept. of Computer Architecture and Computer Technology, University of Granada, Spain}
+\affiliation{\affilnum{1}Dept. of Computer Architecture and Computer Technology, University of Granada, Spain}
 
@@
 
-\corrauth{ANONYMOUS FOR BLIND REVIEW.}
+%\corrauth{ANONYMOUS FOR BLIND REVIEW.}
 
@@
 
-In our preliminary work in \citep{Garcia16hpmoon} we tried to demonstrate that using overlapped sections of the chromosome in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time when the number of islands increases.
+In our preliminary work in \citep{Garcia16hpmoonANONYMOUS} we tried to demonstrate that using overlapped sections of the chromosome in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time when the number of islands increases.
 We discovered that the most adequate overlapping size may vary depending on a relation between the number of islands and the individual size.
@@
 The rest of the paper is organized as follows: after a background in parallelization in MOEAs, 
-the compared algorithms and the used methodology (Section 3) are presented. %PABLO: no puedo usar \ref{sec:met} porque la plantilla de esta revista no lo coge :/
-Then, the results of the experiments are shown (Section 4), followed by conclusions and suggestions for future work lines.
+the compared algorithms and the used methodology are presented. %PABLO: no puedo usar \ref{sec:met} porque la plantilla de esta revista no lo coge :/ (y además no tienen número)
+Then, the results of the experiments are shown, followed by conclusions and suggestions for future work lines.
 
@@
 
-In our previous work \citep{Garcia16hpmoon} we used some of the previous ideas to compare two co-evolutionary dMOEAs.
+In our previous work \citep{Garcia16hpmoonANONYMOUS} we used some of the previous ideas to compare two co-evolutionary dMOEAs.
 The first one divided the chromosome in $P$ sections, being $P$ the number of islands.
@@
 Moreover, previous experiments were performed on a single processor synchronous island model with a limited number of islands (8, 32 and 128).
-In this paper, we have used 8, 16, 32, 64 and 128 islands, and this time, using a real cluster.
+In this paper,  8, 16, 32, 64 and 128 islands have been used, and this time, the experiments have been run on a real cluster.
 Therefore, at the same time we are proposing an adaptive method to divide the individual search space, we are validating the previous methods.
@@
 %
-\section{Methodology and experimental setup}
-\label{sec:met}
 
-This section describes the quality indicators used and the methods compared. The chosen quality indicators, are:
+\section{Coevolutionary algorithms compared}
+\label{sec:coevo}
+
+In this paper we analyse several coevolutionary algorithms we have implemented by using a parallel multi-objective baseline algorithm (B) as a framework.
+Here, we have used the NSGA-II algorithm as the baseline algorithm.
+The population is distributed among $P$ islands.
+After a fixed number of generations, one individual in a given island is migrated to another random island, thus avoiding to synchronize the global Pareto Front (PF) every certain number of generations as other methods described in Section 2 do.
+At the end of the run, the Pareto Fronts of all islands are aggregated into a new one, and the quality measures are evaluated.
+Different coevolutionary alternatives can be devised to evolve the subpopulations according to the decision space to be explored by each islands.
+Here we will consider three methods in which each island only performs crossover and mutation in specific sections of the individuals.
+
+%This algorithm is a regular NSGA-II algorithm distributed along a number $P$ of islands.
+After a fixed number of generations, one individual is migrated to another random island.
+At the end of the run, PFs of all islands are aggregated in a new one in order to compute the quality measures.
+This baseline method has been chosen as it does not require synchronization of the global PF every certain number of generations, as other methods described in Section 2 do.
+%% some justification on why this was chosen - JJ PABLO: Added 
+%
+%% And some liaison to next subsection - JJ
+%This method will be compared to different coevolutionary approaches that are similar to the baseline, with the exception on the decision space to explore in each island.
+%Three different coevolutionary methods have been used. In all these methods, each island only performs crossover and mutation in specific sections of the individuals.
+
+As in the baseline, every certain number of generations, an individual is migrated to another random island.
+In the new island, this individual will be considered as one of the others in the island, crossed and mutated in the same way, depending on the island identifier.
+Note that, on the contrary of other works such as the ones described by Talbi et al.
+\citep{Talbi08Parallel} all the islands deal with complete chromosomes for fitness calculation, so our approach can deal with no decomposable problems.
+The proposed methods  are as follows:
+
+\subsection{Coevolution with disjoint islands (D)} 
+In this approach, each individual of size $L$ is split into $P$ chunks of size $L/P$.
+Every island $p$ only performs crossover and mutation on the $p_{th}$ part of the individuals.
+Figure \ref{fig:disjoint} describes this approach.
+
+\begin{figure*}
+\centering
+\includegraphics[width=12cm]{islandDisjoint.jpg}
+\caption{Disjoint algorithm: every island $p$ only modifies the $p_{th}$ components (in grey) of the individuals.}
+\label{fig:disjoint}
+\end{figure*}
+
+\subsection{Coevolution with overlapping islands (O)}
+This approach is similar to the previous one, but every island also uses the $p+1$ and $p-1$ (module size) chunks of the individual for crossover and migration.
+Therefore, some kind of overlapping of the crossed and mutated parts exists between islands.
+Figure \ref{fig:overlapping} shows the affected parts of the individuals in
+each island.
+
+\begin{figure*}
+\centering
+\includegraphics[width=12cm]{islandNoDisjoint.jpg}
+\caption{Overlapping algorithm: every island $p$ modifies the  $p+1$,
+  $p_{th}$ and $p-1$  components (in grey) of the individuals.}
+  \label{fig:overlapping}
+\end{figure*}
+
+\subsection{Adaptive coevolution with overlapping islands (A)} 
+As in the previous method, the sections to address are overlapped, but instead using one extra section on each side of the $p$ section ($p+1$ and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$), being $c$ a value depending on the number of islands.
+As a first approach to automatically calculate this value the results shown in \citep{Garcia16hpmoonANONYMOUS} have been used as a base to obtain $c$.
+In that work, the overlapped method ($c=1$) obtained better results when the number of islands were $>$8.
+So, we have used the formula $c=round(0.2*P-1)/2$ to calculate the extra sections to overlap.
+Therefore, when $P=8$ then $c=0$ (equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so on.
+Figure \ref{fig:adaptive} explains this method.
+
+\begin{figure*}
+\centering
+\includegraphics[width=12cm]{islandAdaptive.jpg}
+\caption{Adaptive overlapping algorithm: every island $p$ modifies the  $p+c$,
+  $p_{th}$ and $p-c$  components (in grey) of the individuals. $c$ is calculated depending on the number of islands. In this case, $c=2$.}
+  \label{fig:adaptive}
+\end{figure*}
+% --------------------------------------------------------------
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%  EXPERIMENTS AND RESULTS  %%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+\section{Experiments and Results}
+\label{sec:res}
+
+This section describes the quality indicators used and the experimental setup. The chosen quality indicators, are:
 
@@
 
-These metrics have been used extensively, especially in some of the papers presented previously in Section 2.
+These metrics have been used extensively, especially in some of the papers presented in Section 2.
 
-%% --------------------------------------------------------------
-
-\subsection{Baseline algorithm}
-
-This algorithm is a regular NSGA-II algorithm distributed along a number $P$ of islands.
-After a fixed number of generations, one individual is migrated to another random island.
-At the end of the run, all PFs of all islands are aggregated in a new one to compute the quality measures.
-This method as been chosen as it do not require synchronization of the global PF every certain number of generations, as other methods described in Section 2, and because it can {\color{red} QUE MAS SE PUEDE PONER AQUI PARA JUSTIFICARLO?}
-%% some justification on why this was chosen - JJ PABLO: Added 
-%
-%% And some liaison to next subsection - JJ
-This method will be compared to different coevolutionary approaches, that are similar to the baseline, with the exception on the decision space to explore in each island.
-\subsection{Coevolutionary algorithms compared}
-Three different coevolutionary methods have also been used. In all these methods, each island only performs crossover and mutation in specific sections of the individuals.
-
-As in the baseline, every certain number of generations, an individual is migrated to another random island.
-In the new island, this individual will be considered as one of the others in the island, crossed and mutated in the same way, depending of the island identifier.
-Note that, on the contrary of other works such as the ones described by Talbi et al.
-\citep{Talbi08Parallel} all the islands deal with complete chromosomes for fitness calculation, so our approach can deal with no decomposable problems.
-
-\subsubsection{Coevolution with disjoint islands (D)} 
-In this approach, each individual of size $L$ is split into $P$ chunks of size $L/P$.
-Every island $p$ only performs crossover and mutation on the $p_{th}$ part of the individuals.
-Figure \ref{fig:disjoint} describes this approach.
-
-\begin{figure*}
-\centering
-\includegraphics[width=12cm]{islandDisjoint.jpg}
-\caption{Disjoint algorithm: every island $p$ only modifies the $p_{th}$ components (in grey) of the individuals.}
-\label{fig:disjoint}
-\end{figure*}
-
-\subsubsection{Coevolution with overlapping islands (O)}
-This approach is similar to the previous one, but every island also uses the $p+1$ and $p-1$ (module size) chunks of the individual for crossover and migration.
-Therefore, some kind of overlapping of the crossed and mutated parts exists between islands.
-Figure \ref{fig:overlapping} shows the affected parts of the individuals in
-each island.
-
-\begin{figure*}
-\centering
-\includegraphics[width=12cm]{islandNoDisjoint.jpg}
-\caption{Overlapping algorithm: every island $p$ modifies the  $p+1$,
-  $p_{th}$ and $p-1$  components (in grey) of the individuals.}
-  \label{fig:overlapping}
-\end{figure*}
-
-\subsubsection{Adaptive coevolution with overlapping islands (A)} 
-As in the previous method, the sections to address are overlapped, but instead using one extra section on each side of the $p$ section ($p+1$ and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$), being $c$ a value depending on the number of islands.
-As a first approach to automatically calculate this value the results shown in \citep{Garcia16hpmoon} have been used as a base to obtain $c$.
-In that work, the overlapped method ($c=1$) obtained better results when the number of islands were $>$8.
-So, we have used the formula $c=round(0.2*P-1)/2$ to calculate the extra sections to overlap.
-Therefore, when $P=8$ then $c=0$ (equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so on.
-Figure \ref{fig:adaptive} explains this method.
-
-\begin{figure*}
-\centering
-\includegraphics[width=12cm]{islandAdaptive.jpg}
-\caption{Adaptive overlapping algorithm: every island $p$ modifies the  $p+c$,
-  $p_{th}$ and $p-c$  components (in grey) of the individuals. $c$ is calculated depending on the number of islands. In this case, $c=2$.}
-  \label{fig:adaptive}
-\end{figure*}
-% --------------------------------------------------------------
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%  EXPERIMENTS AND RESULTS  %%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-\section{Experiments and Results}
-\label{sec:res}
-
-The four approaches have been run with two different chromosome lengths ($L$): 512 and 2048.
+The previously described four approaches have been run with two different chromosome lengths ($L$): 512 and 2048.
 Different number of islands ($P$) have also been compared: 8, 16, 32, 64 and 128.
 This maximum number of islands have also been  used in previous work in the literature \citep{Martens13asynchronous}.
-The crossover and mutation chosen, SBX and polynomial, have been also used previously by other authors in \citep{Durillo08masterslave}.
+The crossover and mutation chosen, SBX and polynomial, have also been  used previously by other authors in \citep{Durillo08masterslave}.
 
@@
 
-The termination criterion used is the execution time: 25 seconds for dimension 512 and 100 (four times more) for 2048.
-We have used the time instead the number of evaluations firstly because our hypothesis argue that the time saved in crossover in mutation can be spent on improving the sub-populations and more operations and migrations can be achieved.
+Termination criterion used has been the running time: 25 seconds for dimension 512 and 100 (four times more) for 2048.
+We have used the time instead the number of evaluations firstly because our hypothesis argue that the time saved in crossover and mutation can be spent on improving the sub-populations and more operations and migrations can be achieved.
 Also, we are using different number of islands (with different sub-population sizes) that could lead to different execution times, so it would be difficult to compare different times and quality solutions at the same time.
@@
 LGPL V3 License
-\footnote{\url{https://https://github.com/hpmoon/hpmoon-islands}}. The
+%\footnote{\url{https://github.com/hpmoon/hpmoon-islands}}. 
+\footnote{\url{https://ANONYMOUS-REPOSITORY}}. 
+The
 island model has been executed synchronously, using the ECJ Internal
@@
 Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than the obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply these methods.
-This contradicts the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths.
+This contradicts the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoonANONYMOUS}, where the overlapping method obtained better results than the baseline in both dimension lengths.
 This can be explained because the added migration latency between nodes requires more time than the time saved during the crossover and migration.
@@
 %EXPLANATION OF THE RESULTS
-This can be explained comparing the number non-dominated solutions in each island and the average number of generations (Table \ref{tab:sols512} and Table \ref{tab:sols2048}).
+This can be explained comparing the number of non-dominated solutions in each island and the average number of generations (Table \ref{tab:sols512} and Table \ref{tab:sols2048}).
 With both chromosome lengths, increasing the number of islands implies more generations with all the methods (logically, as there are less individuals in each island).
@@
 
-Finally, as happened in \citep{Garcia16hpmoon}, results show that all the quality indicators decrease when the number of islands is increased, as the  sizes of the subpopulations are smaller.
+Finally, as happened in \citep{Garcia16hpmoonANONYMOUS}, results show that all the quality indicators decrease when the number of islands is increased, as the  sizes of the subpopulations are smaller.
 This is consistent with the claim by Dorronsoro et al.
@@
 \begin{acks}
-Acknowledgements
+ANONYMOUS
+%This work has been partially funded by projects TIN2014-56494-C4-3-P y TIN2015-67020-P (Spanish Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio 2015 UGR),  and  MSTR (PRY142/14, Fundaci\'on P\'ublica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci\'on).
 \end{acks}
-
-TIN2014-56494-C4-3-P y TIN2015-67020-P (Ministerio de Economía y Competitividad), PROY-PP2015-06 (Plan Propio 2015 UGR),  y MSTR (PRY142/14, Fundaci\'on P\'ublica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci\'on).
 

### 2016-06-15 hpmoon-hpca.tex
Other @pacastillo suggestion he send me via wassap :P

@@
 Due to the large computational cost these algorithms require, different parallelization and distribution methods have been proposed, with different parallel and distributed computer architectures to cope with them.
-One of the most extended methods are the distributed co-evolutionary evolutionary algorithms, where each processor only deals with a part of the decision space, that is, the individuals belonging to the same sub-population (island) explore the same subset of decision variables.
+One of the most extended methods are the distributed co-evolutionary algorithms, where each processor only deals with a part of the decision space, that is, the individuals belonging to the same sub-population (island) explore the same subset of decision variables.
 
-In this paper, a new method to automatically adapt the overlapping sections of the individuals have been compared to other collaborative evolutionary methods.
+In this paper, a new method to automatically adapt the overlapping sections of the individuals has been compared to other collaborative evolutionary methods.
 Different number of islands, chromosome sizes and problems have been used. The analysis of the obtained experimental results, by using different 
@@
 Also, more distributed implementations in several systems (such as a GPUs or heterogeneous clusters) with more different quantities of islands/processors, will be used to perform a scalability study of the different methods, being the transmission time between islands a relevant issue to address.
-New benchmarks and real problems will also be  used to validate this approach.
+Finally, new benchmarks and real problems will also be  used to validate this approach.
 

### 2016-06-15 hpmoon-hpca.tex
Version to send

@@
 \affiliation{\affilnum{1} ANONYMOUS FOR BLIND REVIEW}
-\affiliation{\affilnum{1}Dept. of Computer Architecture and Computer Technology, University of Granada, Spain}
+%\affiliation{\affilnum{1}Dept. of Computer Architecture and Computer Technology, University of Granada, Spain}
 
@@
 However, with 2048 dimensions, results show that dividing the chromosome produces an improvement in all the quality indicators using the adaptive version (Table \ref{tab:results2048}), even improving the overlapping and disjoint methods.
-Therefore, there exist some kind of limit point in chromosome length where one method will be preferable to another, depending the number of islands, population size and length.
+Therefore, there exist some kind of limit point in chromosome length where one method will be preferable to another, besides depending on the number of islands and population size.
 

### 2016-09-02 response-reviewers.tex
Added response to reviewers file

\documentclass{article}
\usepackage{graphicx}

\begin{document}

\title{Introduction to \LaTeX{}}
\author{Author's Name}

\maketitle

\section{Reviewer 1}

\textbf{Although simple, and possibly not revolutionary, the paper is very nice: well written, well organized, clear and technically sound (except for the fact that, as I report below, only one benchmark problem has been used as test case, which is not enough).}

We appreciate reviewer's comment. As it will be explained next, we have used a real problem to validate our approach.

\textbf{I suggest the following modifications to further improve its quality:}

\textbf{An intuition of the meaning of the term ``overlapping sections of individuals'' should be made clear(er) since the very beginning. For instance, in both the abstract and introduction this term is used but not defined, nor informally introduced. So, basically the true content of the paper becomes clear only with Figure 2 at page 7.}

\textbf{Some choices of this paper deserves a deeper explanation. For instance: why did you use exactly that formula (at the beginning of page 7) to calculate the c value (extra sections to overlap). Why did you use exactly those measures of performance (HV, IGD and Spread) and not others? For instance, I think it would be appropriate to also report the obtained results on the different optimization criteria.}

\textbf{The proposed method has been tested only on one benchmark (ZDT). Although the benchmark is well known in the community, I think this is not enough to demonstrate the generality of the approach. Other benchmarks of different nature, and possibly also real-life applications should be used as test cases.}

\textbf{The conclusions section seems inappropriate for a journal paper, and needs to be deepened.}

\section{Reviewer 2}

\textbf{Authors propose a new method to choose the best overlapping ratio. Particularly, this work extends a previous work done by the authors in the scope of island-based parallel multi-objective algorithms.}

\textbf{I think that, as is, the paper presents not too much novelty. If I am not wrong, the contribution is the equation used for setting the overlapping (and executing the algorithm in a cluster). In my opinion, there are many aspects and issues that should be addressed or fixed. For example:}

\textbf{ 1.- The experimental section compares different strategies: among them and against a baseline NSGA-II. However, there are many different multi-objective algorithms in the literature (for example SPEA, MOEA/D), and also different flavors of them. I think that, at least in the scope of island-based models, the authors should demonstrate that their algorithm (or even strategy) is competitive compared to the state-of-the-art algorithms. I know that performing this kind of analysis is difficult, but otherwise does it has sense to use this strategy if the whole algorithm is not competitive?.}

\textbf{ 2- This is a journal focused on high performance computing. I see no pseudo-codes of the algorithm, communication schemes between islands, and other detail that allow understanding the proposed algorithm. In addition, a performance analysis, speed-ups, communication-computation ratios, and so on would be welcome. Some of these aspects, for example the time required for migrating individuals is mentioned as a drawback of other approaches, but it is not discussed at all.}

\textbf{ 3.- Why a distributed NSGA-II is chosen as the baseline? Would not be fairer to use the sequential version? Related to this, how have running times been assigned? 25/100 seconds for each process (island) independently of the number of islands? If this is the way, this is not a fair comparison, as we are using more global cpu time (more machines) as the number of islands increases. May be I have not understand this correctly.}

\textbf{ I understand that an island-based model is designed for dealing with large problems, which cannot be executed in one computer. In the experimental section, ZDT functions are used, up to 2048 variables, and execution times up to 100 seconds. I would not say that this is a problem that requires HPC. I think that the advantages of this proposal should be tested on large artificial, or even better, real-world problems.}

\textbf{ In addition, I miss some discussion about the relation between islands and diversity. Is this the main advantage of the proposal? Which is the migration ratio, how does this affect diversity and, hence, results?}

\textbf{ Regarding the formula, which is supposed to be the main contribution, does it round or truncation (equation should be properly written)? How has it been calculated, has some regression model or similar technique been used? How does influence the size of the population (it is slower as the number of islands increases)? Why a fixed population is used throughout the experiments? Has it been set according to previous experiments?}

\textbf{ I do not understand the sentence ``This can be explained because added migration latency... ''. I understand that both the previous model and the new one use synchronous migration and, therefore, I would say that this migration is done at the same steps of the execution. It should be better explained.}

\textbf{ Authors claim that, for 2048, the best results for all the quality indicators are obtained by using overlapping. According to Table 3, the baseline approach shows clearly better Spread values, and it not that clear the A option to perform better.}

\textbf{In summary, I think that the authors need to demonstrate that their strategy is valuable and that it can be helpful to improve the behavior of the algorithm, being competitive with state-of-the-art approaches.  As we are in the scope of HPC,  a large problem or problems should be used. In addition, many aspects of the paper should be explained more clearly.}

\end{document}

### 2016-09-04 hpmoon-hpca.tex
Suggestions for improving the abstract
Mainly for @fergunet

@@
 \runninghead{anonymous}
-\title{Parallel Multi-objective optimization using co-evolutionary islands and search space overlapping}
+\title{Parallel Multi-objective optimization using co-evolutionary
+  islands and search space overlapping}
+% Why are you mixing caps and non-caps? - JJ
 
@@
 \begin{abstract}
-Multi-objective optimization methods have gained interest in the last years because the performance they can achieve solving real-world problems.
-Many of these problems usually require a high-dimensional decision space, and multi-objective Evolutionary Algorithms have been successfully used in the past.
-Due to the large computational cost these algorithms require, different parallelization and distribution methods have been proposed, with different parallel and distributed computer architectures to cope with them.
-One of the most extended methods are the distributed co-evolutionary algorithms, where each processor only deals with a part of the decision space, that is, the individuals belonging to the same sub-population (island) explore the same subset of decision variables.
+Multi-objective optimization methods have gained interest in the last
+years because the performance they can achieve solving real-world
+problems. 
+% You can safely supress the sentence above - JJ
+Many of these problems usually require a high-dimensional
+decision space, and multi-objective Evolutionary Algorithms have been
+% random capitalization strikes back - JJ
+successfully used in the past. 
+% Another useless sentence - JJ
+Due to the large computational cost
+these algorithms require, different parallelization and distribution
+methods have been proposed, with different parallel and distributed
+computer architectures to cope with them. One of the most extended
+methods are the distributed co-evolutionary algorithms, where each
+processor deals only with a part of the decision space, that is, the
+individuals belonging to the same sub-population (island) explore the
+same subset of decision variables.
+%After explaining the method, you should say why it might work - JJ
 
-In this paper, a new method to automatically adapt the overlapping sections of the individuals has been compared to other collaborative evolutionary methods.
-Different number of islands, chromosome sizes and problems have been used. The analysis of the obtained experimental results, by using different 
-metrics, shows that coevolutionary approaches can provide statistically significant improvements with respect to the base algorithm, being the method to automatically adapt the overlapping size the one to obtain the best performance during the same execution time.
-Results also show that the relation of the number of
-islands (subpopulations) to the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distribute the decision variables.
+In this paper, a new method to automatically adapt the overlapping
+sections of the individuals has been compared to other collaborative
+% what sections? Decision space sections? Besides, you are using
+% section here and before you were using "subset" - JJ
+evolutionary methods. 
+Different number of islands, chromosome sizes and problems have been
+used. The analysis of the obtained experimental results, by using
+different  
+metrics, shows that coevolutionary approaches can provide
+statistically significant improvements with respect to the base
+algorithm, being the method to automatically adapt the overlapping
+size the one to obtain the best performance during the same execution
+time. Results also show that the relation of the number of  
+islands (subpopulations) to the length of the chromosome (number of
+decision variables) is also a relevant factor to determine the most
+efficient alternative to distribute the decision variables.n 
 \end{abstract}

### 2016-09-04 hpmoon-hpca.tex
Corrected several grammar errors
Someone should take a thorough look at the whole paper @fergunet

@@
 
-In our previous work \citep{Garcia16hpmoonANONYMOUS} we used some of the previous ideas to compare two co-evolutionary dMOEAs.
-The first one divided the chromosome in $P$ sections, being $P$ the number of islands.
-Every island $p$ only performed the mutation and crossover in that part ($p_{th}$) of the chromosome, while the fitness was calculated using the whole individual.
-After a certain number of generations, individuals were migrated randomly to other islands.
-The performance metrics were calculated at the end of the run.
-The second method, coevolution with overlapping islands, used the $p_{th-1}$ and $p_{th+1}$ sections of each chromosome, besides the $p_{th}$ part.
-During the same amount of time both methods obtained better results than a baseline algorithm that dealt with the whole chromosome in each island for crossover and mutation.
-We discovered that the performance using one or another method depends on the number of sections of the individuals and the number of islands used.
-This motivates us to find a new adaptive method to select this number of sections of the chromosome to use, depending on the number of islands.
-Moreover, previous experiments were performed on a single processor synchronous island model with a limited number of islands (8, 32 and 128).
-In this paper,  8, 16, 32, 64 and 128 islands have been used, and this time, the experiments have been run on a real cluster.
-Therefore, at the same time we are proposing an adaptive method to divide the individual search space, we are validating the previous methods.
+% ¿Se podría mencionar por algún lado el trabajo en algoritmos de
+% hormigas paralelos de Antonio? - JJ
+In our previous work \citep{Garcia16hpmoonANONYMOUS} we used some of
+the aforementioned ideas to compare two co-evolutionary dMOEAs. The first
+one divided the chromosome in $P$ sections, being $P$ the number of
+islands. Every island $p$ only performed the mutation and crossover in
+that part ($p_{th}$) of the chromosome, while the fitness was
+calculated using the whole individual. After a certain number of
+generations, individuals were migrated randomly to other islands. The
+performance metrics were calculated at the end of the run. The second
+method, coevolution with overlapping islands, used the $p_{th-1}$ and
+$p_{th+1}$ sections of each chromosome, besides the $p_{th}$
+part. During the same amount of time both methods obtained better
+results than a baseline algorithm that dealt with the whole chromosome
+in each island for crossover and mutation. We discovered that the
+performance using one or another method depends on the number of
+sections of the individuals and the number of islands used. This
+motivates us to find a new adaptive method to select this number of
+sections of the chromosome to use, depending on the number of
+islands. Moreover, previous experiments were performed on a single
+processor synchronous island model with a limited number of islands
+(8, 32 and 128). In this paper,  8, 16, 32, 64 and 128 islands have
+been used, and this time, the experiments have been run on a real
+cluster. Therefore, at the same time we are proposing an adaptive
+method to divide the individual search space, we are validating the
+previous methods.
 
@@
 
-Termination criterion used has been the running time: 25 seconds for dimension 512 and 100 (four times more) for 2048.
-We have used the time instead the number of evaluations firstly because our hypothesis argue that the time saved in crossover and mutation can be spent on improving the sub-populations and more operations and migrations can be achieved.
-Also, we are using different number of islands (with different sub-population sizes) that could lead to different execution times, so it would be difficult to compare different times and quality solutions at the same time.
+The criterion used for terminating an experiment has been the running
+time: 25 seconds for dimension 512 and 100s (four times more) for
+2048. We have used time instead of the number of evaluations firstly
+because our hypothesis argues that the time saved in crossover and
+mutation can be spent on improving the sub-populations and more
+operations and migrations can be achieved. Also, we are using
+different number of islands (with different sub-population sizes) that
+could lead to different execution times, so it would be difficult to
+compare different times and quality solutions at the same time.
 

### 2016-09-04 hpmoon-hpca.tex
Corrections here and there

@@
 operations and migrations can be achieved. Also, we are using
-different number of islands (with different sub-population sizes) that
+different number of islands (with different sub-population sizes) and that
 could lead to different execution times, so it would be difficult to
-compare different times and quality solutions at the same time.
+compare different times and quality of solutions at the same time.
 
@@
 Island Model, in a CentOS 5.4 machine with Intel(R) Xeon(R) CPU E5520
-@2.27GHz, 16 GB RAM, with Java Version 1.6.0\_16.
+@2.27GHz, 16 GB RAM and Java Version 1.6.0\_16.
 
-Different metrics, explained in the previous section, have been used to calculate the quality of the obtained PFs in each configuration.
-As some of the metrics  (such as HV) require a reference point to be calculated, the point (1,9) has been chosen as reference, as none of the generated PFs in all runs are dominated by it.
-Metrics are then normalized with respect to that point.
-A Kruskall-Wallis significance test has been performed to the metrics of all runs of the configurations, as the Kolmogorov-Smirnov test detected non-normal distributions.
-The average results for each configuration are shown in Table \ref{tab:results512} (for 512 dimensions) and \ref{tab:results2048} (for 2048).
-As previously explained, when $P=8$ the results of A are equivalent to the obtained with D (because $c=0$), and when $P=16$ they are equivalent to O ($c=1$).
+Different metrics, explained in the previous section, have been used
+to calculate the quality of the obtained PFs in each configuration. As
+some of the metrics  (such as HV) require a reference point to be
+calculated, the point (1,9) has been chosen as reference, as none of
+the generated PFs in all runs are dominated by it. Metrics are then
+normalized with respect to that point. A Kruskall-Wallis significance
+test has been performed to the metrics of all runs of the
+configurations, as the Kolmogorov-Smirnov test detected non-normal
+distributions. The average results for each configuration are shown in
+Table \ref{tab:results512} (for 512 dimensions) and
+\ref{tab:results2048} (for 2048). As previously explained, when $P=8$
+the results of A are equivalent to the obtained with D (because
+$c=0$), and when $P=16$ they are equivalent to O ($c=1$).
 
@@
 %\multicolumn{13}{|c|}{2048 dimenOionO}																																													\\ \hline
-\#Island	&	B		&	D		&	O			&	A			&	B		&	D			&	O			&	A			&	B		&	D		&	O		&	A					\\ \hline
+\#Islands	&	B		&	D		&	O			&	A			&	B		&	D			&	O			&	A			&	B		&	D		&	O		&	A					\\ \hline
 \multicolumn{13}{|c|}{ZDT1}																																													\\ \hline
@@
 
-High-performance problems that require a large number of decision variables can leverage the division of the decision space that parallel and distributed algorithms imply.
-This can be done in dMOEAs by dividing the chromosome into different parts, each one modified by a different island.
-This paper compares a baseline distributed NSGA-II with three different strategies to separate the chromosome (disjoint or overlapping parts), using a high number of islands.
-Results show that these methods can achieve better quality metrics than the baseline in the same amount of time, with larger chromosome lengths.
+High-performance problems % problems are not high-performance. They
+                          % _require_ high performance
+ that require a large number of decision variables can leverage the
+ division of the decision space that parallel and distributed
+ algorithms imply. This can be done in dMOEAs by dividing the
+ chromosome into different parts, each one modified by a different
+ island. This paper compares a baseline distributed NSGA-II with three
+ different strategies to separate the chromosome (disjoint or
+ overlapping parts), using a high number of islands. Results show that
+ these methods can achieve better quality metrics than the baseline in
+ the same amount of time, with larger chromosome lengths.
 
-Results also show that when increasing the number of islands, the adaptive overlapping method significantly improves the results with respect to the disjoint and overlapped methods.
-However, this is only apparent with larger chromosome sizes.
-Therefore, the length of the chromosome is also a key factor to take into account in adaptive methods, and not only the number of islands.
-Studying this factor with more types of problems, and new configurations of population size and chromosome lengths will be addressed in the future.%
-%
+Results also show that when increasing the number of islands, the
+adaptive overlapping method significantly improves the results with
+respect to the disjoint and overlapped methods. However, this is only
+apparent with larger chromosome sizes. Therefore, the length of the
+chromosome is also a key factor to take into account in adaptive
+methods, and not only the number of islands. Studying this factor with
+more types of problems, and new configurations of population size and
+chromosome lengths will be addressed in the future.% 
+% More discussion should be added. Why is adaptive better? Is the high
+% performance really needed? - JJ
 
-Also, more distributed implementations in several systems (such as a GPUs or heterogeneous clusters) with more different quantities of islands/processors, will be used to perform a scalability study of the different methods, being the transmission time between islands a relevant issue to address.
-Finally, new benchmarks and real problems will also be  used to validate this approach.
+Also, more distributed implementations in several systems (such as a
+GPUs or heterogeneous clusters) with different amounts of
+islands/processors, will be used to perform a scalability study of the
+different methods, being the transmission time between islands a
+relevant issue to address. Finally, new benchmarks and real problems
+will also be  used to validate this approach.
 

### 2016-09-13 hpmoon-hpca.tex
Added some changes to add pseudocode for issue #6

@@
 \usepackage{moreverb,url,color}
+\usepackage{algorithm}
+\usepackage{algorithmic}
 \usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
@@
 
+\textcolor{red}{Pseudo-code of the proposed algorithms is described in Figure \ref{fig:pseudo}.}
+
+\begin{algorithm}[htb]
+
+\begin{algorithmic}
+\STATE FOR EACH ISLAND
+\STATE population $\gets$ initialisePopulation()
+\WHILE {stopping criterion not met}
+    \STATE parents $\gets$ selection(population)
+    \FOR each 2 chromosome in parents
+    	\STATE children  $\gets$ parents
+
+    \STATE offspring $\gets$ recombination(parents)
+    \STATE offspring $\gets$ mutation(offspring)
+    \STATE O $\gets$ offspring.size {\em //O is also equal to the number of parents selected}
+    \STATE population $\gets$ population + offspring
+
+    \IF {time to migrate}
+      \STATE migrants $\gets$ selectMigrants(population)
+      \STATE remoteBuffer.send(migrants)
+    \ENDIF
+
+    \IF {localBuffer.size $\neq$ zero}
+      \STATE immigrants $\gets$ localBuffer.read()
+      \STATE I $\gets$ immigrants.size()
+      \STATE population $\gets$ population + immigrants
+    \ENDIF
+
+    \IF {localBuffer.size $\neq$ zero}
+      \STATE population $\gets$ population + localBuffer.read()
+    \ENDIF
+    \STATE population $\gets$ population - population.getTheWorst(O + I)
+\ENDWHILE
+
+\STATE SEND FRONT TO SERVER
+\STATE RETURN NEW FRONT CO ALL ISLANDS
+
+\end{algorithmic}
+
+\caption{Pseudo-code of the used EA: a distributed NSGA-II algorithm }
+\label{alg:EA}
+\end{algorithm}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%  EXPERIMENTS AND RESULTS  %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 These metrics have been used extensively, especially in some of the papers presented in Section 2.
+
+\subsection{Benchmark problems}
+\textcolor{red}{The first part of the experiments...}
 
@@
 
+\subsection{Real problem}
+\textcolor{red}{A real problem has also been used.}
+
 %Surprisingly, the average

### 2016-09-13 hpmoon-hpca.tex
Changes to pseudocode for issue #6

--- 2016-09-04 hpmoon-hpca.tex
@@
 \runninghead{anonymous}
-\title{Parallel Multi-objective optimization using co-evolutionary
+\title{Parallel multi-objective optimization using co-evolutionary
   islands and search space overlapping}
-% Why are you mixing caps and non-caps? - JJ
+% Why are you mixing caps and non-caps? - JJ Pablo: fixed
 
@@
 
+\textcolor{red}{Pseudo-code of the proposed algorithms is described in Algorithm \ref{fig:pseudo}.}
+
+\begin{algorithm}[htb]
+
+\begin{algorithmic}
+\STATE \textit{//In each island $i$}
+\STATE population $\gets$ initialisePopulation()
+\STATE \textit{//Select which part modify in this island $i$}
+\STATE section $\gets$ getComponentsToModify($i$)
+\WHILE {stopping criterion not met}
+    \STATE parents $\gets$ nsgaSelection(population)
+    \FORALL{each 2 chromosome in parents}
+    	\STATE \textit{//Crossovers only the part for island $i$}
+    	\STATE children  $\gets$ crossover(parents,section)
+    	\STATE offspring $\gets$ offspring + children
+    \ENDFOR
+    \FORALL{chromosome in offspring}
+    	\IF {mutationProb $>$ random()}
+    		\STATE \textit{//Mutates only the part for island $i$}
+    		\STATE chromosome $\gets$ mutation(chromosome,section)
+    		\STATE offspring $\gets$ chromosome + offspring
+    	\ENDIF
+    \ENDFOR
+    \STATE population $\gets$ population + offspring
+
+    \IF {time to migrate}
+      \STATE migrants $\gets$ binaryTournament(population)
+      \STATE remoteBuffer $\gets$ getRandomIslandBuffer()
+      \STATE remoteBuffer.send(migrants)
+    \ENDIF
+
+    \IF {localBuffer.size $\neq$ zero}
+      \STATE immigrants $\gets$ localBuffer.read()
+      \STATE population $\gets$ population + immigrants
+    \ENDIF
+\ENDWHILE
+
+\STATE sendIslandParetoFrontToServer()
+\STATE \textit{Final Pareto Front from all islands is returned by the server}
+\end{algorithmic}
+
+\caption{Pseudo-code of the used EA in every island: a distributed NSGA-II algorithm }
+\label{alg:EA}
+\end{algorithm}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%  EXPERIMENTS AND RESULTS  %%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-09-14 hpmoon-hpca.tex
Explaining real problem for issue #3

@@
 
-\subsection{Real problem}
-\textcolor{red}{A real problem has also been used.}
+\subsection{Real problem benchmark: Unsupervised Feature Selection}
+\textcolor{red}{A real problem has also been used to BLABLABLA.
+In this case, the problem used to solve is the unsupervised feature selection.
+A dataset formed by EEG signals from Brain Computer Interface (BCI) is used as a benchmark \cite{Kimovski15Parallel}, due to the required high computational cost and chromosome length.
+Individuals in this case are binary vectors indicating if a specific feature is selected or not.
+To evaluate a set of features different clustering validation indexes (CVIs) can be used.}
+
+\textcolor{red}{In this case, the two objectives to compare the three methods are the inter-cluster separation ($f1$) and the intra-cluster separation ($f2$).
+To obtain this measures, and after applying the projection to the dataset, a method based in the one presented  \cite{Kimovski15Parallel} is applied.
+Starting with a random value of the projection, the distance to the closer one is stored, and so on.
+After ordering these distances from lower to higher, we consider the intra-cluster distance ($f1$) as the one in the position 1/4 of the list, while the inter-cluster ($f2$) distance is in the position 3/4.
+The intra-cluster distance objective needs to be minimized, while the inter-cluster is maximized.
+Figure \ref{fig:cvis} explains this method using a extremely simplified example.
+Note that the goal of this paper is not obtain better CVI values than other methods, but to study the different overlapping schemes in parallel MOEAs.}
+
+\begin{figure}
+\centering
+\includegraphics[width=10cm]{clusterCVI.pdf}
+\caption{\textcolor{red}{Method to calculate the two objectives for the Feature Selection problem.
+Starting from a random $d$ point of the projection of the features, the distance to the closer point is calculated iteratively.
+After ordering these distances, the one in the position 1/4 (a) is considered the intra-cluster distance, while the one in position 3/4 (b) is considered the inter-cluster one.}}
+\label{fig:cvis}
+\end{figure}
+
+\textcolor{red}{The Dataset used is ...
+Due to the high computational cost required for the fitness function, the running time for each run has been set to 4 hours, with two generations before sending the individual to another random island.
+Table \ref{tab:parametersBCI} summarizes the specific parameters for this experiment (the rest of the parameters are the same than the previous experiment, shown in Table \ref{tab:parameters} ).
+As there is no optimal PF known for this problem, we have used the paretos obtained from all runs to obtain the optimal PF to apply the IGD quality metric.}
+
+\textcolor{red}{
+\begin{table*}
+\begin{center}
+\begin{tabular}{|c|c|}
+\hline
+{\em Parameter Name} & {\em Value} \\ \hline
+Number of islands ($P$) & 8, 32 and 128 \\ \hline
+Chromosome size ($L$) & 3600 \\ \hline
+Crossover type & One-point \\ \hline
+Mutation  type & flip\\ \hline
+Generations between migration & 2 \\ \hline
+Runs per configuration & 10 \\ \hline
+\end{tabular}
+\caption{\textcolor{red}{Parameters and operators used in the experiments for Feature Selection problem (the rest of the parameters are the ones described in Table \ref{tab:parameters}).}}
+\label{tab:parametersBCI}
+\end{center}
+\end{table*}
+}
 

### 2016-11-18 hpmoon-hpca.tex
Fixed pseudocodefor issue #6
Changed format to FGCS

--- 2016-09-13 hpmoon-hpca.tex
@@
-% sage_latex_guidelines.tex V1.01, 11 June 2015
-
-%\documentclass[Afour,sagev,times]{sagej}
-\documentclass[Crown,sagev,times,doublespace]{sagej}
-
-\usepackage{moreverb,url,color}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
-
-\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
-T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-
-\def\volumeyear{2016}
-
-\begin{document}
-
-%\runninghead{Garc\'ia-S\'anchez et al.}
-\runninghead{anonymous}
-\title{Parallel multi-objective optimization using co-evolutionary
-  islands and search space overlapping}
-% Why are you mixing caps and non-caps? - JJ Pablo: fixed
-
-%\author{Pablo Garc\'ia-S\'anchez, Julio Ortega, Jes\'us Gonz\'alez, \\Pedro Angel Castillo and Juan Juli\'an Merelo\affilnum{1}}
-\author{ANONYMOUS FOR BLIND REVIEW \affilnum{1}}
-\affiliation{\affilnum{1} ANONYMOUS FOR BLIND REVIEW}
 %\affiliation{\affilnum{1}Dept. of Computer Architecture and Computer Technology, University of Granada, Spain}
@@
 
-%\corrauth{ANONYMOUS FOR BLIND REVIEW.}
+\documentclass[preprint]{elsarticle}
+\usepackage[latin1]{inputenc}
+\usepackage[english]{babel}
+\usepackage{moreverb,url,color}
+\usepackage{algorithm}
+\usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{color}
+\usepackage{url}
+\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
 
-%\email{pablogarcia@ugr.es}
-\email{anonymous}
+\begin{document}
+
+\begin{frontmatter}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\title{Parallel multi-objective optimization using co-evolutionary
+  islands and search space overlapping}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   AUTHORS   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\author{P. Garc\'ia-S\'anchez$^1$, J. Ortega$^2$, J. Gonz\'alez$^2$, P. A. Castillo$^2$ and J.J. Merelo$^2$}
+\ead{pablo.garciasanchez@uca.es, \{jortega, jgonzalez, pacv, jmerelo\}@ugr.es}
+\address{
+$^1$ Department of Computer Science and Engineering. ESI. University of C\'adiz, Spain\\
+$^2$ Department of Computer Architecture and Computer Technology.\\ ETSIIT - CITIC. University of Granada, Spain\\
+}
 
@@
 problems. 
-% You can safely supress the sentence above - JJ
 Many of these problems usually require a high-dimensional
 decision space, and multi-objective Evolutionary Algorithms have been
-% random capitalization strikes back - JJ
 successfully used in the past. 
-% Another useless sentence - JJ
 Due to the large computational cost
@@
 
-\keywords{Multi-objective algorithms, NSGA-II, Island model, distributed evolutionary algorithms, coevolution}
+\begin{keyword}
+Multi-objective algorithms \sep NSGA-II \sep Island model \sep distributed evolutionary algorithms \sep coevolution
+\end{keyword}
 
-\maketitle
+\end{frontmatter}
 
@@
 The rest of the paper is organized as follows: after a background in parallelization in MOEAs, 
-the compared algorithms and the used methodology are presented. %PABLO: no puedo usar \ref{sec:met} porque la plantilla de esta revista no lo coge :/ (y además no tienen número)
-Then, the results of the experiments are shown, followed by conclusions and suggestions for future work lines.
+the compared algorithms and the used methodology are presented in Section \ref{sec:coevo}.
+%PABLO: no puedo usar \ref{sec:met} porque la plantilla de esta revista no lo coge :/ (y además no tienen número)
+Then, the results of the experiments are shown (Section \ref{sec:res}), followed by conclusions and suggestions for future work lines.
 
@@
 
-\textcolor{red}{Pseudo-code of the proposed algorithms is described in Algorithm \ref{fig:pseudo}.}
+Pseudo-code of the proposed algorithms is described in Algorithm \ref{fig:pseudo}.
 
@@
 \STATE section $\gets$ getComponentsToModify($i$)
+\IF {type = Baseline}
+	\STATE $c=P/2$
+\ELSIF {type = Disjoint}
+	\STATE $c=0$
+\ELSIF {type = Overlapping}
+	\STATE $c=1$
+\ELSIF {type = Adaptive}
+	\STATE $c=round(0.2*P-1)/2$
+\ENDIF
+
 \WHILE {stopping criterion not met}
@@
     \FORALL{each 2 chromosome in parents}
-    	\STATE \textit{//Crossovers only the part for island $i$}
-    	\STATE children  $\gets$ crossover(parents,section)
+    	\STATE \textit{//Crossovers only the part for island $i$ (c components left and right)}
+    	\STATE children  $\gets$ crossover(parentA[i-c:i+c],parentB[i-c:i+c])
     	\STATE offspring $\gets$ offspring + children
@@
     		\STATE \textit{//Mutates only the part for island $i$}
-    		\STATE chromosome $\gets$ mutation(chromosome,section)
+    		\STATE chromosome $\gets$ mutation(chromosome[i-c:i+c])
     		\STATE offspring $\gets$ chromosome + offspring
@@
 
-\subsection{Benchmark problems}
-\textcolor{red}{The first part of the experiments...}
+%\subsection{Benchmark problems}
 
@@
 
-\subsection{Real problem}
-\textcolor{red}{A real problem has also been used.}
+%%%%REAL PROBLEM
+%\subsection{Real problem benchmark: Unsupervised Feature Selection}
+%\textcolor{red}{A real problem has also been used to BLABLABLA.
+In this case, the problem used to solve is the unsupervised feature selection.
+A dataset formed by EEG signals from Brain Computer Interface (BCI) is used as a benchmark \cite{Kimovski15Parallel}, due to the required high computational cost and chromosome length.
+Individuals in this case are binary vectors indicating if a specific feature is selected or not.
+To evaluate a set of features different clustering validation indexes (CVIs) can be used.}
 
-%Surprisingly, the average
-%number of solutions of PFs per island in the baseline configuration is significantly
-%higher in some configurations (mostly with 128 islands), but their
-%combination in the final PF never attains higher values than Disjoint
-%and Overlapping methods.
+%\textcolor{red}{In this case, the two objectives to compare the three methods are the inter-cluster separation ($f1$) and the intra-cluster separation ($f2$).
+To obtain this measures, and after applying the projection to the dataset, a method based in the one presented  \cite{Kimovski15Parallel} is applied.
+Starting with a random value of the projection, the distance to the closer one is stored, and so on.
+After ordering these distances from lower to higher, we consider the intra-cluster distance ($f1$) as the one in the position 1/4 of the list, while the inter-cluster ($f2$) distance is in the position 3/4.
+The intra-cluster distance objective needs to be minimized, while the inter-cluster is maximized.
+Figure \ref{fig:cvis} explains this method using a extremely simplified example.
+Note that the goal of this paper is not obtain better CVI values than other methods, but to study the different overlapping schemes in parallel MOEAs.}
 
-%configurations, with respect to the baseline.  Paying attention to the disjoint and
-%overlapping methods, only when using 8 islands the disjoint method
-%always attain better metrics, and even more times with the 2048 chromosome
-%length. This can be explained because only 1/8 of the individual is
-%changed in each island, while in the overlapping, 3/8 of the island
-%may be more similar to the baseline configuration. 
-%
+%\begin{figure}
+%\centering
+%\includegraphics[width=10cm]{clusterCVI.pdf}
+%\caption{\textcolor{red}{Method to calculate the two objectives for the Feature Selection problem.
+Starting from a random $d$ point of the projection of the features, the distance to the closer point is calculated iteratively.
+After ordering these distances, the one in the position 1/4 (a) is considered the intra-cluster distance, while the one in position 3/4 (b) is considered the inter-cluster one.}}
+%\label{fig:cvis}
+%\end{figure}
+
+%\textcolor{red}{The Dataset used is ...
+Due to the high computational cost required for the fitness function, the running time for each run has been set to 4 hours, with two generations before sending the individual to another random island.
+Table \ref{tab:parametersBCI} summarizes the specific parameters for this experiment (the rest of the parameters are the same than the previous experiment, shown in Table \ref{tab:parameters} ).
+As there is no optimal PF known for this problem, we have used the paretos obtained from all runs to obtain the optimal PF to apply the IGD quality metric.}
+
+%\textcolor{red}{
+%\begin{table*}
+%\begin{center}
+%\begin{tabular}{|c|c|}
+%\hline
+%{\em Parameter Name} & {\em Value} \\ \hline
+%Number of islands ($P$) & 8, 32 and 128 \\ \hline
+%Chromosome size ($L$) & 3600 \\ \hline
+%Crossover type & One-point \\ \hline
+%Mutation  type & flip\\ \hline
+%Generations between migration & 2 \\ \hline
+%Runs per configuration & 10 \\ \hline
+%\end{tabular}
+%\caption{\textcolor{red}{Parameters and operators used in the experiments for Feature Selection problem (the rest of the parameters are the ones described in Table \ref{tab:parameters}).}}
+%\label{tab:parametersBCI}
+%\end{center}
+%\end{table*}
+%}
 
@@
 
-\begin{acks}
+\section*{Acknowledgements}
 ANONYMOUS
 %This work has been partially funded by projects TIN2014-56494-C4-3-P y TIN2015-67020-P (Spanish Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio 2015 UGR),  and  MSTR (PRY142/14, Fundaci\'on P\'ublica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci\'on).
-\end{acks}
 
-\bibliographystyle{SageV}
+\bibliographystyle{elsarticle-num}
 

### 2016-11-18 bio.tex
Changed names and all for FGCS

Pablo García-Sánchez received his Degree (2007), MSc degree (2008) and PhD (2014) in computer science and engineering at the University of Granada (Spain). He is currently a substitute professor in the University of Cádiz. He has participated and lead several national research projects related to e-Health, web-services, videogames and optimization, whose results have been published in conferences (such as GECCO, PPSN or EVO*) and international journals (such as Applied Soft Computing). Also, he has been a visitor researcher to the Vrije Universiteit Amsterdam. His interests include service-oriented computing, evolutionary computation, computational intelligence in videogames and distributed algorithms.

### 2016-11-18 highlights.tex
Changed names and all for FGCS

\documentclass{article}
\usepackage{graphicx}

\begin{document}

%\title{Introduction to \LaTeX{}}
%\author{Author's Name}

%\maketitle

%\section{Reviewer 1}

\begin{itemize}
\item A study on methods to overlap the search space in distributed multi-objective evolutionary algorithms is carried out
\item A new adaptive overlapping mechanism is presented
\item Different combinations of number of islands, genome sizes, benchmarks and methods are used
\item Different quality metrics have been compared
\item Results are validated in a real system
\item All overlapping schemes outperform the baseline, being the adaptive method the one that obtains the best performance
\end{itemize}
\end{document}

### 2016-11-18 hpmoon-fgcs.tex
Changed names and all for FGCS

--- 2016-11-18 hpmoon-hpca.tex
@@
 \author{P. Garc\'ia-S\'anchez$^1$, J. Ortega$^2$, J. Gonz\'alez$^2$, P. A. Castillo$^2$ and J.J. Merelo$^2$}
-\ead{pablo.garciasanchez@uca.es, \{jortega, jgonzalez, pacv, jmerelo\}@ugr.es}
+\ead{pablo.garciasanchez@uca.es, \{jortega, jesusgonzalez, pacv, jmerelo\}@ugr.es}
 \address{
@@
 decision variables) is also a relevant factor to determine the most
-efficient alternative to distribute the decision variables.n 
+efficient alternative to distribute the decision variables.
 \end{abstract}
@@
 
-In our preliminary work in \citep{Garcia16hpmoonANONYMOUS} we tried to demonstrate that using overlapped sections of the chromosome in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time when the number of islands increases.
+In our preliminary work in \citep{Garcia16hpmoon} we tried to demonstrate that using overlapped sections of the chromosome in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time when the number of islands increases.
 We discovered that the most adequate overlapping size may vary depending on a relation between the number of islands and the individual size.
@@
 % hormigas paralelos de Antonio? - JJ
-In our previous work \citep{Garcia16hpmoonANONYMOUS} we used some of
+In our previous work \citep{Garcia16hpmoon} we used some of
 the aforementioned ideas to compare two co-evolutionary dMOEAs. The first
@@
 As in the previous method, the sections to address are overlapped, but instead using one extra section on each side of the $p$ section ($p+1$ and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$), being $c$ a value depending on the number of islands.
-As a first approach to automatically calculate this value the results shown in \citep{Garcia16hpmoonANONYMOUS} have been used as a base to obtain $c$.
+As a first approach to automatically calculate this value the results shown in \citep{Garcia16hpmoon} have been used as a base to obtain $c$.
 In that work, the overlapped method ($c=1$) obtained better results when the number of islands were $>$8.
@@
 \centering
-\includegraphics[width=6cm]{hypervolume.pdf}
+\includegraphics[width=6cm]{hypervolume.jpg}
 \caption{Hypervolume calculation. Areas from Pareto Front solutions (black points) to a reference point (white point) are added.}
@@
 LGPL V3 License
-%\footnote{\url{https://github.com/hpmoon/hpmoon-islands}}. 
-\footnote{\url{https://ANONYMOUS-REPOSITORY}}. 
+\footnote{\url{https://github.com/hpmoon/hpmoon-islands}}. 
+%\footnote{\url{https://ANONYMOUS-REPOSITORY}}. 
 The
@@
 Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than the obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply these methods.
-This contradicts the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoonANONYMOUS}, where the overlapping method obtained better results than the baseline in both dimension lengths.
+This contradicts the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths.
 This can be explained because the added migration latency between nodes requires more time than the time saved during the crossover and migration.
@@
 
-Finally, as happened in \citep{Garcia16hpmoonANONYMOUS}, results show that all the quality indicators decrease when the number of islands is increased, as the  sizes of the subpopulations are smaller.
+Finally, as happened in \citep{Garcia16hpmoon}, results show that all the quality indicators decrease when the number of islands is increased, as the  sizes of the subpopulations are smaller.
 This is consistent with the claim by Dorronsoro et al.
@@
 \section*{Acknowledgements}
-ANONYMOUS
-%This work has been partially funded by projects TIN2014-56494-C4-3-P y TIN2015-67020-P (Spanish Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio 2015 UGR),  and  MSTR (PRY142/14, Fundaci\'on P\'ublica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci\'on).
+This work has been partially funded by projects TIN2014-56494-C4-3-P y TIN2015-67020-P (Spanish Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio 2015 UGR),  and  MSTR (PRY142/14, Fundaci\'on P\'ublica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci\'on).
 
@@
 
-\bibliography{hpmoon-hpca}
+\bibliography{hpmoon-fgcs}
 %\begin{thebibliography}{99}

### 2016-12-05 hpmoon-eswa.tex
Final version sent to ESWA

--- 2016-11-18 hpmoon-fgcs.tex
@@
 
-\title{Parallel multi-objective optimization using co-evolutionary
-  islands and search space overlapping}
+\title{Parallel multi-objective optimization using co-evolutionary islands and search space overlapping}
 
@@
 \begin{abstract}
-Multi-objective optimization methods have gained interest in the last
-years because the performance they can achieve solving real-world
-problems. 
-Many of these problems usually require a high-dimensional
-decision space, and multi-objective Evolutionary Algorithms have been
-successfully used in the past. 
-Due to the large computational cost
-these algorithms require, different parallelization and distribution
-methods have been proposed, with different parallel and distributed
-computer architectures to cope with them. One of the most extended
-methods are the distributed co-evolutionary algorithms, where each
-processor deals only with a part of the decision space, that is, the
-individuals belonging to the same sub-population (island) explore the
-same subset of decision variables.
-%After explaining the method, you should say why it might work - JJ
+Multi-objective optimization methods have gained interest in the last years because the performance they can achieve solving real-world problems.
+Many of these problems usually require a high-dimensional decision space, and multi-objective Evolutionary Algorithms have been successfully used in the past.
+Due to the large computational cost these algorithms require, different parallelization and distribution methods have been proposed, with different parallel and distributed computer architectures to cope with them.
+One of the most extended methods are the distributed co-evolutionary algorithms, where each processor deals only with a part of the decision space, that is, the individuals belonging to the same sub-population (island) explore the same subset of decision variables.
 
-In this paper, a new method to automatically adapt the overlapping
-sections of the individuals has been compared to other collaborative
-% what sections? Decision space sections? Besides, you are using
-% section here and before you were using "subset" - JJ
-evolutionary methods. 
-Different number of islands, chromosome sizes and problems have been
-used. The analysis of the obtained experimental results, by using
-different  
-metrics, shows that coevolutionary approaches can provide
-statistically significant improvements with respect to the base
-algorithm, being the method to automatically adapt the overlapping
-size the one to obtain the best performance during the same execution
-time. Results also show that the relation of the number of  
-islands (subpopulations) to the length of the chromosome (number of
-decision variables) is also a relevant factor to determine the most
-efficient alternative to distribute the decision variables.
+In this paper, a new method to automatically adapt the overlapping sections of the individuals has been compared to other collaborative evolutionary methods.
+Different number of islands, chromosome sizes and problems have been used.
+The analysis of the obtained experimental results, by using different metrics, shows that coevolutionary approaches can provide statistically significant improvements with respect to the base algorithm, being the method to automatically adapt the overlapping size the one to obtain the best performance during the same execution time.
+Results also show that the relation of the number of islands (subpopulations) to the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distribute the decision variables.
 \end{abstract}
@@
 
-\bibliographystyle{elsarticle-num}
+%\bibliographystyle{elsarticle-num}
 
-\bibliography{hpmoon-fgcs}
-%\begin{thebibliography}{99}
-%\bibitem[Kopka and Daly(2003)]{R1}
-%Kopka~H and Daly~PW (2003) \textit{A Guide to \LaTeX}, 4th~edn.
-%Addison-Wesley.%
+%\bibliography{hpmoon-eswa}
 
-%\bibitem[Lamport(1994)]{R2}
-%Lamport~L (1994) \textit{\LaTeX: a Document Preparation System},
-%2nd~edn. Addison-Wesley.%
+\begin{thebibliography}{10}
+\expandafter\ifx\csname url\endcsname\relax
+  \def\url#1{\texttt{#1}}\fi
+\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+\expandafter\ifx\csname href\endcsname\relax
+  \def\href#1#2{#2} \def\path#1{#1}\fi
 
-%\bibitem[Mittelbach and Goossens(2004)]{R3}
-%Mittelbach~F and Goossens~M (2004) \textit{The \LaTeX\ Companion},
-%2nd~edn. Addison-Wesley.%
+\bibitem{Alba13parallel}
+E.~Alba, G.~Luque, S.~Nesmachnow, Parallel metaheuristics: recent advances and
+  new trends, International Transactions in Operational Research 20~(1) (2013)
+  1--48.
+\newblock \href {http://dx.doi.org/10.1111/j.1475-3995.2012.00862.x}
+  {\path{doi:10.1111/j.1475-3995.2012.00862.x}}.
 
-%\end{thebibliography}
+\bibitem{Folino03cellular}
+G.~Folino, C.~Pizzuti, G.~Spezzano, A scalable cellular implementation of
+  parallel genetic programming, {IEEE} Trans. Evolutionary Computation 7~(1)
+  (2003) 37--53.
+
+\bibitem{Alba02Parallelism}
+E.~Alba, M.~Tomassini, Parallelism and evolutionary algorithms, {IEEE} Trans.
+  Evolutionary Computation 6~(5) (2002) 443--462.
+
+\bibitem{Luna15Survey}
+F.~Luna, E.~Alba, Parallel multiobjective evolutionary algorithms, in:
+  J.~Kacprzyk, W.~Pedrycz (Eds.), Springer Handbook of Computational
+  Intelligence, Springer, 2015, pp. 1017--1031.
+
+\bibitem{Branke04Parallelizingcone}
+J.~Branke, H.~Schmeck, K.~Deb, R.~S. Maheshwar, Parallelizing multi-objective
+  evolutionary algorithms: cone separation, in: Proceedings of the {IEEE}
+  Congress on Evolutionary Computation, {CEC} 2004, 19-23 June 2004, Portland,
+  OR, {USA}, {IEEE}, 2004, pp. 1952--1957.
+
+\bibitem{Mukhopadhyay14Survey}
+A.~Mukhopadhyay, U.~Maulik, S.~Bandyopadhyay, C.~A.~C. Coello, A survey of
+  multiobjective evolutionary algorithms for data mining: Part {I}, {IEEE}
+  Trans. Evolutionary Computation 18~(1) (2014) 4--19.
+
+\bibitem{Chavez15MO}
+F.~C. de~la O, E.~Clemente, D.~E. Hern{\'{a}}ndez, F.~F. de~Vega, G.~Olague, A
+  multi-objective evolutionary algorithm for interaction systems based on laser
+  pointers, in: A.~M. Mora, G.~Squillero (Eds.), Applications of Evolutionary
+  Computation - 18th European Conference, EvoApplications 2015, Copenhagen,
+  Denmark, April 8-10, 2015, Proceedings, Vol. 9028 of Lecture Notes in
+  Computer Science, Springer, 2015, pp. 504--516.
+\newblock \href {http://dx.doi.org/10.1007/978-3-319-16549-3}
+  {\path{doi:10.1007/978-3-319-16549-3}}.
+
+\bibitem{Hidalgo16residualstress}
+J.~I. Hidalgo, R.~Fern{\'{a}}ndez, J.~M. Colmenar, F.~Cioffi, J.~L.
+  Risco{-}Mart{\'{\i}}n, G.~Gonz{\'{a}}lez{-}Doncel, Using evolutionary
+  algorithms to determine the residual stress profile across welds of
+  age-hardenable aluminum alloys, Appl. Soft Comput. 40 (2016) 429--438.
+\newblock \href {http://dx.doi.org/10.1016/j.asoc.2015.11.004}
+  {\path{doi:10.1016/j.asoc.2015.11.004}}.
+
+\bibitem{Gong15models}
+Y.~Gong, W.~Chen, Z.~Zhan, J.~Zhang, Y.~Li, Q.~Zhang, J.~Li, Distributed
+  evolutionary algorithms and their models: {A} survey of the state-of-the-art,
+  Appl. Soft Comput. 34 (2015) 286--300.
+\newblock \href {http://dx.doi.org/10.1016/j.asoc.2015.04.061}
+  {\path{doi:10.1016/j.asoc.2015.04.061}}.
+
+\bibitem{Tonda12cooperative}
+A.~P. Tonda, E.~Lutton, G.~Squillero, A benchmark for cooperative coevolution,
+  Memetic Computing 4~(4) (2012) 263--277.
+\newblock \href {http://dx.doi.org/10.1007/s12293-012-0095-x}
+  {\path{doi:10.1007/s12293-012-0095-x}}.
+
+\bibitem{Kimovski15Parallel}
+D.~Kimovski, J.~Ortega, A.~Ortiz, R.~Ba{\~{n}}os, Parallel alternatives for
+  evolutionary multi-objective optimization in unsupervised feature selection,
+  Expert Syst. Appl. 42~(9) (2015) 4239--4252.
+\newblock \href {http://dx.doi.org/10.1016/j.eswa.2015.01.061}
+  {\path{doi:10.1016/j.eswa.2015.01.061}}.
+
+\bibitem{Dorronsoro13superlinear}
+B.~Dorronsoro, G.~Danoy, A.~J. Nebro, P.~Bouvry, Achieving super-linear
+  performance in parallel multi-objective evolutionary algorithms by means of
+  cooperative coevolution, Computers {\&} {OR} 40~(6) (2013) 1552--1563.
+\newblock \href {http://dx.doi.org/10.1016/j.cor.2011.11.014}
+  {\path{doi:10.1016/j.cor.2011.11.014}}.
+
+\bibitem{Garcia16hpmoon}
+P.~Garc{\'{\i}}a{-}S{\'{a}}nchez, J.~Ortega, J.~Gonz{\'{a}}lez, P.~A. Castillo,
+  J.~J. Merelo, Addressing high dimensional multi-objective optimization
+  problems by coevolutionary islands with overlapping search spaces, in:
+  G.~Squillero, P.~Burelli (Eds.), Applications of Evolutionary Computation -
+  19th European Conference, EvoApplications 2016, Porto, Portugal, March 30 -
+  April 1, 2016, Proceedings, Part {II}, Vol. 9598 of Lecture Notes in Computer
+  Science, Springer, 2016, pp. 107--117.
+
+\bibitem{Deb00NSGAII}
+K.~Deb, S.~Agrawal, A.~Pratap, T.~Meyarivan, A fast elitist non-dominated
+  sorting genetic algorithm for multi-objective optimisation: {NSGA-II}, in:
+  M.~Schoenauer, K.~Deb, G.~Rudolph, X.~Yao, E.~Lutton, J.~J.~M. Guerv{\'{o}}s,
+  H.~Schwefel (Eds.), Parallel Problem Solving from Nature - {PPSN} VI, 6th
+  International Conference, Paris, France, September 18-20, 2000, Proceedings,
+  Vol. 1917 of Lecture Notes in Computer Science, Springer, 2000, pp. 849--858.
+
+\bibitem{DBLP:series/ncs/EibenS15}
+A.~E. Eiben, J.~E. Smith, Introduction to Evolutionary Computing, Natural
+  Computing Series, Springer, 2015.
+\newblock \href {http://dx.doi.org/10.1007/978-3-662-44874-8}
+  {\path{doi:10.1007/978-3-662-44874-8}}.
+
+\bibitem{DeJong2006}
+K.~A. De~Jong, Evolutionary computation: a unified approach, MIT press, 2006.
+
+\bibitem{Mora13paretobased}
+A.~M. Mora, P.~Garc{\'{\i}}a{-}S{\'{a}}nchez, J.~J.~M. Guerv{\'{o}}s, P.~A.
+  Castillo, Pareto-based multi-colony multi-objective ant colony optimization
+  algorithms: an island model proposal, Soft Comput. 17~(7) (2013) 1175--1207.
+\newblock \href {http://dx.doi.org/10.1007/s00500-013-0993-y}
+  {\path{doi:10.1007/s00500-013-0993-y}}.
+
+\bibitem{Talbi08Parallel}
+E.~Talbi, S.~Mostaghim, T.~Okabe, H.~Ishibuchi, G.~Rudolph, C.~A.~C. Coello,
+  Parallel approaches for multiobjective optimization, in: J.~Branke, K.~Deb,
+  K.~Miettinen, R.~Slowinski (Eds.), Multiobjective Optimization, Interactive
+  and Evolutionary Approaches [outcome of Dagstuhl seminars]., Vol. 5252 of
+  Lecture Notes in Computer Science, Springer, 2008, pp. 349--372.
+
+\bibitem{Durillo08masterslave}
+A.~J. Nebro, J.~J. Durillo, A study of the parallelization of the
+  multi-objective metaheuristic {MOEA/D}, in: C.~Blum, R.~Battiti (Eds.),
+  Learning and Intelligent Optimization, 4th International Conference, {LION}
+  4, Venice, Italy, January 18-22, 2010. Selected Papers, Vol. 6073 of Lecture
+  Notes in Computer Science, Springer, 2010, pp. 303--317.
+\newblock \href {http://dx.doi.org/10.1007/978-3-642-13800-3}
+  {\path{doi:10.1007/978-3-642-13800-3}}.
+
+\bibitem{Hiroyasu07discussion}
+T.~Hiroyasu, K.~Yoshii, M.~Miki, Discussion of parallel model of
+  multi-objective genetic algorithms on heterogeneous computational resources,
+  in: H.~Lipson (Ed.), Genetic and Evolutionary Computation Conference, {GECCO}
+  2007, Proceedings, London, England, UK, July 7-11, 2007, {ACM}, 2007, p. 904.
+
+\bibitem{Deb03distributed}
+K.~Deb, P.~Zope, A.~Jain, Distributed computing of pareto-optimal solutions
+  with evolutionary algorithms, in: C.~M. Fonseca, P.~J. Fleming, E.~Zitzler,
+  K.~Deb, L.~Thiele (Eds.), Evolutionary Multi-Criterion Optimization, Second
+  International Conference, {EMO} 2003, Faro, Portugal, April 8-11, 2003,
+  Proceedings, Vol. 2632 of Lecture Notes in Computer Science, Springer, 2003,
+  pp. 534--549.
+
+\bibitem{Xiao03specialized}
+N.~Xiao, M.~P. Armstrong, A specialized island model and its application in
+  multiobjective optimization, in: E.~Cant{\'{u}}{-}Paz, J.~A. Foster, K.~Deb,
+  L.~Davis, R.~Roy, U.~O'Reilly, H.~Beyer, R.~K. Standish, G.~Kendall, S.~W.
+  Wilson, M.~Harman, J.~Wegener, D.~Dasgupta, M.~A. Potter, A.~C. Schultz,
+  K.~A. Dowsland, N.~Jonoska, J.~F. Miller (Eds.), Genetic and Evolutionary
+  Computation - {GECCO} 2003, Genetic and Evolutionary Computation Conference,
+  Chicago, IL, USA, July 12-16, 2003. Proceedings, Part {II}, Vol. 2724 of
+  Lecture Notes in Computer Science, Springer, 2003, pp. 1530--1540.
+
+\bibitem{Wang09parallel}
+W.~Zhi-xin, G.~Ju, A parallel genetic algorithm in multi-objective
+  optimization, in: Control and Decision Conference, 2009. CCDC '09. Chinese,
+  2009, pp. 3497--3501.
+\newblock \href {http://dx.doi.org/10.1109/CCDC.2009.5192490}
+  {\path{doi:10.1109/CCDC.2009.5192490}}.
+
+\bibitem{Martens13asynchronous}
+M.~M{\"{a}}rtens, D.~Izzo, The asynchronous island model and {NSGA-II:} study
+  of a new migration operator and its performance, in: C.~Blum, E.~Alba (Eds.),
+  Genetic and Evolutionary Computation Conference, {GECCO} '13, Amsterdam, The
+  Netherlands, July 6-10, 2013, {ACM}, 2013, pp. 1173--1180.
+
+\bibitem{cheng2015adaptive}
+R.~Cheng, Y.~Jin, K.~Narukawa, Adaptive reference vector generation for inverse
+  model based evolutionary multiobjective optimization with degenerate and
+  disconnected pareto fronts, in: Evolutionary Multi-Criterion Optimization,
+  Springer International Publishing, 2015, pp. 127--140.
+
+\bibitem{zdt2000a}
+E.~Zitzler, K.~Deb, L.~Thiele, {Comparison of Multiobjective Evolutionary
+  Algorithms: Empirical Results}, Evolutionary Computation 8~(2) (2000)
+  173--195.
+
+\bibitem{ECJ}
+S.~Luke, et~al., {ECJ: A Java-based Evolutionary Computation and Genetic
+  Programming Research System}, available at
+  \url{http://www.cs.umd.edu/projects/plus/ec/ecj} (2009).
+
+\end{thebibliography}
 

### 2016-12-13 hpmoon-coor.tex
Explain some stuff about migration. Closes #11

--- 2016-12-05 hpmoon-eswa.tex
@@
 \begin{keyword}
-Multi-objective algorithms \sep NSGA-II \sep Island model \sep distributed evolutionary algorithms \sep coevolution
+Multi-objective algorithms \sep coevolution \sep NSGA-II  \sep distributed evolutionary algorithms \sep Island model
 \end{keyword}
@@
 The
-island model has been executed synchronously, using the ECJ Internal
-Island Model, in a CentOS 5.4 machine with Intel(R) Xeon(R) CPU E5520
-@2.27GHz, 16 GB RAM and Java Version 1.6.0\_16.
+island model has been executed asynchronously, using the ECJ distributed inter-population exchange
+ model, in a cluster of 16 nodes, each one with 16 Intel(R) Xeon(R) CPU E5520
+@2.27GHz processors, 16 GB RAM, Broadcom NetXtreme II BCM5716 1000Base-T (C0) PCI Express network cards, CentOS 6.8 and Java Version 1.8.0\_80.
+Islands have been first distributed among the nodes.
+That means that, for example, the run of 8 islands requires 8 different nodes, instead of the usage of the 8 processors of a single node.
 
@@
 This contradicts the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths.
-This can be explained because the added migration latency between nodes requires more time than the time saved during the crossover and migration.
+This can be explained because the added migration latency between nodes of the cluster requires more time than the time saved during the crossover and migration.
+This was not a problem in the mono-processor version, where the individuals shared the same memory space.
 

### 2016-12-13 hpmoon-coor.tex
Explained why NSGA2. Closes #5

--- 2016-11-18 hpmoon-fgcs.tex
@@
 In this paper we analyse several coevolutionary algorithms we have implemented by using a parallel multi-objective baseline algorithm (B) as a framework.
-Here, we have used the NSGA-II algorithm as the baseline algorithm.
+Our proposed methods are based in NSGA-II, as almost all the previous works discussed before \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}.
+Therefore, we have used a basic distributed NSGA-II algorithm without overlapping sections as the baseline (B).
 The population is distributed among $P$ islands.
@@
 different methods, being the transmission time between islands a
-relevant issue to address. Finally, new benchmarks and real problems
+relevant issue to address. Other MOEA algorithms available in the literature, such as SPEA or MOEA/D will be compared. Finally, new benchmarks and real problems
 will also be  used to validate this approach.
@@
 \bibliographystyle{elsarticle-num}
-
-\bibliography{hpmoon-fgcs}
-%\begin{thebibliography}{99}
-%\bibitem[Kopka and Daly(2003)]{R1}
-%Kopka~H and Daly~PW (2003) \textit{A Guide to \LaTeX}, 4th~edn.
-%Addison-Wesley.%
-
-%\bibitem[Lamport(1994)]{R2}
-%Lamport~L (1994) \textit{\LaTeX: a Document Preparation System},
-%2nd~edn. Addison-Wesley.%
-
-%\bibitem[Mittelbach and Goossens(2004)]{R3}
-%Mittelbach~F and Goossens~M (2004) \textit{The \LaTeX\ Companion},
-%2nd~edn. Addison-Wesley.%
-
-%\end{thebibliography}
+\bibliography{hpmoon-coor}
 

### 2016-12-13 hpmoon-coor.tex
Explaining the overlapped stuff. Closes #1

@@
 One of the most extended methods are the distributed co-evolutionary algorithms, where each processor deals only with a part of the decision space, that is, the individuals belonging to the same sub-population (island) explore the same subset of decision variables.
+These subsets are usually disjoint sets.
 
-In this paper, a new method to automatically adapt the overlapping sections of the individuals has been compared to other collaborative evolutionary methods.
+In our previous work we demonstrated that extending the length of these subsets, and therefore, sharing some search space between islands, implies an improvement in the results.
+In this paper, a new method to automatically adapt the size of the overlapping, or shared, sections of the individuals has been compared to other collaborative evolutionary techniques.
 Different number of islands, chromosome sizes and problems have been used.
@@
 
-In our preliminary work in \citep{Garcia16hpmoon} we tried to demonstrate that using overlapped sections of the chromosome in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time when the number of islands increases.
+In our preliminary work in \citep{Garcia16hpmoon} we tried to demonstrate that, instead focus every island in a disjoint subset of the chromosome, the usage of overlapped (shared) sections of the chromosome in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time when the number of islands increases.
 We discovered that the most adequate overlapping size may vary depending on a relation between the number of islands and the individual size.

### 2016-12-13 hpmoon-coor.tex
Some choices explained. Closes #2

@@
 In that work, the overlapped method ($c=1$) obtained better results when the number of islands were $>$8.
-So, we have used the formula $c=round(0.2*P-1)/2$ to calculate the extra sections to overlap.
+On the contrary, when the number of islands is small, no overlapping is necessary.
+So, we have used this knowledge to create the formula $c=round(0.2*P-1)/2$ to calculate the extra sections to overlap.
 Therefore, when $P=8$ then $c=0$ (equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so on.
@@
 
-These metrics have been used extensively, especially in some of the papers presented in Section 2.
+We have chosen those metrics because they have been used extensively, especially in some of the papers presented in Section 2 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous}.
 

### 2016-12-15 hpmoon-coor.tex
Added Antonio's paper and some SOA modifications. Closes #13

@@
 The hypothesis of this paper is that using overlapped sections of the chromosome, calculated depending the number of islands to use, in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time with respect to the baseline, disjoint and partly overlapped methods.
-To demonstrate this, a new overlapping islands scheme has been compared with a baseline version of a distributed NSGA-II \citep{Deb00NSGAII}, a coevolutionary disjoint section approach, and a fixed-size overlapped method.
+To demonstrate this, different overlapping islands schemes have been compared: a baseline version of a distributed NSGA-II \citep{Deb00NSGAII}, a coevolutionary disjoint section approach version of it, a fixed-size overlapped version and our new adaptive method.
 Different benchmarks problems and different large number of islands have been used.
@@
 
-The rest of the paper is organized as follows: after a background in parallelization in MOEAs, 
-the compared algorithms and the used methodology are presented in Section \ref{sec:coevo}.
-%PABLO: no puedo usar \ref{sec:met} porque la plantilla de esta revista no lo coge :/ (y además no tienen número)
-Then, the results of the experiments are shown (Section \ref{sec:res}), followed by conclusions and suggestions for future work lines.
+The rest of the paper is organized as follows: after the State of the Art in distributed and coevolutionary MOEAs, 
+the used methodology and the compared algorithms are described in Section \ref{sec:coevo}. 
+Then, the results of the experiments are presented (Section \ref{sec:res}), Finally, the conclusions and future work are discussed.
 
@@
 \citep{Deb03distributed} was one of the first approaches for distributed MOEAs (dMOEAs).
-In that work, the dominance of solutions was divided into the islands using a transformation of coordinates.
-Their authors concluded that dividing the search space is a good idea, but achieve this is not trivial.
-Other approaches for dividing the search space include objective separation in different processors \citep{Xiao03specialized}, or divide in two populations: one for elite and other search \citep{Wang09parallel}.
-Martens, in \citep{Martens13asynchronous} generated a Barabasi-Albert network as the island topology, and selection based on migrating individuals from a not-crowded area and acceptance based on diversity.
+In that work, the dominance of the solutions was divided into the islands using a coordinate transformation.
+Their authors concluded that dividing the search space is a good idea, although achieve this is not trivial.
+Dividing the search space has been explored by other researchers, for example, dividing the population in elite and search sub-populations \citep{Wang09parallel}, or separation in processors by objective \citep{Xiao03specialized}.
+Other authors, such as Martens \citep{Martens13asynchronous} use migration to accept individuals based on diversity, and migrating from not-crowded areas.
 
-More similar approaches to the one presented here were studied in the
-next two works, also using cooperative coevolution for high-dimensional problems. 
-Dorronsoro et al. \citep{Dorronsoro13superlinear} obtained super-linear performance
-in several instances using cooperative coevolution, focusing each island on a portion of the chromosome. However, in some instances the parallel version 
-improved the sequential version. Kimovski et al. \citep{Kimovski15Parallel} proposed a
-master-slave method that splits the population into several processors,
-each one running in parallel a MOEA that only affects some portion of
-the individuals. After a certain number of generations, the master
-process receives all the sub-populations to be combined. Different
-combination alternatives in this step are compared. Up to 8 processors
-were used in the experimental setup. Our approach in this paper does not
-broadcast all solutions to all islands for recombination, as previous
-works, but only one solution to a random island, needing less
-communication time. Besides, the maximum number of islands of
-Dorronsoro or Kimovsky approaches was 8, while in this paper we have
+Addressing high-dimensional problems with cooperative coevolution has also been studied in several works with approaches more similar to the one presented here.
+The approach to focus on a portion of the chromosome, as in our overlapped method, was firstly used in the work by Dorronsoro et al. \citep{Dorronsoro13superlinear}, obtaining super-linear performance
+in several instances. This approach has also been used by Kimovski et al. \citep{Kimovski15Parallel}, but using a
+master-slave method that splits the population into several processors. As in previous work, each node
+runs a parallel MOEA that only affects some portion of 
+the individuals and the master
+process receives all the sub-populations to be combined every certain number of generations. Up to 8 processors
+were used in the experimental setup, and several
+combination alternatives were compared. The main difference of our work with respect to previous works is that our approach does not 
+broadcast all solutions to all islands for recombination, but only one solution to a random island, needing less
+communication time. Moreover, Dorronsoro or Kimovsky approaches limited the maximum number of islands to 8, while in this paper we have
 used up to 128 islands.
 
-Lately, some researchers \citep{cheng2015adaptive} have focused on
-working on solution space, dividing the Pareto front in different
-clusters in order to model it. This {\em divide and conquer} approach
-is readily paralellizable and, in the sense of giving the
-responsibility of different parts of the search space to different
-modules, is similar to the one presented in this paper.
+Giving the responsibility of different parts of the search space to different modules, has also been explored lately by some researchers.
+For example, some authors focus on the solution space modeling the PF by dividing it in different clusters, allowing an easily parallelizable {\em divide and conquer} approach \citep{cheng2015adaptive}.
+Even other types of metaheuristics, such as the Multi-Objective Ant Colony Optimization (MOACO), can rely on island models to divide the search space depending on the node to achieve better results \cite{Mora13Moacos}.
 
 % ¿Se podría mencionar por algún lado el trabajo en algoritmos de
-% hormigas paralelos de Antonio? - JJ
+% hormigas paralelos de Antonio? - JJ Fergu: DONE
 In our previous work \citep{Garcia16hpmoon} we used some of
@@
 sections of the chromosome to use, depending on the number of
-islands. Moreover, previous experiments were performed on a single
+islands. Besides, previous experiments were performed on a single
 processor synchronous island model with a limited number of islands
@@
 
-As in the baseline, every certain number of generations, an individual is migrated to another random island.
+As in the baseline (B), an individual is migrated to another random island after a fixed number of generations.
 In the new island, this individual will be considered as one of the others in the island, crossed and mutated in the same way, depending on the island identifier.
@@
 \citep{Talbi08Parallel} all the islands deal with complete chromosomes for fitness calculation, so our approach can deal with no decomposable problems.
-The proposed methods  are as follows:
+The proposed methods for our experimental section are as follows:
 
@@
 
-Pseudo-code of the proposed algorithms is described in Algorithm \ref{fig:pseudo}.
+Pseudo-code of the proposed algorithms is described in Algorithm \ref{alg:EA}.
 
@@
 {\em Parameter Name} & {\em Value} \\ \hline
-Number of islands ($P$) & 8, 16, 32, 64 and 128 \\ \hline
-Chromosome size ($L$) & 512 and 2048 \\ \hline
-Execution time (s) & 25 (for 512) and 100 (for 2048) \\ \hline \hline
 Global population size ($N$) & 1024 \\ \hline
@@
 Mutation probability & 1/$L$ \\ \hline
+Individuals per migration & 1 \\ \hline
 Generations between migration & 5 \\ \hline
-Individuals per migration & 1 \\ \hline
 Selection for migration & Binary Tournament\\ \hline
-Runs per configuration & 30 \\ \hline
+Runs per configuration & 30 \\ \hline \hline
+Number of islands ($P$) & 8, 16, 32, 64 and 128 \\ \hline
+Chromosome size ($L$) & 512 and 2048 \\ \hline
+Execution time (s) & 25 (for 512) and 100 (for 2048) \\ \hline \hline
 \end{tabular}

### 2016-12-18 hpmoon-coor.tex
Spell check mainly to populate dictionary

@@
 the generated PFs in all runs are dominated by it. Metrics are then
-normalized with respect to that point. A Kruskall-Wallis significance
+normalized with respect to that point. A Kruskal-Wallis significance
 test has been performed to the metrics of all runs of the

### 2016-12-18 hpmoon-coor.tex
New title suggestion
Please @fergunet check it out.
Improving figure layout

@@
 
-\title{Parallel multi-objective optimization using co-evolutionary islands and search space overlapping}
+\title{Parallel multi-objective optimization using co-evolutionary
+  islands with overlapping search space}
+% New title suggestion
 
@@
 \begin{abstract}
-Multi-objective optimization methods have gained interest in the last years because the performance they can achieve solving real-world problems.
-Many of these problems usually require a high-dimensional decision space, and multi-objective Evolutionary Algorithms have been successfully used in the past.
-Due to the large computational cost these algorithms require, different parallelization and distribution methods have been proposed, with different parallel and distributed computer architectures to cope with them.
-One of the most extended methods are the distributed co-evolutionary algorithms, where each processor deals only with a part of the decision space, that is, the individuals belonging to the same sub-population (island) explore the same subset of decision variables.
-These subsets are usually disjoint sets.
-
-In our previous work we demonstrated that extending the length of these subsets, and therefore, sharing some search space between islands, implies an improvement in the results.
-In this paper, a new method to automatically adapt the size of the overlapping, or shared, sections of the individuals has been compared to other collaborative evolutionary techniques.
-Different number of islands, chromosome sizes and problems have been used.
-The analysis of the obtained experimental results, by using different metrics, shows that coevolutionary approaches can provide statistically significant improvements with respect to the base algorithm, being the method to automatically adapt the overlapping size the one to obtain the best performance during the same execution time.
-Results also show that the relation of the number of islands (subpopulations) to the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distribute the decision variables.
+  % First, state the problem!!!! - JJ
+Multi-objective optimization methods have gained interest in the last
+years because of the performance they can achieve solving real-world
+problems. Many of these problems usually require a high-dimensional
+decision space, and multi-objective Evolutionary Algorithms have been
+successfully used in the past. Due to the large computational cost
+these algorithms require, different parallelization and distribution
+methods have been proposed, with different parallel and distributed
+computer architectures to cope with them. One of the most extended
+methods are the distributed co-evolutionary algorithms, where each
+processor deals only with a part of the decision space, that is, the
+individuals belonging to the same sub-population (island) explore the
+same subset of decision variables. These subsets are usually disjoint
+sets. We have previously proved that extending the length of these
+subsets, and therefore, sharing some search space between islands,
+implies an improvement in the results. In this paper, a new method to
+automatically adapt the size of the overlapping, or shared, sections
+of the individuals has been compared to other collaborative
+evolutionary techniques. Different number of islands, chromosome sizes
+and problems have been used. The analysis of the obtained experimental
+results, by using different metrics, shows that coevolutionary
+approaches can provide statistically significant improvements with
+respect to the base algorithm, being the method to automatically adapt
+the overlapping size the one to obtain the best performance during the
+same execution time. Results also show that the relation of the number
+of islands (subpopulations) to the length of the chromosome (number of
+decision variables) is also a relevant factor to determine the most
+efficient alternative to distribute the decision variables. 
 \end{abstract}
@@
 
-Different approaches have been used to parallelize Evolutionary Algorithms (EAs), as each individual can be considered as an independent unit \citep{Alba13parallel}.
-Classic methods, such as the global parallel EAs (Master-Slave), or the spatially structured algorithms (Island model or Cellular EAs) have been applied successfully in the past \citep{Folino03cellular,Alba02Parallelism}.
-In the case of Multi-Objective Evolutionary Algorithms (MOEAs), these approaches \citep{Luna15Survey} need to deal with a whole solution set called Pareto Front (PFs).
-This imply to use different distribution and sharing mechanisms, as there exist a tension between the speedup achievable from parallelization and the need to globally recombine the results to accurately identify the PF \citep{Branke04Parallelizingcone}.
+%Introduction should start in the same way as the abstract. And
+%starting with something that is not really applicable here, talking
+%about general parallel evolutionary algorithms, is even worse - JJ
+Different approaches have been used to parallelize Evolutionary
+Algorithms (EAs), as each individual can be considered as an
+independent unit \citep{Alba13parallel}. Classic methods, such as the
+global parallel EAs (Master-Slave), or the spatially structured
+algorithms (Island model or Cellular EAs) have been applied
+successfully in the past \citep{Folino03cellular,Alba02Parallelism}.
+In the case of Multi-Objective Evolutionary Algorithms (MOEAs), these
+approaches \citep{Luna15Survey} need to deal with a whole solution set
+called Pareto Front (PFs). This imply to use different distribution
+and sharing mechanisms, as there exist a tension between the speedup
+achievable from parallelization and the need to globally recombine the
+results to accurately identify the PF
+\citep{Branke04Parallelizingcone}.
 
@@
 A high dimensional problem was used to compare these
-alternatives.
-In \citep{Dorronsoro13superlinear}, a distributed coevolutionary island model was used.
-Although in both previous works significant speedups were attained, only a low number of nodes were used (8).
-However, when increasing the number of islands, the division of each section of the chromosome becomes smaller, and the scalability may be affected by obtaining lower quality solutions in the same amount of time.
+alternatives. In \citep{Dorronsoro13superlinear}, a distributed
+coevolutionary island model was used.  Although in both previous works
+significant speedups were attained, only a low number of nodes were
+used (8). However, when increasing the number of islands, the division
+of each section of the chromosome becomes smaller, and the scalability
+may be affected by obtaining lower quality solutions in the same
+amount of time.
 
-In our preliminary work in \citep{Garcia16hpmoon} we tried to demonstrate that, instead focus every island in a disjoint subset of the chromosome, the usage of overlapped (shared) sections of the chromosome in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time when the number of islands increases.
-We discovered that the most adequate overlapping size may vary depending on a relation between the number of islands and the individual size.
-Moreover, the experiments were conducted in a mono-processor and synchronous island model.
-This motivates us to continue this research line, but this time, proposing a new method to automatically adapt the size of the overlapped sections, but also, performing all the experiments in a real cluster with up to 128 nodes, with extra number of islands.
+In our preliminary work \citep{Garcia16hpmoon} we tried to demonstrate
+% tried to or actually did it? What did we prove? 
+that,  instead of making every island focus in a disjoint subset of the
+chromosome, the usage of overlapped (shared) sections of the
+chromosome in a coevolutionary multi-objective island-based algorithm
+can improve the quality of the solutions in the same computing time
+when the number of islands increases. We discovered that the most
+adequate overlapping size may vary depending on a relation between the
+number of islands and the individual size. Moreover, the experiments
+were conducted in a mono-processor and synchronous island model. This
+motivates us to continue this research line; in this paper we propose
+a new method that automatically adapts the size of the overlapped
+sections. In order to test the validity of the method we have made
+tests in a real cluster
+with up to 128 nodes, with extra number of islands. % We have to
+                                % enphatize what is actually done. Is
+                                % this an addition to the old paper,
+                                % or a complete rewrite? - JJ
 
-The hypothesis of this paper is that using overlapped sections of the chromosome, calculated depending the number of islands to use, in a coevolutionary multi-objective island-based algorithm can improve the quality of the solutions in the same computing time with respect to the baseline, disjoint and partly overlapped methods.
-To demonstrate this, different overlapping islands schemes have been compared: a baseline version of a distributed NSGA-II \citep{Deb00NSGAII}, a coevolutionary disjoint section approach version of it, a fixed-size overlapped version and our new adaptive method.
-Different benchmarks problems and different large number of islands have been used.
-Results show that this new technique can improve different quality indicators in the same amount of time when the problem size is large.
+The hypothesis of this paper is that using overlapped sections of the
+chromosome, calculated depending the number of islands to use, in a
+coevolutionary multi-objective island-based algorithm can improve the
+quality of the solutions in the same computing time with respect to
+the baseline, disjoint and partly overlapped methods. %That was the
+                                %hypothesis of the previous
+                                %paper. This paper has a new
+                                %hypothesis, right? - JJ
+In order to prove this claim, our new adaptive method has been
+compared different overlapping islands schemes have been compared: a
+baseline version of a distributed NSGA-II \citep{Deb00NSGAII}, a
+coevolutionary disjoint section approach version of it and a
+fixed-size overlapped version. %What was done in the previous paper?
+                               %Are we re-using the results in that
+                               %paper? - JJ
+Different benchmark problems and different large number of islands
+have been used. Results show that this new technique can improve
+different quality indicators in the same amount of time when the
+problem size is large.  % Shouldn't this start with "We are trying to
+                        % prove..." - JJ
 
@@
 Figure \ref{fig:disjoint} describes this approach.
-
-\begin{figure*}
+%
+\begin{figure*}[h!tb]
 \centering
@@
 
-\begin{figure*}
+\begin{figure*}[h!tb]
 \centering
@@
 \subsection{Adaptive coevolution with overlapping islands (A)} 
-As in the previous method, the sections to address are overlapped, but instead using one extra section on each side of the $p$ section ($p+1$ and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$), being $c$ a value depending on the number of islands.
-As a first approach to automatically calculate this value the results shown in \citep{Garcia16hpmoon} have been used as a base to obtain $c$.
-In that work, the overlapped method ($c=1$) obtained better results when the number of islands were $>$8.
-On the contrary, when the number of islands is small, no overlapping is necessary.
-So, we have used this knowledge to create the formula $c=round(0.2*P-1)/2$ to calculate the extra sections to overlap.
-Therefore, when $P=8$ then $c=0$ (equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so on.
-Figure \ref{fig:adaptive} explains this method.
+As in the previous method, the sections to address are overlapped, but
+instead using one extra section on each side of the $p$ section ($p+1$
+and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$),
+being $c$ a value depending on the number of islands. As a first
+approach to automatically calculate this value the results shown in
+\citep{Garcia16hpmoon} have been used as a base to obtain $c$. In that
+work, the overlapped method ($c=1$) obtained better results when the
+number of islands were $>$8. On the contrary, when the number of
+islands is small, no overlapping is necessary. So, we have used this
+knowledge to create the formula $c=round(0.2*P-1)/2$ to calculate the
+extra sections to overlap. Therefore, when $P=8$ then $c=0$
+(equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so
+on. Figure \ref{fig:adaptive} explains this method.
 
-\begin{figure*}
+\begin{figure*}[h!tb]
 \centering

### 2016-12-18 hpmoon-coor.tex
A few changes and suggestions here and there

@@
 
+%This is not state of the art. If it's not an EC journal, it should go
+%to the introduction - JJ
 Evolutionary algorithms (EAs) \citep{DBLP:series/ncs/EibenS15,DeJong2006} are bio-inspired meta-heuristics that can be effectively used to find nearly optimal solutions for optimization problems.
@@
 
-Multi-objective optimization problems (MOP) are those where several objectives have to be simultaneously optimized \citep{Mora13paretobased}.
-Solving a MOP implies maximize or minimize a function composed of several cost functions (one per objective).
-In these problems the aim is to obtain a set of solutions that are better than the rest, considering all the objectives; this set is known as the Pareto Front.
-The solutions in this set are {\em non-dominated}, that is, none is better than the others for all the objectives.
-MOEAs are sub-set of EAs used to solve MOPs.
-One of the most well-known and referenced MOEAs \citep{Dorronsoro13superlinear} is the {\em Non-dominated Sorting Genetic Algorithm} (NSGA-II) \citep{Deb00NSGAII}.
-Classical genetic operators are applied to all the individuals, and divided into different ranks (based on the dominance) to be selected for the next generations.
+% Not EA either. It's an explanation of the techniques you are using,
+% thus Intro - JJ
+Multi-objective optimization problems (MOP) are those where several
+objectives have to be simultaneously optimized
+\citep{Mora13paretobased}. Solving a MOP implies maximize or minimize
+a function composed of several cost functions (one per objective). In
+these problems the aim is to obtain a set of solutions that are better
+than the rest, considering all the objectives; this set is known as
+the Pareto Front. The solutions in this set are {\em non-dominated},
+that is, none is better than the others for all the objectives. MOEAs
+are sub-set of EAs used to solve MOPs. One of the most well-known and
+referenced MOEAs \citep{Dorronsoro13superlinear} is the {\em
+  Non-dominated Sorting Genetic Algorithm} (NSGA-II)
+\citep{Deb00NSGAII}. Classical genetic operators are applied to all
+the individuals, and divided into different ranks (based on the
+dominance) to be selected for the next generations.
 
-Since the early 2000s, the distributed and parallel Evolutionary Algorithms have been used, mostly to take the most from systems such as clusters or grids \citep{Talbi08Parallel}.
-But in the case of MOEAs, the distribution and parallelization is not as direct as in single-objective EAs.
-This is because in different steps of the algorithm a whole set of dependent solutions, the Pareto Front, should be managed as a whole, spending time in gathering all individuals from the different processors or islands.
+Since the early 2000s distributed and parallel Evolutionary
+Algorithms have been used mostly to leverage systems such
+as clusters or grids \citep{Talbi08Parallel}, since a first-order
+approach to EA parallelization is as easy as dividing the population
+and add a simple communication mechanism among them. But in the case of
+MOEAs, the distribution and parallelization is not as direct as in
+single-objective EAs. This is because in different steps of the
+algorithm a whole set of dependent solutions, the Pareto Front, should
+be managed as a whole, spending time in gathering all individuals from
+the different processors or islands.
 
@@
 
-Giving the responsibility of different parts of the search space to different modules, has also been explored lately by some researchers.
-For example, some authors focus on the solution space modeling the PF by dividing it in different clusters, allowing an easily parallelizable {\em divide and conquer} approach \citep{cheng2015adaptive}.
-Even other types of metaheuristics, such as the Multi-Objective Ant Colony Optimization (MOACO), can rely on island models to divide the search space depending on the node to achieve better results \cite{Mora13Moacos}.
+Giving the responsibility of different parts of the search space to
+different modules, has also been explored lately by some
+researchers. For example, some authors focus on the solution space
+modeling the PF by dividing it in different clusters, allowing an
+easily parallelizable {\em divide and conquer} approach
+\citep{cheng2015adaptive}. Even other types of metaheuristics, such as
+the Multi-Objective Ant Colony Optimization (MOACO), can rely on
+island models to divide the search space depending on the node to
+achieve better results \cite{Mora13Moacos}.
 
-% ¿Se podría mencionar por algún lado el trabajo en algoritmos de
-% hormigas paralelos de Antonio? - JJ Fergu: DONE
 In our previous work \citep{Garcia16hpmoon} we used some of
@@
 
-In this paper we analyse several coevolutionary algorithms we have implemented by using a parallel multi-objective baseline algorithm (B) as a framework.
-Our proposed methods are based in NSGA-II, as almost all the previous works discussed before \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}.
-Therefore, we have used a basic distributed NSGA-II algorithm without overlapping sections as the baseline (B).
-The population is distributed among $P$ islands.
-After a fixed number of generations, one individual in a given island is migrated to another random island, thus avoiding to synchronize the global Pareto Front (PF) every certain number of generations as other methods described in Section 2 do.
-At the end of the run, the Pareto Fronts of all islands are aggregated into a new one, and the quality measures are evaluated.
-Different coevolutionary alternatives can be devised to evolve the subpopulations according to the decision space to be explored by each islands.
-Here we will consider three methods in which each island only performs crossover and mutation in specific sections of the individuals.
+In this paper we analyse several coevolutionary algorithms we have
+implemented by using a parallel multi-objective baseline algorithm (B)
+as a basis for comparisons. Our proposed methods %methods or method?
+                                %Which methods? - JJ
+are based in NSGA-II, as almost all the previous works discussed
+before
+\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}. % This is SoA stuff - JJ
+Therefore, we have used a basic distributed NSGA-II algorithm without
+overlapping sections as the baseline (B).
+
+%This probably should deserve a "Algorithm" environment too - JJ
+This basic distributed algorithms spreads the population among $P$
+islands; after a fixed number of generations,
+one individual in a given island is migrated to another random island,
+thus avoiding to synchronize the global Pareto Front (PF) every
+certain number of generations as other methods described in Section 2
+do. At the end of the run, the Pareto Fronts of all islands are
+aggregated into a new one, and the quality measures are evaluated. 
+Different coevolutionary alternatives can be devised to evolve the
+subpopulations according to the decision space to be explored by each
+islands. Here we will consider three methods in which each island only
+performs crossover and mutation in specific sections of the
+individuals.
 
@@
 
-The previously described four approaches have been run with two different chromosome lengths ($L$): 512 and 2048.
-Different number of islands ($P$) have also been compared: 8, 16, 32, 64 and 128.
-This maximum number of islands have also been  used in previous work in the literature \citep{Martens13asynchronous}.
-The crossover and mutation chosen, SBX and polynomial, have also been  used previously by other authors in \citep{Durillo08masterslave}.
+The previously described four approaches have been run with two
+different chromosome lengths ($L$): 512 and 2048. Different number of
+islands ($P$) have also been compared: 8, 16, 32, 64 and 128. This
+maximum number of islands have also been  used in previous work in the
+literature \citep{Martens13asynchronous}. The crossover and mutation
+chosen, SBX and polynomial, have also been  used previously by other
+authors in \citep{Durillo08masterslave}.  % SBX is first mentioned
+                                % here. Has to explain - JJ
 

### 2016-12-18 hpmoon-coor.tex
New papers for the state of the art
Please @fergunet check them out.

@@
 %starting with something that is not really applicable here, talking
-%about general parallel evolutionary algorithms, is even worse - JJ
+%about general parallel evolutionary algorithms, is even worse.
+% Right way (IMNSHO)
+% 1. Multiobjective problems are
+% 2. They usually require a good amount of computation → parallel
+% distributed
+% 3. One way to solve them is to use MOEAs _because_ they can be
+% easily parallelized
+% 4. But the easy paralellization is not necessarily efficient.
+% 5. We have proposed the HPMOON (or whatever) technique to improve
+% it. In paper (whatever) we proved that (whatever)
+% 6. In this paper we will be proving whatever - JJ
 Different approaches have been used to parallelize Evolutionary
@@
 approaches \citep{Luna15Survey} need to deal with a whole solution set
-called Pareto Front (PFs). This imply to use different distribution
+called Pareto Front (PF). This imply to use different distribution
 and sharing mechanisms, as there exist a tension between the speedup
@@
 dominance) to be selected for the next generations.
+
+% Parallel multiobjective optimization is the theme. And there are
+% papers that do that. Please include them in the state of the art:
+% dennis2003parallel (added to bibliography).
 

### 2016-12-18 hpmoon-coor.tex
I don't like "coevolutionary" or "adaptive"
It's simply partial evolution and variable. Why do you call it coevolutionary? Refs #12

@@
 % New title suggestion
+% Should coevolutionary go somewhere? Are they coevolutionary? - jj
 
@@
 alternatives. In \citep{Dorronsoro13superlinear}, a distributed
-coevolutionary island model was used.  Although in both previous works
+coevolutionary island model was used.  Although in both papers
 significant speedups were attained, only a low number of nodes were
-used (8). However, when increasing the number of islands, the division
+employed (8). However, when the number of islands is increased, the division
 of each section of the chromosome becomes smaller, and the scalability
@@
 with up to 128 nodes, with extra number of islands. % We have to
-                                % enphatize what is actually done. Is
+                                % emphasize what is actually done. Is
                                 % this an addition to the old paper,
@@
 
-\section{Coevolutionary algorithms compared}
+\section{Coevolutionary algorithms compared} % This should be called
+                                % methodology. The object of the
+                                % section is to explain the
+                                % methodology used to test the
+                                % problem, in order to do that we have
+                                % tested different versions that prove
+                                % that our methodology works for the
+                                % precise reasons we think it works- JJ
 \label{sec:coevo}
@@
 
-As in the baseline (B), an individual is migrated to another random island after a fixed number of generations.
-In the new island, this individual will be considered as one of the others in the island, crossed and mutated in the same way, depending on the island identifier.
-Note that, on the contrary of other works such as the ones described by Talbi et al.
-\citep{Talbi08Parallel} all the islands deal with complete chromosomes for fitness calculation, so our approach can deal with no decomposable problems.
-The proposed methods for our experimental section are as follows:
+As in the baseline (B), an individual is migrated to another random
+island after a fixed number of generations. In the new island, this
+individual will be considered as one of the others in the island,
+crossed and mutated in the same way, depending on the island
+identifier. Note that, differently from other works such as the ones
+described by Talbi et al. \citep{Talbi08Parallel} all the islands deal
+with complete chromosomes for fitness calculation, so our approach can
+deal with no decomposable problems. %Don't understand what you say
+                                %here. What you are saying is that our
+                                %approach can't deal with decomposable
+                                %problems, actually. - JJ
+
+The methods we have tested are presented in the next subsections.
 
 \subsection{Coevolution with disjoint islands (D)} 
-In this approach, each individual of size $L$ is split into $P$ chunks of size $L/P$.
-Every island $p$ only performs crossover and mutation on the $p_{th}$ part of the individuals.
-Figure \ref{fig:disjoint} describes this approach.
+In this approach, each individual of size $L$ is split into $P$ chunks
+of size $L/P$. Every island $p$ only performs crossover and mutation
+on the $p_{th}$ part of the individuals. Figure \ref{fig:disjoint}
+describes this approach.   
 %
@@
 and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$),
-being $c$ a value depending on the number of islands. As a first
+being $c$ a value depending on the number of islands.
+% That's not adaptive. It's simply variable - JJ
+As a first
 approach to automatically calculate this value the results shown in

### 2016-12-18 hpmoon-coor.tex
Wondering about coevolution
This goes to the correct #15 issue.

@@
 
-To solve this issue, some authors have proposed the usage of Master-Slave approaches.
+To solve this issue, some authors have proposed using Master-Slave approaches.
 For example,  \citep{Durillo08masterslave} compared different master-slave approaches: synchronous generational, asynchronous generational and asynchronous steady-state, being the latter the most promising option.
@@
 
+%This is an improvement over the previous? What is the relationship?
 The work by Deb et al.
@@
 
-Addressing high-dimensional problems with cooperative coevolution has also been studied in several works with approaches more similar to the one presented here.
-The approach to focus on a portion of the chromosome, as in our overlapped method, was firstly used in the work by Dorronsoro et al. \citep{Dorronsoro13superlinear}, obtaining super-linear performance
+% Is this really cooperative coevolution? - JJ
+Addressing high-dimensional problems with cooperative coevolution has
+also been studied in several works with approaches closer to the one
+presented here. The approach to focus on a portion of the chromosome,
+as in our overlapped method, was firstly used in the work by
+Dorronsoro et al. \citep{Dorronsoro13superlinear}, obtaining
+super-linear performance 
 in several instances. This approach has also been used by Kimovski et al. \citep{Kimovski15Parallel}, but using a

### 2017-01-10 hpmoon-coor.tex
Re-organizing introduction according @JJ 's proposed new order. Some of his comments STILL need to be adressed by me

@@
 % it. In paper (whatever) we proved that (whatever)
-% 6. In this paper we will be proving whatever - JJ
-Different approaches have been used to parallelize Evolutionary
-Algorithms (EAs), as each individual can be considered as an
+% 6. In this paper we will be proving whatever - JJ FERGU: Addressing JJ order
+
+%1. MOP ARE
+Multi-objective optimization problems (MOP) are those where several
+objectives have to be simultaneously optimized
+\citep{Mora13paretobased}. Solving a MOP implies maximize or minimize
+a function composed of several cost functions (one per objective). In
+these problems the aim is to obtain a set of solutions that are better
+than the rest, considering all the objectives; this set is known as
+the Pareto Front (PF). The solutions in this set are {\em non-dominated},
+that is, none is better than the others for all the objectives.
+
+%2 COMPUTATION -> PARALLEL
+These kind of problems require a high demand of computational time, and that is the reason why easily parallelizable methods to solve them have appeared \citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress}.
+%FERGU: TODO reescribir esta frase tan basura
+
+%3 ONE WAY IS TO USE MOEAS BECAUSE
+One example of easily parallelizable algorithms to solve MOPs are the Multi-Objective Evolutionary Algorithms (MOEAs), a sub-set of Evolutionary algorithms (EAs).
+EAs \citep{DBLP:series/ncs/EibenS15DeJong2006} are bio-inspired meta-heuristics that can be effectively used to find nearly optimal solutions for optimization problems.
+Usually an EA starts by generating a set of random solutions, called \emph{population}, following a user-defined description.
+Then, it evaluates each candidate solution, called \emph{individual}, assigning it a \emph{fitness} value, that describes how good the individual is, with regards to the target problem.
+New solutions are then generated by the application of \emph{operators} that either mutate a single solution or recombine different existing solutions.
+After each iteration, called \emph{generation}, the least fit individuals are removed, and the process continues until a user-defined stop condition is met.
+
+ One of the most well-known and referenced MOEAs \citep{Dorronsoro13superlinear} is the {\em
+  Non-dominated Sorting Genetic Algorithm} (NSGA-II)
+\citep{Deb00NSGAII}. Classical genetic operators are applied to all
+the individuals, and divided into different ranks (based on the
+dominance) to be selected for the next generations.
+
+%4 BUT THE EASY PARALLELIZATION IS NOT NECESSARILY EFFICIENT
+
+Different approaches have been used to parallelize EAs, as each individual can be considered as an
 independent unit \citep{Alba13parallel}. Classic methods, such as the
@@
 successfully in the past \citep{Folino03cellular,Alba02Parallelism}.
-In the case of Multi-Objective Evolutionary Algorithms (MOEAs), these
-approaches \citep{Luna15Survey} need to deal with a whole solution set
-called Pareto Front (PF). This imply to use different distribution
+However, in the case of MOEAs, these
+approaches \citep{Luna15Survey} need to deal with the whole solution set, the PF.
+ This imply to use different distribution
 and sharing mechanisms, as there exist a tension between the speedup
@@
 
-The application of MOEAs to solve real-world problems have gained attention in the last years \citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress}.
-These kind of problems requires a high number of variables, meaning that the EAs need to deal with large individuals and spent significant extra time for crossover, mutation and migration.
+MOPs usually require a high number of variables, meaning that the MOEAs need to deal with large individuals and spent significant extra time for crossover, mutation and migration.
 Different authors have proposed methods to divide the decision space (the chromosome) to improve the performance and solution quality.
@@
 amount of time.
+
+%5 WE HAVE PROPOSED HPMOON
 
@@
                                 % or a complete rewrite? - JJ
+
+%6 IN THIS PAPER WE WILL BE PROVING
 
@@
 \label{sec:soa}
-
-%This is not state of the art. If it's not an EC journal, it should go
-%to the introduction - JJ
-Evolutionary algorithms (EAs) \citep{DBLP:series/ncs/EibenS15,DeJong2006} are bio-inspired meta-heuristics that can be effectively used to find nearly optimal solutions for optimization problems.
-Usually an EA starts by generating a set of random solutions, called \emph{population}, following a user-defined description.
-Then, it evaluates each candidate solution, called \emph{individual}, assigning it a \emph{fitness} value, that describes how good the individual is, with regards to the target problem.
-New solutions are then generated by the application of \emph{operators} that either mutate a single solution or recombine different existing solutions.
-After each iteration, called \emph{generation}, the least fit individuals are removed, and the process continues until a user-defined stop condition is met.
-
-% Not EA either. It's an explanation of the techniques you are using,
-% thus Intro - JJ
-Multi-objective optimization problems (MOP) are those where several
-objectives have to be simultaneously optimized
-\citep{Mora13paretobased}. Solving a MOP implies maximize or minimize
-a function composed of several cost functions (one per objective). In
-these problems the aim is to obtain a set of solutions that are better
-than the rest, considering all the objectives; this set is known as
-the Pareto Front. The solutions in this set are {\em non-dominated},
-that is, none is better than the others for all the objectives. MOEAs
-are sub-set of EAs used to solve MOPs. One of the most well-known and
-referenced MOEAs \citep{Dorronsoro13superlinear} is the {\em
-  Non-dominated Sorting Genetic Algorithm} (NSGA-II)
-\citep{Deb00NSGAII}. Classical genetic operators are applied to all
-the individuals, and divided into different ranks (based on the
-dominance) to be selected for the next generations.
 

### 2017-02-10 hpmoon-coor.tex
Addressing more @JJ comments(not all of them). Also, a name to use instead cooperative-coevolutive is still needed

@@
 methods have been proposed, with different parallel and distributed
-computer architectures to cope with them. One of the most extended
+computer architectures to cope with them.
+
+One of the most extended
 methods are the distributed co-evolutionary algorithms, where each
@@
 subsets, and therefore, sharing some search space between islands,
-implies an improvement in the results. In this paper, a new method to
+implies an improvement in the results.
+
+In this paper, a new method to
 automatically adapt the size of the overlapping, or shared, sections
@@
 %2 COMPUTATION -> PARALLEL
-These kind of problems require a high demand of computational time, and that is the reason why easily parallelizable methods to solve them have appeared \citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress}.
-%FERGU: TODO reescribir esta frase tan basura
-
+These kind of problems require a high demand of computational time, leading to the apparition of easily parallelizable methods to solve them \citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress}.
 %3 ONE WAY IS TO USE MOEAS BECAUSE
 One example of easily parallelizable algorithms to solve MOPs are the Multi-Objective Evolutionary Algorithms (MOEAs), a sub-set of Evolutionary algorithms (EAs).
-EAs \citep{DBLP:series/ncs/EibenS15DeJong2006} are bio-inspired meta-heuristics that can be effectively used to find nearly optimal solutions for optimization problems.
+EAs \citep{DBLP:series/ncs/EibenS15} are bio-inspired meta-heuristics that can be effectively used to find nearly optimal solutions for optimization problems.
 Usually an EA starts by generating a set of random solutions, called \emph{population}, following a user-defined description.
@@
 After each iteration, called \emph{generation}, the least fit individuals are removed, and the process continues until a user-defined stop condition is met.
-
 One of the most well-known and referenced MOEAs \citep{Dorronsoro13superlinear} is the {\em
@@
 
-In our preliminary work \citep{Garcia16hpmoon} we tried to demonstrate
-% tried to or actually did it? What did we prove? 
+In our preliminary work \citep{Garcia16hpmoon} we proved
+% tried to or actually did it? What did we prove? FERGU: Done
 that,  instead of making every island focus in a disjoint subset of the
@@
 adequate overlapping size may vary depending on a relation between the
-number of islands and the individual size. Moreover, the experiments
-were conducted in a mono-processor and synchronous island model. This
-motivates us to continue this research line; in this paper we propose
+number of islands and the individual size. However, the experiments
+were conducted in a limited experimental system: mono-processor and synchronous island model. This
+motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more complete parameter setting.
+Besides comparing previous methods in this new experimental setup, in this paper we propose
 a new method that automatically adapts the size of the overlapped
-sections. In order to test the validity of the method we have made
-tests in a real cluster
-with up to 128 nodes, with extra number of islands. % We have to
+sections depending on the number of islands to use, comparing it with the previous versions. 
+% We have to
                                 % emphasize what is actually done. Is
                                 % this an addition to the old paper,
-                                % or a complete rewrite? - JJ
+                                % or a complete rewrite? - JJ FERGU: rewritten previous paragraph
 
@@
 chromosome, calculated depending the number of islands to use, in a
-coevolutionary multi-objective island-based algorithm can improve the
+coevolutionary multi-objective island-based algorithm, in a real computational environment, can improve the
 quality of the solutions in the same computing time with respect to
@@
                                 %paper. This paper has a new
-                                %hypothesis, right? - JJ
+                                %hypothesis, right? - JJ FERGU: no, this is the hypothesis of this paper (comparing adaptive with partly overlapped), but clarifying it
 In order to prove this claim, our new adaptive method has been
-compared different overlapping islands schemes have been compared: a
+compared against different overlapping islands schemes: a
 baseline version of a distributed NSGA-II \citep{Deb00NSGAII}, a
@@
                                %Are we re-using the results in that
-                               %paper? - JJ
+                               %paper? - JJ FERGU: explained before that we are showing new results.
 Different benchmark problems and different large number of islands
@@
 problem size is large.  % Shouldn't this start with "We are trying to
-                        % prove..." - JJ
+                        % prove..." - JJ FERGU: Already writed in previous paragraph
 
@@
 % dennis2003parallel (added to bibliography).
+FERGU: why this paper in particular?
+It parallelizes the fitness function steps and it is not multi-objective.
+It does not even describes the GA in detail.
 
@@
 
-%This is an improvement over the previous? What is the relationship?
+%This is an improvement over the previous? What is the relationship? FERGU: linked
+Other kind of approaches have also been explored.
 The work by Deb et al.
@@
 
-% Is this really cooperative coevolution? - JJ
+% Is this really cooperative coevolution? - JJ FERGU: You mean the Dorronsoro one? The title says it
 Addressing high-dimensional problems with cooperative coevolution has
@@
 
-\section{Coevolutionary algorithms compared} % This should be called
+\section{Methodology} % This should be called
                                 % methodology. The object of the
@@
                                 % that our methodology works for the
-                                % precise reasons we think it works- JJ
+                                % precise reasons we think it works- JJ FERGU: Done, and explained
 \label{sec:coevo}
+
+The objective of this section is to explain the methodology we have followed to
+compare the different versions of the overlapping schemes.
 
@@
 before
-\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}. % This is SoA stuff - JJ
+\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}.
+% This is SoA stuff - JJ FERGU: Yes, I added it here againg because a reviewer wasn't very attentive
 Therefore, we have used a basic distributed NSGA-II algorithm without
@@
 
-%This probably should deserve a "Algorithm" environment too - JJ
+%This probably should deserve a "Algorithm" environment too - JJ FERGU: You mean the LaTeX one? I've used it in the pseudocode figures
 This basic distributed algorithms spreads the population among $P$
@@
 with complete chromosomes for fitness calculation, so our approach can
-deal with no decomposable problems. %Don't understand what you say
+deal with decomposable and no decomposable problems. %Don't understand what you say
                                 %here. What you are saying is that our
                                 %approach can't deal with decomposable
-                                %problems, actually. - JJ
+                                %problems, actually. - JJ FERGU: you are right, fixed
 
@@
 being $c$ a value depending on the number of islands.
-% That's not adaptive. It's simply variable - JJ
+% That's not adaptive. It's simply variable - JJ FERGU: it depends on the number of islands. What term do you suggest?
 As a first

### 2017-05-17 hpmoon-coor.tex
Changed title and abstract to avoid the coevolutionary cooperative term

@@
 
-\title{Parallel multi-objective optimization using co-evolutionary
-  islands with overlapping search space}
+\title{Parallel multi-objective optimization using selective operation application
+  islands}
 % New title suggestion
 % Should coevolutionary go somewhere? Are they coevolutionary? - jj
+% PABLO: Renaming again to avoid using the coevolutionary and cooperative
 
@@
 individuals belonging to the same sub-population (island) explore the
-same subset of decision variables. These subsets are usually disjoint
-sets. We have previously proved that extending the length of these
-subsets, and therefore, sharing some search space between islands,
-implies an improvement in the results.
+same subset of decision variables. However, these methods only works with decomposable problems.
+
+A similar idea is presented here to deal with un-decomposable problems: 
+instead of sharing parts of individuals, each processor applies the variation 
+operators to a specific subset of the whole individual. We have previously proved 
+that extending the length of these subsets, and therefore, sharing some search 
+space between islands, implies an improvement in the results.
 
@@
 and problems have been used. The analysis of the obtained experimental
-results, by using different metrics, shows that coevolutionary
+results, by using different metrics, shows that selective operation application
 approaches can provide statistically significant improvements with
@@
 \begin{keyword}
-Multi-objective algorithms \sep coevolution \sep NSGA-II  \sep distributed evolutionary algorithms \sep Island model
+Multi-objective algorithms \sep NSGA-II  \sep distributed evolutionary algorithms \sep Island model
 \end{keyword}

### 2017-06-07 hpmoon-coor.tex
Removed all references to cooperative coevolutionary in our method. Closes #15

@@
 % New title suggestion
-% Should coevolutionary go somewhere? Are they coevolutionary? - jj
-% PABLO: Renaming again to avoid using the coevolutionary and cooperative
+% Should co-evolutionary go somewhere? Are they co-evolutionary? - jj
+% PABLO: Renaming again to avoid using the co-evolutionary and cooperative
 
@@
 
-A similar idea is presented here to deal with un-decomposable problems: 
+A similar idea is presented here to deal with un-decomposable problems, the selective operation application:
 instead of sharing parts of individuals, each processor applies the variation 
@@
 alternatives. In \citep{Dorronsoro13superlinear}, a distributed
-coevolutionary island model was used.  Although in both papers
+co-evolutionary island model was used.  Although in both papers
 significant speedups were attained, only a low number of nodes were
@@
 
+A similar approach used to solve this kind of problems is the {\em selective operation application}.
+In this case, each island deals with the whole chromosome, but only focuses in a fragment of it in the crossover and mutation phase, using the whole chromosome for fitness calculation.
+This allows to deal with un-decomposable problems.
 In our preliminary work \citep{Garcia16hpmoon} we proved
 % tried to or actually did it? What did we prove? FERGU: Done
-that,  instead of making every island focus in a disjoint subset of the
+that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time in a multi-objective island-based algorithm.
+Moreover, instead of making every island focus in a disjoint subset of the
 chromosome, the usage of overlapped (shared) sections of the
-chromosome in a coevolutionary multi-objective island-based algorithm
-can improve the quality of the solutions in the same computing time
+chromosome 
+can improve the quality of the solutions 
 when the number of islands increases. We discovered that the most
@@
 The hypothesis of this paper is that using overlapped sections of the
-chromosome, calculated depending the number of islands to use, in a
-coevolutionary multi-objective island-based algorithm, in a real computational environment, can improve the
+chromosome for the selective operation application, calculated depending the number of islands to use, in a
+multi-objective island-based algorithm, in a real computational environment, can improve the
 quality of the solutions in the same computing time with respect to
@@
 baseline version of a distributed NSGA-II \citep{Deb00NSGAII}, a
-coevolutionary disjoint section approach version of it and a
+selective operation application version with disjoint sections and a
 fixed-size overlapped version. %What was done in the previous paper?
@@
 
-The rest of the paper is organized as follows: after the State of the Art in distributed and coevolutionary MOEAs, 
-the used methodology and the compared algorithms are described in Section \ref{sec:coevo}. 
+The rest of the paper is organized as follows: after the State of the Art in distributed and co-evolutionary MOEAs, 
+the used methodology and the compared algorithms are described in Section \ref{sec:co-evo}. 
 Then, the results of the experiments are presented (Section \ref{sec:res}), Finally, the conclusions and future work are discussed.
@@
 
-% Is this really cooperative coevolution? - JJ FERGU: You mean the Dorronsoro one? The title says it
-Addressing high-dimensional problems with cooperative coevolution has
+% Is this really cooperative co-evolution? - JJ FERGU: You mean the Dorronsoro one? The title says it
+Addressing high-dimensional problems with cooperative co-evolution has
 also been studied in several works with approaches closer to the one
@@
 In our previous work \citep{Garcia16hpmoon} we used some of
-the aforementioned ideas to compare two co-evolutionary dMOEAs. The first
+the aforementioned ideas to compare two different dMOEAs. The first
 one divided the chromosome in $P$ sections, being $P$ the number of
 islands. Every island $p$ only performed the mutation and crossover in
-that part ($p_{th}$) of the chromosome, while the fitness was
+that part ($p_{th}$) of the chromosome (the selective operation application), while the fitness was
 calculated using the whole individual. After a certain number of
@@
 performance metrics were calculated at the end of the run. The second
-method, coevolution with overlapping islands, used the $p_{th-1}$ and
+method, selective operation application with overlapping islands, used the $p_{th-1}$ and
 $p_{th+1}$ sections of each chromosome, besides the $p_{th}$
@@
                                 % precise reasons we think it works- JJ FERGU: Done, and explained
-\label{sec:coevo}
+\label{sec:co-evo}
 
@@
 
-In this paper we analyse several coevolutionary algorithms we have
+In this paper we analyse several selective operation application algorithms we have
 implemented by using a parallel multi-objective baseline algorithm (B)
@@
 aggregated into a new one, and the quality measures are evaluated. 
-Different coevolutionary alternatives can be devised to evolve the
+Different  selective operation application alternatives can be devised to evolve the
 subpopulations according to the decision space to be explored by each
@@
 %% And some liaison to next subsection - JJ
-%This method will be compared to different coevolutionary approaches that are similar to the baseline, with the exception on the decision space to explore in each island.
-%Three different coevolutionary methods have been used. In all these methods, each island only performs crossover and mutation in specific sections of the individuals.
+%This method will be compared to different co-evolutionary approaches that are similar to the baseline, with the exception on the decision space to explore in each island.
+%Three different co-evolutionary methods have been used. In all these methods, each island only performs crossover and mutation in specific sections of the individuals.
 
@@
 
-\subsection{Coevolution with disjoint islands (D)} 
+\subsection{Selective operation application with disjoint islands (D)} 
 In this approach, each individual of size $L$ is split into $P$ chunks
@@
 
-\subsection{Coevolution with overlapping islands (O)}
+\subsection{Selective operation application with overlapping islands (O)}
 This approach is similar to the previous one, but every island also uses the $p+1$ and $p-1$ (module size) chunks of the individual for crossover and migration.
@@
 
-\subsection{Adaptive coevolution with overlapping islands (A)} 
+\subsection{Adaptive selective operation application with overlapping islands (A)} 
 As in the previous method, the sections to address are overlapped, but
@@
 With both chromosome lengths, increasing the number of islands implies more generations with all the methods (logically, as there are less individuals in each island).
-But also, the co-evolutionary methods approach to the number of generations with the baseline when increasing the number of islands.
+But also, the selective operation application methods approach to the number of generations with the baseline when increasing the number of islands.
 However, with $L=2048$ the migration time is enough big to almost not improve the number of generations with respect to the baseline, even in the lower number of islands, as it happens with $L=512$.
@@
 This is consistent with the claim by Dorronsoro et al.
-\citep{Dorronsoro13superlinear}, who found that cooperative coevolutionary MOEAs work better on bigger populations (more than 100 individuals).
+\citep{Dorronsoro13superlinear}, who found that cooperative co-evolutionary MOEAs work better on bigger populations (more than 100 individuals).
 
@@
 
-High-performance problems % problems are not high-performance. They
-                          % _require_ high performance
- that require a large number of decision variables can leverage the
+Problems that require high-performance % problems are not high-performance. They
+                          % _require_ high performance Fergu: done
+ and deal with a large number of decision variables can leverage the
  division of the decision space that parallel and distributed
- algorithms imply. This can be done in dMOEAs by dividing the
+ algorithms imply. This can be done in dMOEAs by selective operation application, that is, dividing the
  chromosome into different parts, each one modified by a different

### 2017-06-13 hpmoon-coor.tex
Revises bibliography
And eliminates duplicates reference.

@@
 % Should co-evolutionary go somewhere? Are they co-evolutionary? - jj
-% PABLO: Renaming again to avoid using the co-evolutionary and cooperative
+% PABLO: Renaming again to avoid using the co-evolutionary and
+% cooperative
+% Ok - JJ
 
@@
 island models to divide the search space depending on the node to
-achieve better results \cite{Mora13Moacos}.
+achieve better results \cite{Mora13paretobased}.
 

### 2017-06-13 hpmoon-coor.tex
Some comments here and there
And some comments not addressed so far. Please @fergunet take a look
at them.

@@
 %EXPLANATION OF THE RESULTS
-This can be explained comparing the number of non-dominated solutions in each island and the average number of generations (Table \ref{tab:sols512} and Table \ref{tab:sols2048}).
-With both chromosome lengths, increasing the number of islands implies more generations with all the methods (logically, as there are less individuals in each island).
-But also, the selective operation application methods approach to the number of generations with the baseline when increasing the number of islands.
-However, with $L=2048$ the migration time is enough big to almost not improve the number of generations with respect to the baseline, even in the lower number of islands, as it happens with $L=512$.
-Therefore, more generations do not necessarily improve the solution of the global PF, but focusing on different elements of the chromosome.
-As indicated previously, every island is unaware of the other islands PFs, and they are trying to optimize their solutions independently.
-With respect to the average number of solutions in each island, there is a clear difference in number with the baseline with $L=512$, where this value is in the most of the cases, less than a half.
-The number of non-dominated solutions also improves a better Spread indicator, where the baseline almost always obtains better values %TENGO QUE COMENTAR MAS LOS RESULTADOS Y ENTENDERLO TODO Y JUSTIFICARLO FINAMENTE
+This can be explained comparing the number of non-dominated solutions
+in each island and the average number of generations (Table
+\ref{tab:sols512} and Table \ref{tab:sols2048}). With both chromosome
+lengths, increasing the number of islands implies more generations
+with all the methods (logically, as there are less individuals in each
+island). But also, the selective operation application methods
+approach to the number of generations with the baseline when
+increasing the number of islands. However, with $L=2048$ the migration
+time is enough big to almost not improve the number of generations
+with respect to the baseline, even in the lower number of islands, as
+it happens with $L=512$. Therefore, more generations do not
+necessarily improve the solution of the global PF, but focusing on
+different elements of the chromosome. As indicated previously, every
+island is unaware of the other islands PFs, and they are trying to
+optimize their solutions independently. With respect to the average
+number of solutions in each island, there is a clear difference in
+number with the baseline with $L=512$, where this value is in the most
+of the cases, less than a half. The number of non-dominated solutions
+also improves a better Spread indicator, where the baseline almost
+always obtains better values. %TENGO QUE COMENTAR MAS LOS RESULTADOS Y
+                              %ENTENDERLO TODO Y JUSTIFICARLO
+                              %FINAMENTE
+%Almost always no es muy preciso - JJ
 
-Finally, as happened in \citep{Garcia16hpmoon}, results show that all the quality indicators decrease when the number of islands is increased, as the  sizes of the subpopulations are smaller.
+Finally, as was already observed in \citep{Garcia16hpmoon}, results
+show that all the quality indicators decrease in value when the number of islands is increased, as the  sizes of the subpopulations are smaller.
 This is consistent with the claim by Dorronsoro et al.
@@
 % performance really needed? - JJ
+% STILL more discussion should be needed. For instance, the last
+% paragraph of results begs an explanation of the influence of diversity on
+% results - JJ
 

### 2017-06-22 hpmoon-coor.tex
Addressing Jesus and @JJ suggestions, but others are still pending

@@
 
-\title{Parallel multi-objective optimization using selective operation application
+\title{Parallel multi-objective optimization using selective operator application
   islands}
@@
 \begin{abstract}
-  % First, state the problem!!!! - JJ
+  % First, state the problem!!!! - JJ Pablo: ok!
+Real-world optimization problems usually require to deal with several objectives.
 Multi-objective optimization methods have gained interest in the last
-years because of the performance they can achieve solving real-world
-problems. Many of these problems usually require a high-dimensional
+years because of the performance they can achieve solving this kind of problems. 
+Many of them usually require a high-dimensional
 decision space, and multi-objective Evolutionary Algorithms have been
@@
 
-A similar idea is presented here to deal with un-decomposable problems, the selective operation application:
+A similar idea is presented here to deal with un-decomposable problems, the selective operator application:
 instead of sharing parts of individuals, each processor applies the variation 
@@
 In this paper, a new method to
-automatically adapt the size of the overlapping, or shared, sections
+automatically adapt the size of the overlapping, or shared sections,
 of the individuals has been compared to other collaborative
@@
 and problems have been used. The analysis of the obtained experimental
-results, by using different metrics, shows that selective operation application
+results, by using different metrics, shows that selective operator application
 approaches can provide statistically significant improvements with
@@
 objectives have to be simultaneously optimized
-\citep{Mora13paretobased}. Solving a MOP implies maximize or minimize
+\citep{Mora13paretobased}. Solving a MOP implies maximizing or minimizing
 a function composed of several cost functions (one per objective). In
@@
 Usually an EA starts by generating a set of random solutions, called \emph{population}, following a user-defined description.
-Then, it evaluates each candidate solution, called \emph{individual}, assigning it a \emph{fitness} value, that describes how good the individual is, with regards to the target problem.
+Then, it evaluates each candidate solution, called \emph{individual}, assigning it a \emph{fitness} value, that describes how good the individual is, with regard to the target problem.
 New solutions are then generated by the application of \emph{operators} that either mutate a single solution or recombine different existing solutions.
@@
 
-MOPs usually require a high number of variables, meaning that the MOEAs need to deal with large individuals and spent significant extra time for crossover, mutation and migration.
+MOPs usually require a high number of variables, meaning that the MOEAs need to deal with large individuals and spend significant extra time for crossover, mutation and migration.
 Different authors have proposed methods to divide the decision space (the chromosome) to improve the performance and solution quality.
@@
 
-A similar approach used to solve this kind of problems is the {\em selective operation application}.
-In this case, each island deals with the whole chromosome, but only focuses in a fragment of it in the crossover and mutation phase, using the whole chromosome for fitness calculation.
+A similar approach used to solve this kind of problems is the {\em selective operator application} (SLA).
+In this case, each island deals with the whole chromosome, but only modifies a fragment of it in the crossover and mutation phase depending on the number of islands, using the whole chromosome for fitness calculation.
 This allows to deal with un-decomposable problems.
-In our preliminary work \citep{Garcia16hpmoon} we proved
-% tried to or actually did it? What did we prove? FERGU: Done
-that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time in a multi-objective island-based algorithm.
-Moreover, instead of making every island focus in a disjoint subset of the
+In our preliminary work \citep{Garcia16hpmoon} we used this method in a preliminary experimental setup, although it is worth mentioning we are establishing its name and acronym in this paper for the first time.
+We proved
+that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
+Moreover, instead of making every island focus on a disjoint subset of the
 chromosome, the usage of overlapped (shared) sections of the
@@
 can improve the quality of the solutions 
-when the number of islands increases. We discovered that the most
+when the number of islands is increased. We discovered that the most
 adequate overlapping size may vary depending on a relation between the
@@
 a new method that automatically adapts the size of the overlapped
-sections depending on the number of islands to use, comparing it with the previous versions. 
+sections depending on the number of available islands, comparing it with previous versions. 
 % We have to
@@
 The hypothesis of this paper is that using overlapped sections of the
-chromosome for the selective operation application, calculated depending the number of islands to use, in a
+chromosome for the SLA, and obtaining the number of sections automatically from the number of available islands, in a
 multi-objective island-based algorithm, in a real computational environment, can improve the
@@
 baseline version of a distributed NSGA-II \citep{Deb00NSGAII}, a
-selective operation application version with disjoint sections and a
+SLA version with disjoint sections and a SLA
 fixed-size overlapped version. %What was done in the previous paper?
@@
 In that work, the dominance of the solutions was divided into the islands using a coordinate transformation.
-Their authors concluded that dividing the search space is a good idea, although achieve this is not trivial.
-Dividing the search space has been explored by other researchers, for example, dividing the population in elite and search sub-populations \citep{Wang09parallel}, or separation in processors by objective \citep{Xiao03specialized}.
+Their authors concluded that dividing the search space is a good idea, although achieving this is not trivial.
+The division of the search space has been explored by other researchers, for example, dividing the population in elite and search sub-populations \citep{Wang09parallel}, or separation in processors by objective \citep{Xiao03specialized}.
 Other authors, such as Martens \citep{Martens13asynchronous} use migration to accept individuals based on diversity, and migrating from not-crowded areas.
@@
 islands. Every island $p$ only performed the mutation and crossover in
-that part ($p_{th}$) of the chromosome (the selective operation application), while the fitness was
+that part ($p_{th}$) of the chromosome (the selective operator application), while the fitness was
 calculated using the whole individual. After a certain number of
@@
 performance metrics were calculated at the end of the run. The second
-method, selective operation application with overlapping islands, used the $p_{th-1}$ and
+method, selective operator application with overlapping islands, used the $p_{th-1}$ and
 $p_{th+1}$ sections of each chromosome, besides the $p_{th}$
@@
 sections of the individuals and the number of islands used. This
-motivates us to find a new adaptive method to select this number of
+motivated us to find a new adaptive method to select this number of
 sections of the chromosome to use, depending on the number of
@@
 cluster. Therefore, at the same time we are proposing an adaptive
-method to divide the individual search space, we are validating the
+method to divide the individual search space, and also validating the
 previous methods.
@@
 
-In this paper we analyse several selective operation application algorithms we have
-implemented by using a parallel multi-objective baseline algorithm (B)
-as a basis for comparisons. Our proposed methods %methods or method?
-                                %Which methods? - JJ
-are based in NSGA-II, as almost all the previous works discussed
+In this paper we analyse several SLA algorithms we have
+implemented by using a parallel multi-objective baseline algorithm
+as a basis for comparisons. Our proposed methods, using different overlapping schemes, %methods or method?
+                                %Which methods? - JJ Fergu: clarifying
+are based on NSGA-II, as almost all the previous works discussed
 before
@@
 %This probably should deserve a "Algorithm" environment too - JJ FERGU: You mean the LaTeX one? I've used it in the pseudocode figures
-This basic distributed algorithms spreads the population among $P$
+This basic distributed algorithms spread the population among $P$
 islands; after a fixed number of generations,
@@
 aggregated into a new one, and the quality measures are evaluated. 
-Different  selective operation application alternatives can be devised to evolve the
+Different  SLA alternatives can be devised to evolve the
 subpopulations according to the decision space to be explored by each
@@
 
-\subsection{Selective operation application with disjoint islands (D)} 
+\subsection{SLA with disjoint islands (D)} 
 In this approach, each individual of size $L$ is split into $P$ chunks
@@
 \includegraphics[width=12cm]{islandDisjoint.jpg}
-\caption{Disjoint algorithm: every island $p$ only modifies the $p_{th}$ components (in grey) of the individuals.}
+\caption{SLA with disjoint islands (D): every island $p$ only modifies the $p_{th}$ components (in grey) of the individuals.}
 \label{fig:disjoint}
@@
 
-\subsection{Selective operation application with overlapping islands (O)}
+\subsection{SLA with overlapping islands (O)}
 This approach is similar to the previous one, but every island also uses the $p+1$ and $p-1$ (module size) chunks of the individual for crossover and migration.
@@
 \includegraphics[width=12cm]{islandNoDisjoint.jpg}
-\caption{Overlapping algorithm: every island $p$ modifies the  $p+1$,
+\caption{SLA with overlapping islands (O): every island $p$ modifies the  $p+1$,
   $p_{th}$ and $p-1$  components (in grey) of the individuals.}
@@
 
-\subsection{Adaptive selective operation application with overlapping islands (A)} 
+\subsection{Adaptive SLA with overlapping islands (A)} 
 As in the previous method, the sections to address are overlapped, but
@@
 As a first
-approach to automatically calculate this value the results shown in
+approach to automatically calculate this value, the results shown in
 \citep{Garcia16hpmoon} have been used as a base to obtain $c$. In that
@@
 (equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so
-on. Figure \ref{fig:adaptive} explains this method.
+on. As mentioned, this is only a first approach to obtain $c$, and future work will study new methods to calculate it. Figure \ref{fig:adaptive} explains this method.
 
@@
 \includegraphics[width=12cm]{islandAdaptive.jpg}
-\caption{Adaptive overlapping algorithm: every island $p$ modifies the  $p+c$,
+\caption{Adaptive SLA with overlapping islands (A): every island $p$ modifies the  $p+c$,
   $p_{th}$ and $p-c$  components (in grey) of the individuals. $c$ is calculated depending on the number of islands. In this case, $c=2$.}
@@
 \begin{itemize}
-\item Hypervolume (HV): measures the area formed by all non-dominated solutions found with, respect to a reference point.
+\item Hypervolume (HV): measures the area formed by all non-dominated solutions found with respect to a reference point.
 Higher values imply better quality of the PF.
@@
 with all the methods (logically, as there are less individuals in each
-island). But also, the selective operation application methods
+island). But also, the SLA methods
 approach to the number of generations with the baseline when
@@
  division of the decision space that parallel and distributed
- algorithms imply. This can be done in dMOEAs by selective operation application, that is, dividing the
+ algorithms imply. This can be done in dMOEAs by selective operator application (SLA), that is, dividing the
  chromosome into different parts, each one modified by a different

### 2017-07-03 hpmoon-coor.tex
Addressing more changes by jesus, julio and @jj

@@
   % First, state the problem!!!! - JJ Pablo: ok!
-Real-world optimization problems usually require to deal with several objectives.
-Multi-objective optimization methods have gained interest in the last
-years because of the performance they can achieve solving this kind of problems. 
-Many of them usually require a high-dimensional
-decision space, and multi-objective Evolutionary Algorithms have been
-successfully used in the past. Due to the large computational cost
-these algorithms require, different parallelization and distribution
-methods have been proposed, with different parallel and distributed
-computer architectures to cope with them.
+%Real-world optimization problems usually require to deal with several objectives.
+%Multi-objective optimization methods have gained interest in the last
+%years because of the performance they can achieve solving this kind of problems. 
+%Many of them usually require a high-dimensional
+%decision space, and multi-objective Evolutionary Algorithms have been
+%successfully used in the past. Due to the large computational cost
+%these algorithms require, different parallelization and distribution
+%methods have been proposed, with different parallel and distributed
+%computer architectures to cope with them.
 
 One of the most extended
-methods are the distributed co-evolutionary algorithms, where each
+methods to deal with high-dimensional multi-objective optimization problems are the distributed co-evolutionary algorithms. In these methods each
 processor deals only with a part of the decision space, that is, the
 individuals belonging to the same sub-population (island) explore the
-same subset of decision variables. However, these methods only works with decomposable problems.
+same subset of decision variables. However, only decomposable problems could be strictly implemented in parallel this way. %these methods only works with decomposable problems.
 
-A similar idea is presented here to deal with un-decomposable problems, the selective operator application:
+A new approach is presented here to deal with un-decomposable problems, the selective operator application:
 instead of sharing parts of individuals, each processor applies the variation 
@@
 and problems have been used. The analysis of the obtained experimental
-results, by using different metrics, shows that selective operator application
-approaches can provide statistically significant improvements with
-respect to the base algorithm, being the method to automatically adapt
-the overlapping size the one to obtain the best performance during the
-same execution time. Results also show that the relation of the number
-of islands (subpopulations) to the length of the chromosome (number of
+results, by using different metrics, shows that our approach can provide statistically significant improvements with
+respect to the base algorithm.%, being the method to automatically adapt
+%the overlapping size the one to obtain the best performance during the
+%same execution time. 
+ Results also show that the relation between the number
+of islands (subpopulations) and the length of the chromosome (number of
 decision variables) is also a relevant factor to determine the most
@@
 %2 COMPUTATION -> PARALLEL
-These kind of problems require a high demand of computational time, leading to the apparition of easily parallelizable methods to solve them \citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress}.
+These kind of problems implies a high demand of computational time, leading to the apparition of easily parallelizable methods to solve them \citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress}.
 %3 ONE WAY IS TO USE MOEAS BECAUSE
@@
 approaches \citep{Luna15Survey} need to deal with the whole solution set, the PF.
- This imply to use different distribution
-and sharing mechanisms, as there exist a tension between the speedup
+ This implies to use different distribution
+and sharing mechanisms, as there exist a tradeoff between the speedup
 achievable from parallelization and the need to globally recombine the
@@
 Different authors have proposed methods to divide the decision space (the chromosome) to improve the performance and solution quality.
-In this aspect, the co-evolution model is a dimension-distributed model where a high-dimensional problem is divided into lower dimensional problems \citep{Gong15models,Tonda12cooperative}, and evolved separately.
+In this aspect, the co-evolution model is a dimension-distributed model where a high-dimensional problem is divided into lower dimensional ones \citep{Gong15models,Tonda12cooperative}, and evolved separately.
 One example of application of this technique was described in \citep{Kimovski15Parallel}.
@@
 
-The hypothesis of this paper is that using overlapped sections of the
-chromosome for the SLA, and obtaining the number of sections automatically from the number of available islands, in a
-multi-objective island-based algorithm, in a real computational environment, can improve the
+The hypothesis of this paper is that the use of automatically calculated overlapped sections of the
+chromosome for the SLA, can improve the
 quality of the solutions in the same computing time with respect to
-the baseline, disjoint and partly overlapped methods. %That was the
+the baseline, disjoint and partly overlapped methods. 
+These overlapped sections are calculated from the number of available islands, in a
+multi-objective island-based algorithm, and tested in a real computational environment.
+
+%That was the
                                 %hypothesis of the previous
@@
 in several instances. This approach has also been used by Kimovski et al. \citep{Kimovski15Parallel}, but using a
-master-slave method that splits the population into several processors. As in previous work, each node
+master-slave method that splits the population into several processors. As in previous works, each node
 runs a parallel MOEA that only affects some portion of 
@@
 the aforementioned ideas to compare two different dMOEAs. The first
-one divided the chromosome in $P$ sections, being $P$ the number of
+one divided the chromosome into $P$ sections, being $P$ the number of
 islands. Every island $p$ only performed the mutation and crossover in
@@
 (8, 32 and 128). In this paper,  8, 16, 32, 64 and 128 islands have
-been used, and this time, the experiments have been run on a real
+been used, and this time, the experiments have been run on a parallel
 cluster. Therefore, at the same time we are proposing an adaptive
@@
 %This probably should deserve a "Algorithm" environment too - JJ FERGU: You mean the LaTeX one? I've used it in the pseudocode figures
-This basic distributed algorithms spread the population among $P$
+This basic distributed algorithm spreads the population among $P$
 islands; after a fixed number of generations,
@@
 compare different times and quality of solutions at the same time.
+ The whole parameter set is summarized in Table \ref{tab:parameters}.
 
@@
 
-Different metrics, explained in the previous section, have been used
+Different metrics, previously explained, have been used
 to calculate the quality of the obtained PFs in each configuration. As
@@
 the results of A are equivalent to the obtained with D (because
-$c=0$), and when $P=16$ they are equivalent to O ($c=1$).
+$c=0$), and when $P=16$ they are equivalent to O ($c=1$). We refer this equivalence with the word {\em Equiv.} in tables.
 
@@
 Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than the obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply these methods.
-This contradicts the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths.
+A contradictions arises with respect to the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths.
 This can be explained because the added migration latency between nodes of the cluster requires more time than the time saved during the crossover and migration.
@@
 increasing the number of islands. However, with $L=2048$ the migration
-time is enough big to almost not improve the number of generations
+time is big enough  to not improve the number of generations
 with respect to the baseline, even in the lower number of islands, as
@@
 optimize their solutions independently. With respect to the average
-number of solutions in each island, there is a clear difference in
-number with the baseline with $L=512$, where this value is in the most
+number of solutions in each island, there is a clear difference 
+ with the baseline with $L=512$, where this value is in the most
 of the cases, less than a half. The number of non-dominated solutions
-also improves a better Spread indicator, where the baseline almost
-always obtains better values. %TENGO QUE COMENTAR MAS LOS RESULTADOS Y
+also implies a better Spread indicator, where the baseline 
+ obtains better (or not significantly different) values in the majority of the compared configurations. %TENGO QUE COMENTAR MAS LOS RESULTADOS Y
                               %ENTENDERLO TODO Y JUSTIFICARLO
                               %FINAMENTE
-%Almost always no es muy preciso - JJ
+%Almost always no es muy preciso - JJ Pablo: arreglao
 
@@
  these methods can achieve better quality metrics than the baseline in
- the same amount of time, with larger chromosome lengths.
+ the same amount of time, with large chromosome lengths.
 
@@
 more types of problems, and new configurations of population size and
-chromosome lengths will be addressed in the future.% 
+chromosome lengths could be addressed in the future. For example, comparing 
+different ways to calculate $c$ using linear, logarithmic or exponential functions
+depending on these values. Moreover, a diversity analysis of the individuals
+in each island during the algorithm run could be carried out to understand its influence
+on results.
+% 
 % More discussion should be added. Why is adaptive better? Is the high
@@
 % paragraph of results begs an explanation of the influence of diversity on
-% results - JJ
+% results - JJ Pablo: extending this section
 
@@
 GPUs or heterogeneous clusters) with different amounts of
-islands/processors, will be used to perform a scalability study of the
+islands/processors, could be used to perform a scalability study of the
 different methods, being the transmission time between islands a
-relevant issue to address. Other MOEA algorithms available in the literature, such as SPEA or MOEA/D will be compared. Finally, new benchmarks and real problems
-will also be  used to validate this approach.
+relevant issue to be addressed. Other MOEA algorithms available in the literature, such as SPEA or MOEA/D could be compared. Finally, new benchmarks and real problems
+could also be  used to validate this approach.
 
 \section*{Acknowledgements}
-This work has been partially funded by projects TIN2014-56494-C4-3-P y TIN2015-67020-P (Spanish Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio 2015 UGR),  and  MSTR (PRY142/14, Fundaci\'on P\'ublica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci\'on).
+This work has been partially funded by projects TIN2014-56494-C4-3-P and TIN2015-67020-P (Spanish Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio 2015 UGR),  and  MSTR (PRY142/14, Fundaci\'on P\'ublica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci\'on).
 

### 2017-07-04 hpmoon-coor.tex
Adding @pacastillo comments and renaming sections according to @JJ. I will submit it this afternoon

@@
 
-In this paper, a new method to
+Specifically, in this paper, a new method to
 automatically adapt the size of the overlapping, or shared sections,
@@
 The rest of the paper is organized as follows: after the State of the Art in distributed and co-evolutionary MOEAs, 
-the used methodology and the compared algorithms are described in Section \ref{sec:co-evo}. 
-Then, the results of the experiments are presented (Section \ref{sec:res}), Finally, the conclusions and future work are discussed.
+the used methodology and the compared algorithms are described in Section \ref{sec:methodology}. 
+Then, the results of the experiments are presented (Section \ref{sec:results}), Finally, the conclusions and future work are discussed.
 
@@
 
-Since the early 2000s distributed and parallel Evolutionary
-Algorithms have been used mostly to leverage systems such
+Since the early 2000s distributed and parallel EAs
+ have been used mostly to leverage systems such
 as clusters or grids \citep{Talbi08Parallel}, since a first-order
@@
 For example,  \citep{Durillo08masterslave} compared different master-slave approaches: synchronous generational, asynchronous generational and asynchronous steady-state, being the latter the most promising option.
-The method proposed by Hiroyasu \citep{Hiroyasu07discussion} generates offspring depending on the computational power.
+On the other hand, the method proposed by Hiroyasu \citep{Hiroyasu07discussion} generates offspring depending on the computational power.
 
@@
 In that work, the dominance of the solutions was divided into the islands using a coordinate transformation.
-Their authors concluded that dividing the search space is a good idea, although achieving this is not trivial.
-The division of the search space has been explored by other researchers, for example, dividing the population in elite and search sub-populations \citep{Wang09parallel}, or separation in processors by objective \citep{Xiao03specialized}.
+In that paper, authors concluded that dividing the search space is a good idea, although achieving this is not trivial.
+The division of the search space has been explored by other researchers, for example, dividing the population in elite and search sub-populations \citep{Wang09parallel}, or separating it in processors by objective \citep{Xiao03specialized}.
 Other authors, such as Martens \citep{Martens13asynchronous} use migration to accept individuals based on diversity, and migrating from not-crowded areas.
@@
                                 % precise reasons we think it works- JJ FERGU: Done, and explained
-\label{sec:co-evo}
+\label{sec:methodology}
 
@@
 
+\subsection{Proposed methods}
 In this paper we analyse several SLA algorithms we have
@@
 subpopulations according to the decision space to be explored by each
-islands. Here we will consider three methods in which each island only
+island. Here we will consider three methods in which each island only
 performs crossover and mutation in specific sections of the
@@
 crossed and mutated in the same way, depending on the island
-identifier. Note that, differently from other works such as the ones
-described by Talbi et al. \citep{Talbi08Parallel} all the islands deal
+identifier (from 1 to $P$). Note that, differently from other works such as the ones
+described by Talbi et al. \citep{Talbi08Parallel}, all the islands deal
 with complete chromosomes for fitness calculation, so our approach can
@@
 
-\subsection{SLA with disjoint islands (D)} 
+\subsubsection{SLA with disjoint islands (D)} 
 In this approach, each individual of size $L$ is split into $P$ chunks
@@
 
-\subsection{SLA with overlapping islands (O)}
+\subsubsection{SLA with overlapping islands (O)}
 This approach is similar to the previous one, but every island also uses the $p+1$ and $p-1$ (module size) chunks of the individual for crossover and migration.
@@
 
-\subsection{Adaptive SLA with overlapping islands (A)} 
-As in the previous method, the sections to address are overlapped, but
-instead using one extra section on each side of the $p$ section ($p+1$
+\subsubsection{Adaptive SLA with overlapping islands (A)} 
+As in the previous method, the sections to address by the operators are overlapped, but
+instead of using one extra section on each side of the $p$ section ($p+1$
 and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$),
@@
 %
-\section{Experiments and Results}
-\label{sec:res}
+\subsection{Experimental setup}
 
-This section describes the quality indicators used and the experimental setup. The chosen quality indicators, are:
+This subsection describes the quality indicators used and the experimental setup. The chosen quality indicators, are:
 
@@
 Islands have been first distributed among the nodes.
-That means that, for example, the run of 8 islands requires 8 different nodes, instead of the usage of the 8 processors of a single node.
+That means that, for example, running with 8 islands requires 8 different nodes, instead of the usage of the 8 processors of a single node.
+
+\section{Results}
+\label{sec:results}
 
@@
 necessarily improve the solution of the global PF, but focusing on
-different elements of the chromosome. As indicated previously, every
+different elements of the chromosome. As  previously stated, every
 island is unaware of the other islands PFs, and they are trying to
@@
 \section*{Acknowledgements}
-This work has been partially funded by projects TIN2014-56494-C4-3-P and TIN2015-67020-P (Spanish Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio 2015 UGR),  and  MSTR (PRY142/14, Fundaci\'on P\'ublica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci\'on).
+This work has been partially funded by projects TIN2014-56494-C4-3-P and TIN2015-67020-P (Spanish Ministry of Economy and Competitivity).
 

### 2017-10-31 hpmoon-coor.tex
Modified title
Addressing reviewers suggestions

@@
 
-\title{Parallel multi-objective optimization using selective operator application
-  islands}
+\title{Distributed multi-objective evolutionary optimization using island-based selective operator application}
 % New title suggestion
@@
 We have chosen those metrics because they have been used extensively, especially in some of the papers presented in Section 2 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous}.
+Mathematical formulation of these metrics can be seen in \cite{Dorronsoro13superlinear}.
 
@@
 ZDT \citep{zdt2000a} has been chosen as a benchmark, since it is the most widely used in this area \citep{Deb03distributed,Martens13asynchronous,Wang09parallel,Durillo08masterslave}.
+This benchmark includes several functions, with different features that are representative of real world optimization problems.
+Mathematical formulation of each function is available in \citep{zdt2000a}.
 The optimal PF distribution used for comparison has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.}.
@@
 time: 25 seconds for dimension 512 and 100s (four times more) for
-2048. We have used time instead of the number of evaluations firstly
+2048.
+According to Alba and Luque \cite{EVALUATIONPARALLEL}, other stop criteria such as the number of evaluations required to attain a solution, may be misleading depending on the studied scenario.
+In our case we have used time instead of the number of evaluations firstly
 because our hypothesis argues that the time saved in crossover and
@@
 compare different times and quality of solutions at the same time.
+The number of generations between migrations has been set to 5, as this number is usually repeated in the literature \cite{Deb03distributed,Martens13asynchronous}.
  The whole parameter set is summarized in Table \ref{tab:parameters}.
@@
 The ECJ framework \citep{ECJ} has been used to run the
-experiments. Specific operators have been developed as new modules for
+experiments, including its own random number generation implementation. Specific operators have been developed as new modules for
 ECJ, and they can be downloaded from our GitHub repository under a
@@
 the results of A are equivalent to the obtained with D (because
-$c=0$), and when $P=16$ they are equivalent to O ($c=1$). We refer this equivalence with the word {\em Equiv.} in tables.
+$c=0$), and when $P=16$ they are equivalent to O ($c=1$).
+We refer this equivalence with the word {\em Equiv-} in tables.
+For example, Equiv-D in an HV cell  means that the HV of A is the same than the one in D column, because the behaviour of this configuration is the same than executing D.
 
@@
 \multicolumn{13}{|c|}{ZDT1}																																													\\ \hline
-8	&	0.900		&	0.816		& \textbf{	0.926	}		&	Equiv. D			& \textbf{	0.729	}	&	1.041			&	0.898			&	Equiv. D			&	0.013		&	0.029		& \textbf{	0.007	}	&	Equiv. D					\\
-16	& \textbf{	0.880	}	&	0.675		&	0.839			&	Equiv. O			& \textbf{	0.721	}	&	0.897			&	0.983		D	&	Equiv. O			& \textbf{	0.017	}	&	0.062		&	0.025		&	Equiv. O					\\
+8	&	0.900		&	0.816		& \textbf{	0.926	}		&	Equiv-D			& \textbf{	0.729	}	&	1.041			&	0.898			&	Equiv-D			&	0.013		&	0.029		& \textbf{	0.007	}	&	Equiv-D					\\
+16	& \textbf{	0.880	}	&	0.675		&	0.839			&	Equiv-O			& \textbf{	0.721	}	&	0.897			&	0.983		D	&	Equiv-O			& \textbf{	0.017	}	&	0.062		&	0.025		&	Equiv-O					\\
 32	& \textbf{	0.829	}	&	0.618		&	0.698			&	0.790			& \textbf{	0.763	}	&	0.879			&	0.886		D	&	0.913	DO		& \textbf{	0.027	}	&	0.076		&	0.056		&	0.036					\\
@@
 \multicolumn{13}{|c|}{ZDT2}																																													\\ \hline
-8	&	0.830		&	0.786		& \textbf{	0.851	}		&	Equiv. D			& \textbf{	0.866	}	&	0.996			&	0.987		D	&	Equiv. D			&	0.023		&	0.037		& \textbf{	0.017	}	&	Equiv. D					\\
-16	& \textbf{	0.810	}	&	0.601		&	0.776			&	Equiv. O			& \textbf{	0.916	}	&	0.990			&	1.005		D	&	Equiv. O			& \textbf{	0.029	}	&	0.091		&	0.040		&	Equiv. O					\\
+8	&	0.830		&	0.786		& \textbf{	0.851	}		&	Equiv-D			& \textbf{	0.866	}	&	0.996			&	0.987		D	&	Equiv-D			&	0.023		&	0.037		& \textbf{	0.017	}	&	Equiv-D					\\
+16	& \textbf{	0.810	}	&	0.601		&	0.776			&	Equiv-O			& \textbf{	0.916	}	&	0.990			&	1.005		D	&	Equiv-O			& \textbf{	0.029	}	&	0.091		&	0.040		&	Equiv-O					\\
 32	& \textbf{	0.756	}	&	0.498		&	0.617			&	0.682			& \textbf{	0.976	}	& \textbf{	0.976	}	B	& \textbf{	0.978	}	BD	&	1.054			& \textbf{	0.045	}	&	0.119		&	0.086		&	0.068					\\
@@
 \multicolumn{13}{|c|}{ZDT3}																																													\\ \hline
-8	&	0.928		&	0.838		& \textbf{	0.951	}		&	Equiv. D			& \textbf{	0.869	}	&	1.028			&	0.983		D	&	Equiv. D			& \textbf{	0.008	}	&	0.018		&	0.005		&	Equiv. D					\\
-16	& \textbf{	0.903	}	&	0.715		&	0.870			&	Equiv. O			& \textbf{	0.846	}	&	0.899			&	0.960			&	Equiv. O			& \textbf{	0.011	}	&	0.032		&	0.014		&	Equiv. O					\\
+8	&	0.928		&	0.838		& \textbf{	0.951	}		&	Equiv-D			& \textbf{	0.869	}	&	1.028			&	0.983		D	&	Equiv-D			& \textbf{	0.008	}	&	0.018		&	0.005		&	Equiv-D					\\
+16	& \textbf{	0.903	}	&	0.715		&	0.870			&	Equiv-O			& \textbf{	0.846	}	&	0.899			&	0.960			&	Equiv-O			& \textbf{	0.011	}	&	0.032		&	0.014		&	Equiv-O					\\
 32	& \textbf{	0.857	}	&	0.655		&	0.737			&	0.824			& \textbf{	0.845	}	&	0.879			&	0.873		D	&	0.881	DO		& \textbf{	0.016	}	&	0.039		&	0.030		&	0.019					\\
@@
 \multicolumn{13}{|c|}{ZDT6}																																													\\ \hline
-8	&	0.268		&	0.223		& \textbf{	0.298	}		&	Equiv. D			& \textbf{	0.988	}	& \textbf{	0.972	}	B	& \textbf{	0.996	}	B	&	Equiv. D			& \textbf{	0.173	}	&	0.191		&	0.160		&	Equiv. D					\\
-16	& \textbf{	0.243	}	&	0.113		&	0.219			&	Equiv. O			& \textbf{	0.995	}	& \textbf{	0.987	}	B	& \textbf{	0.987	}	BD	&	Equiv. O			& \textbf{	0.184	}	&	0.240		&	0.193		&	Equiv. O					\\
+8	&	0.268		&	0.223		& \textbf{	0.298	}		&	Equiv-D			& \textbf{	0.988	}	& \textbf{	0.972	}	B	& \textbf{	0.996	}	B	&	Equiv-D			& \textbf{	0.173	}	&	0.191		&	0.160		&	Equiv-D					\\
+16	& \textbf{	0.243	}	&	0.113		&	0.219			&	Equiv-O			& \textbf{	0.995	}	& \textbf{	0.987	}	B	& \textbf{	0.987	}	BD	&	Equiv-O			& \textbf{	0.184	}	&	0.240		&	0.193		&	Equiv-O					\\
 32	& \textbf{	0.196	}	&	0.071		&	0.115			&	0.162			& \textbf{	0.998	}	& \textbf{	0.989	}	B	& \textbf{	0.988	}	BD	&	1.005	B		& \textbf{	0.204	}	&	0.257		&	0.238		&	0.220					\\
@@
 \multicolumn{13}{|c|}{ZDT1}																																													\\ \hline
-8	&	0.891		& \textbf{	0.953	}	&	0.937			&	Equiv. D			& \textbf{	0.681	}	& \textbf{	0.635	}	B	&	0.661		D	&	Equiv. D			&	0.015		& \textbf{	0.002	}	&	0.005		&	Equiv. D					\\
-16	&	0.884		&	0.850		& \textbf{	0.942	}		&	Equiv. O			& \textbf{	0.705	}	&	0.908			& \textbf{	0.670	}	B	&	Equiv. O			&	0.016		&	0.022		& \textbf{	0.004	}	&	Equiv. O					\\
+8	&	0.891		& \textbf{	0.953	}	&	0.937			&	Equiv-D			& \textbf{	0.681	}	& \textbf{	0.635	}	B	&	0.661		D	&	Equiv-D			&	0.015		& \textbf{	0.002	}	&	0.005		&	Equiv-D					\\
+16	&	0.884		&	0.850		& \textbf{	0.942	}		&	Equiv-O			& \textbf{	0.705	}	&	0.908			& \textbf{	0.670	}	B	&	Equiv-O			&	0.016		&	0.022		& \textbf{	0.004	}	&	Equiv-O					\\
 32	&	0.851		&	0.674		&	0.859		B	& \textbf{	0.900	}		& \textbf{	0.754	}	&	0.868			&	0.826		D	& \textbf{	0.763	}	B	&	0.023		&	0.062		&	0.020	B	& \textbf{	0.012	}				\\
@@
 \multicolumn{13}{|c|}{ZDT2}																																													\\ \hline
-8	&	0.832		& \textbf{	0.895	}	&	0.869			&	Equiv. D			& \textbf{	0.849	}	& \textbf{	0.886	}	B	&	0.853		D	&	Equiv. D			&	0.023		& \textbf{	0.006	}	&	0.013		&	Equiv. D					\\
-16	&	0.831		&	0.833	B	& \textbf{	0.884	}		&	Equiv. O			& \textbf{	0.810	}	&	1.001			& \textbf{	0.802	}	B	&	Equiv. O			&	0.023		&	0.022	B	& \textbf{	0.009	}	&	Equiv. O					\\
+8	&	0.832		& \textbf{	0.895	}	&	0.869			&	Equiv-D			& \textbf{	0.849	}	& \textbf{	0.886	}	B	&	0.853		D	&	Equiv-D			&	0.023		& \textbf{	0.006	}	&	0.013		&	Equiv-D					\\
+16	&	0.831		&	0.833	B	& \textbf{	0.884	}		&	Equiv-O			& \textbf{	0.810	}	&	1.001			& \textbf{	0.802	}	B	&	Equiv-O			&	0.023		&	0.022	B	& \textbf{	0.009	}	&	Equiv-O					\\
 32	&	0.800		&	0.628		&	0.800		B	& \textbf{	0.817	}		& \textbf{	0.848	}	&	0.974			&	0.983		D	&	0.908			&	0.031		&	0.082		&	0.032	B	& \textbf{	0.027	}				\\
@@
 \multicolumn{13}{|c|}{ZDT3}																																													\\ \hline
-8	&	0.917		& \textbf{	0.971	}	&	0.960			&	Equiv. D			& \textbf{	0.843	}	& \textbf{	0.854	}	B	&	0.868		D	&	Equiv. D			&	0.009		& \textbf{	0.001	}	&	0.004		&	Equiv. D					\\
-16	&	0.911		&	0.876	B	& \textbf{	0.963	}		&	Equiv. O			& \textbf{	0.864	}	&	0.899		B	& \textbf{	0.837	}	B	&	Equiv. O			&	0.010		&	0.014		& \textbf{	0.003	}	&	Equiv. O					\\
+8	&	0.917		& \textbf{	0.971	}	&	0.960			&	Equiv-D			& \textbf{	0.843	}	& \textbf{	0.854	}	B	&	0.868		D	&	Equiv-D			&	0.009		& \textbf{	0.001	}	&	0.004		&	Equiv-D					\\
+16	&	0.911		&	0.876	B	& \textbf{	0.963	}		&	Equiv-O			& \textbf{	0.864	}	&	0.899		B	& \textbf{	0.837	}	B	&	Equiv-O			&	0.010		&	0.014		& \textbf{	0.003	}	&	Equiv-O					\\
 32	&	0.884		&	0.710		&	0.883		B	& \textbf{	0.931	}		& \textbf{	0.856	}	& \textbf{	0.870	}	B	& \textbf{	0.842	}	B	& \textbf{	0.842	}	BDO	&	0.013		&	0.032		&	0.013	B	& \textbf{	0.008	}				\\
@@
 \multicolumn{13}{|c|}{ZDT6}																																													\\ \hline
-8	&	0.271		& \textbf{	0.398	}	&	0.323			&	Equiv. D			& \textbf{	0.982	}	& \textbf{	0.982	}	B	&	0.994			&	Equiv. D			&	0.171		& \textbf{	0.115	}	&	0.149		&	Equiv. D					\\
-16	&	0.275		&	0.295	B	& \textbf{	0.354	}		&	Equiv. O			& \textbf{	0.981	}	& \textbf{	0.970	}	B	&	1.006			&	Equiv. O			&	0.170		&	0.161	B	& \textbf{	0.136	}	&	Equiv. O					\\
+8	&	0.271		& \textbf{	0.398	}	&	0.323			&	Equiv-D			& \textbf{	0.982	}	& \textbf{	0.982	}	B	&	0.994			&	Equiv-D			&	0.171		& \textbf{	0.115	}	&	0.149		&	Equiv-D					\\
+16	&	0.275		&	0.295	B	& \textbf{	0.354	}		&	Equiv-O			& \textbf{	0.981	}	& \textbf{	0.970	}	B	&	1.006			&	Equiv-O			&	0.170		&	0.161	B	& \textbf{	0.136	}	&	Equiv-O					\\
 32	&	0.239		&	0.123		&	0.240			& \textbf{	0.254	}		& \textbf{	0.989	}	& \textbf{	0.991	}	B	& \textbf{	0.982	}	BD	& \textbf{	0.999	}	BD	&	0.186		&	0.235		&	0.185	B	& \textbf{	0.179	}				\\
@@
 \hline
-	&	\multicolumn{4}{|c|}{Average solutions per island}													&	\multicolumn{4}{|c|}{Generations}															\\ \hline
+	&	\multicolumn{4}{|c|}{Average solutions per front}													&	\multicolumn{4}{|c|}{Generations}															\\ \hline
 
@@
 \multicolumn{9}{|c|}{ZDT1}																				\\ \hline
-8	&	182.700		&	128.500		&	158.167			&	Equiv. D			&	397.367		&	776.967			&	603.667			&	Equiv. D				\\
-16	&	132.567		&	43.633		&	76.167			&	Equiv. O			&	567.933		&	908.467			&	838.000			&	Equiv. O				\\
+8	&	182.700		&	128.500		&	158.167			&	Equiv-D			&	397.367		&	776.967			&	603.667			&	Equiv-D				\\
+16	&	132.567		&	43.633		&	76.167			&	Equiv-O			&	567.933		&	908.467			&	838.000			&	Equiv-O				\\
 32	&	102.200		&	37.533		&	34.133	D		&	52.033			&	731.067		&	959.067			&	938.167			&	917.000				\\
@@
 \multicolumn{9}{|c|}{ZDT2}																															\\ \hline
-8	&	122.700		&	91.633		&	108.833	BD		&	Equiv. D			&	398.167		&	772.000			&	605.100			&	Equiv. D				\\
-16	&	94.867		&	28.033		&	62.467			&	Equiv. O			&	574.567		&	908.433			&	840.900			&	Equiv. O				\\
+8	&	122.700		&	91.633		&	108.833	BD		&	Equiv-D			&	398.167		&	772.000			&	605.100			&	Equiv-D				\\
+16	&	94.867		&	28.033		&	62.467			&	Equiv-O			&	574.567		&	908.433			&	840.900			&	Equiv-O				\\
 32	&	56.633		&	11.433		&	19.467	D		&	31.567			&	735.867		&	960.167			&	939.200			&	904.900				\\
@@
 \multicolumn{9}{|c|}{ZDT3}																															\\ \hline
-8	&	212.900		&	129.233		&	171.367			&	Equiv. D			&	398.633		&	776.000			&	603.333			&	Equiv. D				\\
-16	&	176.133		&	43.567		&	90.100			&	Equiv. O			&	573.033		&	908.667			&	838.000			&	Equiv. O				\\
+8	&	212.900		&	129.233		&	171.367			&	Equiv-D			&	398.633		&	776.000			&	603.333			&	Equiv-D				\\
+16	&	176.133		&	43.567		&	90.100			&	Equiv-O			&	573.033		&	908.667			&	838.000			&	Equiv-O				\\
 32	&	121.500		&	42.800		&	33.200			&	56.900			&	733.233		&	959.000			&	937.967			&	918.833				\\
@@
 \multicolumn{9}{|c|}{ZDT6}																															\\ \hline
-8	&	42.233		&	28.633		&	35.967	BD		&	Equiv. D			&	396.900		&	773.400			&	603.533			&	Equiv. D				\\
-16	&	43.733		&	7.733		&	18.967			&	Equiv. O			&	568.200		&	908.900			&	836.033			&	Equiv. O				\\
+8	&	42.233		&	28.633		&	35.967	BD		&	Equiv-D			&	396.900		&	773.400			&	603.533			&	Equiv-D				\\
+16	&	43.733		&	7.733		&	18.967			&	Equiv-O			&	568.200		&	908.900			&	836.033			&	Equiv-O				\\
 32	&	35.533		&	8.033		&	8.633	D		&	16.233		DO	&	735.700		&	958.900			&	938.600			&	926.167				\\
@@
 }
-\caption{Average number of generations and average number of solutions per island, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 512 dimensions.
+\caption{Average number of generations and average number of solutions of the front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 512 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.}
@@
 \hline
-	&	\multicolumn{4}{|c|}{Average solutions per island}													&	\multicolumn{4}{|c|}{Generations}															\\ \hline
+	&	\multicolumn{4}{|c|}{Average solutions per front}													&	\multicolumn{4}{|c|}{Generations}															\\ \hline
 %\multicolumn{13}{|c|}{2048 dimensions}																															\\ \hline
@@
 \multicolumn{9}{|c|}{ZDT1}																					\\ \hline
-8	&	137.733		&	47.167		&	119.933	B		&	Equiv. D			&	175.067		&	225.667			&	207.933			&	Equiv. D				\\
-16	&	92.633		&	38.233		&	47.533	D		&	Equiv. O			&	204.867		&	238.533			&	232.900			&	Equiv. O				\\
+8	&	137.733		&	47.167		&	119.933	B		&	Equiv-D			&	175.067		&	225.667			&	207.933			&	Equiv-D				\\
+16	&	92.633		&	38.233		&	47.533	D		&	Equiv-O			&	204.867		&	238.533			&	232.900			&	Equiv-O				\\
 32	&	56.167		&	41.167		&	28.667			&	32.567	O		&	225.433		&	243.833			&	242.533			&	242.000	O			\\
@@
 \multicolumn{9}{|c|}{ZDT2}																															\\ \hline
-8	&	64.267		&	22.733		&	56.867	B		&	Equiv. D			&	175.633		&	226.000			&	208.100			&	Equiv. D				\\
-16	&	52.300		&	10.733		&	20.067	D		&	Equiv. O			&	205.033		&	238.867			&	233.100			&	Equiv. O				\\
+8	&	64.267		&	22.733		&	56.867	B		&	Equiv-D			&	175.633		&	226.000			&	208.100			&	Equiv-D				\\
+16	&	52.300		&	10.733		&	20.067	D		&	Equiv-O			&	205.033		&	238.867			&	233.100			&	Equiv-O				\\
 32	&	34.400		&	10.367		&	10.433	D		&	17.900	O		&	225.600		&	244.267			&	242.633			&	242.000	O			\\
@@
 \multicolumn{9}{|c|}{ZDT3}																															\\ \hline
-8	&	163.767		&	83.367		&	119.467			&	Equiv. D			&	176.533		&	226.400			&	207.700			&	Equiv. D				\\
-16	&	108.467		&	49.433		&	47.700	D		&	Equiv. O			&	205.333		&	238.467			&	232.933			&	Equiv. O				\\
+8	&	163.767		&	83.367		&	119.467			&	Equiv-D			&	176.533		&	226.400			&	207.700			&	Equiv-D				\\
+16	&	108.467		&	49.433		&	47.700	D		&	Equiv-O			&	205.333		&	238.467			&	232.933			&	Equiv-O				\\
 32	&	72.133		&	44.333		&	31.833			&	36.533	O		&	225.100		&	243.900			&	242.433			&	242.000	O			\\
@@
 \multicolumn{9}{|c|}{ZDT6}																															\\ \hline
-8	&	22.133		&	13.833		&	14.433	D		&	Equiv. D			&	175.733		&	226.100			&	207.767			&	Equiv. D				\\
-16	&	20.767		&	15.867		&	13.300	D		&	Equiv. O			&	205.033		&	238.433			&	232.933			&	Equiv. O				\\
+8	&	22.133		&	13.833		&	14.433	D		&	Equiv-D			&	175.733		&	226.100			&	207.767			&	Equiv-D				\\
+16	&	20.767		&	15.867		&	13.300	D		&	Equiv-O			&	205.033		&	238.433			&	232.933			&	Equiv-O				\\
 32	&	22.600		&	10.700		&	10.033	D		&	11.967	DO		&	225.833		&	243.667			&	242.500			&	242.000	O			\\
@@
 }
-\caption{Average number of generations and average number of solutions per island, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 2048 dimensions.
+\caption{Average number of generations and average number of solutions per front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 2048 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.}
@@
 This can be explained comparing the number of non-dominated solutions
-in each island and the average number of generations (Table
+of each front and the average number of generations (Table
 \ref{tab:sols512} and Table \ref{tab:sols2048}). With both chromosome
@@
 optimize their solutions independently. With respect to the average
-number of solutions in each island, there is a clear difference 
+number of solutions per front, there is a clear difference 
  with the baseline with $L=512$, where this value is in the most

### 2017-11-15 hpmoon-asoco.tex
Changed to ASOCO

--- 2017-10-31 hpmoon-coor.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\journal{Applied Soft Computing}
 \title{Distributed multi-objective evolutionary optimization using island-based selective operator application}
@@
 
-We have chosen those metrics because they have been used extensively, especially in some of the papers presented in Section 2 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous}.
+We have chosen those metrics not only because they have been used extensively, especially in some of the papers presented in Section 2 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous}, but also because they cover different quality criteria.
 Mathematical formulation of these metrics can be seen in \cite{Dorronsoro13superlinear}.
@@
 We refer this equivalence with the word {\em Equiv-} in tables.
-For example, Equiv-D in an HV cell  means that the HV of A is the same than the one in D column, because the behaviour of this configuration is the same than executing D.
+For example, Equiv-D in an HV cell  means that the HV of A is the same than the value in D column, because the behaviour of this configuration is the same than executing D.
 
@@
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
-Best values are marked in bold.}
+Best values are marked in bold.
+Equiv-$X$ implies that value is the same as executing $X$, since both configurations would be the same.}
 \label{tab:results512}
@@
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
-Best values are marked in bold.}
+Best values are marked in bold.
+Equiv-$X$ implies that value is the same as executing $X$, since both configurations would be the same.}
 \label{tab:results2048}
@@
 \caption{Average number of generations and average number of solutions of the front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 512 dimensions.
-Acronyms next to values indicate that there is not significant difference with respect to that method for that value.}
+Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
+Equiv-$X$ implies that value is the same as executing $X$, since both configurations would be the same.}
 \label{tab:sols512}
@@
 \caption{Average number of generations and average number of solutions per front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 2048 dimensions.
-Acronyms next to values indicate that there is not significant difference with respect to that method for that value.}
+Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
+Equiv-$X$ implies that value is the same as executing $X$, since both configurations would be the same.}
 \label{tab:sols2048}
@@
 \bibliographystyle{elsarticle-num}
-\bibliography{hpmoon-coor}
+\bibliography{hpmoon-asoco}
 

### 2017-11-20 hpmoon-asoco.tex
Addressing changes by Julio and @pacastillo. Final version sent to ASOCO

@@
 One example of application of this technique was described in \citep{Kimovski15Parallel}.
-The method presented in that works involves different workers that evolve sub-populations created and recombined by a master process, which performs different recombination alternatives from the parts returned by worker processes.
+The method presented in that work involves different workers that evolve sub-populations created and recombined by a master process, which performs different recombination alternatives from the parts returned by worker processes.
 A high dimensional problem was used to compare these
@@
 This allows to deal with un-decomposable problems.
-In our preliminary work \citep{Garcia16hpmoon} we used this method in a preliminary experimental setup, although it is worth mentioning we are establishing its name and acronym in this paper for the first time.
+In our previous work \citep{Garcia16hpmoon} we used this method in a preliminary experimental setup, although it is worth mentioning we are establishing its name and acronym in this paper for the first time.
 We proved
@@
 (8, 32 and 128). In this paper,  8, 16, 32, 64 and 128 islands have
-been used, and this time, the experiments have been run on a parallel
+been used, and on this occasion, the experiments have been run on a parallel
 cluster. Therefore, at the same time we are proposing an adaptive
@@
 one individual in a given island is migrated to another random island,
-thus avoiding to synchronize the global Pareto Front (PF) every
+thus avoiding to synchronize the global PF every
 certain number of generations as other methods described in Section 2
-do. At the end of the run, the Pareto Fronts of all islands are
+do. At the end of the run, the PFs of all islands are
 aggregated into a new one, and the quality measures are evaluated. 
@@
 We have chosen those metrics not only because they have been used extensively, especially in some of the papers presented in Section 2 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous}, but also because they cover different quality criteria.
-Mathematical formulation of these metrics can be seen in \cite{Dorronsoro13superlinear}.
+Mathematical formulation of these metrics can be found in \cite{Dorronsoro13superlinear}.
 
@@
 islands ($P$) have also been compared: 8, 16, 32, 64 and 128. This
-maximum number of islands have also been  used in previous work in the
+maximum number of islands has also been  used in a previous work in the
 literature \citep{Martens13asynchronous}. The crossover and mutation
@@
 experiments, including its own random number generation implementation. Specific operators have been developed as new modules for
-ECJ, and they can be downloaded from our GitHub repository under a
+ECJ, and their source code can be downloaded from our GitHub repository under a
 LGPL V3 License
@@
 the generated PFs in all runs are dominated by it. Metrics are then
-normalized with respect to that point. A Kruskal-Wallis significance
+normalized respecting to that point. A Kruskal-Wallis significance
 test has been performed to the metrics of all runs of the
@@
 distributions. The average results for each configuration are shown in
-Table \ref{tab:results512} (for 512 dimensions) and
+Table \ref{tab:results512} (for 512 dimensions) and Table
 \ref{tab:results2048} (for 2048). As previously explained, when $P=8$
@@
 
-Finally, as was already observed in \citep{Garcia16hpmoon}, results
+Finally, as it was already observed in \citep{Garcia16hpmoon}, results
 show that all the quality indicators decrease in value when the number of islands is increased, as the  sizes of the subpopulations are smaller.
@@
 
-Results also show that when increasing the number of islands, the
+Obtained esults also show that when increasing the number of islands, the
 adaptive overlapping method significantly improves the results with
@@
 \section*{Acknowledgements}
-This work has been partially funded by projects TIN2014-56494-C4-3-P and TIN2015-67020-P (Spanish Ministry of Economy and Competitivity).
+This work has been partially funded by projects TIN2014-56494-C4-3-P, TIN2015-67020-P and TIN2017-85727-C4-2-P (Spanish Ministry of Economy and Competitiveness and FEDER).
 

### 2017-11-27 hpmoon-asoco.tex
Addressing @JJ 's comments on cover letter

@@
 
-One of the most extended
-methods to deal with high-dimensional multi-objective optimization problems are the distributed co-evolutionary algorithms. In these methods each
-processor deals only with a part of the decision space, that is, the
-individuals belonging to the same sub-population (island) explore the
-same subset of decision variables. However, only decomposable problems could be strictly implemented in parallel this way. %these methods only works with decomposable problems.
-
-A new approach is presented here to deal with un-decomposable problems, the selective operator application:
-instead of sharing parts of individuals, each processor applies the variation 
-operators to a specific subset of the whole individual. We have previously proved 
-that extending the length of these subsets, and therefore, sharing some search 
-space between islands, implies an improvement in the results.
-
-Specifically, in this paper, a new method to
-automatically adapt the size of the overlapping, or shared sections,
-of the individuals has been compared to other collaborative
-evolutionary techniques. Different number of islands, chromosome sizes
-and problems have been used. The analysis of the obtained experimental
-results, by using different metrics, shows that our approach can provide statistically significant improvements with
-respect to the base algorithm.%, being the method to automatically adapt
-%the overlapping size the one to obtain the best performance during the
-%same execution time. 
- Results also show that the relation between the number
-of islands (subpopulations) and the length of the chromosome (number of
-decision variables) is also a relevant factor to determine the most
-efficient alternative to distribute the decision variables. 
+One of the most extended methods to deal with high-dimensional multi-objective optimization problems are the distributed co-evolutionary algorithms.
+In these methods each processor deals only with a part of the decision space, that is, the individuals belonging to the same sub-population (island) explore the same subset of decision variables.
+However, only decomposable problems could be strictly implemented in parallel this way.
+A new approach is presented here to deal with un-decomposable problems, the selective operator application: instead of sharing parts of individuals, each processor applies the variation operators to a specific subset of the whole individual.
+We have previously proved that extending the length of these subsets, and therefore, sharing some search space between islands, implies an improvement in the results.
+Specifically, in this paper, a new method to automatically adapt the size of the overlapping, or shared sections, of the individuals has been compared to other collaborative evolutionary techniques.
+Different number of islands, chromosome sizes and problems have been used.
+The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm.
+Results also show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distribute the decision variables.
 \end{abstract}
@@
 can improve the quality of the solutions 
-when the number of islands is increased. We discovered that the most
+when the number of islands is increased. We discovered on that paper that the most
 adequate overlapping size may vary depending on a relation between the
-number of islands and the individual size. However, the experiments
+number of islands and the individual size. However, it was a proof-of-concept, and the experiments
 were conducted in a limited experimental system: mono-processor and synchronous island model. This
@@
 method to divide the individual search space, and also validating the
-previous methods.
+previous approach.
 

### 2017-11-28 hpmoon-asoco.tex
Addressing @julioortega final comments

@@
 We have previously proved that extending the length of these subsets, and therefore, sharing some search space between islands, implies an improvement in the results.
-Specifically, in this paper, a new method to automatically adapt the size of the overlapping, or shared sections, of the individuals has been compared to other collaborative evolutionary techniques.
-Different number of islands, chromosome sizes and problems have been used.
+Specifically, in this paper, a new method to automatically adapt the size of the overlapping, or shared sections, of the individuals has been compared to other collaborative evolutionary techniques considering different number of islands, chromosome sizes and benchmarks.
 The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm.
 Results also show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distribute the decision variables.
+
 \end{abstract}
@@
 work, the overlapped method ($c=1$) obtained better results when the
-number of islands were $>$8. On the contrary, when the number of
+number of islands were bigger than 8. On the contrary, when the number of
 islands is small, no overlapping is necessary. So, we have used this

### 2018-05-01 hpmoon-asoco.tex
fixing some typos

@@
 In order to prove this claim, our new adaptive method has been
-compared against different overlapping islands schemes: a
+compared against different overlapping island schemes: a
 baseline version of a distributed NSGA-II \citep{Deb00NSGAII}, a

### 2018-05-01 hpmoon-asoco.tex
fixing some typos
adding new references (related to issue #17)

@@
 objectives have to be simultaneously optimized
-\citep{Mora13paretobased}. Solving a MOP implies maximizing or minimizing
+\citep{Mora13paretobased,LIU2017344}. Solving a MOP implies maximizing or minimizing
 a function composed of several cost functions (one per objective). In
@@
 %2 COMPUTATION -> PARALLEL
-These kind of problems implies a high demand of computational time, leading to the apparition of easily parallelizable methods to solve them \citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress}.
+These kind of problems implies a high demand of computational time, leading to the apparition of easily parallelizable methods to solve them \citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress,KAUR2018183,XU2018268}.
 %3 ONE WAY IS TO USE MOEAS BECAUSE
@@
                                %paper? - JJ FERGU: explained before that we are showing new results.
-Different benchmark problems and different large number of islands
+Several benchmark problems and different large number of islands
 have been used. Results show that this new technique can improve
@@
 easily parallelizable {\em divide and conquer} approach
-\citep{cheng2015adaptive}. Even other types of metaheuristics, such as
-the Multi-Objective Ant Colony Optimization (MOACO), can rely on
-island models to divide the search space depending on the node to
-achieve better results \cite{Mora13paretobased}.
+\citep{cheng2015adaptive}. 
+Even other types of metaheuristics, 
+such as the Multi-Objective Ant Colony Optimization (MOACO) 
+or Artificial Bee Colony Algorithm, 
+can rely on island models to divide the search space depending on 
+the node to achieve better results \cite{Mora13paretobased,LUO2017235}.
 

### 2018-05-06 hpmoon-asoco.tex
Commenting on the abstract
Please @fergunet take a look. I think it should be rewritten almost
completely. There's no issue, despite reviewer 1 asking for an
improvement of the abstract.

@@
 
-One of the most extended methods to deal with high-dimensional multi-objective optimization problems are the distributed co-evolutionary algorithms.
-In these methods each processor deals only with a part of the decision space, that is, the individuals belonging to the same sub-population (island) explore the same subset of decision variables.
-However, only decomposable problems could be strictly implemented in parallel this way.
-A new approach is presented here to deal with un-decomposable problems, the selective operator application: instead of sharing parts of individuals, each processor applies the variation operators to a specific subset of the whole individual.
-We have previously proved that extending the length of these subsets, and therefore, sharing some search space between islands, implies an improvement in the results.
-Specifically, in this paper, a new method to automatically adapt the size of the overlapping, or shared sections, of the individuals has been compared to other collaborative evolutionary techniques considering different number of islands, chromosome sizes and benchmarks.
-The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm.
-Results also show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distribute the decision variables.
+  Real world optimization problems usually have many dimensions and
+  several objectives. The high dimensionality requires exceptional
+  computing power, and the fact that several dimensions have to be
+  searched at the same time add additional difficulty.
+% One of the most extended methods to deal with high-dimensional
+% multi-objective optimization problems are the distributed
+% co-evolutionary algorithms.
+% ----------------- This sentence is meaningless. It should be
+% substituted by other stating that co-evolutionary algorithms can
+% deal with it for some reason
+% Besides, we're no longer saying that they are co-evolutionary in the
+% title, but "island-based selective operator application". This
+% should go to the abstract too - JJ
+
+  In these methods %which ones? coevolutionary or selective operator
+                   %application? - JJ
+  each processor deals only with a part of the decision
+space, that is, the individuals belonging to the same sub-population,
+which are called {\em islands} in this context, explore the same subset of decision variables. However, only
+decomposable problems could be strictly implemented in parallel this
+way. A new approach, which we call {\em selective operator application} is presented here to deal with un-decomposable
+problems: % so we are saying that high-dimensional multi-objective
+          % problems are a challenge, but we are presenting a solution
+          % for non-decomposable problems. What's what? - JJ
+instead of sharing parts
+of individuals, each processor applies the variation operators to a
+specific subset of the whole individual. % this solves... - JJ
+We have previously proved
+that extending the length of these subsets, and therefore, sharing
+a part of the search space among islands, implies an improvement in the
+results % which results? - JJ
+but in this paper, a new method to automatically
+adapt the size of the overlapping, or shared sections, of the
+individuals has been compared to other collaborative evolutionary
+techniques considering different number of islands, chromosome sizes
+and benchmarks. The analysis of the obtained experimental results, by
+using different metrics, shows that our approach can provide
+statistically significant improvements with respect to the base
+algorithm. % in high-dimensional multi-objective problems? - JJ
+Results also show that the relation between the number of
+islands (subpopulations) and the length of the chromosome (number of
+decision variables) is also a relevant factor to determine the most
+efficient alternative to distribute the decision variables.  % This
+                                % solves a problem or challenge we
+                                % hadn't stated. - JJ
 

### 2018-05-07 hpmoon-asoco.tex
Adds references
Revised intro
With many suggestions for @fergunet. Please check them out.

@@
 \title{Distributed multi-objective evolutionary optimization using island-based selective operator application}
-% New title suggestion
-% Should co-evolutionary go somewhere? Are they co-evolutionary? - jj
-% PABLO: Renaming again to avoid using the co-evolutionary and
-% cooperative
-% Ok - JJ
 
@@
 % 6. In this paper we will be proving whatever - JJ FERGU: Addressing JJ order
+% OK - JJ
 
@@
 objectives have to be simultaneously optimized
-\citep{Mora13paretobased,LIU2017344}. Solving a MOP implies maximizing or minimizing
-a function composed of several cost functions (one per objective). In
+\citep{Mora13paretobased,LIU2017344}. Solving a MOP implies optimizing a function composed of several independent cost functions, one per objective. In
 these problems the aim is to obtain a set of solutions that are better
@@
 the Pareto Front (PF). The solutions in this set are {\em non-dominated},
-that is, none is better than the others for all the objectives.
+which means that there is no other solution that is equal or better
+for all objectives; the objective of MOP algorithms is to find as many
+solutions in the Pareto Front as possible, and in order to do that the
+exploration of the search space must be very efficient, trying to
+cover many possible exploration paths at the same time.
 
 %2 COMPUTATION -> PARALLEL
-These kind of problems implies a high demand of computational time, leading to the apparition of easily parallelizable methods to solve them \citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress,KAUR2018183,XU2018268}.
+This aspect of searching for non-dominated solutions, as well as, in
+many cases, the size of the search space itself, implies a high demand
+of computational time, leading to the proposal of parallel and distributed methods to solve them
+\citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress,KAUR2018183,XU2018268},
 %3 ONE WAY IS TO USE MOEAS BECAUSE
-One example of easily parallelizable algorithms to solve MOPs are the Multi-Objective Evolutionary Algorithms (MOEAs), a sub-set of Evolutionary algorithms (EAs).
-EAs \citep{DBLP:series/ncs/EibenS15} are bio-inspired meta-heuristics that can be effectively used to find nearly optimal solutions for optimization problems.
-Usually an EA starts by generating a set of random solutions, called \emph{population}, following a user-defined description.
-Then, it evaluates each candidate solution, called \emph{individual}, assigning it a \emph{fitness} value, that describes how good the individual is, with regard to the target problem.
-New solutions are then generated by the application of \emph{operators} that either mutate a single solution or recombine different existing solutions.
-After each iteration, called \emph{generation}, the least fit individuals are removed, and the process continues until a user-defined stop condition is met.
-One of the most well-known and referenced MOEAs \citep{Dorronsoro13superlinear} is the {\em
+one of which are evolutionary algorithms (EAs)
+\citep{DBLP:series/ncs/EibenS15}. EAs are bio-inspired meta-heuristics
+that can be effectively used to find nearly optimal solutions for
+optimization problems and are easily paralellizable, since they are
+population-based and creating a functionally equivalent parallel
+version is as easy as distributing the population in communicating
+computing nodes, which are usually called islands. The fact that
+they are population-based helps find many solutions that compose the
+Pareto fron simultaneously.
+
+Usually an EA starts by generating a set of random solutions, called
+\emph{population}, following a user-defined description. Then, it
+evaluates each candidate solution, called \emph{individual}, assigning
+it a \emph{fitness} value, that describes how good the individual is
+with regard to the target problem. New solutions are then generated by
+the application of \emph{operators} that either mutate a single
+solution or recombine different existing solutions. After each
+iteration, called \emph{generation}, the least fit individuals are
+removed, and the process continues until a user-defined stop condition
+is met.
+
+One of the best known and referenced MOEAs
+\citep{Dorronsoro13superlinear} is the {\em 
   Non-dominated Sorting Genetic Algorithm} (NSGA-II)
 \citep{Deb00NSGAII}. Classical genetic operators are applied to all
-the individuals, and divided into different ranks (based on the
-dominance) to be selected for the next generations.
+the individuals, which are divided into different ranks, based on the
+dominance, to be selected for the next generations. 
+% This paragraph has nothing to do with anything. Is it useful for
+% what you are doing in the paper? Is there any challenge that you
+% will be solving here? For instance, you could talk about the problem
+% it's got for parallelization and how it deals with them - JJ
 
@@
 results to accurately identify the PF
-\citep{Branke04Parallelizingcone}.
+\citep{Branke04Parallelizingcone}. % Is that the case with NSGA? - JJ
 
-MOPs usually require a high number of variables, meaning that the MOEAs need to deal with large individuals and spend significant extra time for crossover, mutation and migration.
-Different authors have proposed methods to divide the decision space (the chromosome) to improve the performance and solution quality.
-In this aspect, the co-evolution model is a dimension-distributed model where a high-dimensional problem is divided into lower dimensional ones \citep{Gong15models,Tonda12cooperative}, and evolved separately.
-One example of application of this technique was described in \citep{Kimovski15Parallel}.
-The method presented in that work involves different workers that evolve sub-populations created and recombined by a master process, which performs different recombination alternatives from the parts returned by worker processes.
-A high dimensional problem was used to compare these
+MOPs usually require a high number of variables, % No they don't, and
+                                % if they do, add a reference - JJ
+meaning that the
+MOEAs need to deal with large individuals and spend significant extra
+time for crossover, mutation and migration. %depending on the
+                                %language, this time might not be
+                                %significant at all, and will depend
+                                %on the length of the chromosome, not
+                                %the part of the chromosome you will
+                                %be applying it to. Besides, this is
+                                %not the critical part of the
+                                %algorithm, the critical part is
+                                %searching the solution space. 
+Different authors have % this is only one possibility. You should talk
+                       % about simple island models, too - JJ
+proposed methods to divide the decision space (the chromosome) to
+improve the performance and solution quality. In this aspect, the
+co-evolution model is a dimension-distributed model where a % first
+                                % reference to co-evolution in this
+                                % paper. Is it still a paper about
+                                % co-evolution? - JJ
+high-dimensional problem is divided into lower dimensional ones
+\citep{Gong15models,Tonda12cooperative}, and evolved separately. One
+example of application of this technique was described in
+\citep{Kimovski15Parallel}. The method presented in that work involves
+different workers that evolve sub-populations created and recombined
+by a master process, which performs different recombination
+alternatives from the parts returned by worker processes. A high
+dimensional problem was used to compare these 
 alternatives. In \citep{Dorronsoro13superlinear}, a distributed
@@
 
-A similar approach used to solve this kind of problems is the {\em selective operator application} (SLA).
-In this case, each island deals with the whole chromosome, but only modifies a fragment of it in the crossover and mutation phase depending on the number of islands, using the whole chromosome for fitness calculation.
-This allows to deal with un-decomposable problems.
-In our previous work \citep{Garcia16hpmoon} we used this method in a preliminary experimental setup, although it is worth mentioning we are establishing its name and acronym in this paper for the first time.
+A similar approach used to solve this kind of problems is the {\em
+  selective operator application} (SLA). In this case, each island
+deals with the whole chromosome, but only modifies a fragment of it in
+the crossover and mutation phase depending on the number of islands,
+using the whole chromosome for fitness calculation. This allows to
+deal with un-decomposable problems. % if the whole chromosome is used,
+                                % mutation and crossover will take the
+                                % same time. You are modifying the
+                                % search space, though. 
+In our previous work \citep{Garcia16hpmoon} we used this method in a
+preliminary experimental setup, although it is worth mentioning we are
+establishing its name and acronym in this paper for the first time.
 We proved 
@@
 can improve the quality of the solutions 
-when the number of islands is increased. We discovered on that paper that the most
+when the number of islands is increased. On that paper we proved that the most
 adequate overlapping size may vary depending on a relation between the
 number of islands and the individual size. However, it was a proof-of-concept, and the experiments
-were conducted in a limited experimental system: mono-processor and synchronous island model. This
+were conducted in a limited experimental system: mono-processor and
+synchronous island model. %where we couldn't prove that... Or, we
+                          %couldn't experiment... - JJ
+This
 motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more complete parameter setting.
@@
 The hypothesis of this paper is that the use of automatically calculated overlapped sections of the
-chromosome for the SLA, can improve the
+chromosome for the SLA can improve the
 quality of the solutions in the same computing time with respect to
@@
 
-%That was the
-                                %hypothesis of the previous
-                                %paper. This paper has a new
-                                %hypothesis, right? - JJ FERGU: no, this is the hypothesis of this paper (comparing adaptive with partly overlapped), but clarifying it
 In order to prove this claim, our new adaptive method has been
@@
 SLA version with disjoint sections and a SLA
-fixed-size overlapped version. %What was done in the previous paper?
-                               %Are we re-using the results in that
-                               %paper? - JJ FERGU: explained before that we are showing new results.
+fixed-size overlapped version. 
 Several benchmark problems and different large number of islands
@@
 different quality indicators in the same amount of time when the
-problem size is large.  % Shouldn't this start with "We are trying to
-                        % prove..." - JJ FERGU: Already writed in previous paragraph
+problem size is large.
 
@@
 
+\section*{References}
+
 \bibliographystyle{elsarticle-num}

### 2018-05-14 hpmoon-asoco.tex
Adding comments on the calculation of c for reviewer 2. Reviewer 3 still needs to be pleased. issue #19

@@
 % That's not adaptive. It's simply variable - JJ FERGU: it depends on the number of islands. What term do you suggest?
+
 As a first
@@
 (equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so
-on. As mentioned, this is only a first approach to obtain $c$, and future work will study new methods to calculate it. Figure \ref{fig:adaptive} explains this method.
+on.
+\textcolor{blue}{Dividing individuals by blocks of equal size, instead a percentage, allow the future integration of our method with other recombination mechanisms, such as the ones presented in \cite{Dorronsoro13superlinear} or \cite{Kimovski15Parallel}}.
+Also, as mentioned, this is only a first approach to obtain $c$, and future work will study new methods to calculate it. Figure \ref{fig:adaptive} explains this method.
 
@@
 
-Obtained esults also show that when increasing the number of islands, the
+Obtained results also show that when increasing the number of islands, the
 adaptive overlapping method significantly improves the results with
@@
 more types of problems, and new configurations of population size and
-chromosome lengths could be addressed in the future. For example, comparing 
+chromosome lengths could be addressed in the future.
+\textcolor{blue}{Since our method divides the individuals into blocks of divisible size, aggregation methods after migration, such as the ones used in \cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be also tested.
+But as we are dealing with complete individuals in each island, the possibility of using a real number, such as 0.3 (30\% overlapping) instead an integer value opens future experimental setups.}
+For example, comparing 
 different ways to calculate $c$ using linear, logarithmic or exponential functions
-depending on these values. Moreover, a diversity analysis of the individuals
+depending \textcolor{blue}{on population size, number of islands, or other values}. Moreover, a diversity analysis of the individuals
 in each island during the algorithm run could be carried out to understand its influence

### 2018-05-28 hpmoon-asoco.tex
Added more references for issue #17 and migration explanation for issues #18 #21

@@
 The division of the search space has been explored by other researchers, for example, dividing the population in elite and search sub-populations \citep{Wang09parallel}, or separating it in processors by objective \citep{Xiao03specialized}.
-Other authors, such as Martens \citep{Martens13asynchronous} use migration to accept individuals based on diversity, and migrating from not-crowded areas.
+\textcolor{blue}{For example, in \cite{Zhang17DECAL}, a weighted function is used to decompose the objective function and every subpopulation is responsible to solve the problem defined by a weighted vector.} Other authors, such as Martens \citep{Martens13asynchronous} use migration to accept individuals based on diversity, and migrating from not-crowded areas.
 
 % Is this really cooperative co-evolution? - JJ FERGU: You mean the Dorronsoro one? The title says it
-Addressing high-dimensional problems with cooperative co-evolution has
+\textcolor{blue}{Many real-world problems require high-dimensionality \cite{Zhang17DECAL,XU2018268}.
+Addressing this kind of problems with cooperative co-evolution has
 also been studied in several works with approaches closer to the one
-presented here. The approach to focus on a portion of the chromosome,
+presented here.} The approach to focus on a portion of the chromosome,
 as in our overlapped method, was firstly used in the work by
@@
 super-linear performance 
-in several instances. This approach has also been used by Kimovski et al. \citep{Kimovski15Parallel}, but using a
+in several instances.
+\textcolor{blue}{Recently, this approach has also been tested using a Particle Swarm Optimization (PSO) algorithm \cite{DorronsoroPSO2018}, also obtaining significant improvements in speedups and solution quality}.
+
+The approach described by Dorronsoro et al. has also been used by Kimovski et al. \citep{Kimovski15Parallel}, but using a
 master-slave method that splits the population into several processors. As in previous works, each node
@@
 The number of generations between migrations has been set to 5, as this number is usually repeated in the literature \cite{Deb03distributed,Martens13asynchronous}.
+\textcolor{blue}{The individual chosen to migrate is selected using Binary Tournament, as it has been previously used by other authors \cite{xiong2003parallel,Xiao03specialized}.
+As there is not a synchronization step to arrange the individual parts besides the specific crossover and mutation operations, the destination island after migration is chosen randomly to ensure that the modified parts of the migrated individual can be shared in the whole set of different islands.
+Migration is performed asynchronously, as it have the advantage of being a non-blocking operation \cite{TalbiUnified18}.}.
  The whole parameter set is summarized in Table \ref{tab:parameters}.

### 2018-05-30 hpmoon-asoco.tex
Added figures for issue #22 and addressing some @JJ 's comments

@@
 
-  Real world optimization problems usually have many dimensions and
+  \textcolor{blue}{Real world optimization problems usually have many dimensions and
   several objectives. The high dimensionality requires exceptional
   computing power, and the fact that several dimensions have to be
-  searched at the same time add additional difficulty.
+  searched at the same time add additional difficulty.}
 % One of the most extended methods to deal with high-dimensional
@@
 space, that is, the individuals belonging to the same sub-population,
-which are called {\em islands} in this context, explore the same subset of decision variables. However, only
+\textcolor{blue}{which are called {\em islands} in this context}, explore the same subset of decision variables. However, only
 decomposable problems could be strictly implemented in parallel this
-way. A new approach, which we call {\em selective operator application} is presented here to deal with un-decomposable
-problems: % so we are saying that high-dimensional multi-objective
+way. \textcolor{blue}{A new approach, which we call {\em selective operator application} is presented here to deal with un-decomposable
+problems:} % so we are saying that high-dimensional multi-objective
           % problems are a challenge, but we are presenting a solution
@@
 that extending the length of these subsets, and therefore, sharing
-a part of the search space among islands, implies an improvement in the
-results % which results? - JJ
-but in this paper, a new method to automatically
+\textcolor{blue}{some search space between islands, implies an improvement in different performance metrics}.
+ % which results? - JJ PABLO: answered
+But in this paper, a new method to automatically
 adapt the size of the overlapping, or shared sections, of the
@@
 statistically significant improvements with respect to the base
-algorithm. % in high-dimensional multi-objective problems? - JJ
+algorithm \textcolor{blue}{in high-dimensional multi-objective problems}. % in high-dimensional multi-objective problems? - JJ PABLO: ok, puesto
 Results also show that the relation between the number of
@@
 decision variables) is also a relevant factor to determine the most
-efficient alternative to distribute the decision variables.  % This
+efficient alternative to distribute the decision variables.  
+\textcolor{blue}{This opens up a new challenge that can be addressed in the future.}
+% This
                                 % solves a problem or challenge we
-                                % hadn't stated. - JJ
+                                % hadn't stated. - JJ Pablo: metido, mira a ver si queda frase memorable
 
@@
 %Pablo: theoretical?
-\item Spread (S): Measures the spread between solutions, taking into account the euclidean distance between consecutive solutions.
+\item Spread (S): Measures the spread between solutions, taking into account the \textcolor{blue}{Euclidean} distance between consecutive solutions.
 As in previous metric, the lower value, the better, as it implies solutions distributed along all the PF.
@@
 calculated, the point (1,9) has been chosen as reference, as none of
-the generated PFs in all runs are dominated by it. Metrics are then
+the generated PFs in all runs \textcolor{blue}{is} dominated by it. Metrics are then
 normalized respecting to that point. A Kruskal-Wallis significance
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=12cm]{plot_zdt1_512.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and adaptive overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt1_512}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=12cm]{plot_zdt2_512.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and adaptive overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt2_512}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=12cm]{plot_zdt3_512.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and adaptive overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt3_512}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=12cm]{plot_zdt6_512.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and adaptive overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt6_512}
+\end{figure}
+
+%%%%%2018
+
+\begin{figure}
+\centering
+\includegraphics[width=12cm]{plot_zdt1_2048.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and adaptive overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt1_2048}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=12cm]{plot_zdt2_2048.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and adaptive overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt2_2048}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=12cm]{plot_zdt3_2048.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and adaptive overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt3_2048}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=12cm]{plot_zdt6_2048.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and adaptive overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt6_2048}
+\end{figure}
+
 %EXPLANATION OF THE RESULTS
@@
 also implies a better Spread indicator, where the baseline 
- obtains better (or not significantly different) values in the majority of the compared configurations. %TENGO QUE COMENTAR MAS LOS RESULTADOS Y
-                              %ENTENDERLO TODO Y JUSTIFICARLO
-                              %FINAMENTE
-%Almost always no es muy preciso - JJ Pablo: arreglao
+ obtains better (or not significantly different) values in the majority of the compared configurations.
 

### 2018-06-04 hpmoon-asoco.tex
Changed Adaptive to Automatic. Closes #24

@@
 
-In order to prove this claim, our new adaptive method has been
+In order to prove this claim, our new automatic method has been
 compared against different overlapping island schemes: a
@@
 sections of the individuals and the number of islands used. This
-motivated us to find a new adaptive method to select this number of
+motivated us to find a new automatic method to select this number of
 sections of the chromosome to use, depending on the number of
@@
 been used, and on this occasion, the experiments have been run on a parallel
-cluster. Therefore, at the same time we are proposing an adaptive
+cluster. Therefore, at the same time we are proposing an automatic
 method to divide the individual search space, and also validating the
@@
 
-\subsubsection{Adaptive SLA with overlapping islands (A)} 
+\subsubsection{\textcolor{blue}{Automatic} SLA with overlapping islands (A)} 
 As in the previous method, the sections to address by the operators are overlapped, but
@@
 % That's not adaptive. It's simply variable - JJ FERGU: it depends on the number of islands. What term do you suggest?
-
+% FERGU: changed to Automatic
 As a first
@@
 \includegraphics[width=12cm]{islandAdaptive.jpg}
-\caption{Adaptive SLA with overlapping islands (A): every island $p$ modifies the  $p+c$,
+\caption{\textcolor{blue}{Automatic} SLA with overlapping islands (A): every island $p$ modifies the  $p+c$,
   $p_{th}$ and $p-c$  components (in grey) of the individuals. $c$ is calculated depending on the number of islands. In this case, $c=2$.}
@@
 	\STATE $c=1$
-\ELSIF {type = Adaptive}
+\ELSIF {type = Automatic}
 	\STATE $c=round(0.2*P-1)/2$
@@
 }
-\caption{Average quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 512 dimensions.
+\caption{Average quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 512 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 }
-\caption{Average quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 2048 dimensions.
+\caption{Average quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 2048 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 }
-\caption{Average number of generations and average number of solutions of the front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 512 dimensions.
+\caption{Average number of generations and average number of solutions of the front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 512 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 }
-\caption{Average number of generations and average number of solutions per front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 2048 dimensions.
+\caption{Average number of generations and average number of solutions per front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 2048 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 
-However, with 2048 dimensions, results show that dividing the chromosome produces an improvement in all the quality indicators using the adaptive version (Table \ref{tab:results2048}), even improving the overlapping and disjoint methods.
+However, with 2048 dimensions, results show that dividing the chromosome produces an improvement in all the quality indicators using the automatic ($A$) version (Table \ref{tab:results2048}), even improving the overlapping and disjoint methods.
 Therefore, there exist some kind of limit point in chromosome length where one method will be preferable to another, besides depending on the number of islands and population size.
@@
 \includegraphics[width=12cm]{plot_zdt1_512.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and adaptive overlapped ($A$).
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
 Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
@@
 \includegraphics[width=12cm]{plot_zdt2_512.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and adaptive overlapped ($A$).
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
 Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
@@
 \includegraphics[width=12cm]{plot_zdt3_512.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and adaptive overlapped ($A$).
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
 Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
@@
 \includegraphics[width=12cm]{plot_zdt6_512.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and adaptive overlapped ($A$).
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
 Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
@@
 \includegraphics[width=12cm]{plot_zdt1_2048.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and adaptive overlapped ($A$).
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
 Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
@@
 \includegraphics[width=12cm]{plot_zdt2_2048.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and adaptive overlapped ($A$).
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
 Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
@@
 \includegraphics[width=12cm]{plot_zdt3_2048.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and adaptive overlapped ($A$).
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
 Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
@@
 \includegraphics[width=12cm]{plot_zdt6_2048.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and adaptive overlapped ($A$).
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
 Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
@@
 Obtained results also show that when increasing the number of islands, the
-adaptive overlapping method significantly improves the results with
+automatic overlapping method ($A$) significantly improves the results with
 respect to the disjoint and overlapped methods. However, this is only
 apparent with larger chromosome sizes. Therefore, the length of the
-chromosome is also a key factor to take into account in adaptive
+chromosome is also a key factor to take into account in automatic overlapping
 methods, and not only the number of islands. Studying this factor with

### 2018-06-04 hpmoon-asoco.tex
Minor change in reference
More comments on results and images for issue #22

@@
 As there is not a synchronization step to arrange the individual parts besides the specific crossover and mutation operations, the destination island after migration is chosen randomly to ensure that the modified parts of the migrated individual can be shared in the whole set of different islands.
-Migration is performed asynchronously, as it have the advantage of being a non-blocking operation \cite{TalbiUnified18}.}.
+Migration is performed asynchronously, as it have the advantage of being a non-blocking operation \cite{TalbiUnified2018}.}
  The whole parameter set is summarized in Table \ref{tab:parameters}.
@@
 
+%ZDT1
 \begin{figure}
@@
 \centering
+\includegraphics[width=12cm]{plot_zdt1_2048.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt1_2048}
+\end{figure}
+
+%ZDT2
+\begin{figure}
+\centering
 \includegraphics[width=12cm]{plot_zdt2_512.png}
@@
 \centering
+\includegraphics[width=12cm]{plot_zdt2_2048.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt2_2048}
+\end{figure}
+
+%ZDT3
+\begin{figure}
+\centering
 \includegraphics[width=12cm]{plot_zdt3_512.png}
@@
 \centering
+\includegraphics[width=12cm]{plot_zdt3_2048.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt3_2048}
+\end{figure}
+
+%ZDT6
+\begin{figure}
+\centering
 \includegraphics[width=12cm]{plot_zdt6_512.png}
@@
 \label{fig:plot_zdt6_512}
-\end{figure}
-
-%%%%%2018
-
-\begin{figure}
-\centering
-\includegraphics[width=12cm]{plot_zdt1_2048.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}}
-\label{fig:plot_zdt1_2048}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=12cm]{plot_zdt2_2048.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}}
-\label{fig:plot_zdt2_2048}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=12cm]{plot_zdt3_2048.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}}
-\label{fig:plot_zdt3_2048}
 \end{figure}
@@
 
+%%%%%%FERGU: WARNING, THIS SECTION IS STILL SHIT
+%ZDT1 
+\textcolor{blue}{FINISH THIS SECTION!!!!
+Plotting the final PFs of each combination of parameters, problems and sizes also allow to see the different ....
+ZDT1 has a convex Pareto-optimal front.
+Comparing results from $L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=512$ (Figure \ref{fig:plot_zdt1_2048}) it is visually clear that the quality of the generated PFs depends on the chromosome size.
+Specifically, with $L=512$ it can be seen that the PFs quality decreases in Spread and HV with all configurations, but the SLA methods behave worse than $B$, as it also was shown in average in Table \ref{tab:results512}.
+But if we focus on the plots obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this difference is less clear.
+It can be seen in Figure \ref{fig:plot_zdt1_2048}) that solutions obtained by the SLA methods are more dispersed than the baseline as $P$ grows.
+However, with $A$, the area covered by the PF is larger.}
+
+%ZDT2
+\textcolor{blue}{ZDT2 has a non-convex Pareto-optimal front.
+This is the reason that some solutions ....WHAT.
+As in previous problem, there is a decrease of quality in all configurations when increasing the size of $P$.}
+
+%ZDT3
+\textcolor{blue}{ZDT3 Pareto-optimal front is formed by non-contiguous convex parts, and plots for both chromosome sizes (Figures \ref{fig:plot_zdt3_512} and \ref{fig:plot_zdt3_2048}) show solutions gathered in similar regions in all configurations.
+However, with $L=512$, some the $A$ configurations skip the last region on the right with $P=8$  and $P=16$ (being equivalent to $O$ and $A$).
+This can be explained because...
+In the case of $L=2048$...}
+
+\textcolor{blue}{In ZDT6, the Pareto-optimal solutions are not only non-uniformly distributed along the PF, but their density also increases as we move further away from it.
+That is the reason why some PFs obtained have a extremely low number of solutions in some configurations, and also, they are aggregated toward the areas with more density...}
+
 Finally, as it was already observed in \citep{Garcia16hpmoon}, results
@@
 
-Problems that require high-performance % problems are not high-performance. They
-                          % _require_ high performance Fergu: done
+Problems that require high-performance 
  and deal with a large number of decision variables can leverage the

### 2018-06-05 hpmoon-asoco.tex
More explanations, closes #26 #23 and continue working on #22

@@
 
+%The availability of metaheuristics which are able to efficiently approach these multi-objective optimization problems have made it possible to cope with many real applications from such multi-objective point of view [4, 5, 6, 7, 8].
+Evolutionary algorithms (EAs) [9] are bio-inspired meta-heuristics that can be effectively used to find nearly optimal solutions for optimization problems and have been extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) [29].
+
 Usually an EA starts by generating a set of random solutions, called
@@
 
+\textcolor{blue}{EAs have been extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}}.
 One of the best known and referenced MOEAs
@@
 % will be solving here? For instance, you could talk about the problem
-% it's got for parallelization and how it deals with them - JJ
+% it's got for parallelization and how it deals with them - JJ FERGU: Could you add some paragraph to justify it? (use \textcolor{blue}{} please)
 
@@
 Different approaches have been used to parallelize EAs, as each individual can be considered as an
-independent unit \citep{Alba13parallel}. Classic methods, such as the
+independent unit \citep{Alba13parallel,Gong15models}. Classic methods, such as the
 global parallel EAs (Master-Slave), or the spatially structured
@@
 
-MOPs usually require a high number of variables, % No they don't, and
-                                % if they do, add a reference - JJ
+\textcolor{blue}{MOPs usually require a high number of decision variables \cite{Zhang17DECAL,XU2018268}}, % No they don't, and
+                                % if they do, add a reference - JJ FERGU: added references
 meaning that the
@@
 Besides comparing previous methods in this new experimental setup, in this paper we propose
-a new method that automatically adapts the size of the overlapped
+a new method that automatically \textcolor{blue}{sets} the size of the overlapped
 sections depending on the number of available islands, comparing it with previous versions.
+
 % We have to
@@
 
-The hypothesis of this paper is that the use of automatically calculated overlapped sections of the
+The hypothesis of this paper is that the use of \textcolor{blue}{automatically} calculated overlapped sections of the
 chromosome for the SLA can improve the
@@
 the baseline, disjoint and partly overlapped methods. 
-These overlapped sections are calculated from the number of available islands, in a
-multi-objective island-based algorithm, and tested in a real computational environment.
+\textcolor{blue}{The size of the overlapped sections are calculated from  the number of available subpopulations in the multi-objective evolutionary algorithm, and tested in a real computational environment.}
 
@@
 
-% Parallel multiobjective optimization is the theme. And there are
-% papers that do that. Please include them in the state of the art:
-% dennis2003parallel (added to bibliography).
-FERGU: why this paper in particular?
-It parallelizes the fitness function steps and it is not multi-objective.
-It does not even describes the GA in detail.
+%FERGU: Texto que me ha pasado Julio
+%\textcolor{blue}{Multi-objective optimization evolutionary algorithms (MOEAs) can take advantage of parallel and distributed processing \cite{Gong15models} not only to improve the quality of the solutions found, but also to speed up the execution times.
+Among the functional and data decomposition alternatives to parallelize an algorithm, parallel evolutionary algorithms usually implement data decomposition by identifying tasks that have to be repeatedly executed on different data.
+For example, in an evolutionary algorithm, the evaluation of the fitness function and the application of mutation operators to the individuals of the population can be independently applied to each individual.
+Moreover, in the context of data decomposition, two main alternatives can be distinguished.
+In the first one, the individuals of the population are distributed among several processes that independently compute their corresponding fitness functions.
+Once each process completes the fitness evaluation of the individuals allocated to it, another process applies the corresponding evolutionary operators to the individuals of the whole population to determine the population for the next generation.
+Then, the population is distributed again among the processes to obtain the new values of the fitness and so on until the end condition (a given number of generations, or a solution quality level) is met.
+It is clear that this alternative does not modify the convergence characteristics of the corresponding sequential evolutionary algorithm, although to complete each iteration communication is required between the process that applies the evolutionary operators to the population and the processes that evaluate the fitness values of the population.
+In the second alternative, several parallel processes execute iterations of the corresponding evolutionary algorithm on different subpopulations.
+In this case, the convergence behaviour could be different in sequential and parallel versions of the algorithms as the different subpopulations evolve in parallel and only exchange information about their individuals after completing a given number of generations.
+The number of individuals in the subpopulations (the grain size of the parallel procedure), and the characteristics of the communication (frequency of communication, character synchronous or asynchronous of the communication, characteristics of the communicated data, etc.) determine the performance of the parallel procedure.
+This second parallelization alternative (concurrent execution of evolutionary algorithms over multiple subpopulations) is the one considered in this paper.
+It can be implemented either by a master-worker approximation or by assigning each subpopulation to a different processor and communicating this processor with the others when it is required.
+In this second approach, according to the size of the grain (number of individuals in the subpopulations), two main alternatives can be also distinguished: the island parallel approach (coarse grain) and the cellular or diffusion approach (fine grain).
+In the master-worker approximation, the master distributes the subpopulations among the workers that communicate through the master.
+This way, as the communications increase (with the number of subpopulations and/or the frequency of communications among subpopulations) the master could become a bottleneck that reduces the efficiency of the parallel procedure.}
 
@@
 and add a simple communication mechanism among them. But in the case of
-MOEAs, the distribution and parallelization is not as direct as in
+MOEAs, the distribution and parallelization is \textcolor{blue}{more difficult}
 single-objective EAs. This is because in different steps of the
@@
 \citep{cheng2015adaptive}. 
-Even other types of metaheuristics, 
-such as the Multi-Objective Ant Colony Optimization (MOACO) 
-or Artificial Bee Colony Algorithm, 
+\textcolor{blue}{Even other types of metaheuristics, 
+such as the Multi-Objective Ant Colony Optimization (MOACO) \cite{Mora13paretobased}
+or Artificial Bee Colony Algorithm \cite{LUO2017235}, 
 can rely on island models to divide the search space depending on 
-the node to achieve better results \cite{Mora13paretobased,LUO2017235}.
+the node to achieve better results. }
 
@@
 been used, and on this occasion, the experiments have been run on a parallel
-cluster. Therefore, at the same time we are proposing an automatic
-method to divide the individual search space, and also validating the
-previous approach.
+cluster. 
+\textcolor{blue}{Therefore, at the same time, we are proposing a new method to divide the individual search space according to the number of evolved subpopulations, and also validating the previous approach.}
 
@@
 
-\section{Methodology} % This should be called
-                                % methodology. The object of the
-                                % section is to explain the
-                                % methodology used to test the
-                                % problem, in order to do that we have
-                                % tested different versions that prove
-                                % that our methodology works for the
-                                % precise reasons we think it works- JJ FERGU: Done, and explained
+\section{Methodology} 
 \label{sec:methodology}
@@
 
-%This probably should deserve a "Algorithm" environment too - JJ FERGU: You mean the LaTeX one? I've used it in the pseudocode figures
 This basic distributed algorithm spreads the population among $P$
@@
 \includegraphics[width=12cm]{islandDisjoint.jpg}
-\caption{SLA with disjoint islands (D): every island $p$ only modifies the $p_{th}$ components (in grey) of the individuals.}
+\caption{SLA with disjoint islands (D): every island $p$ only modifies the $p_{th}$ components (in grey) of the individuals \textcolor{blue}{using genetic operators (crossover and mutation).
+Also, every island evaluates its own individuals using the complete chromosome.
+After a given number of generations it cooperates with the other islands through migration.}}
 \label{fig:disjoint}
@@
 \caption{SLA with overlapping islands (O): every island $p$ modifies the  $p+1$,
-  $p_{th}$ and $p-1$  components (in grey) of the individuals.}
+  $p_{th}$ and $p-1$  components (in grey) of the individuals \textcolor{blue}{using genetic operators (crossover and mutation).
+Also, every island evaluates its own individuals using the complete chromosome.
+After a given number of generations it cooperates with the other islands through migration.}}
   \label{fig:overlapping}
@@
 \caption{\textcolor{blue}{Automatic} SLA with overlapping islands (A): every island $p$ modifies the  $p+c$,
-  $p_{th}$ and $p-c$  components (in grey) of the individuals. $c$ is calculated depending on the number of islands. In this case, $c=2$.}
+  $p_{th}$ and $p-c$  components (in grey) of the individuals \textcolor{blue}{using genetic operators (crossover and mutation).
+Also, every island evaluates its own individuals using the complete chromosome.
+After a given number of generations it cooperates with the other islands through migration.} $c$ is calculated depending on the number of islands.
+In this case, $c=2$.}
   \label{fig:adaptive}
@@
 Mathematical formulation of each function is available in \citep{zdt2000a}.
-The optimal PF distribution used for comparison has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.}.
 
@@
 The ECJ framework \citep{ECJ} has been used to run the
-experiments, including its own random number generation implementation. Specific operators have been developed as new modules for
-ECJ, and their source code can be downloaded from our GitHub repository under a
+experiments, including its own random number generation implementation.  \textcolor{blue}{The specific modifications to deal with the proposed approaches have been developed as new modules for
+ECJ}, and their source code can be downloaded from our GitHub repository under a
 LGPL V3 License
-\footnote{\url{https://github.com/hpmoon/hpmoon-islands}}. 
-%\footnote{\url{https://ANONYMOUS-REPOSITORY}}. 
+\footnote{\url{https://github.com/hpmoon/hpmoon-islands}}. \textcolor{blue}{The quality metrics (HV, Spread and IGD) have been calculated using the jMetal \cite{Durillo11Jmetal} library.}
+
 The
@@
 Different metrics, previously explained, have been used
-to calculate the quality of the obtained PFs in each configuration. As
-some of the metrics  (such as HV) require a reference point to be
-calculated, the point (1,9) has been chosen as reference, as none of
-the generated PFs in all runs \textcolor{blue}{is} dominated by it. Metrics are then
-normalized respecting to that point. A Kruskal-Wallis significance
+to calculate the quality of the obtained PFs in each configuration. \textcolor{blue}{As HV require a reference point to be
+calculated (see Figure \ref{fig:hypervolume}), we have chosen the value (1,9) as none of the existing solutions on all fronts obtained during all executions is dominated by it.
+In other words, as we are minimizing in both objectives, this reference point is required to be numerically larger or equal in each objective, and strictly larger in at least one of them (dominated) for all solutions in the PFs we are going to measure.
+HV is then
+normalized respecting to that point.
+Also, the optimal reference PF distribution used to calculate the IGD and Spread metrics has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.} }.
+A Kruskal-Wallis significance
 test has been performed to the metrics of all runs of the
@@
 %ZDT1 
-\textcolor{blue}{FINISH THIS SECTION!!!!
-Plotting the final PFs of each combination of parameters, problems and sizes also allow to see the different ....
-ZDT1 has a convex Pareto-optimal front.
+\textcolor{blue}{Plotting the final PFs of each parameter combination also allow to see visually the effect of the different chromosome sizes and number of islands in each different problem.
+The first one, ZDT1, has a convex Pareto-optimal front.
 Comparing results from $L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=512$ (Figure \ref{fig:plot_zdt1_2048}) it is visually clear that the quality of the generated PFs depends on the chromosome size.
@@
 It can be seen in Figure \ref{fig:plot_zdt1_2048}) that solutions obtained by the SLA methods are more dispersed than the baseline as $P$ grows.
-However, with $A$, the area covered by the PF is larger.}
+However, with $A$, the area covered by the PF is still larger.}
 
@@
 \textcolor{blue}{ZDT2 has a non-convex Pareto-optimal front.
-This is the reason that some solutions ....WHAT.
-As in previous problem, there is a decrease of quality in all configurations when increasing the size of $P$.}
+This is the reason that some solutions ....WHAT......
+With $L=512$ As in previous problem, there is a decrease of quality in all configurations when increasing the size of $P$.}
 
@@
 This can be explained because...
-In the case of $L=2048$...}
+WHAT  In the case of $L=2048$, the rightmost part appears in all configurations, and being the Spread metric not significantly different between all the configurations (as shown in Table \ref{tab:results2048}), the HV metric is the only that can be used can be used to show the effectiveness of our approach in this type of problem with non-continuous PFs.}
 
 \textcolor{blue}{In ZDT6, the Pareto-optimal solutions are not only non-uniformly distributed along the PF, but their density also increases as we move further away from it.
-That is the reason why some PFs obtained have a extremely low number of solutions in some configurations, and also, they are aggregated toward the areas with more density...}
+That is the reason why some PFs obtained have a extremely low number of solutions in some configurations, and also, they are aggregated toward the areas with more density.
+Moreover, all configurations, including $B$, obtained PFs relatively far away from the optimal PF, as opposed as in previous problems.
+Spread is very similar between all methods with the different $L$ sizes, that there was not significant difference between methods, with some exceptions: Spread using $A$ with $L=512$ was significantly worse.
+As in previous approaches it is visually clear than increasing the number of islands, and therefore, reducing the number of individual per island, imply a decrease in quality of the HV.}
 

### 2018-06-06 hpmoon-asoco.tex
Addressing @julioortega comments and a lot of explanations about parameters, so closing #25 #21 #20

@@
 
-In these methods %which ones? coevolutionary or selective operator
+%In these methods %which ones? coevolutionary or selective operator
                    %application? - JJ
-  each processor deals only with a part of the decision
-space, that is, the individuals belonging to the same sub-population,
-\textcolor{blue}{which are called {\em islands} in this context}, explore the same subset of decision variables. However, only
+%  each processor deals only with a part of the decision
+%space, that is, the individuals belonging to the same sub-population,
+%\textcolor{blue}{which are called {\em islands} in this context}, explore the same subset of decision variables. 
+\textcolor{blue}{An approach to cope with these issues is to allocate parts of the decision space to different
+processors. Thus, each processor only deals with the individuals of a sub-population (called
+island in this context) that explores the part of the decision space allocated to the processor.}
+
+However, only
 decomposable problems could be strictly implemented in parallel this
@@
  % which results? - JJ PABLO: answered
-But in this paper, a new method to automatically
+In this paper, a new method to automatically
 adapt the size of the overlapping, or shared sections, of the
@@
 efficient alternative to distribute the decision variables.  
-\textcolor{blue}{This opens up a new challenge that can be addressed in the future.}
+\textcolor{blue}{This opens up a new challenge that to be addressed in the future.}
 % This
@@
 for all objectives; the objective of MOP algorithms is to find as many
-solutions in the Pareto Front as possible, and in order to do that the
+solutions equally distributed in the Pareto Front as possible, and in order to do that the
 exploration of the search space must be very efficient, trying to
@@
 they are population-based helps find many solutions that compose the
-Pareto fron simultaneously.
+Pareto front simultaneously.
 
@@
 evaluates each candidate solution, called \emph{individual}, assigning
-it a \emph{fitness} value, that describes how good the individual is
+it a \emph{fitness} value that describes how good the individual is
 with regard to the target problem. New solutions are then generated by
@@
 
-\textcolor{blue}{MOPs usually require a high number of decision variables \cite{Zhang17DECAL,XU2018268}}, % No they don't, and
+\textcolor{blue}{Real-world MOPs usually require a high number of decision variables \cite{Zhang17DECAL,XU2018268}}, % No they don't, and
                                 % if they do, add a reference - JJ FERGU: added references
@@
 A similar approach used to solve this kind of problems is the {\em
-  selective operator application} (SLA). In this case, each island
+  selective operator application} (SLA) \textcolor{blue}{presented in this paper}. In this case, each island
 deals with the whole chromosome, but only modifies a fragment of it in
@@
 can improve the quality of the solutions 
-when the number of islands is increased. On that paper we proved that the most
+when the number of islands is increased. On that paper we showed that the most
 adequate overlapping size may vary depending on a relation between the
@@
 The division of the search space has been explored by other researchers, for example, dividing the population in elite and search sub-populations \citep{Wang09parallel}, or separating it in processors by objective \citep{Xiao03specialized}.
-\textcolor{blue}{For example, in \cite{Zhang17DECAL}, a weighted function is used to decompose the objective function and every subpopulation is responsible to solve the problem defined by a weighted vector.} Other authors, such as Martens \citep{Martens13asynchronous} use migration to accept individuals based on diversity, and migrating from not-crowded areas.
+\textcolor{blue}{For example, in \cite{Zhang17DECAL}, a weighted function is used to decompose the objective function and every subpopulation is responsible to solve the problem defined by a weighted vector.} Other authors, such as M{\"a}rtens \citep{Martens13asynchronous} use migration to accept individuals based on diversity, and migrating from not-crowded areas.
 
@@
 
-The approach described by Dorronsoro et al. has also been used by Kimovski et al. \citep{Kimovski15Parallel}, but using a
+The approach described by Dorronsoro et al. has also been used by Kimovski et al. \citep{Kimovski15Parallel}, but implementing a
 master-slave method that splits the population into several processors. As in previous works, each node
@@
 number of islands were bigger than 8. On the contrary, when the number of
-islands is small, no overlapping is necessary. So, we have used this
-knowledge to create the formula $c=round(0.2*P-1)/2$ to calculate the
-extra sections to overlap. Therefore, when $P=8$ then $c=0$
+islands is small, no overlapping is necessary. \textcolor{blue}{So, we have used this
+knowledge to propose the formula $c=round(0.2*P-1)/2$ to calculate the
+extra sections to overlap}. Therefore, when $P=8$ then $c=0$
 (equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so
 on.
-\textcolor{blue}{Dividing individuals by blocks of equal size, instead a percentage, allow the future integration of our method with other recombination mechanisms, such as the ones presented in \cite{Dorronsoro13superlinear} or \cite{Kimovski15Parallel}}.
-Also, as mentioned, this is only a first approach to obtain $c$, and future work will study new methods to calculate it. Figure \ref{fig:adaptive} explains this method.
+\textcolor{blue}{Dividing individuals by blocks of equal size, instead a percentage, allow the future integration of our method with other recombination mechanisms, such as the ones presented in \cite{Dorronsoro13superlinear} or \cite{Kimovski15Parallel}.
+Also, as mentioned, this is only a possible formula to reach above described behaviour for $c$, and future work will study new methods or alternative formulas to determine it, for example using Taguchi Method \cite{Keratmatpour2018Taguchi}.
+Figure \ref{fig:adaptive} explains the $A$ method, assuming that $c=2$, for example.
+}
 
@@
 maximum number of islands has also been  used in a previous work in the
-literature \citep{Martens13asynchronous}. The crossover and mutation
+literature \cite{Martens13asynchronous}. The crossover and mutation
 chosen, SBX and polynomial, have also been  used previously by other
-authors in \citep{Durillo08masterslave}.  % SBX is first mentioned
+authors in \cite{Durillo08masterslave}.  % SBX is first mentioned
                                 % here. Has to explain - JJ
@@
 Mathematical formulation of each function is available in \citep{zdt2000a}.
+
+\textcolor{blue}{The global population size is set to 1024.
+We have decided to use that value for two reasons: the first is that it is large enough to have 8 individuals per island by dividing that number when using 128 islands and small enough to have 128 individuals when using 8 islands.
+This is the minimum and maximum population size per island used by M{\''a}rtens et al.
+in his work \cite{Martens13asynchronous}.}
 
@@
 \textcolor{blue}{The individual chosen to migrate is selected using Binary Tournament, as it has been previously used by other authors \cite{xiong2003parallel,Xiao03specialized}.
-As there is not a synchronization step to arrange the individual parts besides the specific crossover and mutation operations, the destination island after migration is chosen randomly to ensure that the modified parts of the migrated individual can be shared in the whole set of different islands.
+As there is not a synchronization step to arrange the individual parts besides the specific crossover and mutation operations, the destination island after migration is chosen randomly to ensure that the modified parts of the migrated individual can be taken into account by the whole set of  islands.
 Migration is performed asynchronously, as it have the advantage of being a non-blocking operation \cite{TalbiUnified2018}.}
  The whole parameter set is summarized in Table \ref{tab:parameters}. 
+ \textcolor{blue}{It is important to point out that we have carried out experiments modifying only the number of islands and the size of the problem, as other researchers have done \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}, who did not carry out studies on other parameters apart from these.
+This allows us to focus on the objective of this article, which is to demonstrate that on equal terms, the use of SLA can lead to improved performance depending on the combination of the number of islands and the size of the chromosome.}
 
@@
 @2.27GHz processors, 16 GB RAM, Broadcom NetXtreme II BCM5716 1000Base-T (C0) PCI Express network cards, CentOS 6.8 and Java Version 1.8.0\_80.
-Islands have been first distributed among the nodes.
-That means that, for example, running with 8 islands requires 8 different nodes, instead of the usage of the 8 processors of a single node.
+\textcolor{blue}{Islands are allocated to nodes in a round-robin way.
+That means that, for example, running with 8 islands requires 8 different nodes, instead of using several cores of a single node.}
 
@@
 Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than the obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply these methods.
-A contradictions arises with respect to the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths.
+A contradiction arises with respect to the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths.
 This can be explained because the added migration latency between nodes of the cluster requires more time than the time saved during the crossover and migration.
@@
 
-However, with 2048 dimensions, results show that dividing the chromosome produces an improvement in all the quality indicators using the automatic ($A$) version (Table \ref{tab:results2048}), even improving the overlapping and disjoint methods.
+However, with 2048 dimensions, results show that dividing the chromosome produces an improvement in all the quality indicators using the automatic ($A$) version (Table \ref{tab:results2048}), even overcoming the overlapping ($O$) and disjoint ($D$) methods.
 Therefore, there exist some kind of limit point in chromosome length where one method will be preferable to another, besides depending on the number of islands and population size.
@@
 it happens with $L=512$. Therefore, more generations do not
-necessarily improve the solution of the global PF, but focusing on
+necessarily mean improve the solution of the global PF, but focusing on
 different elements of the chromosome. As  previously stated, every
@@
 %ZDT1 
-\textcolor{blue}{Plotting the final PFs of each parameter combination also allow to see visually the effect of the different chromosome sizes and number of islands in each different problem.
+\textcolor{blue}{Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048}, showing the final PFs of one run of each combination, also allow to visualize the effect of the different chromosome sizes and number of islands in each different benchmark.
 The first one, ZDT1, has a convex Pareto-optimal front.
-Comparing results from $L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=512$ (Figure \ref{fig:plot_zdt1_2048}) it is visually clear that the quality of the generated PFs depends on the chromosome size.
+Comparing results from $L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) it is apparent that the quality of the generated PFs depends on the chromosome size.
 Specifically, with $L=512$ it can be seen that the PFs quality decreases in Spread and HV with all configurations, but the SLA methods behave worse than $B$, as it also was shown in average in Table \ref{tab:results512}.
-But if we focus on the plots obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this difference is less clear.
-It can be seen in Figure \ref{fig:plot_zdt1_2048}) that solutions obtained by the SLA methods are more dispersed than the baseline as $P$ grows.
+Nevertheless, if we focus on the plots obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this difference is less clear.
+It can be seen in Figure \ref{fig:plot_zdt1_2048} that solutions obtained by the SLA methods are more dispersed than the baseline as $P$ grows.
 However, with $A$, the area covered by the PF is still larger.}
@@
 %ZDT2
-\textcolor{blue}{ZDT2 has a non-convex Pareto-optimal front.
-This is the reason that some solutions ....WHAT......
-With $L=512$ As in previous problem, there is a decrease of quality in all configurations when increasing the size of $P$.}
+\textcolor{blue}{ZDT2 has a non-convex Pareto front as it is shown in Figures 7 and 8.
+From these figures is clear that, as in the previous problem ZDT1, there is a decrease of quality for all configurations as the size of $P$ increases.
+Nevertheless, for this benchmark, there is not a clear decrease in the PF quality when $L$ goes from 512 to 2048.}
 
@@
 \textcolor{blue}{ZDT3 Pareto-optimal front is formed by non-contiguous convex parts, and plots for both chromosome sizes (Figures \ref{fig:plot_zdt3_512} and \ref{fig:plot_zdt3_2048}) show solutions gathered in similar regions in all configurations.
-However, with $L=512$, some the $A$ configurations skip the last region on the right with $P=8$  and $P=16$ (being equivalent to $O$ and $A$).
-This can be explained because...
-WHAT  In the case of $L=2048$, the rightmost part appears in all configurations, and being the Spread metric not significantly different between all the configurations (as shown in Table \ref{tab:results2048}), the HV metric is the only that can be used can be used to show the effectiveness of our approach in this type of problem with non-continuous PFs.}
+However, with $L=512$, some of the $A$ configurations skip the last region on the right with $P=8$  and $P=16$ (being equivalent to alternatives $O$ and $A$).
+In the case of $L=2048$, the rightmost part appears in all configurations, and being the Spread metric not significantly different between all the configurations (as shown in Table \ref{tab:results2048}), the HV metric is the only one that can be used to show the effectiveness of our approach in this type of problem with non-continuous PFs.}
 
 \textcolor{blue}{In ZDT6, the Pareto-optimal solutions are not only non-uniformly distributed along the PF, but their density also increases as we move further away from it.
-That is the reason why some PFs obtained have a extremely low number of solutions in some configurations, and also, they are aggregated toward the areas with more density.
+That is the reason why some PFs obtained have an extremely low number of solutions in some configurations, and also, they are aggregated toward the areas with more density.
 Moreover, all configurations, including $B$, obtained PFs relatively far away from the optimal PF, as opposed as in previous problems.
-Spread is very similar between all methods with the different $L$ sizes, that there was not significant difference between methods, with some exceptions: Spread using $A$ with $L=512$ was significantly worse.
-As in previous approaches it is visually clear than increasing the number of islands, and therefore, reducing the number of individual per island, imply a decrease in quality of the HV.}
-
-Finally, as it was already observed in \citep{Garcia16hpmoon}, results
-show that all the quality indicators decrease in value when the number of islands is increased, as the  sizes of the subpopulations are smaller.
+Spread is very similar for all methods $B$, $D$, $O$, $A$ across different $L$ sizes.
+Indeed, there is not significant difference between methods, with an exception: Spread using $A$ with $L=512$ is significantly worse.
+As in previous approaches it is visually clear that increasing the number of islands, and therefore, reducing the number of individuals per island, imply a decrease in quality of the HV.}
+
+\textcolor{blue}{Finally, as it was already observed in \citep{Garcia16hpmoon}, all the performance indicators show worse values as the number of islands increases, and so the  sizes of the subpopulations are smaller.
 This is consistent with the claim by Dorronsoro et al.
-\citep{Dorronsoro13superlinear}, who found that cooperative co-evolutionary MOEAs work better on bigger populations (more than 100 individuals).
+\citep{Dorronsoro13superlinear}, who found that cooperative co-evolutionary MOEAs work better on bigger populations (more than 100 individuals).}
 
@@
 different ways to calculate $c$ using linear, logarithmic or exponential functions
-depending \textcolor{blue}{on population size, number of islands, or other values}. Moreover, a diversity analysis of the individuals
+depending \textcolor{blue}{on population size, number of islands, or other values, or using some statistical parameter setting method, such as Taguchi's \cite{Keratmatpour2018Taguchi}}.
+Moreover, a diversity analysis of the individuals
 in each island during the algorithm run could be carried out to understand its influence
@@
 different methods, being the transmission time between islands a
-relevant issue to be addressed. Other MOEA algorithms available in the literature, such as SPEA or MOEA/D could be compared. Finally, new benchmarks and real problems
-could also be  used to validate this approach.
+relevant issue to be addressed. \textcolor{blue}{Other MOEA algorithms available in the literature, such as SPEA or MOEA/D could also be compared. Moreover, new benchmarks and real problems
+could be  used to validate this approach.}
 
 \section*{Acknowledgements}
-This work has been partially funded by projects TIN2014-56494-C4-3-P, TIN2015-67020-P and TIN2017-85727-C4-2-P (Spanish Ministry of Economy and Competitiveness and FEDER).
+
+This work has been partially funded by projects SPIP2017-02116, EphemeCH TIN2014-56494-C4-3-P, DeepBio TIN2017-85727-C4-2-P and TEC2015-68752.
+We would like to express our gratitude to the editorial team and the reviewers, whose valuable comments on this paper have significantly improved its quality.
 

### 2018-06-07 hpmoon-asoco.tex
More changes by Julio

@@
 The number of generations between migrations has been set to 5, as this number is usually repeated in the literature \cite{Deb03distributed,Martens13asynchronous}.
-\textcolor{blue}{The individual chosen to migrate is selected using Binary Tournament, as it has been previously used by other authors \cite{xiong2003parallel,Xiao03specialized}.
-As there is not a synchronization step to arrange the individual parts besides the specific crossover and mutation operations, the destination island after migration is chosen randomly to ensure that the modified parts of the migrated individual can be taken into account by the whole set of  islands.
-Migration is performed asynchronously, as it have the advantage of being a non-blocking operation \cite{TalbiUnified2018}.}
+\textcolor{blue}{Migration is performed asynchronously, as it has the advantage of being a non-blocking operation \cite{TalbiUnified2018}.
+The individual chosen to migrate is selected using Binary Tournament, as proposed in previous papers  \cite{xiong2003parallel,Xiao03specialized}.
+Whenever an island starts the migration step, the migrated individual is sent to another randomly selected island.
+This makes it possible a dissemination of the modified parts of the individuals among the whole set of islands, thus avoiding a specific synchronization step to compose solutions obtained by different islands, as occurs other works \cite{Dorronsoro13superlinear}.}
  The whole parameter set is summarized in Table \ref{tab:parameters}. 
@@
 %ZDT1 
-\textcolor{blue}{Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048}, showing the final PFs of one run of each combination, also allow to visualize the effect of the different chromosome sizes and number of islands in each different benchmark.
+\textcolor{blue}{Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048}, showing the final PFs of one arbitrary sample run of each combination.
+These figures allow to visualize the effect of the different chromosome sizes and number of islands in each different benchmark.
 The first one, ZDT1, has a convex Pareto-optimal front.
@@
 %ZDT2
-\textcolor{blue}{ZDT2 has a non-convex Pareto front as it is shown in Figures 7 and 8.
-From these figures is clear that, as in the previous problem ZDT1, there is a decrease of quality for all configurations as the size of $P$ increases.
+\textcolor{blue}{ZDT2 has a non-convex Pareto front.
+From Figures \cite{fig:plot_zdt2_512} and \cite{fig:plot_zdt2_2048} is clear that, as in the previous problem ZDT1, there is a decrease of quality for all configurations as the size of $P$ increases.
 Nevertheless, for this benchmark, there is not a clear decrease in the PF quality when $L$ goes from 512 to 2048.}
@@
 \textcolor{blue}{ZDT3 Pareto-optimal front is formed by non-contiguous convex parts, and plots for both chromosome sizes (Figures \ref{fig:plot_zdt3_512} and \ref{fig:plot_zdt3_2048}) show solutions gathered in similar regions in all configurations.
-However, with $L=512$, some of the $A$ configurations skip the last region on the right with $P=8$  and $P=16$ (being equivalent to alternatives $O$ and $A$).
-In the case of $L=2048$, the rightmost part appears in all configurations, and being the Spread metric not significantly different between all the configurations (as shown in Table \ref{tab:results2048}), the HV metric is the only one that can be used to show the effectiveness of our approach in this type of problem with non-continuous PFs.}
+However, with $L=512$, the rightmost part of the obtaninde non-dominated solutions is not obtained in the $A$ alternative with $P=8$  and $P=16$ (being equivalent to alternatives $O$ and $D$).
+This explains why with this chromosome length, the SLA methods not improve the results obtained by $B$.
+This problem does not appear when $L=2048$.
+Although the differences in the Spread metric are not significant for the different alternatives for this benchmark, (as shown in Table \ref{tab:results2048}), the HV and IGD metrics are the ones that can be used to show the effectiveness of our approach in this type of problem with non-continuous PFs.}
 
@@
 
-This work has been partially funded by projects SPIP2017-02116, EphemeCH TIN2014-56494-C4-3-P, DeepBio TIN2017-85727-C4-2-P and TEC2015-68752.
+This work has been partially funded by project SPIP2017-02116 (Spanish ``Direcci\'on General de Tr\'afico''), and projects EphemeCH TIN2014-56494-C4-3-P, TIN2015-67020-P, DeepBio TIN2017-85727-C4-2-P  and TEC2015-68752 (Spanish ``Ministerio de
+Econom{\'ia}a y Competitividad'' and ERDF funds).
 We would like to express our gratitude to the editorial team and the reviewers, whose valuable comments on this paper have significantly improved its quality.

### 2018-06-07 hpmoon-asoco.tex
Some typos fixed

@@
 to calculate the quality of the obtained PFs in each configuration. \textcolor{blue}{As HV require a reference point to be
-calculated (see Figure \ref{fig:hypervolume}), we have chosen the value (1,9) as none of the existing solutions on all fronts obtained during all executions is dominated by it.
+calculated (see Figure \ref{fig:hypervolume}), we have chosen the value (1,9) as none of the existing solutions on all fronts obtained during all executions are dominated by it.
 In other words, as we are minimizing in both objectives, this reference point is required to be numerically larger or equal in each objective, and strictly larger in at least one of them (dominated) for all solutions in the PFs we are going to measure.

### 2018-06-08 hpmoon-asoco.tex
some other typos fixed

@@
 \usepackage{url}
+%\usepackage{refcheck}
 \usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
@@
 can improve the quality of the solutions 
-when the number of islands is increased. On that paper we showed that the most
+when the number of islands is increased. In that paper, we showed that the most
 adequate overlapping size may vary depending on a relation between the
@@
 %This is an improvement over the previous? What is the relationship? FERGU: linked
-Other kind of approaches have also been explored.
+\textcolor{blue}{Another kind of approaches has also been explored}.
 The work by Deb et al.
@@
 In that work, the dominance of the solutions was divided into the islands using a coordinate transformation.
-In that paper, authors concluded that dividing the search space is a good idea, although achieving this is not trivial.
+In that paper, the authors concluded that dividing the search space is a good idea, although achieving this is not trivial.
 The division of the search space has been explored by other researchers, for example, dividing the population in elite and search sub-populations \citep{Wang09parallel}, or separating it in processors by objective \citep{Xiao03specialized}.
@@
 in several instances.
-\textcolor{blue}{Recently, this approach has also been tested using a Particle Swarm Optimization (PSO) algorithm \cite{DorronsoroPSO2018}, also obtaining significant improvements in speedups and solution quality}.
+\textcolor{blue}{Recently, this approach has also been tested using a Particle Swarm Optimization (PSO) algorithm \cite{DorronsoroPSO2018}, also obtaining significant improvements in speedups and solution quality.
+Others authors, such as Cao et al.
+\cite{CaoZLL17} separate the decision variables into several subpopulations after performing an interdependence analysis, but using a fixed number of processors.}
 
@@
 crossed and mutated in the same way, depending on the island
-identifier (from 1 to $P$). Note that, differently from other works such as the ones
-described by Talbi et al. \citep{Talbi08Parallel}, all the islands deal
+identifier (from 1 to $P$). \textcolor{blue}{Note that, unlike the other works such as the ones
+described by Talbi et al. \citep{Talbi08Parallel}}, all the islands deal
 with complete chromosomes for fitness calculation, so our approach can
@@
 \includegraphics[width=6cm]{hypervolume.jpg}
-\caption{Hypervolume calculation. Areas from Pareto Front solutions (black points) to a reference point (white point) are added.}
+\caption{Hypervolume calculation.
+\textcolor{blue}{Areas from Pareto Front solutions (black points) to a reference point (white point) are used to calculate the value of the hypervolume (all the gray area)}.}
 \label{fig:hypervolume}
@@
 chosen, SBX and polynomial, have also been  used previously by other
-authors in \cite{Durillo08masterslave}.  % SBX is first mentioned
+authors in \cite{Durillo08masterslave,CaoZLL17}.  % SBX is first mentioned
                                 % here. Has to explain - JJ
@@
 We have decided to use that value for two reasons: the first is that it is large enough to have 8 individuals per island by dividing that number when using 128 islands and small enough to have 128 individuals when using 8 islands.
-This is the minimum and maximum population size per island used by M{\''a}rtens et al.
+This is the minimum and maximum population size per island used by M{\"a}rtens et al.
 in his work \cite{Martens13asynchronous}.}
@@
 \ref{tab:results2048} (for 2048). As previously explained, when $P=8$
-the results of A are equivalent to the obtained with D (because
+the results of A are equivalent to the obtained by D (because
 $c=0$), and when $P=16$ they are equivalent to O ($c=1$).
@@
 Comparing results from $L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) it is apparent that the quality of the generated PFs depends on the chromosome size.
-Specifically, with $L=512$ it can be seen that the PFs quality decreases in Spread and HV with all configurations, but the SLA methods behave worse than $B$, as it also was shown in average in Table \ref{tab:results512}.
+Specifically, with $L=512$ it can be seen that the PFs quality decreases in Spread and HV with all configurations, but the SLA methods behave worse than $B$, as it also was shown on average in Table \ref{tab:results512}.
 Nevertheless, if we focus on the plots obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this difference is less clear.
@@
 \textcolor{blue}{ZDT2 has a non-convex Pareto front.
-From Figures \cite{fig:plot_zdt2_512} and \cite{fig:plot_zdt2_2048} is clear that, as in the previous problem ZDT1, there is a decrease of quality for all configurations as the size of $P$ increases.
+From Figures \ref{fig:plot_zdt2_512} and \ref{fig:plot_zdt2_2048} is clear that, as in the previous problem ZDT1, there is a decrease of quality for all configurations as the size of $P$ increases.
 Nevertheless, for this benchmark, there is not a clear decrease in the PF quality when $L$ goes from 512 to 2048.}
@@
 However, with $L=512$, the rightmost part of the obtaninde non-dominated solutions is not obtained in the $A$ alternative with $P=8$  and $P=16$ (being equivalent to alternatives $O$ and $D$).
-This explains why with this chromosome length, the SLA methods not improve the results obtained by $B$.
+This explains why with this chromosome length, the SLA methods do not improve the results obtained by $B$.
 This problem does not appear when $L=2048$.
@@
 Spread is very similar for all methods $B$, $D$, $O$, $A$ across different $L$ sizes.
-Indeed, there is not significant difference between methods, with an exception: Spread using $A$ with $L=512$ is significantly worse.
+Indeed, there is not a significant difference between methods, with an exception: Spread using $A$ with $L=512$ is significantly worse.
 As in previous approaches it is visually clear that increasing the number of islands, and therefore, reducing the number of individuals per island, imply a decrease in quality of the HV.}
@@
 in each island during the algorithm run could be carried out to understand its influence
-on results.
+on the results.
 % 

### 2018-06-10 hpmoon-asoco.tex
Addressing some @JJ comments

@@
 \textcolor{blue}{Migration is performed asynchronously, as it has the advantage of being a non-blocking operation \cite{TalbiUnified2018}.
-The individual chosen to migrate is selected using Binary Tournament, as proposed in previous papers  \cite{xiong2003parallel,Xiao03specialized}.
+The individual chosen to migrate is selected from the subpopulation using Binary Tournament, as proposed in previous papers  \cite{xiong2003parallel,Xiao03specialized}.
 Whenever an island starts the migration step, the migrated individual is sent to another randomly selected island.
@@
 normalized respecting to that point.
-Also, the optimal reference PF distribution used to calculate the IGD and Spread metrics has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.} }.
+Also, the optimal reference PF distribution used to calculate the IGD and Spread metrics \cite{Durillo11Jmetal} has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.} }.
 A Kruskal-Wallis significance

### 2018-06-10 hpmoon-asoco.tex
Things not addressed since first version @fergunet

@@
 % here. Has to explain - JJ
+% Still not done - JJ
 
@@
 compare different times and quality of solutions at the same time.
-The number of generations between migrations has been set to 5, as this number is usually repeated in the literature \cite{Deb03distributed,Martens13asynchronous}.
-\textcolor{blue}{Migration is performed asynchronously, as it has the advantage of being a non-blocking operation \cite{TalbiUnified2018}.
-The individual chosen to migrate is selected from the subpopulation using Binary Tournament, as proposed in previous papers  \cite{xiong2003parallel,Xiao03specialized}.
-Whenever an island starts the migration step, the migrated individual is sent to another randomly selected island.
-This makes it possible a dissemination of the modified parts of the individuals among the whole set of islands, thus avoiding a specific synchronization step to compose solutions obtained by different islands, as occurs other works \cite{Dorronsoro13superlinear}.}
+
+The number of generations between migrations has been set to 5, as
+this number is usually repeated in the literature
+\cite{Deb03distributed,Martens13asynchronous}. \textcolor{blue}{Migration
+  is performed asynchronously, as it has the advantage of being a
+  non-blocking operation \cite{TalbiUnified2018}. The individual
+  chosen to migrate is selected from the subpopulation using Binary
+  Tournament, as proposed in previous papers
+  \cite{xiong2003parallel,Xiao03specialized}. Whenever an island
+  starts the migration step, the migrated individual is sent to
+  another randomly selected island. This makes it possible a
+  dissemination of the modified parts of the individuals among the
+  whole set of islands, thus avoiding a specific synchronization step
+  to compose solutions obtained by different islands, as occurs other
+  works \cite{Dorronsoro13superlinear}.} 
  The whole parameter set is summarized in Table \ref{tab:parameters}. 

### 2018-06-10 hpmoon-asoco.tex
Justification of the migration gap.
Adding what Martens said, but stating the obvious: it's not the focus
of this paper.

@@
 
-We have chosen those metrics not only because they have been used extensively, especially in some of the papers presented in Section 2 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous}, but also because they cover different quality criteria.
-Mathematical formulation of these metrics can be found in \cite{Dorronsoro13superlinear}.
+We have chosen those metrics not only because they have been used
+extensively, especially in some of the papers presented in Section 2
+% Still section 2? Please create a reference and use it - JJ
+\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous},
+but also because they cover different quality criteria. Mathematical
+formulation of these metrics can be found in
+\cite{Dorronsoro13superlinear}.
 
@@
 
-ZDT \citep{zdt2000a} has been chosen as a benchmark, since it is the most widely used in this area \citep{Deb03distributed,Martens13asynchronous,Wang09parallel,Durillo08masterslave}.
-This benchmark includes several functions, with different features that are representative of real world optimization problems.
-Mathematical formulation of each function is available in \citep{zdt2000a}.
+ZDT \citep{zdt2000a} has been chosen as a benchmark, since it is the
+most widely used in this area
+\citep{Deb03distributed,Martens13asynchronous,Wang09parallel,Durillo08masterslave}. This
+benchmark includes several functions, with different features that are
+representative of real world optimization problems. Mathematical
+formulation of each function is available in \citep{zdt2000a}.
 
@@
 
-The number of generations between migrations has been set to 5, as
-this number is usually repeated in the literature
-\cite{Deb03distributed,Martens13asynchronous}. \textcolor{blue}{Migration
+The number of generations between migrations has been set to 5,
+\textcolor{blue} as
+reported by \cite{Deb03distributed,Martens13asynchronous}. In general
+\cite{cantu1998survey}, this migration gap has contradictory effects
+on the result: by increasing it, we make the system closer to a
+single-node one, since populations tend to mix without restriction; by
+decreasing it, we make the isolate islands more prone to being stuck
+in local minima. \cite{Martens13asynchronous} mentions that several
+values were tested with no influence in the result; in our particular
+case, the mixing is essential for the algorithm to spread the result
+to all parts of the chromosome, so while we tend to agree with
+Martens on the small influence of this value on the result, we also
+think that making this value much bigger in our case would havea
+negative inpact. However, a precise fine-tuning of this value is left
+as future work, as the main focus of this paper was to prove the
+general concept, and not tune the values for a maximum performance}.
+
+\textcolor{blue}{This migration
   is performed asynchronously, as it has the advantage of being a

### 2018-06-10 hpmoon-asoco.tex
Fixing the generation-gap paragraph

@@
 The number of generations between migrations has been set to 5,
-\textcolor{blue} as
+\textcolor{blue}{as
 reported by \cite{Deb03distributed,Martens13asynchronous}. In general
+and as affirmed by 
 \cite{cantu1998survey}, this migration gap has contradictory effects
@@
 Martens on the small influence of this value on the result, we also
-think that making this value much bigger in our case would havea
-negative inpact. However, a precise fine-tuning of this value is left
+think that making this value much bigger in our case would have a
+negative impact. However, a precise fine-tuning of this value is left
 as future work, as the main focus of this paper was to prove the

### 2018-06-10 hpmoon-asoco.tex
Justififying the study of two parameters

@@
   works \cite{Dorronsoro13superlinear}.}
+
  The whole parameter set is summarized in Table \ref{tab:parameters}. 
- \textcolor{blue}{It is important to point out that we have carried out experiments modifying only the number of islands and the size of the problem, as other researchers have done \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}, who did not carry out studies on other parameters apart from these.
-This allows us to focus on the objective of this article, which is to demonstrate that on equal terms, the use of SLA can lead to improved performance depending on the combination of the number of islands and the size of the chromosome.}
+ \textcolor{blue}{The main parameters in the proposed system were the number of islands and the size
+   of the problem, as pointed out by other authors 
+   \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}. This is why those have been the focus of this particular
+   article. Although all the parameters indicated above have an
+   influence on the general result of the MOEA, their general effect
+   is well understood and, although there will be an interplay between
+ them and the number of islands and problem size, this is left mainly
+ as future work.}
 

### 2018-06-10 hpmoon-asoco.tex
Please review the abstract @fergunet

@@
 However, only
-decomposable problems could be strictly implemented in parallel this
+decomposable problems could strictly be implemented in parallel this
 way. \textcolor{blue}{A new approach, which we call {\em selective operator application} is presented here to deal with un-decomposable
@@
           % for non-decomposable problems. What's what? - JJ
+% Still not addressed - JJ
 instead of sharing parts
@@
 specific subset of the whole individual. % this solves... - JJ
+% not addressed - JJ
 We have previously proved
 that extending the length of these subsets, and therefore, sharing
-\textcolor{blue}{some search space between islands, implies an improvement in different performance metrics}.
- % which results? - JJ PABLO: answered
-In this paper, a new method to automatically
-adapt the size of the overlapping, or shared sections, of the
+\textcolor{blue}{some search space between islands, implies an
+  improvement in different performance metrics}.
+% In this paper, we intend to prove that adapting the size of the
+% overlapping section, since it improves *, is able to obtain better
+% results than a non-adaptive strategy. In order to prove that, we
+% compare - JJ
+In this paper, a new method for automatically
+adapting the size of the overlapping, or shared, sections of the
 individuals has been compared to other collaborative evolutionary
@@
 statistically significant improvements with respect to the base
-algorithm \textcolor{blue}{in high-dimensional multi-objective problems}. % in high-dimensional multi-objective problems? - JJ PABLO: ok, puesto
+algorithm \textcolor{blue}{in high-dimensional multi-objective problems}. 
 Results also show that the relation between the number of
@@
 decision variables) is also a relevant factor to determine the most
-efficient alternative to distribute the decision variables.  
+efficient alternative to distribute the decision variables.   % Say
+                                % something how it's relevant, and
+                                % what you have to do if you have so
+                                % many decision variables - JJ
 \textcolor{blue}{This opens up a new challenge that to be addressed in the future.}

### 2018-06-10 hpmoon-asoco.tex
Clarifying how selection to migrate is done
Address some comments

@@
   chosen to migrate is selected from the subpopulation using Binary
-  Tournament, as proposed in previous papers
+  Tournament from a randomly selected couple, as proposed in previous papers
   \cite{xiong2003parallel,Xiao03specialized}. Whenever an island
@@
 \caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+Results for 8 and 16 islands of $A$ are equivalent to running $D$ and $O$ respectively.
 }}
@@
 \caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+Results for 8 and 16 islands of $A$ are equivalent to running $D$ and $O$ respectively.
 }}
@@
 \caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+Results for 8 and 16 islands of $A$ are equivalent to running $D$ and $O$ respectively.
 }}
@@
 \caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+Results for 8 and 16 islands of $A$ are equivalent to running $D$ and $O$ respectively.
 }}
@@
 \caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+Results for 8 and 16 islands of $A$ are equivalent to running $D$ and $O$ respectively.
 }}
@@
 \includegraphics[width=12cm]{plot_zdt3_2048.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the
+    ZDT3 problem with a chromosome size ($L$) of 2048 for each
+    combination of number of islands ($P$) and method: baseline ($B$),
+    disjoint ($D$), overlapped ($O$) and automatic overlapped
+    ($A$). Results for 8 and 16 islands of $A$ are equivalent to
+    running $D$ and $O$ respectively. }}
+% It would be interesting to comment something about what is the key
+% thing here and what's good about it. Without an a priori idea, I
+% wouldn't know which one looks the best - JJ
 \label{fig:plot_zdt3_2048}
@@
 
-%%%%%%FERGU: WARNING, THIS SECTION IS STILL SHIT
+ %%%%%% FERGU: WARNING, THIS SECTION IS STILL SHIT
+ % By now, maybe it should not be (or you should delete this
+ % comment) - JJ
 %ZDT1 

### 2018-06-10 hpmoon-asoco.tex
Minor change to abstract before merging

--- 2018-06-10 hpmoon-asoco.tex
@@
   \textcolor{blue}{Real world optimization problems usually have many dimensions and
-  several objectives. The high dimensionality requires exceptional
+  several objectives, and are usually tackled using Multi-Objective Evolutionary Algorithms. The high dimensionality requires exceptional
   computing power, and the fact that several dimensions have to be
@@
 However, only
-decomposable problems could be strictly implemented in parallel this
+decomposable problems \textcolor{blue}{, those whose decision variables are independent of each other,} could be strictly implemented in parallel this
 way. \textcolor{blue}{A new approach, which we call {\em selective operator application} is presented here to deal with un-decomposable
@@
 A similar approach used to solve this kind of problems is the {\em
-  selective operator application} (SLA) \textcolor{blue}{presented in this paper}. In this case, each island
+  SeLective operator Application} (SLA) \textcolor{blue}{presented in this paper}. In this case, each island
 deals with the whole chromosome, but only modifies a fragment of it in
@@
 to all parts of the chromosome, so while we tend to agree with
-Martens on the small influence of this value on the result, we also
+M{\"a}rtens on the small influence of this value on the result, we also
 think that making this value much bigger in our case would have a
@@
   works \cite{Dorronsoro13superlinear}.} 
-
  The whole parameter set is summarized in Table \ref{tab:parameters}. 
- \textcolor{blue}{The main parameters in the proposed system were the number of islands and the size
-   of the problem, as pointed out by other authors 
-   \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}. This is why those have been the focus of this particular
-   article. Although all the parameters indicated above have an
-   influence on the general result of the MOEA, their general effect
-   is well understood and, although there will be an interplay between
- them and the number of islands and problem size, this is left mainly
- as future work.}
+ \textcolor{blue}{It is important to point out that we have carried out experiments modifying only the number of islands and the size of the problem, as other researchers have done \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}, who did not carry out studies on other parameters apart from these.
+This allows us to focus on the objective of this article, which is to demonstrate that on equal terms, the use of SLA can lead to improved performance depending on the combination of the number of islands and the size of the chromosome.}
 

### 2018-06-10 hpmoon-asoco.tex
I've rewritten the abstract, please @JJ let me know if it more clear now, and if all your questions have been properly addressed :)

@@
 
+\newenvironment{bluecolor}{\par\color{blue}}{\par}
+
 \begin{document}
@@
 
-  \textcolor{blue}{Real world optimization problems usually have many dimensions and
-  several objectives, and are usually tackled using Multi-Objective Evolutionary Algorithms. The high dimensionality requires exceptional
-  computing power, and the fact that several dimensions have to be
-  searched at the same time add additional difficulty.}
-% One of the most extended methods to deal with high-dimensional
-% multi-objective optimization problems are the distributed
-% co-evolutionary algorithms.
-% ----------------- This sentence is meaningless. It should be
-% substituted by other stating that co-evolutionary algorithms can
-% deal with it for some reason
-% Besides, we're no longer saying that they are co-evolutionary in the
-% title, but "island-based selective operator application". This
-% should go to the abstract too - JJ
-
-%In these methods %which ones? coevolutionary or selective operator
-                   %application? - JJ
-%  each processor deals only with a part of the decision
-%space, that is, the individuals belonging to the same sub-population,
-%\textcolor{blue}{which are called {\em islands} in this context}, explore the same subset of decision variables. 
-\textcolor{blue}{An approach to cope with these issues is to allocate parts of the decision space to different
-processors. Thus, each processor only deals with the individuals of a sub-population (called
-island in this context) that explores the part of the decision space allocated to the processor.}
-
+%Real world optimization problems usually have many dimensions and
+%  several objectives, thus requiring exceptional computing power to be addressed.
+
+ % The high dimensionality requires exceptional computing power, and the fact that several dimensions have to be searched at the same time add additional difficulty.
+
+%Usually, distributed co-evolutionary algorithms are used to cope with these issues, by allocating parts of the decision space to different processors.
+Thus, each processor only deals with the individuals of a sub-population (called island in this context) that explores a specific part of the decision space.
+
+\begin{bluecolor}
+One of the most extended methods to deal with high-dimensional multi-objective optimization problems are the distributed co-evolutionary algorithms. %Pablo: reducing previous two paragraphs into one
 However, only
 decomposable problems could strictly be implemented in parallel this
-way. \textcolor{blue}{A new approach, which we call {\em selective operator application} is presented here to deal with un-decomposable
-problems:} % so we are saying that high-dimensional multi-objective
+way.
+
+A new approach, which we call {\em selective operator application}, is used here to deal with un-decomposable
+problems: % so we are saying that high-dimensional multi-objective
           % problems are a challenge, but we are presenting a solution
           % for non-decomposable problems. What's what? - JJ
-% Still not addressed - JJ
+% Still not addressed - JJ PABLO: rewritten almost all the abstract.
 instead of sharing parts
 of individuals, each processor applies the variation operators to a
-specific subset of the whole individual. % this solves... - JJ
-% not addressed - JJ
-We have previously proved
-that extending the length of these subsets, and therefore, sharing
-\textcolor{blue}{some search space between islands, implies an
-  improvement in different performance metrics}.
-% In this paper, we intend to prove that adapting the size of the
-% overlapping section, since it improves *, is able to obtain better
-% results than a non-adaptive strategy. In order to prove that, we
-% compare - JJ
-In this paper, a new method for automatically
-adapting the size of the overlapping, or shared, sections of the
-individuals has been compared to other collaborative evolutionary
+specific subset of the whole individual. This avoids extra steps to recompose the complete individuals from other islands before evaluation. 
+% this solves... - JJ
+% not addressed - JJ Pablo: done now
+%We have previously proved that extending the length of these subsets, and therefore, sharing some search space between islands, implies an improvement in different performance metrics.
+
+ In this paper, we intend to prove that automatically setting the size of the
+ overlapping section, since it focus the search between borders of the different search spaces, is able to obtain better
+ results than using the same size independently of the number of islands. In order to prove that, we
+ have compared it to other collaborative evolutionary
 techniques considering different number of islands, chromosome sizes
@@
 statistically significant improvements with respect to the base
-algorithm \textcolor{blue}{in high-dimensional multi-objective problems}. 
+algorithm in high-dimensional multi-objective problems.
+
 Results also show that the relation between the number of
@@
 decision variables) is also a relevant factor to determine the most
-efficient alternative to distribute the decision variables.   % Say
+efficient alternative to distribute the decision variables: it is better to distribute them the higher the dimensionality, and to increase the overlapping size if individuals are distributed in a large number of islands.
+  % Say
                                 % something how it's relevant, and
                                 % what you have to do if you have so
-                                % many decision variables - JJ
-\textcolor{blue}{This opens up a new challenge that to be addressed in the future.}
-% This
-                                % solves a problem or challenge we
-                                % hadn't stated. - JJ Pablo: metido, mira a ver si queda frase memorable
+                                % many decision variables - JJ PABLO: Done
+This opens up a new challenge to be addressed in the future, by experimenting on new ways to calculate the overlapping sizes depending of different factors and parameters.
+\end{bluecolor}
 
@@
 
-\textcolor{blue}{Real-world MOPs usually require a high number of decision variables \cite{Zhang17DECAL,XU2018268}}, % No they don't, and
-                                % if they do, add a reference - JJ FERGU: added references
+\textcolor{blue}{Real-world MOPs usually require a high number of decision variables \cite{Zhang17DECAL,XU2018268}}, 
 meaning that the
@@
 We have chosen those metrics not only because they have been used
-extensively, especially in some of the papers presented in Section 2
-% Still section 2? Please create a reference and use it - JJ
+extensively, especially in some of the papers presented in Section \ref{sec:soa}
+% Still section 2? Please create a reference and use it - JJ Pablo: done
 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous},
@@
 chromosome lengths could be addressed in the future.
-\textcolor{blue}{Since our method divides the individuals into blocks of divisible size, aggregation methods after migration, such as the ones used in \cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be also tested.
-But as we are dealing with complete individuals in each island, the possibility of using a real number, such as 0.3 (30\% overlapping) instead an integer value opens future experimental setups.}
+\begin{bluecolor}Since our method divides the individuals into blocks of divisible size, aggregation methods after migration, such as the ones used in \cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be also tested.
+But as we are dealing with complete individuals in each island, the possibility of using a real number, such as 0.3 (30\% overlapping) instead an integer value opens future experimental setups.
 For example, comparing 
 different ways to calculate $c$ using linear, logarithmic or exponential functions
-depending \textcolor{blue}{on population size, number of islands, or other values, or using some statistical parameter setting method, such as Taguchi's \cite{Keratmatpour2018Taguchi}}.
+depending on population size, number of islands, or other values, or using some statistical parameter setting method, such as Taguchi's \cite{Keratmatpour2018Taguchi}.
 Moreover, a diversity analysis of the individuals
@@
 on the results.
+\end{bluecolor}
 % 

### 2018-06-11 hpmoon-asoco.tex
Revised abstract again. Please @fergunet check and send

@@
-%\affiliation{\affilnum{1}Dept. of Computer Architecture and Computer Technology, University of Granada, Spain}
-
-%\corrauth{Pablo Garc\'ia-S\'anchez,
-%ETS. Ingenier\'ias en Inform\'atica y Telecomunicaci\'on and CITIC-UGR,
-%C/Periodista Daniel Saucedo s/n,
-%Universidad de Granada,
-%18071, Granada, Spain.}
-
 \documentclass[preprint]{elsarticle}
@@
 \begin{bluecolor}
-One of the most extended methods to deal with high-dimensional multi-objective optimization problems are the distributed co-evolutionary algorithms. %Pablo: reducing previous two paragraphs into one
+One of the  methods most extensively used to deal with high-dimensional multi-objective optimization problems are distributed co-evolutionary algorithms.
+%Pablo: reducing previous two paragraphs into one
 However, only
@@
 way. 
-
-A new approach, which we call {\em selective operator application}, is used here to deal with un-decomposable
+A new parallel island-model evolutionary algorithm approach, which we call {\em selective operator application}, is used here to deal with un-decomposable
 problems: % so we are saying that high-dimensional multi-objective
@@
 instead of sharing parts
-of individuals, each processor applies the variation operators to a
+of individuals, each island, hosted by a single processor, applies the variation operators to a
 specific subset of the whole individual. This avoids extra steps to recompose the complete individuals from other islands before evaluation. 
-% this solves... - JJ
-% not addressed - JJ Pablo: done now
-%We have previously proved that extending the length of these subsets, and therefore, sharing some search space between islands, implies an improvement in different performance metrics.
-
- In this paper, we intend to prove that automatically setting the size of the
- overlapping section, since it focus the search between borders of the different search spaces, is able to obtain better
+% 
+ In this paper, we intend to prove that automatically setting the size of these
+ overlapping section, since it focuses the search between borders of the different search spaces, is able to obtain better
  results than using the same size independently of the number of islands. In order to prove that, we
- have compared it to other collaborative evolutionary
+ have compared it to other parallel evolutionary
 techniques considering different number of islands, chromosome sizes
@@
 statistically significant improvements with respect to the base
-algorithm in high-dimensional multi-objective problems.
-
+algorithm in high-dimensional, un-decomposable, multi-objective problems. 
+%
 Results also show that the relation between the number of
@@
 decision variables) is also a relevant factor to determine the most
-efficient alternative to distribute the decision variables: it is better to distribute them the higher the dimensionality, and to increase the overlapping size if individuals are distributed in a large number of islands.
-  % Say
-                                % something how it's relevant, and
-                                % what you have to do if you have so
-                                % many decision variables - JJ PABLO: Done
-This opens up a new challenge to be addressed in the future, by experimenting on new ways to calculate the overlapping sizes depending of different factors and parameters.
+efficient alternative to distribute the decision variables: the higher
+the dimensionality and the overlapping, the greater the benefit of distribution in a
+large number of islands.
+This opens up a new challenge to be addressed in the future, by
+experimenting on new ways to calculate the overlapping sizes depending
+of different factors and parameters.
 \end{bluecolor}

### 2018-06-11 hpmoon-asoco.tex
Spell check

@@
 that can be effectively used to find nearly optimal solutions for
-optimization problems and are easily paralellizable, since they are
+optimization problems and are easily parallelizable, since they are
 population-based and creating a functionally equivalent parallel
@@
 \subsection{Proposed methods}
-In this paper we analyse several SLA algorithms we have
+In this paper we analyze several SLA algorithms we have
 implemented by using a parallel multi-objective baseline algorithm
@@
 \textcolor{blue}{ZDT3 Pareto-optimal front is formed by non-contiguous convex parts, and plots for both chromosome sizes (Figures \ref{fig:plot_zdt3_512} and \ref{fig:plot_zdt3_2048}) show solutions gathered in similar regions in all configurations.
-However, with $L=512$, the rightmost part of the obtaninde non-dominated solutions is not obtained in the $A$ alternative with $P=8$  and $P=16$ (being equivalent to alternatives $O$ and $D$).
+However, with $L=512$, the rightmost part of the obtained non-dominated solutions is not obtained in the $A$ alternative with $P=8$  and $P=16$ (being equivalent to alternatives $O$ and $D$).
 This explains why with this chromosome length, the SLA methods do not improve the results obtained by $B$.

### 2018-06-11 hpmoon-asoco.tex
Some typos fixed

@@
 \begin{bluecolor}
-One of the  methods most extensively used to deal with high-dimensional multi-objective optimization problems are distributed co-evolutionary algorithms.
-%Pablo: reducing previous two paragraphs into one
+One of the  most extensively used methods to deal with high-dimensional, multi-objective optimization problems are distributed co-evolutionary algorithms. 
 However, only
@@
 A new parallel island-model evolutionary algorithm approach, which we call {\em selective operator application}, is used here to deal with un-decomposable
-problems: % so we are saying that high-dimensional multi-objective
-          % problems are a challenge, but we are presenting a solution
-          % for non-decomposable problems. What's what? - JJ
-% Still not addressed - JJ PABLO: rewritten almost all the abstract.
+problems: 
 instead of sharing parts
@@
 specific subset of the whole individual. This avoids extra steps to recompose the complete individuals from other islands before evaluation.
-% 
+
  In this paper, we intend to prove that automatically setting the size of these
- overlapping section, since it focuses the search between borders of the different search spaces, is able to obtain better
+ overlapping sections, since it focuses the search between borders of the different search spaces, is able to obtain better
  results than using the same size independently of the number of islands. In order to prove that, we
- have compared it to other parallel evolutionary
+ have compared this method to other parallel evolutionary
 techniques considering different number of islands, chromosome sizes
@@
 algorithm in high-dimensional, un-decomposable, multi-objective problems.
-%
+
 Results also show that the relation between the number of
@@
 This opens up a new challenge to be addressed in the future, by
-experimenting on new ways to calculate the overlapping sizes depending
+experimenting with new ways to calculate the overlapping sizes depending
 of different factors and parameters.

### 2018-06-11 highlights.tex
Updating highlights

@@
 \item A new adaptive overlapping mechanism is presented
-\item Different combinations of number of islands, genome sizes, benchmarks and methods are used
+\item Different combinations of number of islands, chromosome sizes, benchmarks and methods are used
 \item Different quality metrics have been compared
 \item Results are validated in a real system
-\item All overlapping schemes outperform the baseline, being the adaptive method the one that obtains the best performance
+\item Results show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is a relevant factor to determine the most efficient alternative to distribute the decision variables
+\item The higher the dimensionality and the overlapping, the greater the benefit of distribution in a large number of islands
 \end{itemize}

### 2019-02-11 hpmoon-asoco.tex
Addressing R2 changes for issues #28 #29 #31

@@
 \begin{bluecolor}
-One of the  most extensively used methods to deal with high-dimensional, multi-objective optimization problems are distributed co-evolutionary algorithms. 
-However, only
-decomposable problems could strictly be implemented in parallel this
-way. 
-A new parallel island-model evolutionary algorithm approach, which we call {\em selective operator application}, is used here to deal with un-decomposable
-problems: 
-instead of sharing parts
-of individuals, each island, hosted by a single processor, applies the variation operators to a
-specific subset of the whole individual. This avoids extra steps to recompose the complete individuals from other islands before evaluation.
-
- In this paper, we intend to prove that automatically setting the size of these
- overlapping sections, since it focuses the search between borders of the different search spaces, is able to obtain better
- results than using the same size independently of the number of islands. In order to prove that, we
- have compared this method to other parallel evolutionary
-techniques considering different number of islands, chromosome sizes
-and benchmarks. The analysis of the obtained experimental results, by
-using different metrics, shows that our approach can provide
-statistically significant improvements with respect to the base
-algorithm in high-dimensional, un-decomposable, multi-objective problems.
-
-Results also show that the relation between the number of
-islands (subpopulations) and the length of the chromosome (number of
-decision variables) is also a relevant factor to determine the most
-efficient alternative to distribute the decision variables: the higher
-the dimensionality and the overlapping, the greater the benefit of distribution in a
-large number of islands.
-This opens up a new challenge to be addressed in the future, by
-experimenting with new ways to calculate the overlapping sizes depending
-of different factors and parameters.
+
+%One of the  most extensively used methods to deal with high-dimensional, multi-objective optimization problems are distributed co-evolutionary algorithms.
+However, only decomposable problems could strictly be implemented in parallel this way.
+A new parallel island-model evolutionary algorithm approach, which we call {\em selective operator application}, is used here to deal with un-decomposable problems: instead of sharing parts of individuals, each island, hosted by a single processor, applies the variation operators to a specific subset of the whole individual.
+This avoids extra steps to recompose the complete individuals from other islands before evaluation.
+
+%In this paper, we intend to demonstrate that automatically setting the size of these  overlapping sections, since it focuses the search between borders of the different search spaces, is able to obtain better  results than using the same size independently of the number of islands.
+In order to demonstrate that, we  have compared this method to other parallel evolutionary techniques considering different number of islands, chromosome sizes and benchmarks.
+The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm in high-dimensional, un-decomposable, multi-objective problems.
+
+%Results also show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distribute the decision variables: the higher the dimensionality and the overlapping, the greater the benefit of distribution in a large number of islands.
+This opens up a new challenge to be addressed in the future, by experimenting with new ways to calculate the overlapping sizes depending of different factors and parameters.
+
+%%%NEW AND SHORTED
+Parallel island-model co-evolutionary algorithms are a well-known and suitable methods to deal with large multi-objective optimization problems.
+In these algorithms each island modifies a fragment of the chromosome that encodes a possible solution to the problem.
+In this paper, we want to demonstrate that automatically setting the size of the overlapping fragments depending on the number of islands obtains better results than using the same size.
+We  have compared this method to other parallel evolutionary techniques considering different number of islands, chromosome sizes and benchmarks.
+The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm in high-dimensional, un-decomposable, multi-objective problems.
+This opens a very challenging line to automatically adapt the overlapping sizes.
+
 \end{bluecolor}
@@
 
+\begin{bluecolor}
+One of the  most extensively used methods to deal with high-dimensional, Multi-Objective Optimization problems (MOPs) are distributed co-evolutionary algorithms \cite{Gong15models}.
+However, only decomposable problems could strictly be implemented in parallel this way.
+A new parallel island-model evolutionary algorithm approach \cite{Alba02Parallelism}, is used here to deal with un-decomposable problems: instead of sharing parts of individuals, each island, hosted by a single processor, applies the variation operators to a specific subset of the whole individual.
+This avoids extra steps to recompose the complete individuals from other islands before evaluation.
+\end{bluecolor}
+
 %1. MOP ARE
-Multi-objective optimization problems (MOP) are those where several
+MOPs are those where several
 objectives have to be simultaneously optimized
@@
 
-%The availability of metaheuristics which are able to efficiently approach these multi-objective optimization problems have made it possible to cope with many real applications from such multi-objective point of view [4, 5, 6, 7, 8].
-Evolutionary algorithms (EAs) [9] are bio-inspired meta-heuristics that can be effectively used to find nearly optimal solutions for optimization problems and have been extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) [29].
-
 Usually an EA starts by generating a set of random solutions, called
@@
 
-\textcolor{blue}{EAs have been extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}}.
+EAs have been extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}.
 One of the best known and referenced MOEAs
@@
 dominance, to be selected for the next generations.
-% This paragraph has nothing to do with anything. Is it useful for
-% what you are doing in the paper? Is there any challenge that you
-% will be solving here? For instance, you could talk about the problem
-% it's got for parallelization and how it deals with them - JJ FERGU: Could you add some paragraph to justify it? (use \textcolor{blue}{} please)
 
@@
 MOEAs need to deal with large individuals and spend significant extra
-time for crossover, mutation and migration. %depending on the
-                                %language, this time might not be
-                                %significant at all, and will depend
-                                %on the length of the chromosome, not
-                                %the part of the chromosome you will
-                                %be applying it to. Besides, this is
-                                %not the critical part of the
-                                %algorithm, the critical part is
-                                %searching the solution space. 
-Different authors have % this is only one possibility. You should talk
-                       % about simple island models, too - JJ
+time for crossover, mutation and migration.
+Different authors have 
 proposed methods to divide the decision space (the chromosome) to
 improve the performance and solution quality. In this aspect, the
-co-evolution model is a dimension-distributed model where a % first
-                                % reference to co-evolution in this
-                                % paper. Is it still a paper about
-                                % co-evolution? - JJ
+co-evolution model is a dimension-distributed model where a 
 high-dimensional problem is divided into lower dimensional ones
@@
 using the whole chromosome for fitness calculation. This allows to
-deal with un-decomposable problems. % if the whole chromosome is used,
-                                % mutation and crossover will take the
-                                % same time. You are modifying the
-                                % search space, though. 
+deal with un-decomposable problems.
+
 In our previous work \citep{Garcia16hpmoon} we used this method in a
@@
 were conducted in a limited experimental system: mono-processor and
-synchronous island model. %where we couldn't prove that... Or, we
-                          %couldn't experiment... - JJ
+synchronous island model. 
 This
@@
 sections depending on the number of available islands, comparing it with previous versions.
-
-% We have to
-                                % emphasize what is actually done. Is
-                                % this an addition to the old paper,
-                                % or a complete rewrite? - JJ FERGU: rewritten previous paragraph
 
@@
 problem size is large.
+
+\textcolor{blue}{Results also show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distribute the decision variables: the higher the dimensionality and the overlapping, the greater the benefit of distribution in a large number of islands.
+This opens up a new challenge to be addressed in the future, by experimenting with new ways to calculate the overlapping sizes depending of different factors and parameters.}
 

### 2019-02-12 hpmoon-asoco.tex
Fixing typos

@@
 %%%NEW AND SHORTED
-Parallel island-model co-evolutionary algorithms are a well-known and suitable methods to deal with large multi-objective optimization problems.
-In these algorithms each island modifies a fragment of the chromosome that encodes a possible solution to the problem.
+Parallel island-model co-evolutionary algorithms are well-known and suitable methods to deal with large multi-objective optimization problems.
+In these algorithms, each island modifies a fragment of the chromosome that encodes a possible solution to the problem.
 In this paper, we want to demonstrate that automatically setting the size of the overlapping fragments depending on the number of islands obtains better results than using the same size.
-We  have compared this method to other parallel evolutionary techniques considering different number of islands, chromosome sizes and benchmarks.
+We  have compared this method to other parallel evolutionary techniques considering a different number of islands, chromosome sizes and benchmarks.
 The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm in high-dimensional, un-decomposable, multi-objective problems.
-This opens a very challenging line to automatically adapt the overlapping sizes.
+This opens a very challenging line to automatically adapt the overlapping sizes in this kind of algorithms.
 
@@
 \citep{Deb00NSGAII}. Classical genetic operators are applied to all
-the individuals, which are divided into different ranks, based on the
+the individuals, which are divided into different ranks, based on 
 dominance, to be selected for the next generations.
@@
  This implies to use different distribution
-and sharing mechanisms, as there exist a tradeoff between the speedup
+and sharing mechanisms, as there \textcolor{blue}{exists} a tradeoff between the speedup
 achievable from parallelization and the need to globally recombine the
@@
 \citep{Gong15models,Tonda12cooperative}, and evolved separately. One
-example of application of this technique was described in
+example of the application of this technique was described in
 \citep{Kimovski15Parallel}. The method presented in that work involves
@@
 A similar approach used to solve this kind of problems is the {\em
-  SeLective operator Application} (SLA) \textcolor{blue}{presented in this paper}. In this case, each island
+  SeLective operator Application} (SLA) presented in this paper. In this case, each island
 deals with the whole chromosome, but only modifies a fragment of it in
@@
 establishing its name and acronym in this paper for the first time.
-We proved 
+We \textcolor{blue}{show}
 that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
@@
 the baseline, disjoint and partly overlapped methods. 
-\textcolor{blue}{The size of the overlapped sections are calculated from  the number of available subpopulations in the multi-objective evolutionary algorithm, and tested in a real computational environment.}
-
-In order to prove this claim, our new automatic method has been
+The size of the overlapped sections \textcolor{blue}{is} calculated from  the number of available subpopulations in the multi-objective evolutionary algorithm, and tested in a real computational environment.
+
+In order to \textcolor{blue}{demonstrate} this claim, our new automatic method has been
 compared against different overlapping island schemes: a
@@
 
-\textcolor{blue}{Results also show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distribute the decision variables: the higher the dimensionality and the overlapping, the greater the benefit of distribution in a large number of islands.
-This opens up a new challenge to be addressed in the future, by experimenting with new ways to calculate the overlapping sizes depending of different factors and parameters.}
+\textcolor{blue}{Results also show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to \textcolor{blue}{distributing} the decision variables: the higher the dimensionality and the overlapping, the greater the benefit of distribution in a large number of islands.
+This opens up a new challenge to be addressed in the future, by experimenting with new ways to calculate the overlapping sizes depending \textcolor{blue}{on} different factors and parameters.}
 
@@
 and add a simple communication mechanism among them. But in the case of
-MOEAs, the distribution and parallelization is \textcolor{blue}{more difficult}
+MOEAs, the distribution and parallelization \textcolor{blue}{are} more difficult \textcolor{blue}{than in}
 single-objective EAs. This is because in different steps of the
@@
 %This is an improvement over the previous? What is the relationship? FERGU: linked
-\textcolor{blue}{Another kind of approaches has also been explored}.
+\textcolor{blue}{Other} kind of approaches \textcolor{blue}{have} also been explored.
 The work by Deb et al.
@@
 In that paper, the authors concluded that dividing the search space is a good idea, although achieving this is not trivial.
-The division of the search space has been explored by other researchers, for example, dividing the population in elite and search sub-populations \citep{Wang09parallel}, or separating it in processors by objective \citep{Xiao03specialized}.
-\textcolor{blue}{For example, in \cite{Zhang17DECAL}, a weighted function is used to decompose the objective function and every subpopulation is responsible to solve the problem defined by a weighted vector.} Other authors, such as M{\"a}rtens \citep{Martens13asynchronous} use migration to accept individuals based on diversity, and migrating from not-crowded areas.
+The division of the search space has been explored by other researchers, for example, dividing the population \textcolor{blue}{into} elite and search sub-populations \citep{Wang09parallel}, or separating it in processors by objective \citep{Xiao03specialized}.
+For example, in \cite{Zhang17DECAL}, a weighted function is used to decompose the objective function and every subpopulation is responsible to solve the problem defined by a weighted vector.
+Other authors, such as M{\"a}rtens \citep{Martens13asynchronous} use migration to accept individuals based on diversity, and migrating from not-crowded areas.
 
@@
 \textcolor{blue}{Recently, this approach has also been tested using a Particle Swarm Optimization (PSO) algorithm \cite{DorronsoroPSO2018}, also obtaining significant improvements in speedups and solution quality.
-Others authors, such as Cao et al.
+\textcolor{blue}{Other} authors, such as Cao et al.
 \cite{CaoZLL17} separate the decision variables into several subpopulations after performing an interdependence analysis, but using a fixed number of processors.}
@@
 researchers. For example, some authors focus on the solution space
-modeling the PF by dividing it in different clusters, allowing an
+modeling the PF by dividing it \textcolor{blue}{into} different clusters, allowing an
 easily parallelizable {\em divide and conquer} approach
 \citep{cheng2015adaptive}. 
-\textcolor{blue}{Even other types of metaheuristics, 
+Even other types of metaheuristics, 
 such as the Multi-Objective Ant Colony Optimization (MOACO) \cite{Mora13paretobased}
@@
 can rely on island models to divide the search space depending on 
-the node to achieve better results. }
+the node to achieve better results.
 
@@
 the aforementioned ideas to compare two different dMOEAs. The first
-one divided the chromosome into $P$ sections, being $P$ the number of
+one divided the chromosome into $P$ sections,  \textcolor{blue}{$P$ being} the number of
 islands. Every island $p$ only performed the mutation and crossover in
@@
 $p_{th+1}$ sections of each chromosome, besides the $p_{th}$
-part. During the same amount of time both methods obtained better
+part. During the same amount of time, both methods obtained better
 results than a baseline algorithm that dealt with the whole chromosome
@@
 cluster. 
-\textcolor{blue}{Therefore, at the same time, we are proposing a new method to divide the individual search space according to the number of evolved subpopulations, and also validating the previous approach.}
+Therefore, at the same time, we are proposing a new method to divide the individual search space according to the number of evolved subpopulations, and also validating the previous approach.
 
@@
 crossed and mutated in the same way, depending on the island
-identifier (from 1 to $P$). \textcolor{blue}{Note that, unlike the other works such as the ones
-described by Talbi et al. \citep{Talbi08Parallel}}, all the islands deal
+identifier (from 1 to $P$). Note that, unlike the other works such as the ones
+described by Talbi et al. \citep{Talbi08Parallel}, all the islands deal
 with complete chromosomes for fitness calculation, so our approach can
@@
 \includegraphics[width=12cm]{islandDisjoint.jpg}
-\caption{SLA with disjoint islands (D): every island $p$ only modifies the $p_{th}$ components (in grey) of the individuals \textcolor{blue}{using genetic operators (crossover and mutation).
+\caption{SLA with disjoint islands (D): every island $p$ only modifies the $p_{th}$ components (in grey) of the individuals using genetic operators (crossover and mutation).
 Also, every island evaluates its own individuals using the complete chromosome.
-After a given number of generations it cooperates with the other islands through migration.}}
+After a given number of generations, it cooperates with the other islands through migration.}
 \label{fig:disjoint}
@@
 \caption{SLA with overlapping islands (O): every island $p$ modifies the  $p+1$,
-  $p_{th}$ and $p-1$  components (in grey) of the individuals \textcolor{blue}{using genetic operators (crossover and mutation).
+  $p_{th}$ and $p-1$  components (in grey) of the individuals using genetic operators (crossover and mutation).
 Also, every island evaluates its own individuals using the complete chromosome.
-After a given number of generations it cooperates with the other islands through migration.}}
+After a given number of generations, it cooperates with the other islands through migration.}
   \label{fig:overlapping}
@@
 work, the overlapped method ($c=1$) obtained better results when the
-number of islands were bigger than 8. On the contrary, when the number of
-islands is small, no overlapping is necessary. \textcolor{blue}{So, we have used this
+number of islands \textcolor{blue}{was} bigger than 8. On the contrary, when the number of
+islands is small, no overlapping is necessary. So, we have used this
 knowledge to propose the formula $c=round(0.2*P-1)/2$ to calculate the
-extra sections to overlap}. Therefore, when $P=8$ then $c=0$
+extra sections to overlap. Therefore, when $P=8$ then $c=0$
 (equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so
 on.
-\textcolor{blue}{Dividing individuals by blocks of equal size, instead a percentage, allow the future integration of our method with other recombination mechanisms, such as the ones presented in \cite{Dorronsoro13superlinear} or \cite{Kimovski15Parallel}.
-Also, as mentioned, this is only a possible formula to reach above described behaviour for $c$, and future work will study new methods or alternative formulas to determine it, for example using Taguchi Method \cite{Keratmatpour2018Taguchi}.
+Dividing individuals by blocks of equal size, instead \textcolor{blue}{of} a percentage, allow the future integration of our method with other recombination mechanisms, such as the ones presented in \cite{Dorronsoro13superlinear} or \cite{Kimovski15Parallel}.
+Also, as mentioned, this is only a possible formula to reach above-described behaviour for $c$, and future work will study new methods or alternative formulas to determine it, for example using Taguchi Method \cite{Keratmatpour2018Taguchi}.
 Figure \ref{fig:adaptive} explains the $A$ method, assuming that $c=2$, for example.
-}
 
@@
 \caption{\textcolor{blue}{Automatic} SLA with overlapping islands (A): every island $p$ modifies the  $p+c$,
-  $p_{th}$ and $p-c$  components (in grey) of the individuals \textcolor{blue}{using genetic operators (crossover and mutation).
+  $p_{th}$ and $p-c$  components (in grey) of the individuals using genetic operators (crossover and mutation).
 Also, every island evaluates its own individuals using the complete chromosome.
 After a given number of generations it cooperates with the other islands through migration.} $c$ is calculated depending on the number of islands.
-In this case, $c=2$.}
+In this case, $c=2$.
   \label{fig:adaptive}
@@
 
-This subsection describes the quality indicators used and the experimental setup. The chosen quality indicators, are:
+This subsection describes the quality indicators used and the experimental setup. The chosen quality indicators are:
 
@@
 %Pablo: theoretical?
-\item Spread (S): Measures the spread between solutions, taking into account the \textcolor{blue}{Euclidean} distance between consecutive solutions.
-As in previous metric, the lower value, the better, as it implies solutions distributed along all the PF.
+\item Spread (S): Measures the spread between solutions, taking into account the Euclidean distance between consecutive solutions.
+As in \textcolor{blue}{previous} previous metric, the lower \textcolor{blue}{the} value, the better, as it implies solutions distributed along all the PF.
 \end{itemize}
@@
 \includegraphics[width=6cm]{hypervolume.jpg}
-\caption{Hypervolume calculation.
-\textcolor{blue}{Areas from Pareto Front solutions (black points) to a reference point (white point) are used to calculate the value of the hypervolume (all the gray area)}.}
+\caption{Hypervolume calculation. Areas from Pareto Front solutions (black points) to a reference point (white point) are used to calculate the value of the hypervolume (all the gray area)}.
 \label{fig:hypervolume}
@@
 maximum number of islands has also been  used in a previous work in the
-literature \cite{Martens13asynchronous}. The crossover and mutation
-chosen, SBX and polynomial, have also been  used previously by other
+literature \cite{Martens13asynchronous}. The \textcolor{blue} chosen crossover and mutation, SBX and polynomial, have also been  used previously by other
 authors in \cite{Durillo08masterslave,CaoZLL17}.  % SBX is first mentioned
@@
 benchmark includes several functions, with different features that are
-representative of real world optimization problems. Mathematical
+representative of real-world optimization problems. Mathematical
 formulation of each function is available in \citep{zdt2000a}.
@@
 According to Alba and Luque \cite{EVALUATIONPARALLEL}, other stop criteria such as the number of evaluations required to attain a solution, may be misleading depending on the studied scenario.
-In our case we have used time instead of the number of evaluations firstly
+In our case, we have used time instead of the number of evaluations firstly
 because our hypothesis argues that the time saved in crossover and
@@
 operations and migrations can be achieved. Also, we are using
-different number of islands (with different sub-population sizes) and that
+different \textcolor{blue}{numbers} of islands (with different sub-population sizes) and that
 could lead to different execution times, so it would be difficult to
@@
 The number of generations between migrations has been set to 5,
-\textcolor{blue}{as
+as
 reported by \cite{Deb03distributed,Martens13asynchronous}. In general
@@
 negative impact. However, a precise fine-tuning of this value is left
-as future work, as the main focus of this paper was to prove the
-general concept, and not tune the values for a maximum performance}.
-
-\textcolor{blue}{This migration
+as future work, as the main focus of this paper was to \textcolor{blue}{show} the
+general concept, and not tune the values for maximum performance.
+
+This migration
   is performed asynchronously, as it has the advantage of being a
@@
   to compose solutions obtained by different islands, as occurs other
-  works \cite{Dorronsoro13superlinear}.}
+  works \cite{Dorronsoro13superlinear}.
 
  The whole parameter set is summarized in Table \ref{tab:parameters}. 
- \textcolor{blue}{The main parameters in the proposed system were the number of islands and the size
+The main parameters in the proposed system were the number of islands and the size
    of the problem, as pointed out by other authors 
@@
  them and the number of islands and problem size, this is left mainly
- as future work.}
-
-\begin{table*}
+ as future work.
+
+\begin{table*}[htb]
 \begin{center}
@@
 The ECJ framework \citep{ECJ} has been used to run the
-experiments, including its own random number generation implementation.  \textcolor{blue}{The specific modifications to deal with the proposed approaches have been developed as new modules for
-ECJ}, and their source code can be downloaded from our GitHub repository under a
+experiments, including its own random number generation implementation.  The specific modifications to deal with the proposed approaches have been developed as new modules for
+ECJ, and their source code can be downloaded from our GitHub repository under a
 LGPL V3 License
-\footnote{\url{https://github.com/hpmoon/hpmoon-islands}}. \textcolor{blue}{The quality metrics (HV, Spread and IGD) have been calculated using the jMetal \cite{Durillo11Jmetal} library.}
+\footnote{\url{https://github.com/hpmoon/hpmoon-islands}}. The quality metrics (HV, Spread and IGD) have been calculated using the jMetal \cite{Durillo11Jmetal} library.
 
@@
 @2.27GHz processors, 16 GB RAM, Broadcom NetXtreme II BCM5716 1000Base-T (C0) PCI Express network cards, CentOS 6.8 and Java Version 1.8.0\_80.
-\textcolor{blue}{Islands are allocated to nodes in a round-robin way.
-That means that, for example, running with 8 islands requires 8 different nodes, instead of using several cores of a single node.}
+Islands are allocated to nodes in a round-robin way.
+That means that, for example, running with 8 islands requires 8 different nodes, instead of using several cores of a single node.
 
@@
 Different metrics, previously explained, have been used
-to calculate the quality of the obtained PFs in each configuration. \textcolor{blue}{As HV require a reference point to be
+to calculate the quality of the obtained PFs in each configuration. As HV \textcolor{blue}{requires} a reference point to be
 calculated (see Figure \ref{fig:hypervolume}), we have chosen the value (1,9) as none of the existing solutions on all fronts obtained during all executions are dominated by it.
@@
 HV is then
-normalized respecting to that point.
-Also, the optimal reference PF distribution used to calculate the IGD and Spread metrics \cite{Durillo11Jmetal} has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.} }.
+normalized \textcolor{blue}{in respect to} to that point.
+Also, the optimal reference PF distribution used to calculate the IGD and Spread metrics \cite{Durillo11Jmetal} has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.} .
 A Kruskal-Wallis significance
@@
 Results show that there is a difference in performance when using 512 or 2048 dimensions.
-Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than the obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply these methods.
+Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than \textcolor{blue}{those} obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply these methods.
 A contradiction arises with respect to the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths.
@@
 However, with 2048 dimensions, results show that dividing the chromosome produces an improvement in all the quality indicators using the automatic ($A$) version (Table \ref{tab:results2048}), even overcoming the overlapping ($O$) and disjoint ($D$) methods.
-Therefore, there exist some kind of limit point in chromosome length where one method will be preferable to another, besides depending on the number of islands and population size.
+Therefore, there \textcolor{blue}{exists} some kind of limit point in chromosome length where one method will be preferable to another, besides depending on the number of islands and population size.
 
@@
 \includegraphics[width=12cm]{plot_zdt1_512.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+\caption{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
 Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}}
+}
 \label{fig:plot_zdt1_512}
@@
 \includegraphics[width=12cm]{plot_zdt1_2048.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+\caption{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
 Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}}
+}
 \label{fig:plot_zdt1_2048}
@@
 \includegraphics[width=12cm]{plot_zdt2_512.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+\caption{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
 Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}}
+}
 \label{fig:plot_zdt2_512}
@@
 \includegraphics[width=12cm]{plot_zdt2_2048.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+\caption{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
 Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}}
+}
 \label{fig:plot_zdt2_2048}
@@
 \includegraphics[width=12cm]{plot_zdt3_512.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+\caption{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
 Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}}
+}
 \label{fig:plot_zdt3_512}
@@
 \includegraphics[width=12cm]{plot_zdt3_2048.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+\caption{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
 Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}}
+}
 \label{fig:plot_zdt3_2048}
@@
 \includegraphics[width=12cm]{plot_zdt6_512.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+\caption{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
 Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}}
+}
 \label{fig:plot_zdt6_512}
@@
 \includegraphics[width=12cm]{plot_zdt6_2048.png}
-\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+\caption{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
 Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}}
+}
 \label{fig:plot_zdt6_2048}
@@
 lengths, increasing the number of islands implies more generations
-with all the methods (logically, as there are less individuals in each
+with all the methods (logically, as there are \textcolor{blue}{fewer} individuals in each
 island). But also, the SLA methods
@@
 %ZDT1 
-\textcolor{blue}{Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048}, showing the final PFs of one arbitrary sample run of each combination.
-These figures allow to visualize the effect of the different chromosome sizes and number of islands in each different benchmark.
+Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048}, showing the final PFs of one arbitrary sample run of each combination.
+These figures allow visualizing the effect of the different chromosome sizes and number of islands in each different benchmark.
 The first one, ZDT1, has a convex Pareto-optimal front.
@@
 It can be seen in Figure \ref{fig:plot_zdt1_2048} that solutions obtained by the SLA methods are more dispersed than the baseline as $P$ grows.
-However, with $A$, the area covered by the PF is still larger.}
+However, with $A$, the area covered by the PF is still larger.
 
 %ZDT2
-\textcolor{blue}{ZDT2 has a non-convex Pareto front.
+ZDT2 has a non-convex Pareto front.
 From Figures \ref{fig:plot_zdt2_512} and \ref{fig:plot_zdt2_2048} is clear that, as in the previous problem ZDT1, there is a decrease of quality for all configurations as the size of $P$ increases.
-Nevertheless, for this benchmark, there is not a clear decrease in the PF quality when $L$ goes from 512 to 2048.}
+Nevertheless, for this benchmark, there is not a clear decrease in the PF quality when $L$ goes from 512 to 2048.
 
 %ZDT3
-\textcolor{blue}{ZDT3 Pareto-optimal front is formed by non-contiguous convex parts, and plots for both chromosome sizes (Figures \ref{fig:plot_zdt3_512} and \ref{fig:plot_zdt3_2048}) show solutions gathered in similar regions in all configurations.
+ZDT3 Pareto-optimal front is formed by non-contiguous convex parts, and plots for both chromosome sizes (Figures \ref{fig:plot_zdt3_512} and \ref{fig:plot_zdt3_2048}) show solutions gathered in similar regions in all configurations.
 However, with $L=512$, the rightmost part of the obtained non-dominated solutions is not obtained in the $A$ alternative with $P=8$  and $P=16$ (being equivalent to alternatives $O$ and $D$).
@@
 This problem does not appear when $L=2048$.
-Although the differences in the Spread metric are not significant for the different alternatives for this benchmark, (as shown in Table \ref{tab:results2048}), the HV and IGD metrics are the ones that can be used to show the effectiveness of our approach in this type of problem with non-continuous PFs.}
-
-\textcolor{blue}{In ZDT6, the Pareto-optimal solutions are not only non-uniformly distributed along the PF, but their density also increases as we move further away from it.
+Although the differences in the Spread metric are not significant for the different alternatives for this benchmark, (as shown in Table \ref{tab:results2048}), the HV and IGD metrics are the ones that can be used to show the effectiveness of our approach in this type of problem with non-continuous PFs.
+
+In ZDT6, the Pareto-optimal solutions are not only non-uniformly distributed along the PF, but their density also increases as we move further away from it.
 That is the reason why some PFs obtained have an extremely low number of solutions in some configurations, and also, they are aggregated toward the areas with more density.
@@
 Indeed, there is not a significant difference between methods, with an exception: Spread using $A$ with $L=512$ is significantly worse.
-As in previous approaches it is visually clear that increasing the number of islands, and therefore, reducing the number of individuals per island, imply a decrease in quality of the HV.}
-
-\textcolor{blue}{Finally, as it was already observed in \citep{Garcia16hpmoon}, all the performance indicators show worse values as the number of islands increases, and so the  sizes of the subpopulations are smaller.
+As in previous approaches, it is visually clear that increasing the number of islands, and therefore, reducing the number of individuals per island, \textcolor{blue}{implies} a decrease the in quality of the HV.
+
+Finally, as it was already observed in \citep{Garcia16hpmoon}, all the performance indicators show worse values as the number of islands increases, and so the  sizes of the subpopulations are smaller.
 This is consistent with the claim by Dorronsoro et al.
-\citep{Dorronsoro13superlinear}, who found that cooperative co-evolutionary MOEAs work better on bigger populations (more than 100 individuals).}
+\citep{Dorronsoro13superlinear}, who found that cooperative co-evolutionary MOEAs work better on bigger populations (more than 100 individuals).
 
@@
 chromosome lengths could be addressed in the future.
-\begin{bluecolor}Since our method divides the individuals into blocks of divisible size, aggregation methods after migration, such as the ones used in \cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be also tested.
+Since our method divides the individuals into blocks of divisible size, aggregation methods after migration, such as the ones used in \cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be also tested.
 But as we are dealing with complete individuals in each island, the possibility of using a real number, such as 0.3 (30\% overlapping) instead an integer value opens future experimental setups.
@@
 on the results.
-\end{bluecolor}
+
 % 

### 2019-02-13 hpmoon-asoco.tex
Small typo
Making some small changes

@@
 \begin{abstract}
-  % First, state the problem!!!! - JJ Pablo: ok!
-%Real-world optimization problems usually require to deal with several objectives.
-%Multi-objective optimization methods have gained interest in the last
-%years because of the performance they can achieve solving this kind of problems. 
-%Many of them usually require a high-dimensional
-%decision space, and multi-objective Evolutionary Algorithms have been
-%successfully used in the past. Due to the large computational cost
-%these algorithms require, different parallelization and distribution
-%methods have been proposed, with different parallel and distributed
-%computer architectures to cope with them.
-
-%Real world optimization problems usually have many dimensions and
-%  several objectives, thus requiring exceptional computing power to be addressed.
-
- % The high dimensionality requires exceptional computing power, and the fact that several dimensions have to be searched at the same time add additional difficulty.
-
-%Usually, distributed co-evolutionary algorithms are used to cope with these issues, by allocating parts of the decision space to different processors.
-Thus, each processor only deals with the individuals of a sub-population (called island in this context) that explores a specific part of the decision space.
 
@@
 %%%NEW AND SHORTED
-Parallel island-model co-evolutionary algorithms are well-known and suitable methods to deal with large multi-objective optimization problems.
+Parallel island-model co-evolutionary algorithms are well-known methods, suitable for dealing with large multi-objective optimization problems.
 In these algorithms, each island modifies a fragment of the chromosome that encodes a possible solution to the problem.
@@
 
-%Introduction should start in the same way as the abstract. And
-%starting with something that is not really applicable here, talking
-%about general parallel evolutionary algorithms, is even worse.
-% Right way (IMNSHO)
-% 1. Multiobjective problems are
-% 2. They usually require a good amount of computation → parallel
-% distributed
-% 3. One way to solve them is to use MOEAs _because_ they can be
-% easily parallelized
-% 4. But the easy paralellization is not necessarily efficient.
-% 5. We have proposed the HPMOON (or whatever) technique to improve
-% it. In paper (whatever) we proved that (whatever)
-% 6. In this paper we will be proving whatever - JJ FERGU: Addressing JJ order
-% OK - JJ
-
+% Maybe add a sentence explaining what problems are decomposable and which ones are not. - JJ
 \begin{bluecolor}
-One of the  most extensively used methods to deal with high-dimensional, Multi-Objective Optimization problems (MOPs) are distributed co-evolutionary algorithms \cite{Gong15models}.
+One of the methods that are most extensively used  to deal with high-dimensional, multi-objective optimization problems (MOPs) are distributed co-evolutionary algorithms \cite{Gong15models}.
 However, only decomposable problems could strictly be implemented in parallel this way.
@@
 %1. MOP ARE
-MOPs are those where several
+In MOPs, several
 objectives have to be simultaneously optimized
@@
 these problems the aim is to obtain a set of solutions that are better
-than the rest, considering all the objectives; this set is known as
+than the rest considering all the objectives; this set is known as
 the Pareto Front (PF). The solutions in this set are {\em non-dominated},
@@
 HV is then
-normalized \textcolor{blue}{in respect to} to that point.
+normalized \textcolor{blue}{with respect to} to that point.
 Also, the optimal reference PF distribution used to calculate the IGD and Spread metrics \cite{Durillo11Jmetal} has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.} .

### 2019-02-13 hpmoon-asoco.tex
Some suggestions for captions @fergunet

@@
 }
-\caption{Average quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 512 dimensions.
-Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
-Best values are marked in bold.
-Equiv-$X$ implies that value is the same as executing $X$, since both configurations would be the same.}
+\caption{Average quality metrics obtained after 30 runs per
+  configuration, for the 4 methods compared: baseline (B), disjoint
+  (D), overlapped (O) and \textcolor{blue}{automatic} overlapped
+  (A), % No sería mejor "automatically overlapped" or "automatic
+       % overlap"? This does not sound good - JJ
+  using a chromosome length of 512 dimensions. Acronyms next to values
+  indicate that there is not significant difference with respect to
+  that method for that value. Best values are marked in
+  bold. Equiv-$X$ implies that value is the same as executing $X$,
+  since both configurations would be the same.}  
 \label{tab:results512}

### 2019-02-13 hpmoon-asoco.tex
Rearranges figures to make them embedded in text

@@
 Different metrics, previously explained, have been used
-to calculate the quality of the obtained PFs in each configuration. As HV \textcolor{blue}{requires} a reference point to be
+to calculate the quality of the obtained PFs in every configuration. As HV \textcolor{blue}{requires} a reference point to be
 calculated (see Figure \ref{fig:hypervolume}), we have chosen the value (1,9) as none of the existing solutions on all fronts obtained during all executions are dominated by it.
@@
 configurations, as the Kolmogorov-Smirnov test detected non-normal
-distributions. The average results for each configuration are shown in
-Table \ref{tab:results512} (for 512 dimensions) and Table
-\ref{tab:results2048} (for 2048). As previously explained, when $P=8$
-the results of A are equivalent to the obtained by D (because
-$c=0$), and when $P=16$ they are equivalent to O ($c=1$).
-We refer this equivalence with the word {\em Equiv-} in tables.
-For example, Equiv-D in an HV cell  means that the HV of A is the same than the value in D column, because the behaviour of this configuration is the same than executing D.
-
+distributions.
+%
 \begin{table*}
@@
 
+The average results for each configuration are shown in
+Table \ref{tab:results512} (for 512 dimensions) and Table
+\ref{tab:results2048} (for 2048). As previously explained, when $P=8$
+the results of A are equivalent to the obtained by D (because
+$c=0$), and when $P=16$ they are equivalent to O ($c=1$).
+We refer this equivalence with the word {\em Equiv-} in tables.
+For example, Equiv-D in an HV cell  means that the HV of A is the same than the value in D column, because the behaviour of this configuration is the same than executing D.
+
 \begin{table*}
@@
 
-\begin{table*}
+%DESCRIPTION OF THE RESULTS
+Results show that there is a difference in performance when using 512 or 2048 dimensions.
+Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than \textcolor{blue}{those} obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply these methods.
+A contradiction arises with respect to the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths.
+This can be explained because the added migration latency between nodes of the cluster requires more time than the time saved during the crossover and migration.
+This was not a problem in the mono-processor version, where the individuals shared the same memory space.
+
+However, with 2048 dimensions, results show that dividing the chromosome produces an improvement in all the quality indicators using the automatic ($A$) version (Table \ref{tab:results2048}), even overcoming the overlapping ($O$) and disjoint ($D$) methods.
+Therefore, there \textcolor{blue}{exists} some kind of limit point in chromosome length where one method will be preferable to another, besides depending on the number of islands and population size.
+
+\begin{table*}[h!tb]
 \centering
@@
 }
-\caption{Average number of generations and average number of solutions of the front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 512 dimensions.
+\caption{Average number of generations and  solutions per front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 512 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 \end{table*}
-
-\begin{table*}
+%
+\begin{table*}[h!tb]
 \centering
@@
 }
-\caption{Average number of generations and average number of solutions per front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 2048 dimensions.
+\caption{Average number of generations and solutions per front after 30 runs per configuration, for methods baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 2048 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 \end{table*}
-
-%DESCRIPTION OF THE RESULTS
-Results show that there is a difference in performance when using 512 or 2048 dimensions.
-Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than \textcolor{blue}{those} obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply these methods.
-A contradiction arises with respect to the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths.
-This can be explained because the added migration latency between nodes of the cluster requires more time than the time saved during the crossover and migration.
-This was not a problem in the mono-processor version, where the individuals shared the same memory space.
-
-However, with 2048 dimensions, results show that dividing the chromosome produces an improvement in all the quality indicators using the automatic ($A$) version (Table \ref{tab:results2048}), even overcoming the overlapping ($O$) and disjoint ($D$) methods.
-Therefore, there \textcolor{blue}{exists} some kind of limit point in chromosome length where one method will be preferable to another, besides depending on the number of islands and population size.
-
-%ZDT1
-\begin{figure}
-\centering
-\includegraphics[width=12cm]{plot_zdt1_512.png}
-\caption{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}
-\label{fig:plot_zdt1_512}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=12cm]{plot_zdt1_2048.png}
-\caption{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}
-\label{fig:plot_zdt1_2048}
-\end{figure}
-
-%ZDT2
-\begin{figure}
-\centering
-\includegraphics[width=12cm]{plot_zdt2_512.png}
-\caption{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}
-\label{fig:plot_zdt2_512}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=12cm]{plot_zdt2_2048.png}
-\caption{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}
-\label{fig:plot_zdt2_2048}
-\end{figure}
-
-%ZDT3
-\begin{figure}
-\centering
-\includegraphics[width=12cm]{plot_zdt3_512.png}
-\caption{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}
-\label{fig:plot_zdt3_512}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=12cm]{plot_zdt3_2048.png}
-\caption{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}
-\label{fig:plot_zdt3_2048}
-\end{figure}
-
-%ZDT6
-\begin{figure}
-\centering
-\includegraphics[width=12cm]{plot_zdt6_512.png}
-\caption{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}
-\label{fig:plot_zdt6_512}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=12cm]{plot_zdt6_2048.png}
-\caption{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}
-\label{fig:plot_zdt6_2048}
-\end{figure}
-
+%
 %EXPLANATION OF THE RESULTS
@@
 of each front and the average number of generations (Table
-\ref{tab:sols512} and Table \ref{tab:sols2048}). With both chromosome
+\ref{tab:sols512} and Table \ref{tab:sols2048}).
+
+With both chromosome
 lengths, increasing the number of islands implies more generations
@@
 island is unaware of the other islands PFs, and they are trying to
-optimize their solutions independently. With respect to the average
+optimize their solutions independently.
+
+With respect to the average
 number of solutions per front, there is a clear difference 
@@
  obtains better (or not significantly different) values in the majority of the compared configurations.
+
+%ZDT1
+\begin{figure}[h!tb]
+\centering
+\includegraphics[width=12cm]{plot_zdt1_512.png}
+\caption{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}
+\label{fig:plot_zdt1_512}
+\end{figure}
+%
+\begin{figure}[h!tb]
+\centering
+\includegraphics[width=12cm]{plot_zdt1_2048.png}
+\caption{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}
+\label{fig:plot_zdt1_2048}
+\end{figure}
+%
+%ZDT2
+\begin{figure}[h!tb]
+\centering
+\includegraphics[width=12cm]{plot_zdt2_512.png}
+\caption{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}
+\label{fig:plot_zdt2_512}
+\end{figure}
+%
+\begin{figure}[h!tb]
+\centering
+\includegraphics[width=12cm]{plot_zdt2_2048.png}
+\caption{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}
+\label{fig:plot_zdt2_2048}
+\end{figure}
+%
+%ZDT3
+\begin{figure}[h!tb]
+\centering
+\includegraphics[width=12cm]{plot_zdt3_512.png}
+\caption{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}
+\label{fig:plot_zdt3_512}
+\end{figure}
+%
+\begin{figure}[h!tb]
+\centering
+\includegraphics[width=12cm]{plot_zdt3_2048.png}
+\caption{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}
+\label{fig:plot_zdt3_2048}
+\end{figure}
+%
+%
+%
+%ZDT6
+\begin{figure}[h!tb]
+\centering
+\includegraphics[width=12cm]{plot_zdt6_512.png}
+\caption{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}
+\label{fig:plot_zdt6_512}
+\end{figure}
+%
+\begin{figure}[h!tb]
+\centering
+\includegraphics[width=12cm]{plot_zdt6_2048.png}
+\caption{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}
+\label{fig:plot_zdt6_2048}
+\end{figure}
 

### 2019-02-13 hpmoon-asoco.tex
Made some improvements to explanation of figures

@@
 number of solutions per front, there is a clear difference 
- with the baseline with $L=512$, where this value is in the most
-of the cases, less than a half. The number of non-dominated solutions
+ with the baseline with $L=512$, where this value is in most
+cases, less than a half. The number of non-dominated solutions
 also implies a better Spread indicator, where the baseline 
@@
 %ZDT1 
-Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048}, showing the final PFs of one arbitrary sample run of each combination.
-These figures allow visualizing the effect of the different chromosome sizes and number of islands in each different benchmark.
-The first one, ZDT1, has a convex Pareto-optimal front.
-Comparing results from $L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) it is apparent that the quality of the generated PFs depends on the chromosome size.
-Specifically, with $L=512$ it can be seen that the PFs quality decreases in Spread and HV with all configurations, but the SLA methods behave worse than $B$, as it also was shown on average in Table \ref{tab:results512}.
-Nevertheless, if we focus on the plots obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this difference is less clear.
-It can be seen in Figure \ref{fig:plot_zdt1_2048} that solutions obtained by the SLA methods are more dispersed than the baseline as $P$ grows.
-However, with $A$, the area covered by the PF is still larger.
+After establishing the performance of the new method and in order to
+have some insight on how they work, let's check the effect of the different chromosome sizes and number of
+islands. Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048} show the
+final PFs of one arbitrary sample run of each combination;. The first
+one, ZDT1, has a convex Pareto-optimal front. Comparing results from
+$L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=2048$ (Figure
+\ref{fig:plot_zdt1_2048}) it is apparent that the quality of the
+generated PFs depends on the chromosome size. Specifically, all
+configurations  with
+$L=512$  seem to have a worse Spread and HV, on the other hand, the
+SLA methods behave worse than $B$, as it was also shown on average in
+Table \ref{tab:results512}. Nevertheless, if we focus on the plots
+obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this
+difference is less clear. Figure \ref{fig:plot_zdt1_2048} shows that
+solutions obtained by the SLA methods show higher dispersion than the
+baseline as $P$ grows. However, with $A$, the area covered by the PF
+is still larger.
 
 %ZDT2
-ZDT2 has a non-convex Pareto front.
-From Figures \ref{fig:plot_zdt2_512} and \ref{fig:plot_zdt2_2048} is clear that, as in the previous problem ZDT1, there is a decrease of quality for all configurations as the size of $P$ increases.
+ZDT2 has a non-convex Pareto front. From Figures
+\ref{fig:plot_zdt2_512} and \ref{fig:plot_zdt2_2048} it is clear that, as in the previous problem ZDT1, there is a decrease of quality for all configurations as the size of $P$ increases.
 Nevertheless, for this benchmark, there is not a clear decrease in the PF quality when $L$ goes from 512 to 2048.

### 2019-02-13 hpmoon-asoco.tex
Added reference for issue #8 and some suggestions by @JJ, including the automatic->automatically typo

@@
 The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm in high-dimensional, un-decomposable, multi-objective problems.
-This opens a very challenging line to automatically adapt the overlapping sizes in this kind of algorithms.
+This opens a very promising line to automatically adapt the overlapping sizes in this kind of algorithms.
 
@@
 implemented by using a parallel multi-objective baseline algorithm
-as a basis for comparisons. Our proposed methods, using different overlapping schemes, %methods or method?
-                                %Which methods? - JJ Fergu: clarifying
+as a basis for comparisons. Our proposed methods, using different overlapping schemes, 
 are based on NSGA-II, as almost all the previous works discussed
@@
 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}. 
-% This is SoA stuff - JJ FERGU: Yes, I added it here againg because a reviewer wasn't very attentive
 Therefore, we have used a basic distributed NSGA-II algorithm without
@@
 with complete chromosomes for fitness calculation, so our approach can
-deal with decomposable and no decomposable problems. %Don't understand what you say
-                                %here. What you are saying is that our
-                                %approach can't deal with decomposable
-                                %problems, actually. - JJ FERGU: you are right, fixed
+deal with decomposable and no decomposable problems.
 
@@
 being $c$ a value depending on the number of islands.
-% That's not adaptive. It's simply variable - JJ FERGU: it depends on the number of islands. What term do you suggest?
-% FERGU: changed to Automatic
+
 As a first
@@
 extensively, especially in some of the papers presented in Section \ref{sec:soa}
-% Still section 2? Please create a reference and use it - JJ Pablo: done
 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous},
@@
   to compose solutions obtained by different islands, as occurs other
-  works \cite{Dorronsoro13superlinear}.
-
- The whole parameter set is summarized in Table \ref{tab:parameters}. 
-The main parameters in the proposed system were the number of islands and the size
-   of the problem, as pointed out by other authors 
-   \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}. This is why those have been the focus of this particular
-   article. Although all the parameters indicated above have an
-   influence on the general result of the MOEA, their general effect
-   is well understood and, although there will be an interplay between
- them and the number of islands and problem size, this is left mainly
- as future work.
+  works \cite{Dorronsoro13superlinear}.\textcolor{blue}{The main parameters studied in the proposed system are limited to the number of islands and the size of the problem.
+This decision has been motivated because all previous works described in the state of the art also limit their experimental setting to the same parameters \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}.
+Although all the parameters indicated above have an influence on the general result of the MOEA, their general effect is well understood and, although there will be an interplay between them and the number of islands and problem size, this is left mainly as future work.}
 
@@
   configuration, for the 4 methods compared: baseline (B), disjoint
-  (D), overlapped (O) and \textcolor{blue}{automatic} overlapped
+  (D), overlapped (O) and \textcolor{blue}{automatically} overlapped
   (A), % No sería mejor "automatically overlapped" or "automatic
-       % overlap"? This does not sound good - JJ
+       % overlap"? This does not sound good - JJ FERGU: Done
   using a chromosome length of 512 dimensions. Acronyms next to values
@@
 }
-\caption{Average quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 2048 dimensions.
+\caption{Average quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatically} overlapped (A), using a chromosome length of 2048 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 }
-\caption{Average number of generations and  solutions per front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 512 dimensions.
+\caption{Average number of generations and  solutions per front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatically} overlapped (A), using a chromosome length of 512 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 }
-\caption{Average number of generations and solutions per front after 30 runs per configuration, for methods baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 2048 dimensions.
+\caption{Average number of generations and solutions per front after 30 runs per configuration, for methods baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatically} overlapped (A), using a chromosome length of 2048 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 %ZDT1 
-After establishing the performance of the new method and in order to
+\textcolor{blue}{After establishing the performance of the new method and in order to
 have some insight on how they work, let's check the effect of the different chromosome sizes and number of
-islands. Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048} show the
+islands.
+Plotting the solution sets allows to observe its quality, distribution and shape, specially if they are limited to 2 or 3 objectives, as in this paper \cite{Li17read}.
+} Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048} show the
 final PFs of one arbitrary sample run of each combination;. The first
@@
 in each island during the algorithm run could be carried out to understand its influence
-on the results.
+on the results. \textcolor{blue}{Parallel coordinates will be used when dealing with problems with more than 2 objectives \cite{Li17read}}.
 

### 2019-02-13 hpmoon-asoco.tex
Mentioning the research gaps in conclusion for issue #32

@@
 \textcolor{blue}{After establishing the performance of the new method and in order to
-have some insight on how they work, let's check the effect of the different chromosome sizes and number of
-islands.
+have some insight on how they work, the effect of the different chromosome sizes and number of
+islands can be checked.
 Plotting the solution sets allows to observe its quality, distribution and shape, specially if they are limited to 2 or 3 objectives, as in this paper \cite{Li17read}.
@@
 chromosome is also a key factor to take into account in automatic overlapping
-methods, and not only the number of islands. Studying this factor with
-more types of problems, and new configurations of population size and
-chromosome lengths could be addressed in the future.
+methods, and not only the number of islands. 
+%Studying this factor with more types of problems, and new configurations of population size and chromosome lengths could be addressed in the future. 
 Since our method divides the individuals into blocks of divisible size, aggregation methods after migration, such as the ones used in \cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be also tested.
@@
 depending on population size, number of islands, or other values, or using some statistical parameter setting method, such as Taguchi's \cite{Keratmatpour2018Taguchi}.
-Moreover, a diversity analysis of the individuals
-in each island during the algorithm run could be carried out to understand its influence
-on the results. \textcolor{blue}{Parallel coordinates will be used when dealing with problems with more than 2 objectives \cite{Li17read}}.
+
+\textcolor{blue}{Although the results obtained in this work are promising, it is clear that this method requires more future experiments, in addition to the automatic calculation of $c$.
+These new experiments should involve a more complete parameter study, including a sensitivity analysis, to validate our approach.
+Other benchmarks and real problems should be addressed in the future.
+These problems could involve dealing with more than two objectives, so polar coordinates should be used to visually understand the results \cite{Li17read}.
+Also, other MOEA algorithms available in the literature, such as SPEA or MOEA/D could also be compared.}
+
+% Moreover, a diversity analysis of the individuals in each island during the algorithm run could be carried out to understand its influence on the results.
 
@@
 
-Also, more distributed implementations in several systems (such as a
+Finally, more distributed implementations in several systems (such as a
 GPUs or heterogeneous clusters) with different amounts of
@@
 different methods, being the transmission time between islands a
-relevant issue to be addressed. \textcolor{blue}{Other MOEA algorithms available in the literature, such as SPEA or MOEA/D could also be compared. Moreover, new benchmarks and real problems
-could be  used to validate this approach.}
+relevant issue to be addressed.
 

### 2019-02-13 hpmoon-asoco.tex
More paragraphs divided

@@
 which means that there is no other solution that is equal or better
-for all objectives; the objective of MOP algorithms is to find as many
-solutions equally distributed in the Pareto Front as possible, and in order to do that the
+for all \textcolor{blue}{objectives. The} objective of MOP algorithms is to find as many
+solutions equally distributed in the Pareto Front as \textcolor{blue}{possible. In} order to do that the
 exploration of the search space must be very efficient, trying to
@@
 optimization problems and are easily parallelizable, since they are
-population-based and creating a functionally equivalent parallel
+\textcolor{blue}{population-based. This means that} creating a functionally equivalent parallel
 version is as easy as distributing the population in communicating
@@
 case, the mixing is essential for the algorithm to spread the result
-to all parts of the chromosome, so while we tend to agree with
+to all parts of the \textcolor{blue}{chromosome. So,} while we tend to agree with
 M{\"a}rtens on the small influence of this value on the result, we also

### 2019-02-14 hpmoon-asoco.tex
Fixed typos found by @pacastillo

@@
 \item Spread (S): Measures the spread between solutions, taking into account the Euclidean distance between consecutive solutions.
-As in \textcolor{blue}{previous} previous metric, the lower \textcolor{blue}{the} value, the better, as it implies solutions distributed along all the PF.
+As in \textcolor{blue}{previous} metric, the lower \textcolor{blue}{the} value, the better, as it implies solutions distributed along all the PF.
 \end{itemize}
@@
 HV is then
-normalized \textcolor{blue}{with respect to} to that point.
+normalized \textcolor{blue}{with respect to} that point.
 Also, the optimal reference PF distribution used to calculate the IGD and Spread metrics \cite{Durillo11Jmetal} has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.} .

### 2019-05-07 hpmoon-asoco.tex
Some comments for reviewer #4

@@
 However, only decomposable problems could strictly be implemented in parallel this way.
-A new parallel island-model evolutionary algorithm approach \cite{Alba02Parallelism}, is used here to deal with un-decomposable problems: instead of sharing parts of individuals, each island, hosted by a single processor, applies the variation operators to a specific subset of the whole individual.
+A new parallel island-model evolutionary algorithm approach \cite{Alba02Parallelism} is used here to deal with un-decomposable problems: instead of sharing parts of individuals, each island, hosted by a single processor, applies the variation operators to a specific subset of the whole individual.
 This avoids extra steps to recompose the complete individuals from other islands before evaluation.
@@
 
-Usually an EA starts by generating a set of random solutions, called
-\emph{population}, following a user-defined description. Then, it
+Usually an EA starts by generating a \emph{population}, that is, a set of random solutions, following a user-defined description. Then, it
 evaluates each candidate solution, called \emph{individual}, assigning
 it a \emph{fitness} value that describes how good the individual is
-with regard to the target problem. New solutions are then generated by
+solving the target problem. New solutions are then generated by
 the application of \emph{operators} that either mutate a single
@@
 
-EAs have been extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}.
+EAs were extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}.
 One of the best known and referenced MOEAs
@@
 This
-motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more complete parameter setting.
+motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more extensive parameter evaluation.
 Besides comparing previous methods in this new experimental setup, in this paper we propose
@@
 problem size is large.
+
+% There's no mention of the type of the benchmark problems. Insert here some characterization, including whether they are epistatic or not - JJ
 

### 2019-05-07 hpmoon-asoco.tex
Removed the \textcolor{blue}

@@
 which means that there is no other solution that is equal or better
-for all \textcolor{blue}{objectives. The} objective of MOP algorithms is to find as many
-solutions equally distributed in the Pareto Front as \textcolor{blue}{possible. In} order to do that the
+for all objectives. The objective of MOP algorithms is to find as many
+solutions equally distributed in the Pareto Front as possible. In order to do that the
 exploration of the search space must be very efficient, trying to
@@
 optimization problems and are easily parallelizable, since they are
-\textcolor{blue}{population-based. This means that} creating a functionally equivalent parallel
+population-based. This means that creating a functionally equivalent parallel
 version is as easy as distributing the population in communicating
@@
  This implies to use different distribution
-and sharing mechanisms, as there \textcolor{blue}{exists} a tradeoff between the speedup
+and sharing mechanisms, as there exists a tradeoff between the speedup
 achievable from parallelization and the need to globally recombine the
@@
 
-\textcolor{blue}{Real-world MOPs usually require a high number of decision variables \cite{Zhang17DECAL,XU2018268}}, 
+Real-world MOPs usually require a high number of decision variables \cite{Zhang17DECAL,XU2018268}, 
 meaning that the
@@
 establishing its name and acronym in this paper for the first time.
-We \textcolor{blue}{show}
+We show
 that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
@@
 Besides comparing previous methods in this new experimental setup, in this paper we propose
-a new method that automatically \textcolor{blue}{sets} the size of the overlapped
+a new method that automatically sets the size of the overlapped
 sections depending on the number of available islands, comparing it with previous versions.
@@
 
-The hypothesis of this paper is that the use of \textcolor{blue}{automatically} calculated overlapped sections of the
+The hypothesis of this paper is that the use of automatically calculated overlapped sections of the
 chromosome for the SLA can improve the
@@
 the baseline, disjoint and partly overlapped methods. 
-The size of the overlapped sections \textcolor{blue}{is} calculated from  the number of available subpopulations in the multi-objective evolutionary algorithm, and tested in a real computational environment.
-
-In order to \textcolor{blue}{demonstrate} this claim, our new automatic method has been
+The size of the overlapped sections is calculated from  the number of available subpopulations in the multi-objective evolutionary algorithm, and tested in a real computational environment.
+
+In order to demonstrate this claim, our new automatic method has been
 compared against different overlapping island schemes: a
@@
 
-\textcolor{blue}{Results also show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to \textcolor{blue}{distributing} the decision variables: the higher the dimensionality and the overlapping, the greater the benefit of distribution in a large number of islands.
-This opens up a new challenge to be addressed in the future, by experimenting with new ways to calculate the overlapping sizes depending \textcolor{blue}{on} different factors and parameters.}
+Results also show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distributing the decision variables: the higher the dimensionality and the overlapping, the greater the benefit of distribution in a large number of islands.
+This opens up a new challenge to be addressed in the future, by experimenting with new ways to calculate the overlapping sizes depending on different factors and parameters.
 
@@
 and add a simple communication mechanism among them. But in the case of
-MOEAs, the distribution and parallelization \textcolor{blue}{are} more difficult \textcolor{blue}{than in}
+MOEAs, the distribution and parallelization are more difficult than in
 single-objective EAs. This is because in different steps of the
@@
 %This is an improvement over the previous? What is the relationship? FERGU: linked
-\textcolor{blue}{Other} kind of approaches \textcolor{blue}{have} also been explored.
+Other kind of approaches have also been explored.
 The work by Deb et al.
@@
 In that paper, the authors concluded that dividing the search space is a good idea, although achieving this is not trivial.
-The division of the search space has been explored by other researchers, for example, dividing the population \textcolor{blue}{into} elite and search sub-populations \citep{Wang09parallel}, or separating it in processors by objective \citep{Xiao03specialized}.
+The division of the search space has been explored by other researchers, for example, dividing the population into elite and search sub-populations \citep{Wang09parallel}, or separating it in processors by objective \citep{Xiao03specialized}.
 For example, in \cite{Zhang17DECAL}, a weighted function is used to decompose the objective function and every subpopulation is responsible to solve the problem defined by a weighted vector.
@@
 % Is this really cooperative co-evolution? - JJ FERGU: You mean the Dorronsoro one? The title says it
-\textcolor{blue}{Many real-world problems require high-dimensionality \cite{Zhang17DECAL,XU2018268}.
+Many real-world problems require high-dimensionality \cite{Zhang17DECAL,XU2018268}.
 Addressing this kind of problems with cooperative co-evolution has
 also been studied in several works with approaches closer to the one
-presented here.} The approach to focus on a portion of the chromosome,
+presented here. The approach to focus on a portion of the chromosome,
 as in our overlapped method, was firstly used in the work by
@@
 in several instances.
-\textcolor{blue}{Recently, this approach has also been tested using a Particle Swarm Optimization (PSO) algorithm \cite{DorronsoroPSO2018}, also obtaining significant improvements in speedups and solution quality.
-\textcolor{blue}{Other} authors, such as Cao et al.
-\cite{CaoZLL17} separate the decision variables into several subpopulations after performing an interdependence analysis, but using a fixed number of processors.}
+Recently, this approach has also been tested using a Particle Swarm Optimization (PSO) algorithm \cite{DorronsoroPSO2018}, also obtaining significant improvements in speedups and solution quality.
+Other authors, such as Cao et al.
+\cite{CaoZLL17} separate the decision variables into several subpopulations after performing an interdependence analysis, but using a fixed number of processors.
 
@@
 researchers. For example, some authors focus on the solution space
-modeling the PF by dividing it \textcolor{blue}{into} different clusters, allowing an
+modeling the PF by dividing it into different clusters, allowing an
 easily parallelizable {\em divide and conquer} approach
@@
 the aforementioned ideas to compare two different dMOEAs. The first
-one divided the chromosome into $P$ sections,  \textcolor{blue}{$P$ being} the number of
+one divided the chromosome into $P$ sections,  $P$ being the number of
 islands. Every island $p$ only performed the mutation and crossover in
@@
 
-\subsubsection{\textcolor{blue}{Automatic} SLA with overlapping islands (A)} 
+\subsubsection{Automatic SLA with overlapping islands (A)} 
 As in the previous method, the sections to address by the operators are overlapped, but
@@
 work, the overlapped method ($c=1$) obtained better results when the
-number of islands \textcolor{blue}{was} bigger than 8. On the contrary, when the number of
+number of islands was bigger than 8. On the contrary, when the number of
 islands is small, no overlapping is necessary. So, we have used this
@@
 on.
-Dividing individuals by blocks of equal size, instead \textcolor{blue}{of} a percentage, allow the future integration of our method with other recombination mechanisms, such as the ones presented in \cite{Dorronsoro13superlinear} or \cite{Kimovski15Parallel}.
+Dividing individuals by blocks of equal size, instead of a percentage, allow the future integration of our method with other recombination mechanisms, such as the ones presented in \cite{Dorronsoro13superlinear} or \cite{Kimovski15Parallel}.
 Also, as mentioned, this is only a possible formula to reach above-described behaviour for $c$, and future work will study new methods or alternative formulas to determine it, for example using Taguchi Method \cite{Keratmatpour2018Taguchi}.
@@
 \includegraphics[width=12cm]{islandAdaptive.jpg}
-\caption{\textcolor{blue}{Automatic} SLA with overlapping islands (A): every island $p$ modifies the  $p+c$,
+\caption{Automatic SLA with overlapping islands (A): every island $p$ modifies the  $p+c$,
   $p_{th}$ and $p-c$  components (in grey) of the individuals using genetic operators (crossover and mutation).
@@
 \item Spread (S): Measures the spread between solutions, taking into account the Euclidean distance between consecutive solutions.
-As in \textcolor{blue}{previous} metric, the lower \textcolor{blue}{the} value, the better, as it implies solutions distributed along all the PF.
+As in previous metric, the lower the value, the better, as it implies solutions distributed along all the PF.
 \end{itemize}
@@
 maximum number of islands has also been  used in a previous work in the
-literature \cite{Martens13asynchronous}. The \textcolor{blue} chosen crossover and mutation, SBX and polynomial, have also been  used previously by other
+literature \cite{Martens13asynchronous}. The chosen crossover and mutation, SBX and polynomial, have also been  used previously by other
 authors in \cite{Durillo08masterslave,CaoZLL17}.  % SBX is first mentioned
@@
 
-\textcolor{blue}{The global population size is set to 1024.
+The global population size is set to 1024.
 We have decided to use that value for two reasons: the first is that it is large enough to have 8 individuals per island by dividing that number when using 128 islands and small enough to have 128 individuals when using 8 islands.
 This is the minimum and maximum population size per island used by M{\"a}rtens et al.
-in his work \cite{Martens13asynchronous}.}
+in his work \cite{Martens13asynchronous}.
 
@@
 operations and migrations can be achieved. Also, we are using
-different \textcolor{blue}{numbers} of islands (with different sub-population sizes) and that
+different numbers of islands (with different sub-population sizes) and that
 could lead to different execution times, so it would be difficult to
@@
 case, the mixing is essential for the algorithm to spread the result
-to all parts of the \textcolor{blue}{chromosome. So,} while we tend to agree with
+to all parts of the chromosome. So, while we tend to agree with
 M{\"a}rtens on the small influence of this value on the result, we also
@@
 negative impact. However, a precise fine-tuning of this value is left
-as future work, as the main focus of this paper was to \textcolor{blue}{show} the
+as future work, as the main focus of this paper was to show the
 general concept, and not tune the values for maximum performance.
@@
   to compose solutions obtained by different islands, as occurs other
-  works \cite{Dorronsoro13superlinear}.\textcolor{blue}{The main parameters studied in the proposed system are limited to the number of islands and the size of the problem.
+  works \cite{Dorronsoro13superlinear}.The main parameters studied in the proposed system are limited to the number of islands and the size of the problem.
 This decision has been motivated because all previous works described in the state of the art also limit their experimental setting to the same parameters \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}.
-Although all the parameters indicated above have an influence on the general result of the MOEA, their general effect is well understood and, although there will be an interplay between them and the number of islands and problem size, this is left mainly as future work.}
+Although all the parameters indicated above have an influence on the general result of the MOEA, their general effect is well understood and, although there will be an interplay between them and the number of islands and problem size, this is left mainly as future work.
 
@@
 Different metrics, previously explained, have been used
-to calculate the quality of the obtained PFs in every configuration. As HV \textcolor{blue}{requires} a reference point to be
+to calculate the quality of the obtained PFs in every configuration. As HV requires a reference point to be
 calculated (see Figure \ref{fig:hypervolume}), we have chosen the value (1,9) as none of the existing solutions on all fronts obtained during all executions are dominated by it.
@@
 HV is then
-normalized \textcolor{blue}{with respect to} that point.
+normalized with respect to that point.
 Also, the optimal reference PF distribution used to calculate the IGD and Spread metrics \cite{Durillo11Jmetal} has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.} .
@@
   configuration, for the 4 methods compared: baseline (B), disjoint
-  (D), overlapped (O) and \textcolor{blue}{automatically} overlapped
+  (D), overlapped (O) and automatically overlapped
   (A), % No sería mejor "automatically overlapped" or "automatic
@@
 }
-\caption{Average quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatically} overlapped (A), using a chromosome length of 2048 dimensions.
+\caption{Average quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and automatically overlapped (A), using a chromosome length of 2048 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 Results show that there is a difference in performance when using 512 or 2048 dimensions.
-Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than \textcolor{blue}{those} obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply these methods.
+Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than those obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply these methods.
 A contradiction arises with respect to the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths.
@@
 However, with 2048 dimensions, results show that dividing the chromosome produces an improvement in all the quality indicators using the automatic ($A$) version (Table \ref{tab:results2048}), even overcoming the overlapping ($O$) and disjoint ($D$) methods.
-Therefore, there \textcolor{blue}{exists} some kind of limit point in chromosome length where one method will be preferable to another, besides depending on the number of islands and population size.
+Therefore, there exists some kind of limit point in chromosome length where one method will be preferable to another, besides depending on the number of islands and population size.
 
@@
 }
-\caption{Average number of generations and  solutions per front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatically} overlapped (A), using a chromosome length of 512 dimensions.
+\caption{Average number of generations and  solutions per front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and automatically overlapped (A), using a chromosome length of 512 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 }
-\caption{Average number of generations and solutions per front after 30 runs per configuration, for methods baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatically} overlapped (A), using a chromosome length of 2048 dimensions.
+\caption{Average number of generations and solutions per front after 30 runs per configuration, for methods baseline (B), disjoint (D), overlapped (O) and automatically overlapped (A), using a chromosome length of 2048 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 lengths, increasing the number of islands implies more generations
-with all the methods (logically, as there are \textcolor{blue}{fewer} individuals in each
+with all the methods (logically, as there are fewer individuals in each
 island). But also, the SLA methods
@@
 %ZDT1 
-\textcolor{blue}{After establishing the performance of the new method and in order to
+After establishing the performance of the new method and in order to
 have some insight on how they work, the effect of the different chromosome sizes and number of
@@
 Plotting the solution sets allows to observe its quality, distribution and shape, specially if they are limited to 2 or 3 objectives, as in this paper \cite{Li17read}.
-} Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048} show the
+Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048} show the
 final PFs of one arbitrary sample run of each combination;. The first
@@
 Indeed, there is not a significant difference between methods, with an exception: Spread using $A$ with $L=512$ is significantly worse.
-As in previous approaches, it is visually clear that increasing the number of islands, and therefore, reducing the number of individuals per island, \textcolor{blue}{implies} a decrease the in quality of the HV.
+As in previous approaches, it is visually clear that increasing the number of islands, and therefore, reducing the number of individuals per island, implies a decrease the in quality of the HV.
 
@@
 
-\textcolor{blue}{Although the results obtained in this work are promising, it is clear that this method requires more future experiments, in addition to the automatic calculation of $c$.
+Although the results obtained in this work are promising, it is clear that this method requires more future experiments, in addition to the automatic calculation of $c$.
 These new experiments should involve a more complete parameter study, including a sensitivity analysis, to validate our approach.
@@
 These problems could involve dealing with more than two objectives, so polar coordinates should be used to visually understand the results \cite{Li17read}.
-Also, other MOEA algorithms available in the literature, such as SPEA or MOEA/D could also be compared.}
+Also, other MOEA algorithms available in the literature, such as SPEA or MOEA/D could also be compared.
 

### 2019-05-07 hpmoon-asoco.tex
Added blue to @JJ 's changes, after removing all the previous blue

@@
 
-Usually an EA starts by generating a \emph{population}, that is, a set of random solutions, following a user-defined description. Then, it
+Usually an EA starts by generating \textcolor{blue}{a \emph{population}, that is, a set of random solutions}, following a user-defined description. Then, it
 evaluates each candidate solution, called \emph{individual}, assigning
 it a \emph{fitness} value that describes how good the individual is
-solving the target problem. New solutions are then generated by
+\textcolor{blue}{solving} the target problem. New solutions are then generated by
 the application of \emph{operators} that either mutate a single
@@
 
-EAs were extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}.
+EAs \textcolor{blue}{were} extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}.
 One of the best known and referenced MOEAs
@@
 This
-motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more extensive parameter evaluation.
+motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more \textcolor{blue}{extensive parameter evaluation}.
 Besides comparing previous methods in this new experimental setup, in this paper we propose

### 2019-05-07 hpmoon-asoco.tex
Removed 3rd person references

@@
 
-\begin{bluecolor}
-
 %One of the  most extensively used methods to deal with high-dimensional, multi-objective optimization problems are distributed co-evolutionary algorithms.
@@
 In these algorithms, each island modifies a fragment of the chromosome that encodes a possible solution to the problem.
-In this paper, we want to demonstrate that automatically setting the size of the overlapping fragments depending on the number of islands obtains better results than using the same size.
-We  have compared this method to other parallel evolutionary techniques considering a different number of islands, chromosome sizes and benchmarks.
+\textcolor{blue}{The objective of this paper is} to demonstrate that automatically setting the size of the overlapping fragments depending on the number of islands obtains better results than using the same size.
+\textcolor{blue}{This method has been compared} to other parallel evolutionary techniques considering a different number of islands, chromosome sizes and benchmarks.
 The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm in high-dimensional, un-decomposable, multi-objective problems.
 This opens a very promising line to automatically adapt the overlapping sizes in this kind of algorithms.
-
-\end{bluecolor}
 
@@
 
-In our previous work \citep{Garcia16hpmoon} we used this method in a
-preliminary experimental setup, although it is worth mentioning we are
-establishing its name and acronym in this paper for the first time.
-We show
+In our previous work \citep{Garcia16hpmoon} \textcolor{blue}{this method was used} in a
+preliminary experimental setup, although it is worth mentioning \textcolor{blue}{that its name and acronym is established} in this paper for the first time.
+\textcolor{blue}{It was shown}
 that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
@@
 can improve the quality of the solutions 
-when the number of islands is increased. In that paper, we showed that the most
+when the number of islands is increased. In that paper, \textcolor{blue}{the results showed} that the most
 adequate overlapping size may vary depending on a relation between the
@@
 motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more \textcolor{blue}{extensive parameter evaluation}.
-Besides comparing previous methods in this new experimental setup, in this paper we propose
+Besides comparing previous methods in this new experimental setup, in this paper
 a new method that automatically sets the size of the overlapped
-sections depending on the number of available islands, comparing it with previous versions.
+sections depending on the number of available islands \textcolor{blue}{is proposed}, comparing it with previous versions.
 
@@
 broadcast all solutions to all islands for recombination, but only one solution to a random island, needing less
-communication time. Moreover, Dorronsoro or Kimovsky approaches limited the maximum number of islands to 8, while in this paper we have
-used up to 128 islands.
+communication time. Moreover, Dorronsoro or Kimovsky approaches limited the maximum number of islands to 8, while in this paper \textcolor{blue}{up to 128 islands have been used}.
 
@@
 
-In our previous work \citep{Garcia16hpmoon} we used some of
-the aforementioned ideas to compare two different dMOEAs. The first
+In our previous work \citep{Garcia16hpmoon} some of
+the aforementioned ideas \textcolor{blue}{were used} to compare two different dMOEAs. The first
 one divided the chromosome into $P$ sections,  $P$ being the number of
@@
 results than a baseline algorithm that dealt with the whole chromosome
-in each island for crossover and mutation. We discovered that the
+in each island for crossover and mutation. \textcolor{blue}{It was} discovered that the
 performance using one or another method depends on the number of
@@
 cluster. 
-Therefore, at the same time, we are proposing a new method to divide the individual search space according to the number of evolved subpopulations, and also validating the previous approach.
-
-We will describe how we have tested our approach in the next Section.
+Therefore, at the same time, \textcolor{blue}{a new method is proposed in this paper} to divide the individual search space according to the number of evolved subpopulations, and also validating the previous approach.
+
+%We will describe how we have tested our approach in the next Section.
+\textcolor{blue}{The methodology to test our approach is described in the next Section.}
 
@@
 
-The objective of this section is to explain the methodology we have followed to
+The objective of this section is to explain the methodology followed to
 compare the different versions of the overlapping schemes.
@@
 \subsection{Proposed methods}
-In this paper we analyze several SLA algorithms we have
-implemented by using a parallel multi-objective baseline algorithm
+In this paper \textcolor{blue}{several implemented SLA algorithms are analyzed}
+ by using a parallel multi-objective baseline algorithm
 as a basis for comparisons. Our proposed methods, using different overlapping schemes, 
@@
 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}. 
-Therefore, we have used a basic distributed NSGA-II algorithm without
-overlapping sections as the baseline (B).
+Therefore, a basic distributed NSGA-II algorithm without
+overlapping sections \textcolor{blue}{has been used} as the baseline (B).
 
@@
 subpopulations according to the decision space to be explored by each
-island. Here we will consider three methods in which each island only
+island. Here three methods \textcolor{blue}{will be considered} in which each island only
 performs crossover and mutation in specific sections of the
@@
 
-The methods we have tested are presented in the next subsections.
+The methods tested \textcolor{blue}{in this paper} are presented in the next subsections.
 
@@
 number of islands was bigger than 8. On the contrary, when the number of
-islands is small, no overlapping is necessary. So, we have used this
-knowledge to propose the formula $c=round(0.2*P-1)/2$ to calculate the
+islands is small, no overlapping is necessary. So, this
+knowledge \textcolor{blue}{has been used} to propose the formula $c=round(0.2*P-1)/2$ to calculate the
 extra sections to overlap. Therefore, when $P=8$ then $c=0$
@@
 
-We have chosen those metrics not only because they have been used
+Those metrics \textcolor{blue}{have been chosen} not only because they have been used
 extensively, especially in some of the papers presented in Section \ref{sec:soa}
@@
 The global population size is set to 1024.
-We have decided to use that value for two reasons: the first is that it is large enough to have 8 individuals per island by dividing that number when using 128 islands and small enough to have 128 individuals when using 8 islands.
+\textcolor{blue}{That value has been chosen} for two reasons: the first is that it is large enough to have 8 individuals per island by dividing that number when using 128 islands and small enough to have 128 individuals when using 8 islands.
 This is the minimum and maximum population size per island used by M{\"a}rtens et al.
@@
 According to Alba and Luque \cite{EVALUATIONPARALLEL}, other stop criteria such as the number of evaluations required to attain a solution, may be misleading depending on the studied scenario.
-In our case, we have used time instead of the number of evaluations firstly
+In our case, \textcolor{blue}{time has been used} instead of the number of evaluations firstly
 because our hypothesis argues that the time saved in crossover and
 mutation can be spent on improving the sub-populations and more
-operations and migrations can be achieved. Also, we are using
-different numbers of islands (with different sub-population sizes) and that
+operations and migrations can be achieved. Also, 
+different numbers of islands \textcolor{blue}{has been used} (with different sub-population sizes) and that
 could lead to different execution times, so it would be difficult to
@@
 \cite{cantu1998survey}, this migration gap has contradictory effects
-on the result: by increasing it, we make the system closer to a
+on the result: by increasing it, the system \textcolor{blue}{is made} closer to a
 single-node one, since populations tend to mix without restriction; by
-decreasing it, we make the isolate islands more prone to being stuck
+decreasing it, the isolate islands \textcolor{blue}{are} more prone to being stuck
 in local minima. \cite{Martens13asynchronous} mentions that several
@@
 case, the mixing is essential for the algorithm to spread the result
-to all parts of the chromosome. So, while we tend to agree with
-M{\"a}rtens on the small influence of this value on the result, we also
-think that making this value much bigger in our case would have a
+to all parts of the chromosome. So, while \textcolor{blue}{one might} tend to agree with
+M{\"a}rtens on the small influence of this value on the result, \textcolor{blue}{it is possible} that making this value much bigger in our case would have a
 negative impact. However, a precise fine-tuning of this value is left
@@
 to calculate the quality of the obtained PFs in every configuration. As HV requires a reference point to be
-calculated (see Figure \ref{fig:hypervolume}), we have chosen the value (1,9) as none of the existing solutions on all fronts obtained during all executions are dominated by it.
-In other words, as we are minimizing in both objectives, this reference point is required to be numerically larger or equal in each objective, and strictly larger in at least one of them (dominated) for all solutions in the PFs we are going to measure.
+calculated (see Figure \ref{fig:hypervolume}), the value (1,9) \textcolor{blue}{has been chosen} as none of the existing solutions on all fronts obtained during all executions are dominated by it.
+In other words, as both objectives \textcolor{blue}{are being minimized}, this reference point is required to be numerically larger or equal in each objective, and strictly larger in at least one of them (dominated) for all solutions in the PFs \textcolor{blue}{used} to measure.
 HV is then
@@
 $c=0$), and when $P=16$ they are equivalent to O ($c=1$).
-We refer this equivalence with the word {\em Equiv-} in tables.
+This equivalence \textcolor{blue}{is referred} with the word {\em Equiv-} in tables.
 For example, Equiv-D in an HV cell  means that the HV of A is the same than the value in D column, because the behaviour of this configuration is the same than executing D.
@@
 SLA methods behave worse than $B$, as it was also shown on average in
-Table \ref{tab:results512}. Nevertheless, if we focus on the plots
+Table \ref{tab:results512}. Nevertheless, \textcolor{blue}{when focusing} on the plots
 obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this
@@
 
-In ZDT6, the Pareto-optimal solutions are not only non-uniformly distributed along the PF, but their density also increases as we move further away from it.
+In ZDT6, the Pareto-optimal solutions are not only non-uniformly distributed along the PF, but their density also increases \textcolor{blue}{when moving} further away from it.
 That is the reason why some PFs obtained have an extremely low number of solutions in some configurations, and also, they are aggregated toward the areas with more density.
@@
 Since our method divides the individuals into blocks of divisible size, aggregation methods after migration, such as the ones used in \cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be also tested.
-But as we are dealing with complete individuals in each island, the possibility of using a real number, such as 0.3 (30\% overlapping) instead an integer value opens future experimental setups.
+But as complete individuals \textcolor{blue}{treated} in each island, the possibility of using a real number, such as 0.3 (30\% overlapping) instead an integer value opens future experimental setups.
 For example, comparing 
@@
 
-This work has been partially funded by project SPIP2017-02116 (Spanish ``Direcci\'on General de Tr\'afico''), and projects EphemeCH TIN2014-56494-C4-3-P, TIN2015-67020-P, DeepBio TIN2017-85727-C4-2-P  and TEC2015-68752 (Spanish ``Ministerio de
-Econom{\'ia}a y Competitividad'' and ERDF funds).
+This work has been partially funded by project SPIP2017-02116 (Spanish ``Direcci\'on General de Tr\'afico''), and projects, TIN2015-67020-P, DeepBio TIN2017-85727-C4-2-P  and TEC2015-68752 (Spanish ``Ministerio de
+Econom{\'ia}a y Competitividad'') and PGC2018-098813-B-C31 (Spanish ``Ministerio de Ciencia, Innovación y Universidades''), and by European Regional Development Funds (ERDF).
 We would like to express our gratitude to the editorial team and the reviewers, whose valuable comments on this paper have significantly improved its quality.

### 2019-05-07 highlights.tex
Changes in the highlights

--- 2016-11-18 highlights.tex
@@
 \begin{itemize}
-\item A study on methods to overlap the search space in distributed multi-objective evolutionary algorithms is carried out
-\item A new adaptive overlapping mechanism is presented
-\item Different combinations of number of islands, genome sizes, benchmarks and methods are used
-\item Different quality metrics have been compared
-\item Results are validated in a real system
-\item All overlapping schemes outperform the baseline, being the adaptive method the one that obtains the best performance
+\item ------------------------------------------------------------------------------------
+\item A study on methods to overlap the search space in distributed MOEAs is carried out  
+\item A new automatic overlapping mechanism is presented
+\item Results are validated in a real system, using different quality metrics
+\item Relation between the number of islands and chromosome length is a relevant factor
+\item Best results are obtained when increasing the dimensionality and overlapping size
+%\item A study on methods to overlap the search space in distributed multi-objective evolutionary algorithms is carried out
+%\item A new adaptive overlapping mechanism is presented
+%\item Different combinations of number of islands, chromosome sizes, benchmarks and methods are used
+%\item Different quality metrics have been compared
+%\item Results are validated in a real system
+%\item Results show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is a relevant factor to determine the most efficient alternative to distribute the decision variables
+%\item The higher the dimensionality and the overlapping, the greater the benefit of distribution in a large number of islands
 \end{itemize}

### 2019-05-13 hpmoon-asoco.tex
Checking in changes

--- 2019-05-07 hpmoon-asoco.tex
@@
+%\affiliation{\affilnum{1}Dept. of Computer Architecture and Computer Technology, University of Granada, Spain}
+
+%\corrauth{Pablo Garc\'ia-S\'anchez,
+%ETS. Ingenier\'ias en Inform\'atica y Telecomunicaci\'on and CITIC-UGR,
+%C/Periodista Daniel Saucedo s/n,
+%Universidad de Granada,
+%18071, Granada, Spain.}
+
 \documentclass[preprint]{elsarticle}
@@
 
-\newenvironment{bluecolor}{\par\color{blue}}{\par}
-
 \begin{document}
@@
 \begin{abstract}
-
-\begin{bluecolor}
-
-%One of the  most extensively used methods to deal with high-dimensional, multi-objective optimization problems are distributed co-evolutionary algorithms.
-However, only decomposable problems could strictly be implemented in parallel this way.
-A new parallel island-model evolutionary algorithm approach, which we call {\em selective operator application}, is used here to deal with un-decomposable problems: instead of sharing parts of individuals, each island, hosted by a single processor, applies the variation operators to a specific subset of the whole individual.
-This avoids extra steps to recompose the complete individuals from other islands before evaluation.
-
-%In this paper, we intend to demonstrate that automatically setting the size of these  overlapping sections, since it focuses the search between borders of the different search spaces, is able to obtain better  results than using the same size independently of the number of islands.
-In order to demonstrate that, we  have compared this method to other parallel evolutionary techniques considering different number of islands, chromosome sizes and benchmarks.
-The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm in high-dimensional, un-decomposable, multi-objective problems.
-
-%Results also show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distribute the decision variables: the higher the dimensionality and the overlapping, the greater the benefit of distribution in a large number of islands.
-This opens up a new challenge to be addressed in the future, by experimenting with new ways to calculate the overlapping sizes depending of different factors and parameters.
-
-%%%NEW AND SHORTED
-Parallel island-model co-evolutionary algorithms are well-known methods, suitable for dealing with large multi-objective optimization problems.
-In these algorithms, each island modifies a fragment of the chromosome that encodes a possible solution to the problem.
-In this paper, we want to demonstrate that automatically setting the size of the overlapping fragments depending on the number of islands obtains better results than using the same size.
-We  have compared this method to other parallel evolutionary techniques considering a different number of islands, chromosome sizes and benchmarks.
-The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm in high-dimensional, un-decomposable, multi-objective problems.
-This opens a very promising line to automatically adapt the overlapping sizes in this kind of algorithms.
-
-\end{bluecolor}
+  % First, state the problem!!!! - JJ Pablo: ok!
+%Real-world optimization problems usually require to deal with several objectives.
+%Multi-objective optimization methods have gained interest in the last
+%years because of the performance they can achieve solving this kind of problems. 
+%Many of them usually require a high-dimensional
+%decision space, and multi-objective Evolutionary Algorithms have been
+%successfully used in the past. Due to the large computational cost
+%these algorithms require, different parallelization and distribution
+%methods have been proposed, with different parallel and distributed
+%computer architectures to cope with them.
+
+  \textcolor{blue}{Real world optimization problems usually have many dimensions and
+  several objectives. The high dimensionality requires exceptional
+  computing power, and the fact that several dimensions have to be
+  searched at the same time add additional difficulty.}
+% One of the most extended methods to deal with high-dimensional
+% multi-objective optimization problems are the distributed
+% co-evolutionary algorithms.
+% ----------------- This sentence is meaningless. It should be
+% substituted by other stating that co-evolutionary algorithms can
+% deal with it for some reason
+% Besides, we're no longer saying that they are co-evolutionary in the
+% title, but "island-based selective operator application". This
+% should go to the abstract too - JJ
+
+%In these methods %which ones? coevolutionary or selective operator
+                   %application? - JJ
+%  each processor deals only with a part of the decision
+%space, that is, the individuals belonging to the same sub-population,
+%\textcolor{blue}{which are called {\em islands} in this context}, explore the same subset of decision variables. 
+\textcolor{blue}{An approach to cope with these issues is to allocate parts of the decision space to different
+processors. Thus, each processor only deals with the individuals of a sub-population (called
+island in this context) that explores the part of the decision space allocated to the processor.}
+
+However, only
+decomposable problems could strictly be implemented in parallel this
+way. \textcolor{blue}{A new approach, which we call {\em selective operator application} is presented here to deal with un-decomposable
+problems:} % so we are saying that high-dimensional multi-objective
+          % problems are a challenge, but we are presenting a solution
+          % for non-decomposable problems. What's what? - JJ
+% Still not addressed - JJ
+instead of sharing parts
+of individuals, each processor applies the variation operators to a
+specific subset of the whole individual. % this solves... - JJ
+% not addressed - JJ
+We have previously proved
+that extending the length of these subsets, and therefore, sharing
+\textcolor{blue}{some search space between islands, implies an
+  improvement in different performance metrics}.
+% In this paper, we intend to prove that adapting the size of the
+% overlapping section, since it improves *, is able to obtain better
+% results than a non-adaptive strategy. In order to prove that, we
+% compare - JJ
+In this paper, a new method for automatically
+adapting the size of the overlapping, or shared, sections of the
+individuals has been compared to other collaborative evolutionary
+techniques considering different number of islands, chromosome sizes
+and benchmarks. The analysis of the obtained experimental results, by
+using different metrics, shows that our approach can provide
+statistically significant improvements with respect to the base
+algorithm \textcolor{blue}{in high-dimensional multi-objective problems}. 
+Results also show that the relation between the number of
+islands (subpopulations) and the length of the chromosome (number of
+decision variables) is also a relevant factor to determine the most
+efficient alternative to distribute the decision variables.   % Say
+                                % something how it's relevant, and
+                                % what you have to do if you have so
+                                % many decision variables - JJ
+\textcolor{blue}{This opens up a new challenge that to be addressed in the future.}
+% This
+                                % solves a problem or challenge we
+                                % hadn't stated. - JJ Pablo: metido, mira a ver si queda frase memorable
 
@@
 
-% Maybe add a sentence explaining what problems are decomposable and which ones are not. - JJ
-\begin{bluecolor}
-One of the methods that are most extensively used  to deal with high-dimensional, multi-objective optimization problems (MOPs) are distributed co-evolutionary algorithms \cite{Gong15models}.
-However, only decomposable problems could strictly be implemented in parallel this way.
-A new parallel island-model evolutionary algorithm approach \cite{Alba02Parallelism} is used here to deal with un-decomposable problems: instead of sharing parts of individuals, each island, hosted by a single processor, applies the variation operators to a specific subset of the whole individual.
-This avoids extra steps to recompose the complete individuals from other islands before evaluation.
-\end{bluecolor}
+%Introduction should start in the same way as the abstract. And
+%starting with something that is not really applicable here, talking
+%about general parallel evolutionary algorithms, is even worse.
+% Right way (IMNSHO)
+% 1. Multiobjective problems are
+% 2. They usually require a good amount of computation → parallel
+% distributed
+% 3. One way to solve them is to use MOEAs _because_ they can be
+% easily parallelized
+% 4. But the easy paralellization is not necessarily efficient.
+% 5. We have proposed the HPMOON (or whatever) technique to improve
+% it. In paper (whatever) we proved that (whatever)
+% 6. In this paper we will be proving whatever - JJ FERGU: Addressing JJ order
+% OK - JJ
 
 %1. MOP ARE
-In MOPs, several
+Multi-objective optimization problems (MOP) are those where several
 objectives have to be simultaneously optimized
@@
 these problems the aim is to obtain a set of solutions that are better
-than the rest considering all the objectives; this set is known as
+than the rest, considering all the objectives; this set is known as
 the Pareto Front (PF). The solutions in this set are {\em non-dominated},
 which means that there is no other solution that is equal or better
-for all objectives. The objective of MOP algorithms is to find as many
-solutions equally distributed in the Pareto Front as possible. In order to do that the
+for all objectives; the objective of MOP algorithms is to find as many
+solutions equally distributed in the Pareto Front as possible, and in order to do that the
 exploration of the search space must be very efficient, trying to
@@
 that can be effectively used to find nearly optimal solutions for
-optimization problems and are easily parallelizable, since they are
-population-based. This means that creating a functionally equivalent parallel
+optimization problems and are easily paralellizable, since they are
+population-based and creating a functionally equivalent parallel
 version is as easy as distributing the population in communicating
@@
 
-Usually an EA starts by generating a \emph{population}, that is, a set of random solutions, following a user-defined description. Then, it
+%The availability of metaheuristics which are able to efficiently approach these multi-objective optimization problems have made it possible to cope with many real applications from such multi-objective point of view [4, 5, 6, 7, 8].
+Evolutionary algorithms (EAs) [9] are bio-inspired meta-heuristics that can be effectively used to find nearly optimal solutions for optimization problems and have been extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) [29].
+
+Usually an EA starts by generating a set of random solutions, called
+\emph{population}, following a user-defined description. Then, it
 evaluates each candidate solution, called \emph{individual}, assigning
 it a \emph{fitness} value that describes how good the individual is
-solving the target problem. New solutions are then generated by
+with regard to the target problem. New solutions are then generated by
 the application of \emph{operators} that either mutate a single
@@
 
-EAs were extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}.
+\textcolor{blue}{EAs have been extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}}.
 One of the best known and referenced MOEAs
@@
 \citep{Deb00NSGAII}. Classical genetic operators are applied to all
-the individuals, which are divided into different ranks, based on 
+the individuals, which are divided into different ranks, based on the
 dominance, to be selected for the next generations.
+% This paragraph has nothing to do with anything. Is it useful for
+% what you are doing in the paper? Is there any challenge that you
+% will be solving here? For instance, you could talk about the problem
+% it's got for parallelization and how it deals with them - JJ FERGU: Could you add some paragraph to justify it? (use \textcolor{blue}{} please)
 
@@
  This implies to use different distribution
-and sharing mechanisms, as there exists a tradeoff between the speedup
+and sharing mechanisms, as there exist a tradeoff between the speedup
 achievable from parallelization and the need to globally recombine the
@@
 
-Real-world MOPs usually require a high number of decision variables \cite{Zhang17DECAL,XU2018268}, 
+\textcolor{blue}{Real-world MOPs usually require a high number of decision variables \cite{Zhang17DECAL,XU2018268}}, % No they don't, and
+                                % if they do, add a reference - JJ FERGU: added references
 meaning that the
 MOEAs need to deal with large individuals and spend significant extra
-time for crossover, mutation and migration.
-Different authors have 
+time for crossover, mutation and migration. %depending on the
+                                %language, this time might not be
+                                %significant at all, and will depend
+                                %on the length of the chromosome, not
+                                %the part of the chromosome you will
+                                %be applying it to. Besides, this is
+                                %not the critical part of the
+                                %algorithm, the critical part is
+                                %searching the solution space. 
+Different authors have % this is only one possibility. You should talk
+                       % about simple island models, too - JJ
 proposed methods to divide the decision space (the chromosome) to
 improve the performance and solution quality. In this aspect, the
-co-evolution model is a dimension-distributed model where a 
+co-evolution model is a dimension-distributed model where a % first
+                                % reference to co-evolution in this
+                                % paper. Is it still a paper about
+                                % co-evolution? - JJ
 high-dimensional problem is divided into lower dimensional ones
 \citep{Gong15models,Tonda12cooperative}, and evolved separately. One
-example of the application of this technique was described in
+example of application of this technique was described in
 \citep{Kimovski15Parallel}. The method presented in that work involves
@@
 A similar approach used to solve this kind of problems is the {\em
-  SeLective operator Application} (SLA) presented in this paper. In this case, each island
+  selective operator application} (SLA) \textcolor{blue}{presented in this paper}. In this case, each island
 deals with the whole chromosome, but only modifies a fragment of it in
@@
 using the whole chromosome for fitness calculation. This allows to
-deal with un-decomposable problems.
-
+deal with un-decomposable problems. % if the whole chromosome is used,
+                                % mutation and crossover will take the
+                                % same time. You are modifying the
+                                % search space, though. 
 In our previous work \citep{Garcia16hpmoon} we used this method in a
@@
 establishing its name and acronym in this paper for the first time.
-We show
+We proved 
 that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
@@
 were conducted in a limited experimental system: mono-processor and
-synchronous island model. 
+synchronous island model. %where we couldn't prove that... Or, we
+                          %couldn't experiment... - JJ
 This
-motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more extensive parameter evaluation.
+motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more complete parameter setting.
 Besides comparing previous methods in this new experimental setup, in this paper we propose
-a new method that automatically sets the size of the overlapped
+a new method that automatically \textcolor{blue}{sets} the size of the overlapped
 sections depending on the number of available islands, comparing it with previous versions.
 
+% We have to
+                                % emphasize what is actually done. Is
+                                % this an addition to the old paper,
+                                % or a complete rewrite? - JJ FERGU: rewritten previous paragraph
+
 %6 IN THIS PAPER WE WILL BE PROVING
 
-The hypothesis of this paper is that the use of automatically calculated overlapped sections of the
+The hypothesis of this paper is that the use of \textcolor{blue}{automatically} calculated overlapped sections of the
 chromosome for the SLA can improve the
@@
 the baseline, disjoint and partly overlapped methods. 
-The size of the overlapped sections is calculated from  the number of available subpopulations in the multi-objective evolutionary algorithm, and tested in a real computational environment.
-
-In order to demonstrate this claim, our new automatic method has been
+\textcolor{blue}{The size of the overlapped sections are calculated from  the number of available subpopulations in the multi-objective evolutionary algorithm, and tested in a real computational environment.}
+
+In order to prove this claim, our new automatic method has been
 compared against different overlapping island schemes: a
@@
 problem size is large.
-
-% There's no mention of the type of the benchmark problems. Insert here some characterization, including whether they are epistatic or not - JJ
-
-Results also show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distributing the decision variables: the higher the dimensionality and the overlapping, the greater the benefit of distribution in a large number of islands.
-This opens up a new challenge to be addressed in the future, by experimenting with new ways to calculate the overlapping sizes depending on different factors and parameters.
 
@@
 and add a simple communication mechanism among them. But in the case of
-MOEAs, the distribution and parallelization are more difficult than in
+MOEAs, the distribution and parallelization is \textcolor{blue}{more difficult}
 single-objective EAs. This is because in different steps of the
@@
 In that paper, the authors concluded that dividing the search space is a good idea, although achieving this is not trivial.
-The division of the search space has been explored by other researchers, for example, dividing the population into elite and search sub-populations \citep{Wang09parallel}, or separating it in processors by objective \citep{Xiao03specialized}.
-For example, in \cite{Zhang17DECAL}, a weighted function is used to decompose the objective function and every subpopulation is responsible to solve the problem defined by a weighted vector.
-Other authors, such as M{\"a}rtens \citep{Martens13asynchronous} use migration to accept individuals based on diversity, and migrating from not-crowded areas.
+The division of the search space has been explored by other researchers, for example, dividing the population in elite and search sub-populations \citep{Wang09parallel}, or separating it in processors by objective \citep{Xiao03specialized}.
+\textcolor{blue}{For example, in \cite{Zhang17DECAL}, a weighted function is used to decompose the objective function and every subpopulation is responsible to solve the problem defined by a weighted vector.} Other authors, such as M{\"a}rtens \citep{Martens13asynchronous} use migration to accept individuals based on diversity, and migrating from not-crowded areas.
 
 % Is this really cooperative co-evolution? - JJ FERGU: You mean the Dorronsoro one? The title says it
-Many real-world problems require high-dimensionality \cite{Zhang17DECAL,XU2018268}.
+\textcolor{blue}{Many real-world problems require high-dimensionality \cite{Zhang17DECAL,XU2018268}.
 Addressing this kind of problems with cooperative co-evolution has
 also been studied in several works with approaches closer to the one
-presented here. The approach to focus on a portion of the chromosome,
+presented here.} The approach to focus on a portion of the chromosome,
 as in our overlapped method, was firstly used in the work by
@@
 in several instances.
-Recently, this approach has also been tested using a Particle Swarm Optimization (PSO) algorithm \cite{DorronsoroPSO2018}, also obtaining significant improvements in speedups and solution quality.
-Other authors, such as Cao et al.
-\cite{CaoZLL17} separate the decision variables into several subpopulations after performing an interdependence analysis, but using a fixed number of processors.
+\textcolor{blue}{Recently, this approach has also been tested using a Particle Swarm Optimization (PSO) algorithm \cite{DorronsoroPSO2018}, also obtaining significant improvements in speedups and solution quality.
+Others authors, such as Cao et al.
+\cite{CaoZLL17} separate the decision variables into several subpopulations after performing an interdependence analysis, but using a fixed number of processors.}
 
@@
 researchers. For example, some authors focus on the solution space
-modeling the PF by dividing it into different clusters, allowing an
+modeling the PF by dividing it in different clusters, allowing an
 easily parallelizable {\em divide and conquer} approach
 \citep{cheng2015adaptive}. 
-Even other types of metaheuristics, 
+\textcolor{blue}{Even other types of metaheuristics, 
 such as the Multi-Objective Ant Colony Optimization (MOACO) \cite{Mora13paretobased}
@@
 can rely on island models to divide the search space depending on 
-the node to achieve better results.
+the node to achieve better results. }
 
@@
 the aforementioned ideas to compare two different dMOEAs. The first
-one divided the chromosome into $P$ sections,  $P$ being the number of
+one divided the chromosome into $P$ sections, being $P$ the number of
 islands. Every island $p$ only performed the mutation and crossover in
@@
 $p_{th+1}$ sections of each chromosome, besides the $p_{th}$
-part. During the same amount of time, both methods obtained better
+part. During the same amount of time both methods obtained better
 results than a baseline algorithm that dealt with the whole chromosome
@@
 cluster. 
-Therefore, at the same time, we are proposing a new method to divide the individual search space according to the number of evolved subpopulations, and also validating the previous approach.
+\textcolor{blue}{Therefore, at the same time, we are proposing a new method to divide the individual search space according to the number of evolved subpopulations, and also validating the previous approach.}
 
@@
 \subsection{Proposed methods}
-In this paper we analyze several SLA algorithms we have
+In this paper we analyse several SLA algorithms we have
 implemented by using a parallel multi-objective baseline algorithm
-as a basis for comparisons. Our proposed methods, using different overlapping schemes, 
+as a basis for comparisons. Our proposed methods, using different overlapping schemes, %methods or method?
+                                %Which methods? - JJ Fergu: clarifying
 are based on NSGA-II, as almost all the previous works discussed
@@
 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}.
+% This is SoA stuff - JJ FERGU: Yes, I added it here againg because a reviewer wasn't very attentive
 Therefore, we have used a basic distributed NSGA-II algorithm without
@@
 crossed and mutated in the same way, depending on the island
-identifier (from 1 to $P$). Note that, unlike the other works such as the ones
-described by Talbi et al. \citep{Talbi08Parallel}, all the islands deal
+identifier (from 1 to $P$). \textcolor{blue}{Note that, unlike the other works such as the ones
+described by Talbi et al. \citep{Talbi08Parallel}}, all the islands deal
 with complete chromosomes for fitness calculation, so our approach can
-deal with decomposable and no decomposable problems.
+deal with decomposable and no decomposable problems. %Don't understand what you say
+                                %here. What you are saying is that our
+                                %approach can't deal with decomposable
+                                %problems, actually. - JJ FERGU: you are right, fixed
 
@@
 \includegraphics[width=12cm]{islandDisjoint.jpg}
-\caption{SLA with disjoint islands (D): every island $p$ only modifies the $p_{th}$ components (in grey) of the individuals using genetic operators (crossover and mutation).
+\caption{SLA with disjoint islands (D): every island $p$ only modifies the $p_{th}$ components (in grey) of the individuals \textcolor{blue}{using genetic operators (crossover and mutation).
 Also, every island evaluates its own individuals using the complete chromosome.
-After a given number of generations, it cooperates with the other islands through migration.}
+After a given number of generations it cooperates with the other islands through migration.}}
 \label{fig:disjoint}
@@
 \caption{SLA with overlapping islands (O): every island $p$ modifies the  $p+1$,
-  $p_{th}$ and $p-1$  components (in grey) of the individuals using genetic operators (crossover and mutation).
+  $p_{th}$ and $p-1$  components (in grey) of the individuals \textcolor{blue}{using genetic operators (crossover and mutation).
 Also, every island evaluates its own individuals using the complete chromosome.
-After a given number of generations, it cooperates with the other islands through migration.}
+After a given number of generations it cooperates with the other islands through migration.}}
   \label{fig:overlapping}
@@
 
-\subsubsection{Automatic SLA with overlapping islands (A)} 
+\subsubsection{\textcolor{blue}{Automatic} SLA with overlapping islands (A)} 
 As in the previous method, the sections to address by the operators are overlapped, but
@@
 being $c$ a value depending on the number of islands.
-
+% That's not adaptive. It's simply variable - JJ FERGU: it depends on the number of islands. What term do you suggest?
+% FERGU: changed to Automatic
 As a first
@@
 work, the overlapped method ($c=1$) obtained better results when the
-number of islands was bigger than 8. On the contrary, when the number of
-islands is small, no overlapping is necessary. So, we have used this
+number of islands were bigger than 8. On the contrary, when the number of
+islands is small, no overlapping is necessary. \textcolor{blue}{So, we have used this
 knowledge to propose the formula $c=round(0.2*P-1)/2$ to calculate the
-extra sections to overlap. Therefore, when $P=8$ then $c=0$
+extra sections to overlap}. Therefore, when $P=8$ then $c=0$
 (equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so
 on.
-Dividing individuals by blocks of equal size, instead of a percentage, allow the future integration of our method with other recombination mechanisms, such as the ones presented in \cite{Dorronsoro13superlinear} or \cite{Kimovski15Parallel}.
-Also, as mentioned, this is only a possible formula to reach above-described behaviour for $c$, and future work will study new methods or alternative formulas to determine it, for example using Taguchi Method \cite{Keratmatpour2018Taguchi}.
+\textcolor{blue}{Dividing individuals by blocks of equal size, instead a percentage, allow the future integration of our method with other recombination mechanisms, such as the ones presented in \cite{Dorronsoro13superlinear} or \cite{Kimovski15Parallel}.
+Also, as mentioned, this is only a possible formula to reach above described behaviour for $c$, and future work will study new methods or alternative formulas to determine it, for example using Taguchi Method \cite{Keratmatpour2018Taguchi}.
 Figure \ref{fig:adaptive} explains the $A$ method, assuming that $c=2$, for example.
+}
 
@@
 \includegraphics[width=12cm]{islandAdaptive.jpg}
-\caption{Automatic SLA with overlapping islands (A): every island $p$ modifies the  $p+c$,
-  $p_{th}$ and $p-c$  components (in grey) of the individuals using genetic operators (crossover and mutation).
+\caption{\textcolor{blue}{Automatic} SLA with overlapping islands (A): every island $p$ modifies the  $p+c$,
+  $p_{th}$ and $p-c$  components (in grey) of the individuals \textcolor{blue}{using genetic operators (crossover and mutation).
 Also, every island evaluates its own individuals using the complete chromosome.
 After a given number of generations it cooperates with the other islands through migration.} $c$ is calculated depending on the number of islands.
-In this case, $c=2$.
+In this case, $c=2$.}
   \label{fig:adaptive}
@@
 
-This subsection describes the quality indicators used and the experimental setup. The chosen quality indicators are:
+This subsection describes the quality indicators used and the experimental setup. The chosen quality indicators, are:
 
@@
 %Pablo: theoretical?
-\item Spread (S): Measures the spread between solutions, taking into account the Euclidean distance between consecutive solutions.
-As in previous metric, the lower the value, the better, as it implies solutions distributed along all the PF.
+\item Spread (S): Measures the spread between solutions, taking into account the \textcolor{blue}{Euclidean} distance between consecutive solutions.
+As in previous metric, the lower value, the better, as it implies solutions distributed along all the PF.
 \end{itemize}
@@
 \includegraphics[width=6cm]{hypervolume.jpg}
-\caption{Hypervolume calculation. Areas from Pareto Front solutions (black points) to a reference point (white point) are used to calculate the value of the hypervolume (all the gray area)}.
+\caption{Hypervolume calculation.
+\textcolor{blue}{Areas from Pareto Front solutions (black points) to a reference point (white point) are used to calculate the value of the hypervolume (all the gray area)}.}
 \label{fig:hypervolume}
@@
 We have chosen those metrics not only because they have been used
-extensively, especially in some of the papers presented in Section \ref{sec:soa}
+extensively, especially in some of the papers presented in Section 2
+% Still section 2? Please create a reference and use it - JJ
 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous},
@@
 maximum number of islands has also been  used in a previous work in the
-literature \cite{Martens13asynchronous}. The chosen crossover and mutation, SBX and polynomial, have also been  used previously by other
+literature \cite{Martens13asynchronous}. The crossover and mutation
+chosen, SBX and polynomial, have also been  used previously by other
 authors in \cite{Durillo08masterslave,CaoZLL17}.  % SBX is first mentioned
@@
 benchmark includes several functions, with different features that are
-representative of real-world optimization problems. Mathematical
+representative of real world optimization problems. Mathematical
 formulation of each function is available in \citep{zdt2000a}.
 
-The global population size is set to 1024.
+\textcolor{blue}{The global population size is set to 1024.
 We have decided to use that value for two reasons: the first is that it is large enough to have 8 individuals per island by dividing that number when using 128 islands and small enough to have 128 individuals when using 8 islands.
 This is the minimum and maximum population size per island used by M{\"a}rtens et al.
-in his work \cite{Martens13asynchronous}.
+in his work \cite{Martens13asynchronous}.}
 
@@
 According to Alba and Luque \cite{EVALUATIONPARALLEL}, other stop criteria such as the number of evaluations required to attain a solution, may be misleading depending on the studied scenario.
-In our case, we have used time instead of the number of evaluations firstly
+In our case we have used time instead of the number of evaluations firstly
 because our hypothesis argues that the time saved in crossover and
@@
 operations and migrations can be achieved. Also, we are using
-different numbers of islands (with different sub-population sizes) and that
+different number of islands (with different sub-population sizes) and that
 could lead to different execution times, so it would be difficult to
@@
 The number of generations between migrations has been set to 5,
-as
+\textcolor{blue}{as
 reported by \cite{Deb03distributed,Martens13asynchronous}. In general
@@
 case, the mixing is essential for the algorithm to spread the result
-to all parts of the chromosome. So, while we tend to agree with
-M{\"a}rtens on the small influence of this value on the result, we also
+to all parts of the chromosome, so while we tend to agree with
+Martens on the small influence of this value on the result, we also
 think that making this value much bigger in our case would have a
 negative impact. However, a precise fine-tuning of this value is left
-as future work, as the main focus of this paper was to show the
-general concept, and not tune the values for maximum performance.
-
-This migration
+as future work, as the main focus of this paper was to prove the
+general concept, and not tune the values for a maximum performance}.
+
+\textcolor{blue}{This migration
   is performed asynchronously, as it has the advantage of being a
@@
   to compose solutions obtained by different islands, as occurs other
-  works \cite{Dorronsoro13superlinear}.The main parameters studied in the proposed system are limited to the number of islands and the size of the problem.
-This decision has been motivated because all previous works described in the state of the art also limit their experimental setting to the same parameters \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}.
-Although all the parameters indicated above have an influence on the general result of the MOEA, their general effect is well understood and, although there will be an interplay between them and the number of islands and problem size, this is left mainly as future work.
-
-\begin{table*}[htb]
+  works \cite{Dorronsoro13superlinear}.}
+
+ The whole parameter set is summarized in Table \ref{tab:parameters}. 
+ \textcolor{blue}{The main parameters in the proposed system were the number of islands and the size
+   of the problem, as pointed out by other authors 
+   \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}. This is why those have been the focus of this particular
+   article. Although all the parameters indicated above have an
+   influence on the general result of the MOEA, their general effect
+   is well understood and, although there will be an interplay between
+ them and the number of islands and problem size, this is left mainly
+ as future work.}
+
+\begin{table*}
 \begin{center}
@@
 The ECJ framework \citep{ECJ} has been used to run the
-experiments, including its own random number generation implementation.  The specific modifications to deal with the proposed approaches have been developed as new modules for
-ECJ, and their source code can be downloaded from our GitHub repository under a
+experiments, including its own random number generation implementation.  \textcolor{blue}{The specific modifications to deal with the proposed approaches have been developed as new modules for
+ECJ}, and their source code can be downloaded from our GitHub repository under a
 LGPL V3 License
-\footnote{\url{https://github.com/hpmoon/hpmoon-islands}}. The quality metrics (HV, Spread and IGD) have been calculated using the jMetal \cite{Durillo11Jmetal} library.
+\footnote{\url{https://github.com/hpmoon/hpmoon-islands}}. \textcolor{blue}{The quality metrics (HV, Spread and IGD) have been calculated using the jMetal \cite{Durillo11Jmetal} library.}
 
@@
 @2.27GHz processors, 16 GB RAM, Broadcom NetXtreme II BCM5716 1000Base-T (C0) PCI Express network cards, CentOS 6.8 and Java Version 1.8.0\_80.
-Islands are allocated to nodes in a round-robin way.
-That means that, for example, running with 8 islands requires 8 different nodes, instead of using several cores of a single node.
+\textcolor{blue}{Islands are allocated to nodes in a round-robin way.
+That means that, for example, running with 8 islands requires 8 different nodes, instead of using several cores of a single node.}
 
@@
 Different metrics, previously explained, have been used
-to calculate the quality of the obtained PFs in every configuration. As HV requires a reference point to be
+to calculate the quality of the obtained PFs in each configuration. \textcolor{blue}{As HV require a reference point to be
 calculated (see Figure \ref{fig:hypervolume}), we have chosen the value (1,9) as none of the existing solutions on all fronts obtained during all executions are dominated by it.
@@
 HV is then
-normalized with respect to that point.
-Also, the optimal reference PF distribution used to calculate the IGD and Spread metrics \cite{Durillo11Jmetal} has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.} .
+normalized respecting to that point.
+Also, the optimal reference PF distribution used to calculate the IGD and Spread metrics \cite{Durillo11Jmetal} has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.} }.
 A Kruskal-Wallis significance
@@
 configurations, as the Kolmogorov-Smirnov test detected non-normal
-distributions.
-%
+distributions. The average results for each configuration are shown in
+Table \ref{tab:results512} (for 512 dimensions) and Table
+\ref{tab:results2048} (for 2048). As previously explained, when $P=8$
+the results of A are equivalent to the obtained by D (because
+$c=0$), and when $P=16$ they are equivalent to O ($c=1$).
+We refer this equivalence with the word {\em Equiv-} in tables.
+For example, Equiv-D in an HV cell  means that the HV of A is the same than the value in D column, because the behaviour of this configuration is the same than executing D.
+
 \begin{table*}
@@
 }
-\caption{Average quality metrics obtained after 30 runs per
-  configuration, for the 4 methods compared: baseline (B), disjoint
-  (D), overlapped (O) and automatically overlapped
-  (A), % No sería mejor "automatically overlapped" or "automatic
-       % overlap"? This does not sound good - JJ FERGU: Done
-  using a chromosome length of 512 dimensions. Acronyms next to values
-  indicate that there is not significant difference with respect to
-  that method for that value. Best values are marked in
-  bold. Equiv-$X$ implies that value is the same as executing $X$,
-  since both configurations would be the same.}  
+\caption{Average quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 512 dimensions.
+Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
+Best values are marked in bold.
+Equiv-$X$ implies that value is the same as executing $X$, since both configurations would be the same.}
 \label{tab:results512}
 \end{table*}
-
-The average results for each configuration are shown in
-Table \ref{tab:results512} (for 512 dimensions) and Table
-\ref{tab:results2048} (for 2048). As previously explained, when $P=8$
-the results of A are equivalent to the obtained by D (because
-$c=0$), and when $P=16$ they are equivalent to O ($c=1$).
-We refer this equivalence with the word {\em Equiv-} in tables.
-For example, Equiv-D in an HV cell  means that the HV of A is the same than the value in D column, because the behaviour of this configuration is the same than executing D.
 
@@
 }
-\caption{Average quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and automatically overlapped (A), using a chromosome length of 2048 dimensions.
+\caption{Average quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 2048 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 
-%DESCRIPTION OF THE RESULTS
-Results show that there is a difference in performance when using 512 or 2048 dimensions.
-Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than those obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply these methods.
-A contradiction arises with respect to the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths.
-This can be explained because the added migration latency between nodes of the cluster requires more time than the time saved during the crossover and migration.
-This was not a problem in the mono-processor version, where the individuals shared the same memory space.
-
-However, with 2048 dimensions, results show that dividing the chromosome produces an improvement in all the quality indicators using the automatic ($A$) version (Table \ref{tab:results2048}), even overcoming the overlapping ($O$) and disjoint ($D$) methods.
-Therefore, there exists some kind of limit point in chromosome length where one method will be preferable to another, besides depending on the number of islands and population size.
-
-\begin{table*}[h!tb]
+\begin{table*}
 \centering
@@
 }
-\caption{Average number of generations and  solutions per front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and automatically overlapped (A), using a chromosome length of 512 dimensions.
+\caption{Average number of generations and average number of solutions of the front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 512 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 \end{table*}
-%
-\begin{table*}[h!tb]
+
+\begin{table*}
 \centering
@@
 }
-\caption{Average number of generations and solutions per front after 30 runs per configuration, for methods baseline (B), disjoint (D), overlapped (O) and automatically overlapped (A), using a chromosome length of 2048 dimensions.
+\caption{Average number of generations and average number of solutions per front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 2048 dimensions.
 Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
@@
 \end{table*}
-%
+
+%DESCRIPTION OF THE RESULTS
+Results show that there is a difference in performance when using 512 or 2048 dimensions.
+Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than the obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply these methods.
+A contradiction arises with respect to the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths.
+This can be explained because the added migration latency between nodes of the cluster requires more time than the time saved during the crossover and migration.
+This was not a problem in the mono-processor version, where the individuals shared the same memory space.
+
+However, with 2048 dimensions, results show that dividing the chromosome produces an improvement in all the quality indicators using the automatic ($A$) version (Table \ref{tab:results2048}), even overcoming the overlapping ($O$) and disjoint ($D$) methods.
+Therefore, there exist some kind of limit point in chromosome length where one method will be preferable to another, besides depending on the number of islands and population size.
+
+%ZDT1
+\begin{figure}
+\centering
+\includegraphics[width=12cm]{plot_zdt1_512.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent to running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt1_512}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=12cm]{plot_zdt1_2048.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent to running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt1_2048}
+\end{figure}
+
+%ZDT2
+\begin{figure}
+\centering
+\includegraphics[width=12cm]{plot_zdt2_512.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent to running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt2_512}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=12cm]{plot_zdt2_2048.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent to running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt2_2048}
+\end{figure}
+
+%ZDT3
+\begin{figure}
+\centering
+\includegraphics[width=12cm]{plot_zdt3_512.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent to running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt3_512}
+% I really have no idea what this is representing. Maybe plotting the
+% real Pareto front would help. I wouldn't know if this wiggle lines
+% are better or worse than whatever - JJ
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=12cm]{plot_zdt3_2048.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the
+    ZDT3 problem with a chromosome size ($L$) of 2048 for each
+    combination of number of islands ($P$) and method: baseline ($B$),
+    disjoint ($D$), overlapped ($O$) and automatic overlapped
+    ($A$). Results for 8 and 16 islands of $A$ are equivalent to
+    running $D$ and $O$ respectively. }}
+% It would be interesting to comment something about what is the key
+% thing here and what's good about it. Without an a priori idea, I
+% wouldn't know which one looks the best - JJ
+\label{fig:plot_zdt3_2048}
+\end{figure}
+
+%ZDT6
+\begin{figure}
+\centering
+\includegraphics[width=12cm]{plot_zdt6_512.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt6_512}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=12cm]{plot_zdt6_2048.png}
+\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
+Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
+}}
+\label{fig:plot_zdt6_2048}
+\end{figure}
+
 %EXPLANATION OF THE RESULTS
@@
 of each front and the average number of generations (Table
-\ref{tab:sols512} and Table \ref{tab:sols2048}).
-
-With both chromosome
+\ref{tab:sols512} and Table \ref{tab:sols2048}). With both chromosome
 lengths, increasing the number of islands implies more generations
-with all the methods (logically, as there are fewer individuals in each
+with all the methods (logically, as there are less individuals in each
 island). But also, the SLA methods
@@
 island is unaware of the other islands PFs, and they are trying to
-optimize their solutions independently.
-
-With respect to the average
+optimize their solutions independently. With respect to the average
 number of solutions per front, there is a clear difference 
- with the baseline with $L=512$, where this value is in most
-cases, less than a half. The number of non-dominated solutions
+ with the baseline with $L=512$, where this value is in the most
+of the cases, less than a half. The number of non-dominated solutions
 also implies a better Spread indicator, where the baseline 
@@
 
+ %%%%%% FERGU: WARNING, THIS SECTION IS STILL SHIT
+ % By now, maybe it should not be (or you should delete this
+ % comment) - JJ
 %ZDT1 
-\begin{figure}[h!tb]
-\centering
-\includegraphics[width=12cm]{plot_zdt1_512.png}
-\caption{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}
-\label{fig:plot_zdt1_512}
-\end{figure}
-%
-\begin{figure}[h!tb]
-\centering
-\includegraphics[width=12cm]{plot_zdt1_2048.png}
-\caption{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}
-\label{fig:plot_zdt1_2048}
-\end{figure}
-%
+\textcolor{blue}{Figures \ref{fig:plot_zdt1_512} to
+  \ref{fig:plot_zdt6_2048}, show the final PFs of one arbitrary sample
+  run of each combination. % Is it representative? Would it vary much?
+                           % - JJ
+  These figures allow to visualize the effect of the different
+  chromosome sizes and number of islands in each different
+  benchmark. The first one, ZDT1, has a convex Pareto-optimal
+  front. Comparing results from $L=512$ (Figure
+  \ref{fig:plot_zdt1_512}) and $L=2048$ (Figure
+  \ref{fig:plot_zdt1_2048}) it is apparent that the quality of the
+  generated PFs depends on the chromosome size. Specifically, with
+  $L=512$ it can be seen that the PFs quality decreases in Spread and
+  HV with all configurations, but the SLA methods behave worse than
+  $B$, as it also was shown on average in Table
+  \ref{tab:results512}. % Are we supposed to appreciate spread and HV
+                        % by looking at those graphs? - JJ
+  Nevertheless, if we focus on the plots obtained with $L=2048$
+  (Figure \ref{fig:plot_zdt1_2048}) this difference is less clear. It
+  can be seen in Figure \ref{fig:plot_zdt1_2048} that solutions
+  obtained by the SLA methods are more dispersed than the baseline as
+  $P$ grows. However, with $A$, the area covered by the PF is still
+  larger.} % than what? - JJ
+
 %ZDT2
-\begin{figure}[h!tb]
-\centering
-\includegraphics[width=12cm]{plot_zdt2_512.png}
-\caption{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}
-\label{fig:plot_zdt2_512}
-\end{figure}
-%
-\begin{figure}[h!tb]
-\centering
-\includegraphics[width=12cm]{plot_zdt2_2048.png}
-\caption{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}
-\label{fig:plot_zdt2_2048}
-\end{figure}
-%
+\textcolor{blue}{ZDT2 has a non-convex Pareto front. From Figures
+  \ref{fig:plot_zdt2_512} and \ref{fig:plot_zdt2_2048} is clear
+  that, % not to me - JJ
+  as in the previous problem ZDT1, there is a decrease of quality for
+  all configurations as the size of $P$ increases.  Nevertheless, for
+  this benchmark, there is not a clear decrease in the PF quality when
+  $L$ goes from 512 to 2048.}
+
 %ZDT3
-\begin{figure}[h!tb]
-\centering
-\includegraphics[width=12cm]{plot_zdt3_512.png}
-\caption{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}
-\label{fig:plot_zdt3_512}
-\end{figure}
-%
-\begin{figure}[h!tb]
-\centering
-\includegraphics[width=12cm]{plot_zdt3_2048.png}
-\caption{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}
-\label{fig:plot_zdt3_2048}
-\end{figure}
-%
-%
-%
-%ZDT6
-\begin{figure}[h!tb]
-\centering
-\includegraphics[width=12cm]{plot_zdt6_512.png}
-\caption{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}
-\label{fig:plot_zdt6_512}
-\end{figure}
-%
-\begin{figure}[h!tb]
-\centering
-\includegraphics[width=12cm]{plot_zdt6_2048.png}
-\caption{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$).
-Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively.
-}
-\label{fig:plot_zdt6_2048}
-\end{figure}
-
-%%%%%%FERGU: WARNING, THIS SECTION IS STILL SHIT
-%ZDT1 
-After establishing the performance of the new method and in order to
-have some insight on how they work, the effect of the different chromosome sizes and number of
-islands can be checked.
-Plotting the solution sets allows to observe its quality, distribution and shape, specially if they are limited to 2 or 3 objectives, as in this paper \cite{Li17read}.
-Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048} show the
-final PFs of one arbitrary sample run of each combination;. The first
-one, ZDT1, has a convex Pareto-optimal front. Comparing results from
-$L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=2048$ (Figure
-\ref{fig:plot_zdt1_2048}) it is apparent that the quality of the
-generated PFs depends on the chromosome size. Specifically, all
-configurations  with
-$L=512$  seem to have a worse Spread and HV, on the other hand, the
-SLA methods behave worse than $B$, as it was also shown on average in
-Table \ref{tab:results512}. Nevertheless, if we focus on the plots
-obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this
-difference is less clear. Figure \ref{fig:plot_zdt1_2048} shows that
-solutions obtained by the SLA methods show higher dispersion than the
-baseline as $P$ grows. However, with $A$, the area covered by the PF
-is still larger.
-
-%ZDT2
-ZDT2 has a non-convex Pareto front. From Figures
-\ref{fig:plot_zdt2_512} and \ref{fig:plot_zdt2_2048} it is clear that, as in the previous problem ZDT1, there is a decrease of quality for all configurations as the size of $P$ increases.
-Nevertheless, for this benchmark, there is not a clear decrease in the PF quality when $L$ goes from 512 to 2048.
-
-%ZDT3
-ZDT3 Pareto-optimal front is formed by non-contiguous convex parts, and plots for both chromosome sizes (Figures \ref{fig:plot_zdt3_512} and \ref{fig:plot_zdt3_2048}) show solutions gathered in similar regions in all configurations.
-However, with $L=512$, the rightmost part of the obtained non-dominated solutions is not obtained in the $A$ alternative with $P=8$  and $P=16$ (being equivalent to alternatives $O$ and $D$).
+\textcolor{blue}{ZDT3 Pareto-optimal front is formed by non-contiguous convex parts, and plots for both chromosome sizes (Figures \ref{fig:plot_zdt3_512} and \ref{fig:plot_zdt3_2048}) show solutions gathered in similar regions in all configurations.
+However, with $L=512$, the rightmost part of the obtaninde non-dominated solutions is not obtained in the $A$ alternative with $P=8$  and $P=16$ (being equivalent to alternatives $O$ and $D$).
 This explains why with this chromosome length, the SLA methods do not improve the results obtained by $B$.
 This problem does not appear when $L=2048$.
-Although the differences in the Spread metric are not significant for the different alternatives for this benchmark, (as shown in Table \ref{tab:results2048}), the HV and IGD metrics are the ones that can be used to show the effectiveness of our approach in this type of problem with non-continuous PFs.
-
-In ZDT6, the Pareto-optimal solutions are not only non-uniformly distributed along the PF, but their density also increases as we move further away from it.
+Although the differences in the Spread metric are not significant for the different alternatives for this benchmark, (as shown in Table \ref{tab:results2048}), the HV and IGD metrics are the ones that can be used to show the effectiveness of our approach in this type of problem with non-continuous PFs.}
+
+\textcolor{blue}{In ZDT6, the Pareto-optimal solutions are not only non-uniformly distributed along the PF, but their density also increases as we move further away from it.
 That is the reason why some PFs obtained have an extremely low number of solutions in some configurations, and also, they are aggregated toward the areas with more density.
@@
 Indeed, there is not a significant difference between methods, with an exception: Spread using $A$ with $L=512$ is significantly worse.
-As in previous approaches, it is visually clear that increasing the number of islands, and therefore, reducing the number of individuals per island, implies a decrease the in quality of the HV.
-
-Finally, as it was already observed in \citep{Garcia16hpmoon}, all the performance indicators show worse values as the number of islands increases, and so the  sizes of the subpopulations are smaller.
+As in previous approaches it is visually clear that increasing the number of islands, and therefore, reducing the number of individuals per island, imply a decrease in quality of the HV.}
+
+\textcolor{blue}{Finally, as it was already observed in \citep{Garcia16hpmoon}, all the performance indicators show worse values as the number of islands increases, and so the  sizes of the subpopulations are smaller.
 This is consistent with the claim by Dorronsoro et al.
-\citep{Dorronsoro13superlinear}, who found that cooperative co-evolutionary MOEAs work better on bigger populations (more than 100 individuals).
+\citep{Dorronsoro13superlinear}, who found that cooperative co-evolutionary MOEAs work better on bigger populations (more than 100 individuals).}
 
@@
 Obtained results also show that when increasing the number of islands, the
-automatic overlapping method ($A$) significantly improves the results with
-respect to the disjoint and overlapped methods. However, this is only
+automatic overlapping method ($A$) % $A$ or SLA? - JJ
+significantly improves the results with
+respect to the disjoint and overlapped methods. %Always? Which cases?
+                                %Which sizes? Which measure? - JJ
+However, this is only
 apparent with larger chromosome sizes. Therefore, the length of the
 chromosome is also a key factor to take into account in automatic overlapping
-methods, and not only the number of islands. 
-%Studying this factor with more types of problems, and new configurations of population size and chromosome lengths could be addressed in the future. 
-Since our method divides the individuals into blocks of divisible size, aggregation methods after migration, such as the ones used in \cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be also tested.
-But as we are dealing with complete individuals in each island, the possibility of using a real number, such as 0.3 (30\% overlapping) instead an integer value opens future experimental setups.
+methods, and not only the number of islands. % This is the extent of
+                                % the conclusions. The referees have
+                                % said they should be
+                                % expanded. Conclusions should include
+                                % the reasons why this method obtains
+                                % better results. What is the
+                                % influence of adaptativity in the
+                                % result? It closes "gaps" in the
+                                % Pareto front? Does it work better
+                                % when there are no gaps? - JJ
+
+Studying this factor with
+more types of problems, and new configurations of population size and
+chromosome lengths could be addressed in the future.
+\textcolor{blue}{Since our method divides the individuals into blocks of divisible size, aggregation methods after migration, such as the ones used in \cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be also tested.
+But as we are dealing with complete individuals in each island, the possibility of using a real number, such as 0.3 (30\% overlapping) instead an integer value opens future experimental setups.}
 For example, comparing 
 different ways to calculate $c$ using linear, logarithmic or exponential functions
-depending on population size, number of islands, or other values, or using some statistical parameter setting method, such as Taguchi's \cite{Keratmatpour2018Taguchi}.
-
-Although the results obtained in this work are promising, it is clear that this method requires more future experiments, in addition to the automatic calculation of $c$.
-These new experiments should involve a more complete parameter study, including a sensitivity analysis, to validate our approach.
-Other benchmarks and real problems should be addressed in the future.
-These problems could involve dealing with more than two objectives, so polar coordinates should be used to visually understand the results \cite{Li17read}.
-Also, other MOEA algorithms available in the literature, such as SPEA or MOEA/D could also be compared.
-
-% Moreover, a diversity analysis of the individuals in each island during the algorithm run could be carried out to understand its influence on the results.
-
+depending \textcolor{blue}{on population size, number of islands, or other values, or using some statistical parameter setting method, such as Taguchi's \cite{Keratmatpour2018Taguchi}}.
+Moreover, a diversity analysis of the individuals
+in each island during the algorithm run could be carried out to understand its influence
+on the results.
 % 
@@
 
-Finally, more distributed implementations in several systems (such as a
+Also, more distributed implementations in several systems (such as a
 GPUs or heterogeneous clusters) with different amounts of
@@
 different methods, being the transmission time between islands a
-relevant issue to be addressed.
+relevant issue to be addressed. \textcolor{blue}{Other MOEA algorithms available in the literature, such as SPEA or MOEA/D could also be compared. Moreover, new benchmarks and real problems
+could be  used to validate this approach.}
 

### 2019-05-13 hpmoon-asoco.tex
Reflow and rephrases abstract. @fergunet check it out
Some corrections and reflow

--- 2019-05-07 hpmoon-asoco.tex
@@
 %%%NEW AND SHORTED
-Parallel island-model co-evolutionary algorithms are well-known methods, suitable for dealing with large multi-objective optimization problems.
-In these algorithms, each island modifies a fragment of the chromosome that encodes a possible solution to the problem.
-\textcolor{blue}{The objective of this paper is} to demonstrate that automatically setting the size of the overlapping fragments depending on the number of islands obtains better results than using the same size.
-\textcolor{blue}{This method has been compared} to other parallel evolutionary techniques considering a different number of islands, chromosome sizes and benchmarks.
-The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm in high-dimensional, un-decomposable, multi-objective problems.
-This opens a very promising line to automatically adapt the overlapping sizes in this kind of algorithms.
+Parallel island-model co-evolutionary algorithms are well-known
+methods, suitable for dealing with large multi-objective optimization
+problems. \textcolor{blue}{We propose a version of these algorithms where} each island modifies a fragment of the
+chromosome that encodes a possible solution to the
+problem. \textcolor{blue}{The objective of this paper is} to
+demonstrate that automatically setting the size of the overlapping
+fragments depending on the number of islands obtains better results
+than using the same size. \textcolor{blue}{This method has been
+  compared} to other parallel evolutionary techniques considering a
+different number of islands, chromosome sizes and benchmarks. The
+analysis of the obtained experimental results, by using different
+metrics, shows that our approach can provide statistically significant
+improvements with respect to the base algorithm in high-dimensional,
+un-decomposable, multi-objective problems. This opens a very promising
+line to automatically adapt the overlapping sizes in this kind of
+algorithms.
 
@@
 \begin{bluecolor}
-One of the methods that are most extensively used  to deal with high-dimensional, multi-objective optimization problems (MOPs) are distributed co-evolutionary algorithms \cite{Gong15models}.
-However, only decomposable problems could strictly be implemented in parallel this way.
-A new parallel island-model evolutionary algorithm approach \cite{Alba02Parallelism} is used here to deal with un-decomposable problems: instead of sharing parts of individuals, each island, hosted by a single processor, applies the variation operators to a specific subset of the whole individual.
-This avoids extra steps to recompose the complete individuals from other islands before evaluation.
+One of the methods that are most extensively used  to deal with
+high-dimensional, multi-objective optimization problems (MOPs) are
+distributed co-evolutionary algorithms \cite{Gong15models}. However,
+only decomposable problems could strictly be implemented in parallel
+this way. A new parallel island-model evolutionary algorithm approach
+\cite{Alba02Parallelism} is used here to deal with un-decomposable
+problems: instead of sharing parts of individuals, each island, hosted
+by a single processor, applies the variation operators to a specific
+subset of the whole individual. This avoids extra steps (and
+subsequent communication overhead) to recompose the complete
+individuals from other islands before evaluation. 
 \end{bluecolor}
@@
 %1. MOP ARE
-In MOPs, several
+In MOPs, several \textcolor{blue}{independent}
 objectives have to be simultaneously optimized

### 2019-05-13 hpmoon-asoco.tex
Please address the question in the last line @fergunet

@@
 exploration of the search space must be very efficient, trying to
-cover many possible exploration paths at the same time.
+cover \textcolor{blue}{all} possible exploration paths at the same time.
 
@@
 %3 ONE WAY IS TO USE MOEAS BECAUSE
-one of which are evolutionary algorithms (EAs)
+one of which \textcolor{blue}{is} evolutionary algorithms (EAs)
 \citep{DBLP:series/ncs/EibenS15}. EAs are bio-inspired meta-heuristics
@@
 evaluates each candidate solution, called \emph{individual}, assigning
-it a \emph{fitness} value that describes how good the individual is
+it a \emph{fitness} \textcolor{blue}{vector, in the case of MOPs} that describes how good the individual is
 \textcolor{blue}{solving} the target problem. New solutions are then generated by
@@
 EAs \textcolor{blue}{were} extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}.
-One of the best known and referenced MOEAs
+One of the best known and \textcolor{blue}{highly} referenced MOEAs
 \citep{Dorronsoro13superlinear} is the {\em 
@@
 approaches \citep{Luna15Survey} need to deal with the whole solution set, the PF.
- This implies to use different distribution
+ This implies \textcolor{blue}{using} different distribution
 and sharing mechanisms, as there exists a tradeoff between the speedup
@@
 \citep{Branke04Parallelizingcone}. % Is that the case with NSGA? - JJ
+% Please check the last question - JJ
 

### 2019-05-13 hpmoon-asoco.tex
Minor corrections

@@
 meaning that the
-MOEAs need to deal with large individuals and spend significant extra
-time for crossover, mutation and migration.
+MOEAs need to deal with large individuals \textcolor{blue}{representing those variables} and spend significant extra
+time \textcolor{blue}{applying the} crossover, mutation and migration \textcolor{blue}{operators}.
 Different authors have 

### 2019-05-13 hpmoon-asoco.tex
Some suggestions

@@
 time \textcolor{blue}{applying the} crossover, mutation and migration \textcolor{blue}{operators}.
+% If this is the only justification, it should have been assessed at the end. It would be better if it was qualified, in the sense that more exploration is needed or something like that - JJ
 Different authors have 
 proposed methods to divide the decision space (the chromosome) to
-improve the performance and solution quality. In this aspect, the
+improve the performance and solution quality. % Why should it improve quality? - JJ
+In this aspect, the
 co-evolution model is a dimension-distributed model where a 
@@
 co-evolutionary island model was used.  Although in both papers
-significant speedups were attained, only a low number of nodes were
+significant speedups were attained, only a \textcolor{blue}{small} number of nodes were
 employed (8). However, when the number of islands is increased, the division
@@
 This
-motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more \textcolor{blue}{extensive parameter evaluation}.
+motivate\textcolor{blue}{d} us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more \textcolor{blue}{extensive parameter evaluation}.
+%Again, "testing more stuff" is not a good motivation.
+You should try to address a specific research question that might have been raised in the previous paper - JJ
 Besides comparing previous methods in this new experimental setup, in this paper 

### 2019-05-13 hpmoon-asoco.tex
Minor changes and reflow

@@
 dimensional problem was used to compare these 
-alternatives. In \citep{Dorronsoro13superlinear}, a distributed
-co-evolutionary island model was used.  Although in both papers
-significant speedups were attained, only a \textcolor{blue}{small} number of nodes were
+alternatives\textcolor{blue}{; also, i}n \citep{Dorronsoro13superlinear}, a distributed
+co-evolutionary island model was used.  Although  both papers \textcolor{blue}{described}
+significant speedups, only a \textcolor{blue}{small} number of nodes were
 employed (8). However, when the number of islands is increased, the division
@@
 preliminary experimental setup, although it is worth mentioning \textcolor{blue}{that its name and acronym is established} in this paper for the first time.
-\textcolor{blue}{It was shown}
-that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
+\textcolor{blue}{In that paper, it was shown}
+that applying the variation operators only \textcolor{blue}{to} specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
 Moreover, instead of making every island focus on a disjoint subset of the
@@
 
-Results also show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distributing the decision variables: the higher the dimensionality and the overlapping, the greater the benefit of distribution in a large number of islands.
-This opens up a new challenge to be addressed in the future, by experimenting with new ways to calculate the overlapping sizes depending on different factors and parameters.
+Results also show that the relation between the number of islands
+(subpopulations) and the length of the chromosome (number of decision
+variables) is also a relevant factor to determine the most efficient
+alternative to distributing the decision variables: the higher the
+dimensionality and the overlapping, the greater the benefit of
+distribution in a large number of islands. This opens up a new
+challenge to be addressed in the future, by experimenting with new
+ways to calculate the overlapping sizes depending on different factors
+and parameters.
 

### 2019-05-13 hpmoon-asoco.tex
Adds clarification in the problem description section rev #4

@@
 
-This subsection describes the quality indicators used and the experimental setup. The chosen quality indicators are:
-
+% Some introduction. ... We will describe here the design of the
+% experiments bla bla bla--- JJ
+
+This subsection describes the \textcolor{blue}{measurements of
+  quality} used \textcolor{blue}{; these are}:
+
+% Justify this - JJ
 \begin{itemize}
@@
 
+% Move this to the top - JJ
 Those metrics \textcolor{blue}{have been chosen} not only because they have been used
@@
 representative of real-world optimization problems. Mathematical
-formulation of each function is available in \citep{zdt2000a}.
+formulation of each function is available in \citep{zdt2000a}. \textcolor{blue}{Please
+note that the ZDT problems are non-epistatic, so in principle our
+conclusions should be extensible only to multiobjective problems with
+the same nature.}
 

### 2019-05-13 hpmoon-asoco.tex
Taking care of epistasy from rev #4

@@
 
-Obtained results also show that when increasing the number of islands, the
+Obtained results also show that when the number of islands
+\textcolor{blue}{is increased}, the
 automatic overlapping method ($A$) significantly improves the results with
@@
 %Studying this factor with more types of problems, and new configurations of population size and chromosome lengths could be addressed in the future. 
-Since our method divides the individuals into blocks of divisible size, aggregation methods after migration, such as the ones used in \cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be also tested.
-But as complete individuals \textcolor{blue}{treated} in each island, the possibility of using a real number, such as 0.3 (30\% overlapping) instead an integer value opens future experimental setups.
+Since our method divides the individuals into blocks of divisible
+size, aggregation methods after migration, such as the ones used in
+\cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be
+also tested. But as complete individuals \textcolor{blue}{treated} in
+each island, the possibility of using a real number, such as 0.3 (30\%
+overlapping) instead an integer value opens future experimental
+setups. \textcolor{blue}{This should also take care of epistatic
+  interactions between chromosome sizes: although variation operators
+  operate on chromosome fragments, selection and fitness evaluation
+  operates on the whole chromosome; besides, there is migration
+  between islands, so the probability of reaching local minima due to
+  this fact is, in fact, going to be avoided.}
 For example, comparing 

### 2019-05-13 hpmoon-asoco.tex
Addresses more comments by reviewer #4

@@
 it happens with $L=512$. Therefore, more generations do not
-necessarily mean improve the solution of the global PF, but focusing on
+necessarily mean \textcolor{blue}{an improvement in} the solution of the global PF, but focusing on
 different elements of the chromosome. As previously stated, every
@@
 different ways to calculate $c$ using linear, logarithmic or exponential functions
-depending on population size, number of islands, or other values, or using some statistical parameter setting method, such as Taguchi's \cite{Keratmatpour2018Taguchi}.
-
-Although the results obtained in this work are promising, it is clear that this method requires more future experiments, in addition to the automatic calculation of $c$.
-These new experiments should involve a more complete parameter study, including a sensitivity analysis, to validate our approach.
-Other benchmarks and real problems should be addressed in the future.
-These problems could involve dealing with more than two objectives, so polar coordinates should be used to visually understand the results \cite{Li17read}.
-Also, other MOEA algorithms available in the literature, such as SPEA or MOEA/D could also be compared.
+depending on population size, number of islands, or other values, or
+using some statistical parameter setting method, such as Taguchi's
+\cite{Keratmatpour2018Taguchi}. \textcolor{blue}{However, taking into
+  account that the linear change tested in this paper in fact obtains
+  good results with a simple formula, it is our conclusion that
+  further complication would not be necessary.}
+
+Although the results obtained in this work are promising, it is clear
+that this method requires more future experiments. These new
+experiments should involve a more complete parameter study, including
+a sensitivity analysis, to validate our approach. Other benchmarks and
+real problems should be addressed in the future. These problems could
+involve dealing with more than two objectives, so polar coordinates
+should be used to visually understand the results
+\cite{Li17read}. Also, other MOEA algorithms available in the
+literature, such as SPEA or MOEA/D could also be compared.
 

### 2019-05-15 hpmoon-asoco.tex
Addressing @JJ comments

@@
 methods, suitable for dealing with large multi-objective optimization
-problems. \textcolor{blue}{We propose a version of these algorithms where} each island modifies a fragment of the
+problems. \textcolor{blue}{This paper proposes a version of these algorithms where} each island modifies a fragment of the
 chromosome that encodes a possible solution to the
@@
 % Maybe add a sentence explaining what problems are decomposable and which ones are not. - JJ
+% Pablo: ok, done in blue
 \begin{bluecolor}
@@
 distributed co-evolutionary algorithms \cite{Gong15models}. However,
-only decomposable problems could strictly be implemented in parallel
+only decomposable problems \textcolor{blue}{-that is, the ones whose  domain can be divided into subsets, calculate their solutions, and combine them to form the solution of the original problem-,} could strictly be implemented in parallel
 this way. A new parallel island-model evolutionary algorithm approach
 \cite{Alba02Parallelism} is used here to deal with un-decomposable
-problems: instead of sharing parts of individuals, each island, hosted
-by a single processor, applies the variation operators to a specific
-subset of the whole individual. This avoids extra steps (and
+problems: \textcolor{blue}{instead of allocating disjoint subsets of components to the islands hosted by the available processors, it applies the variation operators only to the components  of the subset allocated to a given population, while keeping the rest of the components of the whole individual unaltered.}.
+This avoids extra steps (and
 subsequent communication overhead) to recompose the complete
@@
 results to accurately identify the PF
-\citep{Branke04Parallelizingcone}. % Is that the case with NSGA? - JJ
-% Please check the last question - JJ
+\citep{Branke04Parallelizingcone}. \textcolor{blue}{This is also the case with the NSGA-II.} % Is that the case with NSGA? - JJ
+% Please check the last question - JJ Pablo: done
 
@@
 % Some introduction. ... We will describe here the design of the
-% experiments bla bla bla--- JJ
-
-This subsection describes the \textcolor{blue}{measurements of
-  quality} used \textcolor{blue}{; these are}:
-
-% Justify this - JJ
+% experiments bla bla bla--- JJ Pablo: Done
+\textcolor{blue}{In this subsection, the design of the experiments will be described, starting with the measurements of quality, the benchmark problems, the different configurations compared, and the specific parameter set used.}
+
+% Move this to the top - JJ Pablo: Done
+\textcolor{blue}{Three different quality metrics have been used in this paper. These metrics have been chosen} not only because they have been used
+extensively, especially in some of the papers presented in Section \ref{sec:soa}
+\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous},
+but also because they cover different quality criteria. Mathematical
+formulation of these metrics can be found in
+\cite{Dorronsoro13superlinear}.
+
 \begin{itemize}
@@
 In this metric, the lower the better.
-%Pablo: theoretical?
 \item Spread (S): Measures the spread between solutions, taking into account the Euclidean distance between consecutive solutions.
@@
 \end{figure}
-
-% Move this to the top - JJ
-Those metrics \textcolor{blue}{have been chosen} not only because they have been used
-extensively, especially in some of the papers presented in Section \ref{sec:soa}
-\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous},
-but also because they cover different quality criteria. Mathematical
-formulation of these metrics can be found in
-\cite{Dorronsoro13superlinear}.
 

### 2019-05-15 hpmoon-asoco.tex
More addressings to @JJ comments using Julio's comments

@@
 distributed co-evolutionary algorithms \cite{Gong15models}. However,
-only decomposable problems \textcolor{blue}{-that is, the ones whose  domain can be divided into subsets, calculate their solutions, and combine them to form the solution of the original problem-,} could strictly be implemented in parallel
+only decomposable problems \textcolor{blue}{--that is, the ones whose  domain can be divided into subsets, calculate their partial solutions, and combine them to form the solution of the original problem--,} could strictly be implemented in parallel
 this way. A new parallel island-model evolutionary algorithm approach
@@
 proposed methods to divide the decision space (the chromosome) to
-improve the performance and solution quality. % Why should it improve quality? - JJ
+improve the performance and solution quality. % Why should it improve quality? - JJ Pablo: look at the 2 new paragraphs sent by Julio below (between \begin{bluecolor})
 In this aspect, the
@@
 high-dimensional problem is divided into lower dimensional ones
-\citep{Gong15models,Tonda12cooperative}, and evolved separately. One
-example of the application of this technique was described in
+\citep{Gong15models,Tonda12cooperative}, and evolved separately.
+\textcolor{blue}{To evolve the individuals of a subpopulation, the processor where it has been allocated can operate according to two main alternatives.} One
+example of the application of the \textcolor{blue}{first alternative} was described in
 \citep{Kimovski15Parallel}. The method presented in that work involves
 different workers that evolve sub-populations created and recombined
-by a master process, which performs different recombination
-alternatives from the parts returned by worker processes. A high
+by a master process, which performs \textcolor{blue}{different alternatives for the recombinattion/cooperation of the subpopulations returned by worker processes}. A high
 dimensional problem was used to compare these 
@@
 amount of time.
+\textcolor{blue}{Moreover, in this first alternative, each processor only works with the variables of the individuals in its population.
+Thus, only whenever the cost function is decomposable in such a way that the variables allocated to different processors are not interdependent, the evaluation of the fitness of an individual in the population can be done by composing the cost evaluated separately by each processor from the values of the variables allocated to it.
+Otherwise, it has to be determined after composing the whole solution from the components allocated to each processor the components of the solutions in the subpopulations.}
 
@@
 
-A similar approach used to solve this kind of problems is the {\em
-  SeLective operator Application} (SLA) presented in this paper. In this case, each island
+Another approach used to solve this kind of problems is the {\em
+  SeLective operator Application} (SLA), presented in this paper, \textcolor{blue}{can be considered as the second alternative to evolve the individuals of a subpopulation}. In this case, each island
 deals with the whole chromosome, but only modifies a fragment of it in
@@
 deal with un-decomposable problems.
+
+\begin{bluecolor}
+ Thus, in this second alternative a suitable cooperation function must be defined to select the individuals for the new set of subpopulations.
+Nevertheless, the right approach would be to define an approach that makes it possible to build the right cooperation procedure to improve the convergence and convergence rate of the parallel cooperative co-evolutionary procedure with respect to the base sequential optimization procedure.
+
+This way, the open issues are related with the searching for strategies that mathematically determine convergence rates according to the cost function and associate sampling distributions in the sequential and parallel co-evolutionary procedures including the effect of the communications providing not fully actualized components.
+\end{bluecolor}
 

### 2019-05-20 hpmoon-asoco.tex
More changes by julio

@@
 Thus, only whenever the cost function is decomposable in such a way that the variables allocated to different processors are not interdependent, the evaluation of the fitness of an individual in the population can be done by composing the cost evaluated separately by each processor from the values of the variables allocated to it.
-Otherwise, it has to be determined after composing the whole solution from the components allocated to each processor the components of the solutions in the subpopulations.}
+Otherwise, it has to be determined after composing the whole solution from the components allocated to each processor the components of the solutions in the subpopulations.
+In fact, different strategies to define the way to distribute the components into groups to be allocated to the available processors are required.
+They have been mainly defined according to three categories \cite{Jia19Coevo}: (1) static partitions of variables into groups; (2) random dynamic grouping that changes the variables among groups along the optimization process; and (3) learning-based dynamic grouping to distribute the components by applying techniques to detect the interdependence among variables along the process.
+}
 

### 2019-05-20 hpmoon-asoco.tex
More addressings to @JJ and adding Julio and Jesus comments

@@
 fragments depending on the number of islands obtains better results
-than using the same size. \textcolor{blue}{This method has been
+than using \textcolor{blue}{a fixed overlapping} size. \textcolor{blue}{This method has been
   compared} to other parallel evolutionary techniques considering a
@@
 distributed co-evolutionary algorithms \cite{Gong15models}. However,
-only decomposable problems \textcolor{blue}{--that is, the ones whose  domain can be divided into subsets, calculate their partial solutions, and combine them to form the solution of the original problem--,} could strictly be implemented in parallel
+only decomposable problems \textcolor{blue}{--that is, the ones whose  domain can be divided into subsets to calculate their partial solutions and combine them to form the solution of the original problem--,} could strictly be implemented in parallel
 this way. A new parallel island-model evolutionary algorithm approach
 \cite{Alba02Parallelism} is used here to deal with un-decomposable
-problems: \textcolor{blue}{instead of allocating disjoint subsets of components to the islands hosted by the available processors, it applies the variation operators only to the components  of the subset allocated to a given population, while keeping the rest of the components of the whole individual unaltered.}.
+problems: \textcolor{blue}{instead of allocating disjoint subsets of components to the islands hosted by the available processors, it applies the variation operators only to the components  of the subset allocated to a given population, while keeping the rest of the components of the whole individual unaltered}.
 This avoids extra steps (and
@@
 for all objectives. The objective of MOP algorithms is to find as many
-solutions equally distributed in the Pareto Front as possible. In order to do that the
+solutions equally distributed in the Pareto Front as possible. In order to do that\textcolor{blue}{,} the
 exploration of the search space must be very efficient, trying to
@@
 
-Usually an EA starts by generating \textcolor{blue}{a \emph{population}, that is, a set of random solutions}, following a user-defined description. Then, it
+Usually\textcolor{blue}{,} an EA starts by generating \textcolor{blue}{a \emph{population}, that is, a set of random solutions}, following a user-defined description. Then, it
 evaluates each candidate solution, called \emph{individual}, assigning
@@
 different workers that evolve sub-populations created and recombined
-by a master process, which performs \textcolor{blue}{different alternatives for the recombinattion/cooperation of the subpopulations returned by worker processes}. A high
+by a master process, which performs \textcolor{blue}{different alternatives for the recombination/cooperation of the subpopulations returned by worker processes}. A high
 dimensional problem was used to compare these 
@@
 employed (8). However, when the number of islands is increased, the division
-of each section of the chromosome becomes smaller, and the scalability
+of \textcolor{blue}{the portion of chromosome assigned to a given island} becomes smaller, and the scalability
 may be affected by obtaining lower quality solutions in the same
 amount of time.
-\textcolor{blue}{Moreover, in this first alternative, each processor only works with the variables of the individuals in its population.
+\textcolor{blue}{Moreover, in this first alternative, each processor only works with the variables allocated to it of the individuals in its population.
 Thus, only whenever the cost function is decomposable in such a way that the variables allocated to different processors are not interdependent, the evaluation of the fitness of an individual in the population can be done by composing the cost evaluated separately by each processor from the values of the variables allocated to it.
-Otherwise, it has to be determined after composing the whole solution from the components allocated to each processor the components of the solutions in the subpopulations.
+Otherwise, it has to be determined after composing the whole solution from the components allocated to each processor.
 In fact, different strategies to define the way to distribute the components into groups to be allocated to the available processors are required.
@@
 the crossover and mutation phase depending on the number of islands,
-using the whole chromosome for fitness calculation. This allows to
-deal with un-decomposable problems.
+using the whole chromosome for fitness calculation. This allows \textcolor{blue}{dealing} with un-decomposable problems.
 
 \begin{bluecolor}
- Thus, in this second alternative a suitable cooperation function must be defined to select the individuals for the new set of subpopulations.
-Nevertheless, the right approach would be to define an approach that makes it possible to build the right cooperation procedure to improve the convergence and convergence rate of the parallel cooperative co-evolutionary procedure with respect to the base sequential optimization procedure.
-
-This way, the open issues are related with the searching for strategies that mathematically determine convergence rates according to the cost function and associate sampling distributions in the sequential and parallel co-evolutionary procedures including the effect of the communications providing not fully actualized components.
+ Thus, in this second alternative, a suitable cooperation function must be defined to select the individuals for the new set of subpopulations.
+Nevertheless, the right approach would be to define a suitable procedure that implements an efficient cooperation strategy to improve the convergence and convergence rate of the parallel cooperative co-evolutionary procedure with respect to the base sequential optimization procedure.
+
+This way, the open issues are related to the search for strategies that mathematically determine convergence rates according to the cost function, and associate sampling distributions in the sequential and parallel co-evolutionary procedures including the effect of the communications providing not fully actualized components.
 \end{bluecolor}
@@
 You should try to address a specific research question that might have been raised in the previous paper - JJ
-Besides comparing previous methods in this new experimental setup, in this paper 
+Besides comparing previous methods in this new experimental setup,  
 a new method that automatically sets the size of the overlapped
-sections depending on the number of available islands \textcolor{blue}{is proposed}, comparing it with previous versions.
+sections depending on the number of available islands \textcolor{blue}{is proposed in this paper, and compared} with previous versions.
 
@@
 variables) is also a relevant factor to determine the most efficient
-alternative to distributing the decision variables: the higher the
+alternative to \textcolor{blue}{distribute} the decision variables: the higher the
 dimensionality and the overlapping, the greater the benefit of
@@
 The rest of the paper is organized as follows: after the State of the Art in distributed and co-evolutionary MOEAs, 
-the used methodology and the compared algorithms are described in Section \ref{sec:methodology}. 
+the \textcolor{blue}{proposed} methodology and the compared algorithms are described in Section \ref{sec:methodology}. 
 Then, the results of the experiments are presented (Section \ref{sec:results}), Finally, the conclusions and future work are discussed.
@@
 %This is an improvement over the previous? What is the relationship? FERGU: linked
-Other kind of approaches have also been explored.
+Other \textcolor{blue}{kinds} of approaches have also been explored.
 The work by Deb et al.
@@
 In that paper, the authors concluded that dividing the search space is a good idea, although achieving this is not trivial.
-The division of the search space has been explored by other researchers, for example, dividing the population into elite and search sub-populations \citep{Wang09parallel}, or separating it in processors by objective \citep{Xiao03specialized}.
+The division of the search space has been explored by other researchers, for example, dividing the population into elite and search sub-populations \citep{Wang09parallel}, or separating it \textcolor{blue}{into} processors by objective \citep{Xiao03specialized}.
 For example, in \cite{Zhang17DECAL}, a weighted function is used to decompose the objective function and every subpopulation is responsible to solve the problem defined by a weighted vector.
@@
 % Is this really cooperative co-evolution? - JJ FERGU: You mean the Dorronsoro one? The title says it
-Many real-world problems require high-dimensionality \cite{Zhang17DECAL,XU2018268}.
+Many real-world problems \textcolor{blue}{require} high-dimensional data \cite{Zhang17DECAL,XU2018268}.
 Addressing this kind of problems with cooperative co-evolution has
@@
 researchers. For example, some authors focus on the solution space
-modeling the PF by dividing it into different clusters, allowing an
+\textcolor{blue}{modelling} the PF by dividing it into different clusters, allowing an
 easily parallelizable {\em divide and conquer} approach
@@
 the aforementioned ideas \textcolor{blue}{were used} to compare two different dMOEAs. The first
-one divided the chromosome into $P$ sections,  $P$ being the number of
+one divided the chromosome into $P$ sections,  \textcolor{blue}{with} $P$ being the number of
 islands. Every island $p$ only performed the mutation and crossover in
@@
 results than a baseline algorithm that dealt with the whole chromosome
-in each island for crossover and mutation. \textcolor{blue}{It was} discovered that the
-performance using one or another method depends on the number of
-sections of the individuals and the number of islands used. This
+in each island for crossover and mutation. \textcolor{blue}{It was} discovered \textcolor{blue}{in that paper} that the
+performance using one or another method depends on \textcolor{blue}{both} the number of
+sections \textcolor{blue}{individual's section used by each island} and the number of islands. This
 motivated us to find a new automatic method to select this number of
-sections of the chromosome to use, depending on the number of
+sections of the chromosome to \textcolor{blue}{be used}, depending on the number of
 islands. Besides, previous experiments were performed on a single
-processor synchronous island model with a limited number of islands
+processor \textcolor{blue}{with a} synchronous island model and a limited number of islands
 (8, 32 and 128). In this paper,  8, 16, 32, 64 and 128 islands have
-been used, and on this occasion, the experiments have been run on a parallel
+been used, and \textcolor{blue}{this time}, the experiments have been run on a parallel
 cluster. 
-Therefore, at the same time, \textcolor{blue}{a new method is proposed in this paper} to divide the individual search space according to the number of evolved subpopulations, and also validating the previous approach.
+Therefore, at the same time, \textcolor{blue}{a new method is proposed in this paper} to divide the individual search space according to the number of \textcolor{blue}{evolving} subpopulations, and also validating the previous approach.
 
@@
 \subsection{Proposed methods}
-In this paper \textcolor{blue}{several implemented SLA algorithms are analyzed}
+ \textcolor{blue}{Several implemented SLA algorithms are analyzed in this paper}
  by using a parallel multi-objective baseline algorithm
@@
 Therefore, a basic distributed NSGA-II algorithm without
-overlapping sections \textcolor{blue}{has been used} as the baseline (B).
+overlapping sections \textcolor{blue}{has been used as the baseline option} (B).
 
@@
 
-As in the baseline (B), an individual is migrated to another random
-island after a fixed number of generations. In the new island, this
-individual will be considered as one of the others in the island,
+As in the baseline \textcolor{blue}{method} (B), an individual is migrated to another random
+island after a fixed number of generations. In the \textcolor{blue}{destination} island, this \textcolor{blue}{new}
+individual will be considered as \textcolor{blue}{one more individual in the subpopulation, being}
 crossed and mutated in the same way, depending on the island
@@
 \subsubsection{Automatic SLA with overlapping islands (A)} 
-As in the previous method, the sections to address by the operators are overlapped, but
+As in the previous method, the sections \textcolor{blue}{managed} by the operators are overlapped, but
 instead of using one extra section on each side of the $p$ section ($p+1$
@@
 Dividing individuals by blocks of equal size, instead of a percentage, allow the future integration of our method with other recombination mechanisms, such as the ones presented in \cite{Dorronsoro13superlinear} or \cite{Kimovski15Parallel}.
-Also, as mentioned, this is only a possible formula to reach above-described behaviour for $c$, and future work will study new methods or alternative formulas to determine it, for example using Taguchi Method \cite{Keratmatpour2018Taguchi}.
+Also, as mentioned \textcolor{blue}{before}, this is only a \textcolor{blue}{naive approximation} to reach above-described behaviour for $c$, and future work will study new methods or alternative formulas to determine it, for example using Taguchi Method \cite{Keratmatpour2018Taguchi}.
 Figure \ref{fig:adaptive} explains the $A$ method, assuming that $c=2$, for example.
@@
 Also, every island evaluates its own individuals using the complete chromosome.
-After a given number of generations it cooperates with the other islands through migration.} $c$ is calculated depending on the number of islands.
+After a given number of generations\textcolor{blue}{,} it cooperates with the other islands through migration.} $c$ is calculated depending on the number of islands.
 In this case, $c=2$.
@@
 
-Pseudo-code of the proposed algorithms is described in Algorithm \ref{alg:EA}.
+\textcolor{blue}{The} pseudo-code of the proposed algorithms is described in Algorithm \ref{alg:EA}.
 
@@
 % experiments bla bla bla--- JJ Pablo: Done
-\textcolor{blue}{In this subsection, the design of the experiments will be described, starting with the measurements of quality, the benchmark problems, the different configurations compared, and the specific parameter set used.}
+\textcolor{blue}{The design of the experiments is described in this subsection, starting with the measurements of quality, the benchmark problems, the different configurations compared, and the specific parameter set used.}
 
@@
 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous},
-but also because they cover different quality criteria. Mathematical
+but also because they cover different quality criteria. \textcolor{blue}{The} mathematical
 formulation of these metrics can be found in
@@
 Figure \ref{fig:hypervolume} clarifies how the hypervolume is calculated.
-\item Inverted Generational distance (IGD): calculates the distance of the obtained set of solutions to the optimal PF.
+\item Inverted Generational Distance (IGD): calculates the distance of the obtained set of solutions to the optimal PF.
 Therefore, this metric requires the optimal PF found in the literature, or the theoretical one.
@@
 \item Spread (S): Measures the spread between solutions, taking into account the Euclidean distance between consecutive solutions.
-As in previous metric, the lower the value, the better, as it implies solutions distributed along all the PF.
+As in \textcolor{blue}{the} previous metric, the lower the value, the better, as it implies solutions distributed along all the PF.
 \end{itemize}
@@
 The previously described four approaches have been run with two
-different chromosome lengths ($L$): 512 and 2048. Different number of
+different chromosome lengths ($L$): 512 and 2048. \textcolor{blue}{A} different number of
 islands ($P$) have also been compared: 8, 16, 32, 64 and 128. This
 maximum number of islands has also been  used in a previous work in the
-literature \cite{Martens13asynchronous}. The chosen crossover and mutation, SBX and polynomial, have also been  used previously by other
-authors in \cite{Durillo08masterslave,CaoZLL17}.  % SBX is first mentioned
+literature \cite{Martens13asynchronous}. \textcolor{blue}{The chosen operators, SBX crossover and polynomial mutation, have also been  used previously by other
+authors in \cite{Durillo08masterslave,CaoZLL17}, as its effectiveness has been demonstrated in this type of problems}.  % SBX is first mentioned
 % here. Has to explain - JJ
 % Still not done - JJ
-
-ZDT \citep{zdt2000a} has been chosen as a benchmark, since it is the
-most widely used in this area
+% Pablo: Done, check if this is enough
+
+ZDT \citep{zdt2000a} has been chosen as the benchmark, since it is the
+most widely used \textcolor{blue}{one} in this area
 \citep{Deb03distributed,Martens13asynchronous,Wang09parallel,Durillo08masterslave}. This
 benchmark includes several functions, with different features that are
-representative of real-world optimization problems. Mathematical
+representative of real-world optimization problems. \textcolor{blue}{The} mathematical
 formulation of each function is available in \citep{zdt2000a}. \textcolor{blue}{Please
-note that the ZDT problems are non-epistatic, so in principle our
+note that the ZDT problems are non-epistatic, so in principle, our
 conclusions should be extensible only to multiobjective problems with
@@
 
-The global population size is set to 1024.
+The global population size \textcolor{blue}{has been} set to 1024.
 \textcolor{blue}{That value has been chosen} for two reasons: the first is that it is large enough to have 8 individuals per island by dividing that number when using 128 islands and small enough to have 128 individuals when using 8 islands.
@@
 According to Alba and Luque \cite{EVALUATIONPARALLEL}, other stop criteria such as the number of evaluations required to attain a solution, may be misleading depending on the studied scenario.
-In our case, \textcolor{blue}{time has been used} instead of the number of evaluations firstly
+In our case, \textcolor{blue}{the time has been used} instead of the number of evaluations firstly
 because our hypothesis argues that the time saved in crossover and
@@
 operations and migrations can be achieved. Also, 
-different numbers of islands \textcolor{blue}{has been used} (with different sub-population sizes) and that
+different numbers of islands \textcolor{blue}{have been used} (with different sub-population sizes) and that
 could lead to different execution times, so it would be difficult to
@@
 and as affirmed by 
-\cite{cantu1998survey}, this migration gap has contradictory effects
+\cite{cantu1998survey}, the migration gap has contradictory effects
 on the result: by increasing it, the system \textcolor{blue}{is made} closer to a
 single-node one, since populations tend to mix without restriction; by
-decreasing it, the isolate islands \textcolor{blue}{are} more prone to being stuck
+decreasing it, the \textcolor{blue}{isolated} islands \textcolor{blue}{are} more prone to being stuck
 in local minima. \cite{Martens13asynchronous} mentions that several
@@
 as future work, as the main focus of this paper was to show the
-general concept, and not tune the values for maximum performance.
+general concept, and not \textcolor{blue}{the tuning of} the values for maximum performance.
 
@@
   starts the migration step, the migrated individual is sent to
-  another randomly selected island. This makes it possible a
+  another randomly selected island. \textcolor{blue}{This makes possible the} 
   dissemination of the modified parts of the individuals among the
   whole set of islands, thus avoiding a specific synchronization step
-  to compose solutions obtained by different islands, as occurs other
-  works \cite{Dorronsoro13superlinear}.The main parameters studied in the proposed system are limited to the number of islands and the size of the problem.
+  to compose solutions obtained by different islands, as occurs \textcolor{blue}{in} other
+  works \cite{Dorronsoro13superlinear}.
+The main parameters studied in the proposed system are limited to the number of islands and the size of the problem.
 This decision has been motivated because all previous works described in the state of the art also limit their experimental setting to the same parameters \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}.
@@
 experiments, including its own random number generation implementation.  The specific modifications to deal with the proposed approaches have been developed as new modules for
-ECJ, and their source code can be downloaded from our GitHub repository under a
+ECJ, and their source code can be downloaded from our GitHub repository under \textcolor{blue}{an}
 LGPL V3 License
@@
 calculated (see Figure \ref{fig:hypervolume}), the value (1,9) \textcolor{blue}{has been chosen} as none of the existing solutions on all fronts obtained during all executions are dominated by it.
-In other words, as both objectives \textcolor{blue}{are being minimized}, this reference point is required to be numerically larger or equal in each objective, and strictly larger in at least one of them (dominated) for all solutions in the PFs \textcolor{blue}{used} to measure.
+In other words, as both objectives \textcolor{blue}{are being minimized}, this reference point is required to be numerically larger or equal in each objective, and strictly larger in at least one of them (dominated) for all solutions in the PFs \textcolor{blue}{used to be measured}.
 HV is then
@@
   using a chromosome length of 512 dimensions. Acronyms next to values
-  indicate that there is not significant difference with respect to
+  indicate that there is \textcolor{blue}{no} significant difference with respect to
   that method for that value. Best values are marked in
@@
 \caption{Average quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and automatically overlapped (A), using a chromosome length of 2048 dimensions.
-Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
+Acronyms next to values indicate that there is \textcolor{blue}{no} significant difference with respect to that method for that value.
 Best values are marked in bold.
@@
 Results show that there is a difference in performance when using 512 or 2048 dimensions.
-Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than those obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply these methods.
+Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than those obtained by the baseline, it is clear that 512 dimensions \textcolor{blue}{are} not \textcolor{blue}{a large enough value} to apply these methods.
 A contradiction arises with respect to the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths.
@@
 
-However, with 2048 dimensions, results show that dividing the chromosome produces an improvement in all the quality indicators using the automatic ($A$) version (Table \ref{tab:results2048}), even overcoming the overlapping ($O$) and disjoint ($D$) methods.
+However, with 2048 dimensions, results show that \textcolor{blue}{the division of} the chromosome produces an improvement in all the quality indicators using the automatic ($A$) version (Table \ref{tab:results2048}), even overcoming the overlapping ($O$) and disjoint ($D$) methods.
 Therefore, there exists some kind of limit point in chromosome length where one method will be preferable to another, besides depending on the number of islands and population size.
@@
 \caption{Average number of generations and  solutions per front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and automatically overlapped (A), using a chromosome length of 512 dimensions.
-Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
+Acronyms next to values indicate that there is \textcolor{blue}{no} significant difference with respect to that method for that value.
 Equiv-$X$ implies that value is the same as executing $X$, since both configurations would be the same.}
@@
 \caption{Average number of generations and solutions per front after 30 runs per configuration, for methods baseline (B), disjoint (D), overlapped (O) and automatically overlapped (A), using a chromosome length of 2048 dimensions.
-Acronyms next to values indicate that there is not significant difference with respect to that method for that value.
+Acronyms next to values indicate that there is \textcolor{blue}{no} significant difference with respect to that method for that value.
 Equiv-$X$ implies that value is the same as executing $X$, since both configurations would be the same.}
@@
 island). But also, the SLA methods
-approach to the number of generations with the baseline when
+approach to the number of generations \textcolor{blue}{executed by} the baseline when
 increasing the number of islands. However, with $L=2048$ the migration
 time is big enough  to not improve the number of generations
-with respect to the baseline, even in the lower number of islands, as
+with respect to the baseline, even \textcolor{blue}{with} the lower number of islands, as
 it happens with $L=512$. Therefore, more generations do not
@@
 different elements of the chromosome. As previously stated, every
-island is unaware of the other islands PFs, and they are trying to
+island is unaware of the other islands PFs, \textcolor{blue}{since} they are trying to
 optimize their solutions independently.
@@
 After establishing the performance of the new method and in order to
-have some insight on how they work, the effect of the different chromosome sizes and number of
+have some insight on how they work, the effect of the different chromosome sizes and \textcolor{blue}{the} number of
 islands can be checked.
-Plotting the solution sets allows to observe its quality, distribution and shape, specially if they are limited to 2 or 3 objectives, as in this paper \cite{Li17read}.
+Plotting the solution sets allows to observe its quality, distribution and shape, \textcolor{blue}{especially} if they are limited to 2 or 3 objectives \cite{Li17read}, as in this paper.
 Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048} show the
-final PFs of one arbitrary sample run of each combination;. The first
+final PFs of one arbitrary sample run of each combination. The first
 one, ZDT1, has a convex Pareto-optimal front. Comparing results from
@@
 configurations  with
-$L=512$  seem to have a worse Spread and HV, on the other hand, the
+$L=512$  seem to have a worse Spread and HV. On the other hand, the
 SLA methods behave worse than $B$, as it was also shown on average in
@@
 \ref{fig:plot_zdt2_512} and \ref{fig:plot_zdt2_2048} it is clear that, as in the previous problem ZDT1, there is a decrease of quality for all configurations as the size of $P$ increases.
-Nevertheless, for this benchmark, there is not a clear decrease in the PF quality when $L$ goes from 512 to 2048.
+Nevertheless, there is not a clear decrease in the PF quality \textcolor{blue}{for this benchmark}, when $L$ goes from 512 to 2048.
 
 %ZDT3
-ZDT3 Pareto-optimal front is formed by non-contiguous convex parts, and plots for both chromosome sizes (Figures \ref{fig:plot_zdt3_512} and \ref{fig:plot_zdt3_2048}) show solutions gathered in similar regions in all configurations.
+ZDT3 Pareto-optimal front is formed by non-contiguous convex parts.
+Plots for both chromosome sizes (Figures \ref{fig:plot_zdt3_512} and \ref{fig:plot_zdt3_2048}) show solutions gathered in similar regions in all configurations.
 However, with $L=512$, the rightmost part of the obtained non-dominated solutions is not obtained in the $A$ alternative with $P=8$  and $P=16$ (being equivalent to alternatives $O$ and $D$).
-This explains why with this chromosome length, the SLA methods do not improve the results obtained by $B$.
+This explains why\textcolor{blue}{,} with this chromosome length, the SLA methods do not improve the results obtained by $B$.
 This problem does not appear when $L=2048$.
-Although the differences in the Spread metric are not significant for the different alternatives for this benchmark, (as shown in Table \ref{tab:results2048}), the HV and IGD metrics are the ones that can be used to show the effectiveness of our approach in this type of problem with non-continuous PFs.
+Although the differences in the Spread metric are not significant for the different alternatives for this benchmark, (as shown in Table \ref{tab:results2048}), the HV and IGD metrics can be used to show the effectiveness of our approach in this type of problem with non-continuous PFs.
 
 In ZDT6, the Pareto-optimal solutions are not only non-uniformly distributed along the PF, but their density also increases \textcolor{blue}{when moving} further away from it.
-That is the reason why some PFs obtained have an extremely low number of solutions in some configurations, and also, they are aggregated toward the areas with more density.
+That is the reason why some PFs obtained have an extremely low number of solutions in some configurations, and also, they are aggregated \textcolor{blue}{towards} areas with more density.
 Moreover, all configurations, including $B$, obtained PFs relatively far away from the optimal PF, as opposed as in previous problems.
-Spread is very similar for all methods $B$, $D$, $O$, $A$ across different $L$ sizes.
-Indeed, there is not a significant difference between methods, with an exception: Spread using $A$ with $L=512$ is significantly worse.
-As in previous approaches, it is visually clear that increasing the number of islands, and therefore, reducing the number of individuals per island, implies a decrease the in quality of the HV.
+Spread is very similar for all methods $B$, $D$, $O$and $A$ across different $L$ sizes.
+Indeed, there is \textcolor{blue}{no} a significant difference between methods, with an exception: Spread using $A$ with $L=512$ is significantly worse.
+As in previous approaches, it is visually clear that increasing the number of islands, and therefore, reducing the number of individuals per island, implies a decrease  in \textcolor{blue}{the} quality of the HV.
 
@@
 \cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be
-also tested. But as complete individuals \textcolor{blue}{treated} in
+also tested. But as complete individuals \textcolor{blue}{are treated} in
 each island, the possibility of using a real number, such as 0.3 (30\%
-overlapping) instead an integer value opens future experimental
+overlapping) instead \textcolor{blue}{of} an integer value opens future experimental
 setups. \textcolor{blue}{This should also take care of epistatic

### 2019-05-20 hpmoon-asoco.tex
Added bbl to the tex to set new references in blue

@@
 
-\bibliographystyle{elsarticle-num}
-\bibliography{hpmoon-asoco}
+%\bibliographystyle{elsarticle-num}
+%\bibliography{hpmoon-asoco}
+\begin{thebibliography}{10}
+\expandafter\ifx\csname url\endcsname\relax
+  \def\url#1{\texttt{#1}}\fi
+\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+\expandafter\ifx\csname href\endcsname\relax
+  \def\href#1#2{#2} \def\path#1{#1}\fi
+
+\bibitem{Gong15models}
+Y.~Gong, W.~Chen, Z.~Zhan, J.~Zhang, Y.~Li, Q.~Zhang, J.~Li, Distributed
+  evolutionary algorithms and their models: {A} survey of the state-of-the-art,
+  Appl. Soft Comput. 34 (2015) 286--300.
+
+\bibitem{Alba02Parallelism}
+E.~Alba, M.~Tomassini, Parallelism and evolutionary algorithms, {IEEE} Trans.
+  Evolutionary Computation 6~(5) (2002) 443--462.
+
+\bibitem{Mora13paretobased}
+A.~M. Mora, P.~Garc{\'{\i}}a{-}S{\'{a}}nchez, J.~J. Merelo-Guerv{\'{o}}s, P.~A.
+  Castillo, Pareto-based multi-colony multi-objective ant colony optimization
+  algorithms: an island model proposal, Soft Comput. 17~(7) (2013) 1175--1207.
+
+\bibitem{LIU2017344}
+Y.~Liu, D.~Gong, X.~Sun, Y.~Zhang, Many-objective evolutionary optimization
+  based on reference points, Appl. Soft Comput. 50 (2017) 344 -- 355.
+
+\bibitem{Luna15Survey}
+F.~Luna, E.~Alba, Parallel multiobjective evolutionary algorithms, in:
+  J.~Kacprzyk, W.~Pedrycz (Eds.), Springer Handbook of Computational
+  Intelligence, Springer, 2015, pp. 1017--1031.
+
+\bibitem{Mukhopadhyay14Survey}
+A.~Mukhopadhyay, U.~Maulik, S.~Bandyopadhyay, C.~A.~C. Coello, A survey of
+  multiobjective evolutionary algorithms for data mining: Part {I}, {IEEE} T.
+  Evolut. Comput. 18~(1) (2014) 4--19.
+
+\bibitem{Chavez15MO}
+F.~C. de~la O, E.~Clemente, D.~E. Hern{\'{a}}ndez, F.~F. de~Vega, G.~Olague, A
+  multi-objective evolutionary algorithm for interaction systems based on laser
+  pointers, in: A.~M. Mora, G.~Squillero (Eds.), Applications of Evolutionary
+  Computation - 18th European Conference, EvoApplications 2015, Copenhagen,
+  Denmark, April 8-10, 2015, Proceedings, Vol. 9028 of Lecture Notes in
+  Computer Science, Springer, 2015, pp. 504--516.
+
+\bibitem{Hidalgo16residualstress}
+J.~I. Hidalgo, R.~Fern{\'{a}}ndez, J.~M. Colmenar, F.~Cioffi, J.~L.
+  Risco{-}Mart{\'{\i}}n, G.~Gonz{\'{a}}lez{-}Doncel, Using evolutionary
+  algorithms to determine the residual stress profile across welds of
+  age-hardenable aluminum alloys, Appl. Soft Comput. 40 (2016) 429--438.
+\textcolor{blue}{
+\bibitem{KAUR2018183}
+M.~Kaur, S.~Kadam, A novel multi-objective bacteria foraging optimization
+  algorithm ({MOBFOA}) for multi-objective scheduling, Appl. Soft Comput. 66
+  (2018) 183 -- 195.
+}
+\textcolor{blue}{
+\bibitem{XU2018268}
+Y.~Xu, O.~Ding, R.~Qu, K.~Li, Hybrid multi-objective evolutionary algorithms
+  based on decomposition for wireless sensor network coverage optimization,
+  Appl. Soft Comput. 68 (2018) 268 -- 282.
+}
+
+\bibitem{DBLP:series/ncs/EibenS15}
+A.~E. Eiben, J.~E. Smith, Introduction to Evolutionary Computing, Natural
+  Computing Series, Springer, 2015.
+
+\bibitem{TalbiUnified2018}
+E.-G. Talbi,
+  \href{https://www.sciencedirect.com/science/article/pii/S074373151830279X}{A
+  unified view of parallel multi-objective evolutionary algorithms}, J.
+  Parallel Distrib. Comput. (2018) --In press.
+
+\bibitem{Dorronsoro13superlinear}
+B.~Dorronsoro, G.~Danoy, A.~J. Nebro, P.~Bouvry, Achieving super-linear
+  performance in parallel multi-objective evolutionary algorithms by means of
+  cooperative coevolution, Computers {\&} {OR} 40~(6) (2013) 1552--1563.
+
+\bibitem{Deb00NSGAII}
+K.~Deb, S.~Agrawal, A.~Pratap, T.~Meyarivan, A fast elitist non-dominated
+  sorting genetic algorithm for multi-objective optimisation: {NSGA-II}, in:
+  M.~Schoenauer, K.~Deb, G.~Rudolph, X.~Yao, E.~Lutton, J.~J.~M. Guerv{\'{o}}s,
+  H.~Schwefel (Eds.), Parallel Problem Solving from Nature - {PPSN} VI, 6th
+  International Conference, Paris, France, September 18-20, 2000, Proceedings,
+  Vol. 1917 of Lecture Notes in Computer Science, Springer, 2000, pp. 849--858.
+
+\bibitem{Alba13parallel}
+E.~Alba, G.~Luque, S.~Nesmachnow, Parallel metaheuristics: recent advances and
+  new trends, Int. T. Oper. Res. 20~(1) (2013) 1--48.
+
+\bibitem{Folino03cellular}
+G.~Folino, C.~Pizzuti, G.~Spezzano, A scalable cellular implementation of
+  parallel genetic programming, {IEEE} Trans. Evolutionary Computation 7~(1)
+  (2003) 37--53.
+
+\bibitem{Branke04Parallelizingcone}
+J.~Branke, H.~Schmeck, K.~Deb, R.~S. Maheshwar, Parallelizing multi-objective
+  evolutionary algorithms: cone separation, in: Proceedings of the {IEEE}
+  Congress on Evolutionary Computation, {CEC} 2004, 19-23 June 2004, Portland,
+  OR, {USA}, {IEEE}, 2004, pp. 1952--1957.
+
+\bibitem{Zhang17DECAL}
+Y.~H. Zhang, Y.~J. Gong, T.~L. Gu, H.~Q. Yuan, W.~Zhang, S.~Kwong, J.~Zhang,
+  Decal: Decomposition-based coevolutionary algorithm for many-objective
+  optimization, IEEE T. Cybernetics (2017) 1--15.
+
+\bibitem{Tonda12cooperative}
+A.~P. Tonda, E.~Lutton, G.~Squillero, A benchmark for cooperative coevolution,
+  Memet. Comput. 4~(4) (2012) 263--277.
+
+\bibitem{Kimovski15Parallel}
+D.~Kimovski, J.~Ortega, A.~Ortiz, R.~Ba{\~{n}}os, Parallel alternatives for
+  evolutionary multi-objective optimization in unsupervised feature selection,
+  Expert Syst. Appl. 42~(9) (2015) 4239--4252.
+
+\bibitem{Jia19Coevo}
+Y.~Jia, W.~Chen, T.~Gu, H.~Zhang, H.~Yuan, S.~Kwong, J.~Zhang,
+  Distributed cooperative
+  co-evolution with adaptive computing resource allocation for large scale
+  optimization, {IEEE} Trans. Evolutionary Computation 23~(2) (2019) 188--202.
+
+\bibitem{Garcia16hpmoon}
+P.~Garc{\'{\i}}a{-}S{\'{a}}nchez, J.~Ortega, J.~Gonz{\'{a}}lez, P.~A. Castillo,
+  J.~J. Merelo, Addressing high dimensional multi-objective optimization
+  problems by coevolutionary islands with overlapping search spaces, in:
+  G.~Squillero, P.~Burelli (Eds.), Applications of Evolutionary Computation -
+  19th European Conference, EvoApplications 2016, Porto, Portugal, March 30 -
+  April 1, 2016, Proceedings, Part {II}, Vol. 9598 of Lecture Notes in Computer
+  Science, Springer, 2016, pp. 107--117.
+
+\bibitem{Talbi08Parallel}
+E.~Talbi, S.~Mostaghim, T.~Okabe, H.~Ishibuchi, G.~Rudolph, C.~A.~C. Coello,
+  Parallel approaches for multiobjective optimization, in: J.~Branke, K.~Deb,
+  K.~Miettinen, R.~Slowinski (Eds.), Multiobjective Optimization, Interactive
+  and Evolutionary Approaches [outcome of Dagstuhl seminars]., Vol. 5252 of
+  Lecture Notes in Computer Science, Springer, 2008, pp. 349--372.
+
+\bibitem{Durillo08masterslave}
+A.~J. Nebro, J.~J. Durillo, A study of the parallelization of the
+  multi-objective metaheuristic {MOEA/D}, in: C.~Blum, R.~Battiti (Eds.),
+  Learning and Intelligent Optimization, 4th International Conference, {LION}
+  4, Venice, Italy, January 18-22, 2010. Selected Papers, Vol. 6073 of Lecture
+  Notes in Computer Science, Springer, 2010, pp. 303--317.
+
+\bibitem{Hiroyasu07discussion}
+T.~Hiroyasu, K.~Yoshii, M.~Miki, Discussion of parallel model of
+  multi-objective genetic algorithms on heterogeneous computational resources,
+  in: H.~Lipson (Ed.), Genetic and Evolutionary Computation Conference, {GECCO}
+  2007, Proceedings, London, England, UK, July 7-11, 2007, {ACM}, 2007, p. 904.
+
+\bibitem{Deb03distributed}
+K.~Deb, P.~Zope, A.~Jain, Distributed computing of {Pareto}-optimal solutions
+  with evolutionary algorithms, in: C.~M. Fonseca, P.~J. Fleming, E.~Zitzler,
+  K.~Deb, L.~Thiele (Eds.), Evolutionary Multi-Criterion Optimization, Second
+  International Conference, {EMO} 2003, Faro, Portugal, April 8-11, 2003,
+  Proceedings, Vol. 2632 of Lecture Notes in Computer Science, Springer, 2003,
+  pp. 534--549.
+
+\bibitem{Wang09parallel}
+W.~Zhi-xin, G.~Ju, A parallel genetic algorithm in multi-objective
+  optimization, in: Control and Decision Conference, 2009. CCDC '09. Chinese,
+  2009, pp. 3497--3501.
+
+\bibitem{Xiao03specialized}
+N.~Xiao, M.~P. Armstrong, A specialized island model and its application in
+  multiobjective optimization, in: E.~Cant{\'{u}}{-}Paz, J.~A. Foster, K.~Deb,
+  L.~Davis, R.~Roy, U.~O'Reilly, H.~Beyer, R.~K. Standish, G.~Kendall, S.~W.
+  Wilson, M.~Harman, J.~Wegener, D.~Dasgupta, M.~A. Potter, A.~C. Schultz,
+  K.~A. Dowsland, N.~Jonoska, J.~F. Miller (Eds.), Genetic and Evolutionary
+  Computation - {GECCO} 2003, Genetic and Evolutionary Computation Conference,
+  Chicago, IL, USA, July 12-16, 2003. Proceedings, Part {II}, Vol. 2724 of
+  Lecture Notes in Computer Science, Springer, 2003, pp. 1530--1540.
+
+\bibitem{Martens13asynchronous}
+M.~M{\"{a}}rtens, D.~Izzo, The asynchronous island model and {NSGA-II:} study
+  of a new migration operator and its performance, in: C.~Blum, E.~Alba (Eds.),
+  Genetic and Evolutionary Computation Conference, {GECCO} '13, Amsterdam, The
+  Netherlands, July 6-10, 2013, {ACM}, 2013, pp. 1173--1180.
+\textcolor{blue}{\bibitem{DorronsoroPSO2018}
+A.~Atashpendar, B.~Dorronsoro, G.~Danoy, P.~Bouvry, A scalable parallel
+  cooperative coevolutionary {PSO} algorithm for multi-objective optimization,
+  J. Parallel Distrib. Comput. 112 (2018) 111--125.
+}
+
+\bibitem{CaoZLL17}
+B.~Cao, J.~Zhao, Z.~Lv, X.~Liu, A distributed parallel cooperative
+  coevolutionary multiobjective evolutionary algorithm for large-scale
+  optimization, {IEEE} T. Ind. Inform. 13~(4) (2017) 2030--2038.
+
+\bibitem{cheng2015adaptive}
+R.~Cheng, Y.~Jin, K.~Narukawa, Adaptive reference vector generation for inverse
+  model based evolutionary multiobjective optimization with degenerate and
+  disconnected {Pareto} fronts, in: Evolutionary Multi-Criterion Optimization,
+  Springer International Publishing, 2015, pp. 127--140.
+
+\bibitem{LUO2017235}
+J.~Luo, Q.~Liu, Y.~Yang, X.~Li, M.~rong Chen, W.~Cao, An artificial bee colony
+  algorithm for multi-objective optimisation, Appl. Soft Comput. 50 (2017) 235
+  -- 251.
+\textcolor{blue}{
+\bibitem{Keratmatpour2018Taguchi}
+M.~Keramatpour, S.~T.~A. Niaki, S.~H.~R. Pasandideh, A bi-objective two-level
+  newsvendor problem with discount policies and budget constraint, Comput. Ind.
+  Eng. 120 (2018) 192 -- 205.
+}
+
+\bibitem{zdt2000a}
+E.~Zitzler, K.~Deb, L.~Thiele, {Comparison of Multiobjective Evolutionary
+  Algorithms: Empirical Results}, Evol. Comput. 8~(2) (2000) 173--195.
+
+\bibitem{EVALUATIONPARALLEL}
+E.~Alba, G.~Luque, Evaluation of parallel metaheuristics, in: L.~Paquete,
+  M.~Chiarandini, D.~Basso (Eds.), Empirical Methods for the Analysis of
+  Algorithms, Workshop EMAA 2006, Proceedings, Reykjavik, Iceland, 2006, pp.
+  9--14.
+
+\bibitem{cantu1998survey}
+E.~Cant{\'u}-Paz, A survey of parallel genetic algorithms, Calculateurs
+  paralleles, reseaux et systems repartis 10~(2) (1998) 141--171.
+
+\bibitem{xiong2003parallel}
+S.~Xiong, F.~Li, Parallel strength {Pareto} multi-objective evolutionary
+  algorithm for optimization problems, in: Evolutionary Computation, 2003.
+  CEC'03. The 2003 Congress on, Vol.~4, IEEE, 2003, pp. 2712--2718.
+
+\bibitem{ECJ}
+S.~Luke, et~al., {ECJ: A Java-based Evolutionary Computation and Genetic
+  Programming Research System}, available at
+  \url{http://www.cs.umd.edu/projects/plus/ec/ecj} (2009).
+
+\bibitem{Durillo11Jmetal}
+J.~J. Durillo, A.~J. Nebro, jmetal: {A} java framework for multi-objective
+  optimization, Adv. Eng. Softw. 42~(10) (2011) 760--771.
+\textcolor{blue}{
+\bibitem{Li17read}
+M.~Li, L.~Zhen, X.~Yao, How to read many-objective solution sets in parallel
+  coordinates [educational forum], {IEEE} Comp. Int. Mag. 12~(4) (2017)
+  88--100.
+}
+\end{thebibliography}
 

### 2019-05-22 hpmoon-asoco.tex
Deleting a URL
Minor change in conclusions

@@
   good results with a simple formula, it is our conclusion that
-  further complication would not be necessary.}
+  further complication would not be necessary to validate our approach.}
 
@@
 E.-G. Talbi,
-  \href{https://www.sciencedirect.com/science/article/pii/S074373151830279X}{A
-  unified view of parallel multi-objective evolutionary algorithms}, J.
+  A
+  unified view of parallel multi-objective evolutionary algorithms, J.
   Parallel Distrib. Comput. (2018) --In press.

### 2019-05-23 hpmoon-asoco.tex
Addressing @pacastillo comments

@@
 distributed co-evolutionary algorithms \cite{Gong15models}. However,
-only decomposable problems \textcolor{blue}{--that is, the ones whose  domain can be divided into subsets to calculate their partial solutions and combine them to form the solution of the original problem--,} could strictly be implemented in parallel
+only decomposable problems \textcolor{blue}{--that is, those whose  domain can be divided into subsets to calculate their partial solutions and combine them to form the solution of the original problem--,} could strictly be implemented in parallel
 this way. A new parallel island-model evolutionary algorithm approach
@@
 calculated (see Figure \ref{fig:hypervolume}), the value (1,9) \textcolor{blue}{has been chosen} as none of the existing solutions on all fronts obtained during all executions are dominated by it.
-In other words, as both objectives \textcolor{blue}{are being minimized}, this reference point is required to be numerically larger or equal in each objective, and strictly larger in at least one of them (dominated) for all solutions in the PFs \textcolor{blue}{used to be measured}.
+In other words, as both objectives \textcolor{blue}{are being minimized}, this reference point is required to be numerically larger or equal in each objective, and strictly larger in at least one of them (dominated) for all solutions in the PFs \textcolor{blue}{that are going to be measured}.
 HV is then
@@
 Although the results obtained in this work are promising, it is clear
-that this method requires more future experiments. These new
+that \textcolor{blue}{the proposed method can be tested in more scenarios}. These new
 experiments should involve a more complete parameter study, including
-a sensitivity analysis, to validate our approach. Other benchmarks and
+a sensitivity analysis. Other benchmarks and
 real problems should be addressed in the future. These problems could

### 2019-05-24 hpmoon-asoco.tex
Minor changes

@@
 This work has been partially funded by project SPIP2017-02116 (Spanish ``Direcci\'on General de Tr\'afico''), and projects, TIN2015-67020-P, DeepBio TIN2017-85727-C4-2-P  and TEC2015-68752 (Spanish ``Ministerio de
-Econom{\'ia}a y Competitividad'') and PGC2018-098813-B-C31 (Spanish ``Ministerio de Ciencia, Innovación y Universidades''), and by European Regional Development Funds (ERDF).
+Econom{\'i}a y Competitividad'') and PGC2018-098813-B-C31 (Spanish ``Ministerio de Ciencia, Innovación y Universidades''), and by European Regional Development Funds (ERDF).
 We would like to express our gratitude to the editorial team and the reviewers, whose valuable comments on this paper have significantly improved its quality.

### 2019-09-03 hpmoon-asoco.tex
Adding tag and final version submitted

@@
 
-\newenvironment{bluecolor}{\par\color{blue}}{\par}
+\newenvironment{bluecolor}{\par\color{black}}{\par}
 
@@
 methods, suitable for dealing with large multi-objective optimization
-problems. \textcolor{blue}{This paper proposes a version of these algorithms where} each island modifies a fragment of the
+problems. \textcolor{black}{This paper proposes a version of these algorithms where} each island modifies a fragment of the
 chromosome that encodes a possible solution to the
-problem. \textcolor{blue}{The objective of this paper is} to
+problem. \textcolor{black}{The objective of this paper is} to
 demonstrate that automatically setting the size of the overlapping
 fragments depending on the number of islands obtains better results
-than using \textcolor{blue}{a fixed overlapping} size. \textcolor{blue}{This method has been
+than using \textcolor{black}{a fixed overlapping} size. \textcolor{black}{This method has been
   compared} to other parallel evolutionary techniques considering a
@@
 distributed co-evolutionary algorithms \cite{Gong15models}. However,
-only decomposable problems \textcolor{blue}{--that is, those whose  domain can be divided into subsets to calculate their partial solutions and combine them to form the solution of the original problem--,} could strictly be implemented in parallel
+only decomposable problems \textcolor{black}{--that is, those whose  domain can be divided into subsets to calculate their partial solutions and combine them to form the solution of the original problem--,} could strictly be implemented in parallel
 this way. A new parallel island-model evolutionary algorithm approach
 \cite{Alba02Parallelism} is used here to deal with un-decomposable
-problems: \textcolor{blue}{instead of allocating disjoint subsets of components to the islands hosted by the available processors, it applies the variation operators only to the components  of the subset allocated to a given population, while keeping the rest of the components of the whole individual unaltered}.
+problems: \textcolor{black}{instead of allocating disjoint subsets of components to the islands hosted by the available processors, it applies the variation operators only to the components  of the subset allocated to a given population, while keeping the rest of the components of the whole individual unaltered}.
 This avoids extra steps (and
@@
 %1. MOP ARE
-In MOPs, several \textcolor{blue}{independent}
+In MOPs, several \textcolor{black}{independent}
 objectives have to be simultaneously optimized
@@
 for all objectives. The objective of MOP algorithms is to find as many
-solutions equally distributed in the Pareto Front as possible. In order to do that\textcolor{blue}{,} the
+solutions equally distributed in the Pareto Front as possible. In order to do that\textcolor{black}{,} the
 exploration of the search space must be very efficient, trying to
-cover \textcolor{blue}{all} possible exploration paths at the same time.
+cover \textcolor{black}{all} possible exploration paths at the same time.
 
@@
 %3 ONE WAY IS TO USE MOEAS BECAUSE
-one of which \textcolor{blue}{is} evolutionary algorithms (EAs)
+one of which \textcolor{black}{is} evolutionary algorithms (EAs)
 \citep{DBLP:series/ncs/EibenS15}. EAs are bio-inspired meta-heuristics
@@
 
-Usually\textcolor{blue}{,} an EA starts by generating \textcolor{blue}{a \emph{population}, that is, a set of random solutions}, following a user-defined description. Then, it
+Usually\textcolor{black}{,} an EA starts by generating \textcolor{black}{a \emph{population}, that is, a set of random solutions}, following a user-defined description. Then, it
 evaluates each candidate solution, called \emph{individual}, assigning
-it a \emph{fitness} \textcolor{blue}{vector, in the case of MOPs} that describes how good the individual is
-\textcolor{blue}{solving} the target problem. New solutions are then generated by
+it a \emph{fitness} \textcolor{black}{vector, in the case of MOPs} that describes how good the individual is
+\textcolor{black}{solving} the target problem. New solutions are then generated by
 the application of \emph{operators} that either mutate a single
@@
 
-EAs \textcolor{blue}{were} extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}.
-One of the best known and \textcolor{blue}{highly} referenced MOEAs
+EAs \textcolor{black}{were} extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}.
+One of the best known and \textcolor{black}{highly} referenced MOEAs
 \citep{Dorronsoro13superlinear} is the {\em 
@@
 approaches \citep{Luna15Survey} need to deal with the whole solution set, the PF.
- This implies \textcolor{blue}{using} different distribution
+ This implies \textcolor{black}{using} different distribution
 and sharing mechanisms, as there exists a tradeoff between the speedup
@@
 results to accurately identify the PF
-\citep{Branke04Parallelizingcone}. \textcolor{blue}{This is also the case with the NSGA-II.} % Is that the case with NSGA? - JJ
+\citep{Branke04Parallelizingcone}. \textcolor{black}{This is also the case with the NSGA-II.} % Is that the case with NSGA? - JJ
 % Please check the last question - JJ Pablo: done
@@
 meaning that the
-MOEAs need to deal with large individuals \textcolor{blue}{representing those variables} and spend significant extra
-time \textcolor{blue}{applying the} crossover, mutation and migration \textcolor{blue}{operators}.
+MOEAs need to deal with large individuals \textcolor{black}{representing those variables} and spend significant extra
+time \textcolor{black}{applying the} crossover, mutation and migration \textcolor{black}{operators}.
 % If this is the only justification, it should have been assessed at the end. It would be better if it was qualified, in the sense that more exploration is needed or something like that - JJ
@@
 \citep{Gong15models,Tonda12cooperative}, and evolved separately.
-\textcolor{blue}{To evolve the individuals of a subpopulation, the processor where it has been allocated can operate according to two main alternatives.} One
-example of the application of the \textcolor{blue}{first alternative} was described in
+\textcolor{black}{To evolve the individuals of a subpopulation, the processor where it has been allocated can operate according to two main alternatives.} One
+example of the application of the \textcolor{black}{first alternative} was described in
 \citep{Kimovski15Parallel}. The method presented in that work involves
 different workers that evolve sub-populations created and recombined
-by a master process, which performs \textcolor{blue}{different alternatives for the recombination/cooperation of the subpopulations returned by worker processes}. A high
+by a master process, which performs \textcolor{black}{different alternatives for the recombination/cooperation of the subpopulations returned by worker processes}. A high
 dimensional problem was used to compare these 
-alternatives\textcolor{blue}{; also, i}n \citep{Dorronsoro13superlinear}, a distributed
-co-evolutionary island model was used.  Although  both papers \textcolor{blue}{described}
-significant speedups, only a \textcolor{blue}{small} number of nodes were
+alternatives\textcolor{black}{; also, i}n \citep{Dorronsoro13superlinear}, a distributed
+co-evolutionary island model was used.  Although  both papers \textcolor{black}{described}
+significant speedups, only a \textcolor{black}{small} number of nodes were
 employed (8). However, when the number of islands is increased, the division
-of \textcolor{blue}{the portion of chromosome assigned to a given island} becomes smaller, and the scalability
+of \textcolor{black}{the portion of chromosome assigned to a given island} becomes smaller, and the scalability
 may be affected by obtaining lower quality solutions in the same
 amount of time.
-\textcolor{blue}{Moreover, in this first alternative, each processor only works with the variables allocated to it of the individuals in its population.
+\textcolor{black}{Moreover, in this first alternative, each processor only works with the variables allocated to it of the individuals in its population.
 Thus, only whenever the cost function is decomposable in such a way that the variables allocated to different processors are not interdependent, the evaluation of the fitness of an individual in the population can be done by composing the cost evaluated separately by each processor from the values of the variables allocated to it.
@@
 Another approach used to solve this kind of problems is the {\em
-  SeLective operator Application} (SLA), presented in this paper, \textcolor{blue}{can be considered as the second alternative to evolve the individuals of a subpopulation}. In this case, each island
+  SeLective operator Application} (SLA), presented in this paper, \textcolor{black}{can be considered as the second alternative to evolve the individuals of a subpopulation}. In this case, each island
 deals with the whole chromosome, but only modifies a fragment of it in
 the crossover and mutation phase depending on the number of islands,
-using the whole chromosome for fitness calculation. This allows \textcolor{blue}{dealing} with un-decomposable problems.
+using the whole chromosome for fitness calculation. This allows \textcolor{black}{dealing} with un-decomposable problems.
 
@@
 
-In our previous work \citep{Garcia16hpmoon} \textcolor{blue}{this method was used} in a
-preliminary experimental setup, although it is worth mentioning \textcolor{blue}{that its name and acronym is established} in this paper for the first time.
-\textcolor{blue}{In that paper, it was shown}
-that applying the variation operators only \textcolor{blue}{to} specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
+In our previous work \citep{Garcia16hpmoon} \textcolor{black}{this method was used} in a
+preliminary experimental setup, although it is worth mentioning \textcolor{black}{that its name and acronym is established} in this paper for the first time.
+\textcolor{black}{In that paper, it was shown}
+that applying the variation operators only \textcolor{black}{to} specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
 Moreover, instead of making every island focus on a disjoint subset of the
@@
 can improve the quality of the solutions 
-when the number of islands is increased. In that paper, \textcolor{blue}{the results showed} that the most
+when the number of islands is increased. In that paper, \textcolor{black}{the results showed} that the most
 adequate overlapping size may vary depending on a relation between the
@@
 This
-motivate\textcolor{blue}{d} us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more \textcolor{blue}{extensive parameter evaluation}.
+motivate\textcolor{black}{d} us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more \textcolor{black}{extensive parameter evaluation}.
 %Again, "testing more stuff" is not a good motivation.
@@
 a new method that automatically sets the size of the overlapped
-sections depending on the number of available islands \textcolor{blue}{is proposed in this paper, and compared} with previous versions.
+sections depending on the number of available islands \textcolor{black}{is proposed in this paper, and compared} with previous versions.
 
@@
 variables) is also a relevant factor to determine the most efficient
-alternative to \textcolor{blue}{distribute} the decision variables: the higher the
+alternative to \textcolor{black}{distribute} the decision variables: the higher the
 dimensionality and the overlapping, the greater the benefit of
@@
 The rest of the paper is organized as follows: after the State of the Art in distributed and co-evolutionary MOEAs, 
-the \textcolor{blue}{proposed} methodology and the compared algorithms are described in Section \ref{sec:methodology}. 
+the \textcolor{black}{proposed} methodology and the compared algorithms are described in Section \ref{sec:methodology}. 
 Then, the results of the experiments are presented (Section \ref{sec:results}), Finally, the conclusions and future work are discussed.
@@
 %FERGU: Texto que me ha pasado Julio
-%\textcolor{blue}{Multi-objective optimization evolutionary algorithms (MOEAs) can take advantage of parallel and distributed processing \cite{Gong15models} not only to improve the quality of the solutions found, but also to speed up the execution times.
+%\textcolor{black}{Multi-objective optimization evolutionary algorithms (MOEAs) can take advantage of parallel and distributed processing \cite{Gong15models} not only to improve the quality of the solutions found, but also to speed up the execution times.
 Among the functional and data decomposition alternatives to parallelize an algorithm, parallel evolutionary algorithms usually implement data decomposition by identifying tasks that have to be repeatedly executed on different data.
@@
 %This is an improvement over the previous? What is the relationship? FERGU: linked
-Other \textcolor{blue}{kinds} of approaches have also been explored.
+Other \textcolor{black}{kinds} of approaches have also been explored.
 The work by Deb et al.
@@
 In that paper, the authors concluded that dividing the search space is a good idea, although achieving this is not trivial.
-The division of the search space has been explored by other researchers, for example, dividing the population into elite and search sub-populations \citep{Wang09parallel}, or separating it \textcolor{blue}{into} processors by objective \citep{Xiao03specialized}.
+The division of the search space has been explored by other researchers, for example, dividing the population into elite and search sub-populations \citep{Wang09parallel}, or separating it \textcolor{black}{into} processors by objective \citep{Xiao03specialized}.
 For example, in \cite{Zhang17DECAL}, a weighted function is used to decompose the objective function and every subpopulation is responsible to solve the problem defined by a weighted vector.
@@
 % Is this really cooperative co-evolution? - JJ FERGU: You mean the Dorronsoro one? The title says it
-Many real-world problems \textcolor{blue}{require} high-dimensional data \cite{Zhang17DECAL,XU2018268}.
+Many real-world problems \textcolor{black}{require} high-dimensional data \cite{Zhang17DECAL,XU2018268}.
 Addressing this kind of problems with cooperative co-evolution has
@@
 broadcast all solutions to all islands for recombination, but only one solution to a random island, needing less
-communication time. Moreover, Dorronsoro or Kimovsky approaches limited the maximum number of islands to 8, while in this paper \textcolor{blue}{up to 128 islands have been used}.
+communication time. Moreover, Dorronsoro or Kimovsky approaches limited the maximum number of islands to 8, while in this paper \textcolor{black}{up to 128 islands have been used}.
 
@@
 researchers. For example, some authors focus on the solution space
-\textcolor{blue}{modelling} the PF by dividing it into different clusters, allowing an
+\textcolor{black}{modelling} the PF by dividing it into different clusters, allowing an
 easily parallelizable {\em divide and conquer} approach
@@
 In our previous work \citep{Garcia16hpmoon} some of
-the aforementioned ideas \textcolor{blue}{were used} to compare two different dMOEAs. The first
-one divided the chromosome into $P$ sections,  \textcolor{blue}{with} $P$ being the number of
+the aforementioned ideas \textcolor{black}{were used} to compare two different dMOEAs. The first
+one divided the chromosome into $P$ sections,  \textcolor{black}{with} $P$ being the number of
 islands. Every island $p$ only performed the mutation and crossover in
@@
 results than a baseline algorithm that dealt with the whole chromosome
-in each island for crossover and mutation. \textcolor{blue}{It was} discovered \textcolor{blue}{in that paper} that the
-performance using one or another method depends on \textcolor{blue}{both} the number of
-sections \textcolor{blue}{individual's section used by each island} and the number of islands. This
+in each island for crossover and mutation. \textcolor{black}{It was} discovered \textcolor{black}{in that paper} that the
+performance using one or another method depends on \textcolor{black}{both} the number of
+sections \textcolor{black}{individual's section used by each island} and the number of islands. This
 motivated us to find a new automatic method to select this number of
-sections of the chromosome to \textcolor{blue}{be used}, depending on the number of
+sections of the chromosome to \textcolor{black}{be used}, depending on the number of
 islands. Besides, previous experiments were performed on a single
-processor \textcolor{blue}{with a} synchronous island model and a limited number of islands
+processor \textcolor{black}{with a} synchronous island model and a limited number of islands
 (8, 32 and 128). In this paper,  8, 16, 32, 64 and 128 islands have
-been used, and \textcolor{blue}{this time}, the experiments have been run on a parallel
+been used, and \textcolor{black}{this time}, the experiments have been run on a parallel
 cluster. 
-Therefore, at the same time, \textcolor{blue}{a new method is proposed in this paper} to divide the individual search space according to the number of \textcolor{blue}{evolving} subpopulations, and also validating the previous approach.
+Therefore, at the same time, \textcolor{black}{a new method is proposed in this paper} to divide the individual search space according to the number of \textcolor{black}{evolving} subpopulations, and also validating the previous approach.
 
 %We will describe how we have tested our approach in the next Section.
-\textcolor{blue}{The methodology to test our approach is described in the next Section.}
+\textcolor{black}{The methodology to test our approach is described in the next Section.}
 
@@
 \subsection{Proposed methods}
- \textcolor{blue}{Several implemented SLA algorithms are analyzed in this paper}
+ \textcolor{black}{Several implemented SLA algorithms are analyzed in this paper}
  by using a parallel multi-objective baseline algorithm
@@
 Therefore, a basic distributed NSGA-II algorithm without
-overlapping sections \textcolor{blue}{has been used as the baseline option} (B).
+overlapping sections \textcolor{black}{has been used as the baseline option} (B).
 
@@
 subpopulations according to the decision space to be explored by each
-island. Here three methods \textcolor{blue}{will be considered} in which each island only
+island. Here three methods \textcolor{black}{will be considered} in which each island only
 performs crossover and mutation in specific sections of the
@@
 
-As in the baseline \textcolor{blue}{method} (B), an individual is migrated to another random
-island after a fixed number of generations. In the \textcolor{blue}{destination} island, this \textcolor{blue}{new}
-individual will be considered as \textcolor{blue}{one more individual in the subpopulation, being}
+As in the baseline \textcolor{black}{method} (B), an individual is migrated to another random
+island after a fixed number of generations. In the \textcolor{black}{destination} island, this \textcolor{black}{new}
+individual will be considered as \textcolor{black}{one more individual in the subpopulation, being}
 crossed and mutated in the same way, depending on the island
@@
 
-The methods tested \textcolor{blue}{in this paper} are presented in the next subsections.
+The methods tested \textcolor{black}{in this paper} are presented in the next subsections.
 
@@
 \subsubsection{Automatic SLA with overlapping islands (A)} 
-As in the previous method, the sections \textcolor{blue}{managed} by the operators are overlapped, but
+As in the previous method, the sections \textcolor{black}{managed} by the operators are overlapped, but
 instead of using one extra section on each side of the $p$ section ($p+1$
@@
 islands is small, no overlapping is necessary. So, this
-knowledge \textcolor{blue}{has been used} to propose the formula $c=round(0.2*P-1)/2$ to calculate the
+knowledge \textcolor{black}{has been used} to propose the formula $c=round(0.2*P-1)/2$ to calculate the
 extra sections to overlap. Therefore, when $P=8$ then $c=0$
@@
 Dividing individuals by blocks of equal size, instead of a percentage, allow the future integration of our method with other recombination mechanisms, such as the ones presented in \cite{Dorronsoro13superlinear} or \cite{Kimovski15Parallel}.
-Also, as mentioned \textcolor{blue}{before}, this is only a \textcolor{blue}{naive approximation} to reach above-described behaviour for $c$, and future work will study new methods or alternative formulas to determine it, for example using Taguchi Method \cite{Keratmatpour2018Taguchi}.
+Also, as mentioned \textcolor{black}{before}, this is only a \textcolor{black}{naive approximation} to reach above-described behaviour for $c$, and future work will study new methods or alternative formulas to determine it, for example using Taguchi Method \cite{Keratmatpour2018Taguchi}.
 Figure \ref{fig:adaptive} explains the $A$ method, assuming that $c=2$, for example.
@@
 Also, every island evaluates its own individuals using the complete chromosome.
-After a given number of generations\textcolor{blue}{,} it cooperates with the other islands through migration.} $c$ is calculated depending on the number of islands.
+After a given number of generations\textcolor{black}{,} it cooperates with the other islands through migration.} $c$ is calculated depending on the number of islands.
 In this case, $c=2$.
@@
 
-\textcolor{blue}{The} pseudo-code of the proposed algorithms is described in Algorithm \ref{alg:EA}.
+\textcolor{black}{The} pseudo-code of the proposed algorithms is described in Algorithm \ref{alg:EA}.
 
@@
 % experiments bla bla bla--- JJ Pablo: Done
-\textcolor{blue}{The design of the experiments is described in this subsection, starting with the measurements of quality, the benchmark problems, the different configurations compared, and the specific parameter set used.}
+\textcolor{black}{The design of the experiments is described in this subsection, starting with the measurements of quality, the benchmark problems, the different configurations compared, and the specific parameter set used.}
 
 % Move this to the top - JJ Pablo: Done
-\textcolor{blue}{Three different quality metrics have been used in this paper. These metrics have been chosen} not only because they have been used
+\textcolor{black}{Three different quality metrics have been used in this paper. These metrics have been chosen} not only because they have been used
 extensively, especially in some of the papers presented in Section \ref{sec:soa}
 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous},
-but also because they cover different quality criteria. \textcolor{blue}{The} mathematical
+but also because they cover different quality criteria. \textcolor{black}{The} mathematical
 formulation of these metrics can be found in
@@
 \item Spread (S): Measures the spread between solutions, taking into account the Euclidean distance between consecutive solutions.
-As in \textcolor{blue}{the} previous metric, the lower the value, the better, as it implies solutions distributed along all the PF.
+As in \textcolor{black}{the} previous metric, the lower the value, the better, as it implies solutions distributed along all the PF.
 \end{itemize}
@@
 The previously described four approaches have been run with two
-different chromosome lengths ($L$): 512 and 2048. \textcolor{blue}{A} different number of
+different chromosome lengths ($L$): 512 and 2048. \textcolor{black}{A} different number of
 islands ($P$) have also been compared: 8, 16, 32, 64 and 128. This
 maximum number of islands has also been  used in a previous work in the
-literature \cite{Martens13asynchronous}. \textcolor{blue}{The chosen operators, SBX crossover and polynomial mutation, have also been  used previously by other
+literature \cite{Martens13asynchronous}. \textcolor{black}{The chosen operators, SBX crossover and polynomial mutation, have also been  used previously by other
 authors in \cite{Durillo08masterslave,CaoZLL17}, as its effectiveness has been demonstrated in this type of problems}.  % SBX is first mentioned
@@
 ZDT \citep{zdt2000a} has been chosen as the benchmark, since it is the
-most widely used \textcolor{blue}{one} in this area
+most widely used \textcolor{black}{one} in this area
 \citep{Deb03distributed,Martens13asynchronous,Wang09parallel,Durillo08masterslave}. This
 benchmark includes several functions, with different features that are
-representative of real-world optimization problems. \textcolor{blue}{The} mathematical
-formulation of each function is available in \citep{zdt2000a}. \textcolor{blue}{Please
+representative of real-world optimization problems. \textcolor{black}{The} mathematical
+formulation of each function is available in \citep{zdt2000a}. \textcolor{black}{Please
 note that the ZDT problems are non-epistatic, so in principle, our
@@
 
-The global population size \textcolor{blue}{has been} set to 1024.
-\textcolor{blue}{That value has been chosen} for two reasons: the first is that it is large enough to have 8 individuals per island by dividing that number when using 128 islands and small enough to have 128 individuals when using 8 islands.
+The global population size \textcolor{black}{has been} set to 1024.
+\textcolor{black}{That value has been chosen} for two reasons: the first is that it is large enough to have 8 individuals per island by dividing that number when using 128 islands and small enough to have 128 individuals when using 8 islands.
 This is the minimum and maximum population size per island used by M{\"a}rtens et al.
@@
 According to Alba and Luque \cite{EVALUATIONPARALLEL}, other stop criteria such as the number of evaluations required to attain a solution, may be misleading depending on the studied scenario.
-In our case, \textcolor{blue}{the time has been used} instead of the number of evaluations firstly
+In our case, \textcolor{black}{the time has been used} instead of the number of evaluations firstly
 because our hypothesis argues that the time saved in crossover and
@@
 operations and migrations can be achieved. Also, 
-different numbers of islands \textcolor{blue}{have been used} (with different sub-population sizes) and that
+different numbers of islands \textcolor{black}{have been used} (with different sub-population sizes) and that
 could lead to different execution times, so it would be difficult to
@@
 \cite{cantu1998survey}, the migration gap has contradictory effects
-on the result: by increasing it, the system \textcolor{blue}{is made} closer to a
+on the result: by increasing it, the system \textcolor{black}{is made} closer to a
 single-node one, since populations tend to mix without restriction; by
-decreasing it, the \textcolor{blue}{isolated} islands \textcolor{blue}{are} more prone to being stuck
+decreasing it, the \textcolor{black}{isolated} islands \textcolor{black}{are} more prone to being stuck
 in local minima. \cite{Martens13asynchronous} mentions that several
@@
 case, the mixing is essential for the algorithm to spread the result
-to all parts of the chromosome. So, while \textcolor{blue}{one might} tend to agree with
-M{\"a}rtens on the small influence of this value on the result, \textcolor{blue}{it is possible} that making this value much bigger in our case would have a
+to all parts of the chromosome. So, while \textcolor{black}{one might} tend to agree with
+M{\"a}rtens on the small influence of this value on the result, \textcolor{black}{it is possible} that making this value much bigger in our case would have a
 negative impact. However, a precise fine-tuning of this value is left
 as future work, as the main focus of this paper was to show the
-general concept, and not \textcolor{blue}{the tuning of} the values for maximum performance.
+general concept, and not \textcolor{black}{the tuning of} the values for maximum performance.
 
@@
   starts the migration step, the migrated individual is sent to
-  another randomly selected island. \textcolor{blue}{This makes possible the} 
+  another randomly selected island. \textcolor{black}{This makes possible the} 
   dissemination of the modified parts of the individuals among the
   whole set of islands, thus avoiding a specific synchronization step
-  to compose solutions obtained by different islands, as occurs \textcolor{blue}{in} other
+  to compose solutions obtained by different islands, as occurs \textcolor{black}{in} other
   works \cite{Dorronsoro13superlinear}.
@@
 experiments, including its own random number generation implementation.  The specific modifications to deal with the proposed approaches have been developed as new modules for
-ECJ, and their source code can be downloaded from our GitHub repository under \textcolor{blue}{an}
+ECJ, and their source code can be downloaded from our GitHub repository under \textcolor{black}{an}
 LGPL V3 License
@@
 to calculate the quality of the obtained PFs in every configuration. As HV requires a reference point to be
-calculated (see Figure \ref{fig:hypervolume}), the value (1,9) \textcolor{blue}{has been chosen} as none of the existing solutions on all fronts obtained during all executions are dominated by it.
-In other words, as both objectives \textcolor{blue}{are being minimized}, this reference point is required to be numerically larger or equal in each objective, and strictly larger in at least one of them (dominated) for all solutions in the PFs \textcolor{blue}{that are going to be measured}.
+calculated (see Figure \ref{fig:hypervolume}), the value (1,9) \textcolor{black}{has been chosen} as none of the existing solutions on all fronts obtained during all executions are dominated by it.
+In other words, as both objectives \textcolor{black}{are being minimized}, this reference point is required to be numerically larger or equal in each objective, and strictly larger in at least one of them (dominated) for all solutions in the PFs \textcolor{black}{that are going to be measured}.
 HV is then
@@
   using a chromosome length of 512 dimensions. Acronyms next to values
-  indicate that there is \textcolor{blue}{no} significant difference with respect to
+  indicate that there is \textcolor{black}{no} significant difference with respect to
   that method for that value. Best values are marked in
@@
 $c=0$), and when $P=16$ they are equivalent to O ($c=1$).
-This equivalence \textcolor{blue}{is referred} with the word {\em Equiv-} in tables.
+This equivalence \textcolor{black}{is referred} with the word {\em Equiv-} in tables.
 For example, Equiv-D in an HV cell  means that the HV of A is the same than the value in D column, because the behaviour of this configuration is the same than executing D.
@@
 \caption{Average quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and automatically overlapped (A), using a chromosome length of 2048 dimensions.
-Acronyms next to values indicate that there is \textcolor{blue}{no} significant difference with respect to that method for that value.
+Acronyms next to values indicate that there is \textcolor{black}{no} significant difference with respect to that method for that value.
 Best values are marked in bold.
@@
 Results show that there is a difference in performance when using 512 or 2048 dimensions.
-Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than those obtained by the baseline, it is clear that 512 dimensions \textcolor{blue}{are} not \textcolor{blue}{a large enough value} to apply these methods.
+Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than those obtained by the baseline, it is clear that 512 dimensions \textcolor{black}{are} not \textcolor{black}{a large enough value} to apply these methods.
 A contradiction arises with respect to the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths.
@@
 
-However, with 2048 dimensions, results show that \textcolor{blue}{the division of} the chromosome produces an improvement in all the quality indicators using the automatic ($A$) version (Table \ref{tab:results2048}), even overcoming the overlapping ($O$) and disjoint ($D$) methods.
+However, with 2048 dimensions, results show that \textcolor{black}{the division of} the chromosome produces an improvement in all the quality indicators using the automatic ($A$) version (Table \ref{tab:results2048}), even overcoming the overlapping ($O$) and disjoint ($D$) methods.
 Therefore, there exists some kind of limit point in chromosome length where one method will be preferable to another, besides depending on the number of islands and population size.
@@
 \caption{Average number of generations and  solutions per front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and automatically overlapped (A), using a chromosome length of 512 dimensions.
-Acronyms next to values indicate that there is \textcolor{blue}{no} significant difference with respect to that method for that value.
+Acronyms next to values indicate that there is \textcolor{black}{no} significant difference with respect to that method for that value.
 Equiv-$X$ implies that value is the same as executing $X$, since both configurations would be the same.}
@@
 \caption{Average number of generations and solutions per front after 30 runs per configuration, for methods baseline (B), disjoint (D), overlapped (O) and automatically overlapped (A), using a chromosome length of 2048 dimensions.
-Acronyms next to values indicate that there is \textcolor{blue}{no} significant difference with respect to that method for that value.
+Acronyms next to values indicate that there is \textcolor{black}{no} significant difference with respect to that method for that value.
 Equiv-$X$ implies that value is the same as executing $X$, since both configurations would be the same.}
@@
 island). But also, the SLA methods
-approach to the number of generations \textcolor{blue}{executed by} the baseline when
+approach to the number of generations \textcolor{black}{executed by} the baseline when
 increasing the number of islands. However, with $L=2048$ the migration
 time is big enough  to not improve the number of generations
-with respect to the baseline, even \textcolor{blue}{with} the lower number of islands, as
+with respect to the baseline, even \textcolor{black}{with} the lower number of islands, as
 it happens with $L=512$. Therefore, more generations do not
-necessarily mean \textcolor{blue}{an improvement in} the solution of the global PF, but focusing on
+necessarily mean \textcolor{black}{an improvement in} the solution of the global PF, but focusing on
 different elements of the chromosome. As previously stated, every
-island is unaware of the other islands PFs, \textcolor{blue}{since} they are trying to
+island is unaware of the other islands PFs, \textcolor{black}{since} they are trying to
 optimize their solutions independently.
@@
 After establishing the performance of the new method and in order to
-have some insight on how they work, the effect of the different chromosome sizes and \textcolor{blue}{the} number of
+have some insight on how they work, the effect of the different chromosome sizes and \textcolor{black}{the} number of
 islands can be checked.
-Plotting the solution sets allows to observe its quality, distribution and shape, \textcolor{blue}{especially} if they are limited to 2 or 3 objectives \cite{Li17read}, as in this paper.
+Plotting the solution sets allows to observe its quality, distribution and shape, \textcolor{black}{especially} if they are limited to 2 or 3 objectives \cite{Li17read}, as in this paper.
 Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048} show the
@@
 SLA methods behave worse than $B$, as it was also shown on average in
-Table \ref{tab:results512}. Nevertheless, \textcolor{blue}{when focusing} on the plots
+Table \ref{tab:results512}. Nevertheless, \textcolor{black}{when focusing} on the plots
 obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this
@@
 \ref{fig:plot_zdt2_512} and \ref{fig:plot_zdt2_2048} it is clear that, as in the previous problem ZDT1, there is a decrease of quality for all configurations as the size of $P$ increases.
-Nevertheless, there is not a clear decrease in the PF quality \textcolor{blue}{for this benchmark}, when $L$ goes from 512 to 2048.
+Nevertheless, there is not a clear decrease in the PF quality \textcolor{black}{for this benchmark}, when $L$ goes from 512 to 2048.
 
@@
 However, with $L=512$, the rightmost part of the obtained non-dominated solutions is not obtained in the $A$ alternative with $P=8$  and $P=16$ (being equivalent to alternatives $O$ and $D$).
-This explains why\textcolor{blue}{,} with this chromosome length, the SLA methods do not improve the results obtained by $B$.
+This explains why\textcolor{black}{,} with this chromosome length, the SLA methods do not improve the results obtained by $B$.
 This problem does not appear when $L=2048$.
@@
 
-In ZDT6, the Pareto-optimal solutions are not only non-uniformly distributed along the PF, but their density also increases \textcolor{blue}{when moving} further away from it.
-That is the reason why some PFs obtained have an extremely low number of solutions in some configurations, and also, they are aggregated \textcolor{blue}{towards} areas with more density.
+In ZDT6, the Pareto-optimal solutions are not only non-uniformly distributed along the PF, but their density also increases \textcolor{black}{when moving} further away from it.
+That is the reason why some PFs obtained have an extremely low number of solutions in some configurations, and also, they are aggregated \textcolor{black}{towards} areas with more density.
 Moreover, all configurations, including $B$, obtained PFs relatively far away from the optimal PF, as opposed as in previous problems.
 Spread is very similar for all methods $B$, $D$, $O$and $A$ across different $L$ sizes.
-Indeed, there is \textcolor{blue}{no} a significant difference between methods, with an exception: Spread using $A$ with $L=512$ is significantly worse.
-As in previous approaches, it is visually clear that increasing the number of islands, and therefore, reducing the number of individuals per island, implies a decrease  in \textcolor{blue}{the} quality of the HV.
+Indeed, there is \textcolor{black}{no} a significant difference between methods, with an exception: Spread using $A$ with $L=512$ is significantly worse.
+As in previous approaches, it is visually clear that increasing the number of islands, and therefore, reducing the number of individuals per island, implies a decrease  in \textcolor{black}{the} quality of the HV.
 
@@
 Obtained results also show that when the number of islands
-\textcolor{blue}{is increased}, the
+\textcolor{black}{is increased}, the
 automatic overlapping method ($A$) significantly improves the results with
@@
 \cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be
-also tested. But as complete individuals \textcolor{blue}{are treated} in
+also tested. But as complete individuals \textcolor{black}{are treated} in
 each island, the possibility of using a real number, such as 0.3 (30\%
-overlapping) instead \textcolor{blue}{of} an integer value opens future experimental
-setups. \textcolor{blue}{This should also take care of epistatic
+overlapping) instead \textcolor{black}{of} an integer value opens future experimental
+setups. \textcolor{black}{This should also take care of epistatic
   interactions between chromosome sizes: although variation operators
@@
 using some statistical parameter setting method, such as Taguchi's
-\cite{Keratmatpour2018Taguchi}. \textcolor{blue}{However, taking into
+\cite{Keratmatpour2018Taguchi}. \textcolor{black}{However, taking into
   account that the linear change tested in this paper in fact obtains
@@
 Although the results obtained in this work are promising, it is clear
-that \textcolor{blue}{the proposed method can be tested in more scenarios}. These new
+that \textcolor{black}{the proposed method can be tested in more scenarios}. These new
 experiments should involve a more complete parameter study, including
@@
 Econom{\'i}a y Competitividad'') and PGC2018-098813-B-C31 (Spanish ``Ministerio de Ciencia, Innovación y Universidades''), and by European Regional Development Funds (ERDF).
+First author was also partially supported by ``Ayuda del Programa de Fomento e Impulso de la Actividad Investigadora de la Universidad de C\'adiz''.
 We would like to express our gratitude to the editorial team and the reviewers, whose valuable comments on this paper have significantly improved its quality.
@@
   age-hardenable aluminum alloys, Appl. Soft Comput. 40 (2016) 429--438.
-\textcolor{blue}{
+\textcolor{black}{
 \bibitem{KAUR2018183}
@@
 }
-\textcolor{blue}{
+\textcolor{black}{
 \bibitem{XU2018268}
@@
   Netherlands, July 6-10, 2013, {ACM}, 2013, pp. 1173--1180.
-\textcolor{blue}{\bibitem{DorronsoroPSO2018}
+\textcolor{black}{\bibitem{DorronsoroPSO2018}
 A.~Atashpendar, B.~Dorronsoro, G.~Danoy, P.~Bouvry, A scalable parallel
@@
   -- 251.
-\textcolor{blue}{
+\textcolor{black}{
 \bibitem{Keratmatpour2018Taguchi}
@@
   optimization, Adv. Eng. Softw. 42~(10) (2011) 760--771.
-\textcolor{blue}{
+\textcolor{black}{
 \bibitem{Li17read}
